### 2024-08-12 Paper/Paper.tex
add paper.tex

\documentclass{article}
\usepackage{ctex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{caption}
\RequirePackage{longtable,multirow,array}
\RequirePackage{booktabs}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[style=ieee,sorting=nyt]{biblatex}
\assignrefcontextentries[]{*}
\addbibresource{References.bib}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\hypersetup{hidelinks}
\hypersetup{bookmarksnumbered=true,
	bookmarksopen=true,
	colorlinks=true,
	linkcolor=black,
	citecolor=blue,
	urlcolor=black}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{mhchem}
\pgfplotsset{compat=1.18}
\captionsetup{justification=centering}
\captionsetup[figure]{name={Fig.},labelsep=space,labelfont=bf}
\captionsetup[table]{name={Table},labelsep=space,labelfont=bf}
\CTEXoptions[today=old, contentsname=Contents]
\newcommand{\authyear}[1]{\citeauthor{#1} (\citeyear{#1})}
\setmainfont{Arial}

\newcommand{\toB}[1]{\color{blue}#1\color{black}}

\begin{document}
	\title{\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System}
	\author{Jerry Pan}
	\date{}
	\maketitle

	\vspace{0.5cm}
	\tableofcontents

	\pagebreak

	\section{Background}

		Ocular diseases can be diagnosed through various methods, including using optical coherence tomography (OCT) and color fundus images. Ophthalmologists usually identify ocular abnormalities to deduce the disease.  Traditionally, the diagnosis primarily depends on the professional experience and knowledge of the ophthalmologists, which may result in high misdiagnosis rate and under-utilization of medical data.  With the widespread application of artificial intelligence (AI), deep learning (DL) has made great contributions in providing support to patients in remote areas by sharing expert knowledge \autocite{Ichhpujani_Thakur_2021}.  By leveraging DL, researchers have developed auxiliary diagnosis programs to help doctors in the process. Many studies use convolutional neural network (CNN) to analyze ocular images. Some commonly used CNNs are VGG16, ResNet50, and Inception \autocite{daich2023artificial}.  And for segmenting images and finding abnormalities, U-net is widely used \autocite{Ronneberger_Fischer_Brox_2015}. In training CNNs, most studies use transferred learning, which consists of three steps: learning, fine-tuning, and validation.

		Some studies directly predict the disease from OCT images.
		\authyear{li2019deep} used ResNet to analyze OCT images and distinguish between choroidal neovascularization (CNV), diabetic macular edema (DME), drusen, and normal eyes. In addition, they performed occlusion testing to find out the regions that are the most important in diagnosis \autocite{li2019deep}. 
		\authyear{yoo2021feasibility} used generative adversarial network (GAN) and Inception-v3 together with a few-shot dataset to investigate the feasibility of improving OCT diagnosis of rare ocular diseases \autocite{yoo2021feasibility}.  They cleverly handled the issues of training image shortage and data imbalance by creating ocular disease OCT images from healthy OCT images. \authyear{Kermany2018} conducts medical diagnosis and identifies treatable diseases by image-based deep learning.  They also provided a widely used database including more than one hundred thousand OCT labeled images for 3 diseases \autocite{Kermany2018}.

		Some other studies can identify ocular abnormalities from annotated OCT images.
		\authyear{camino2018deep} used DL to identify the region of preserved photoreceptors on \textit{en face} OCT in choroideremia and retinitis pigmentosa (RP) \autocite{camino2018deep}. 
		\authyear{srinivasan2014fully} detected DME and dry age-related macular degeneration (dry AMD) from OCT images by flattening the image and using support vector machine (SVM) to extract the thickness information of the retinal layers \autocite{srinivasan2014fully}. 
		\authyear{leandro2023oct} implemented VGG to identify up to 8 kinds of key abnormalities and hence detect multiple diseases by using central fovea cross-section OCT \autocite{leandro2023oct}.  \authyear{Fang_Wang2019} developed a novel lesion-aware CNN, called LACNN, to simulate the ophthalmologists' diagnosis that focuses on ocular abnormalities.  The LACNN is a U-net-like CNN which incorporates VGG16 as the baseline, and the result is impressive \autocite{Fang_Wang2019}.

		Other studies use fundus images to predict ocular diseases.
		\authyear{masumoto2019accuracy} trained deep CNN with ultrawide-field fundus images to make the CNN capable of diagnosing RP \autocite{masumoto2019accuracy}. 
		\authyear{chen2021artificial} uses color fundus photographs and multiple types of CNN (Inception V3, Inception Resnet V2, and Xception) to develop a method of early detection of RP \autocite{chen2021artificial}. 
		\authyear{li2022development} uses CNN to detect up to 12 fundus diseases based on colour fundus photography \autocite{li2022development}.  \authyear{Son2023} presented a novel architectural and algorithmic design to comprehensively identify 15 abnormalities and diagnose 8 major ocular diseases from macula-centered fundus images.  They defined a notion of counterfactual attribution ratio (CAR) to interpret the system's diagnostic reason and disclose the relationship between abnormalities and diseases \autocite{Son2023}.

		In recent years, more and more DL systems began to use multi-modal information to predict ocular diseases.  For automated detection system, retrieving features from both OCT images and fundus images can effectively keep the diagnosis away from bias and incompleteness.  It is not always necessary to yield a better automated diagnosis result, but it does help ophthalmologist to make more accurate and holistic clinical decisions.  For instance, \authyear{liu2023prediction} combined OCT and fundus images to evaluate visual impairment in RP in terms of best-corrected visual acuity(BCVA) \autocite{liu2023prediction}.  \authyear{Xu2021} leveraged a bi-modal CNN to diagnose AMD and polypoidal choroidal vasculopathy (PCV), where the architecture uses fundus and OCT images as input for transferred learning CNN and concatenates the retrieved features to classify 3 diseases including dry AMD, wet AMD and PCV \autocite{Xu2021}.  And \author{Andrearczyk2018} ingeniously combined medical images and biomedical textual information to discriminate different diseases, which is a novel method for the usage of multi-modal application \autocite{Andrearczyk2018}.

		The key technical problem of multi-modal diagnosis is how to fuse the results from multifarious sources.  There are three types of fusion, namely early, late, and hybrid fusion.  Deciding on the optimal type of fusion is part of the exploratory process in the application of DL methods \autocite{Ichhpujani_Thakur_2021}.

	\section{Purpose}

		We will develop an Ocular Disease Auxiliary Diagnosis System (ODADS).

		\vspace{0.3cm}

		\textbf{First, the ODADS aims to simulate the comprehensive diagnosis process by considering information from both fundus and OCT images.} While both types of images can respectively indicate different diseases, they can also strengthen certain disease discrimination.  Considering both sources can result in a more comprehensive disease diagnosis.

		\vspace{0.1cm}

		\textbf{Second, the ODADS aims to present more interpretable findings.}  Most studies provide end-to-end systems for classifying diseases as black boxes, which may not be convincing enough when their results are different from ophthalmologists'.  The ODADS will provide 2 types of results, namely abnormalities and disease.  We will highlight all the abnormalities and use them to deduce diseases, so that the ODADS could provide as much information as possible.  Even when the ODADS does not automate diagnosis correctly, the results can still be references for users.

		\vspace{0.1cm}

		\textbf{Third, the ODADS aims to provide the probabilities of ocular diseases.}  Most studies only do the classification, which is not enough in some scenarios.  The symptoms could be complex, where multiple disease could be in the same case.  Providing diseases probabilities than simple discrimination can enable users to be aware of actual ocular conditions and potentially improve treatment.

		\vspace{0.1cm}

		\textbf{Fourth, The ODADS aims to be accessible to all people.}  While most studies design models dedicated to ophthalmologists, the ODADS will contain a website and a mobile application (APP) to serve people including ophthalmologists, patients and their families, and all others.

		\vspace{0.1cm}

		\textbf{Last, The ODADS aims to be more flexible by allowing user to input multiple images.}  Most studies only consider limited images.  In other words, mono-modal systems only work on one fundus image or one OCT image and bi-modal systems only work on 2 images.  The ODADS will enable user to input more than 2 images, especially for OCT images, which could result in more accurate diagnosis.

	\section{Models}

		The ODADS will consist of two parts.

		The first part is a back-end model, which has fundus and OCT images as input and features and probabilities as output. The second part is a front-end user interface (UI), including a website and an APP, which implements the back-end model and provides users with diagnosis information.

		The back-end model will be built based on multiple sub-models including several OCT-Models, several Fundus-Models and one Diagnosis-Model.  Each OCT-Model and Fundus-Model will contain a classifier which will be trained separately by a backboned ResNet50.  Diagnosis-Model will consist of a neural network for determining the deduction from abnormalities to diseases.  We will study the optimal OCT-Model and Fundus-Model number and compare different fusion timing to determine the best architecture.  The back-end model will output 2 sets of results to the front-end UI, one containing the probabilities of potential ocular diseases and the other containing abnormalities and their locations in each image.

		The front-end UI will enable users to upload OCT and fundus images, which can be got by taking photos in the APP or selecting image files from disk on the website. The UI will generate a report, including the ocular abnormalities, their locations, and the probabilities of different ocular diseases, etc. Ophthalmologists can use the APP or website to assist their diagnosis. And if patients and their families can get their OCT and fundus images from the hospital, they can also use the UI to view the report, which can be a supplementary reference to clinical diagnosis.  The front-end UI will also provide some functionalities like viewing the locations of abnormalities interactively and revising the automated diagnosis results of diseases and abnormalities and upload the revision to server for improving the back-end model in the future.

	\pagebreak
	\section{Abnormalities and Diseases} \label{sec:ab_di}

	\subsection{OCT Abnormalities}

		Fig.\ref{fig:oct-abnormalities} shows the OCT abnormalities in the ODADS.
		Table \ref{tb:oct-abnormalites} lists the description of abnormalities.

		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{lp{3.8in}}
				\caption{OCT Abnormalities}
				\label{tb:oct-abnormalites}\\
				\toprule
				Abnormality&Description\\
				\toprule

				\multicolumn{1}{l}{Central serous chorioretinopathy (CSC)}
				& \multicolumn{1}{l}{The accumulation of fluid underneath the retina.}\\

				\multicolumn{1}{l}{Epiretinal membrane (ERM)}
				& A thin layer of fibrous tissue forms on the surface of the retina, particularly the macula.\\

				\multicolumn{1}{l}{Macular hole (MH)}
				& Disruption or discontinuity in the normal retinal layers surrounding the macular hole.\\

				\multicolumn{1}{l}{Retinal detachment}
				& The separation between the neurosensory retina and the underlying retinal pigment epithelium (RPE) or choroid.\\

				\multicolumn{1}{l}{Stargardt disease}
				& Thinning and atrophy of the retina. Disruption of photoreceptor layers. Presence of subretinal deposits.\\

				\multicolumn{1}{l}{Retinitis pigmentosa (RP)}
				& Thinning of the Retinal Layers. Disruption of Photoreceptor Layers. Attenuation of Retinal Vasculature.\\

				\multicolumn{1}{l}{Macular telangiectasia (Mactel)}
				& Abnormalities in the macular blood vessels, leading to changes in the macular structure and function\\

				\multicolumn{1}{l}{Diabetic macular edema (DME)}
				& The accumulation of fluid in the macula. \\

				\multicolumn{1}{l}{Macular neovascularization}
				& The abnormal growth of new blood vessels in the macular region of the retina.\\

				\multicolumn{1}{l}{Subretinal fluid}
				&  The accumulation of fluid between the neurosensory retina and the retinal pigment epithelium (RPE)\\

				\multicolumn{1}{l}{Intraretinal fluid}
				& The accumulation of fluid within the layers of the retina.\\

				\multicolumn{1}{l}{Drusen}
				& Small deposits of extracellular material that accumulate beneath the retinal pigment epithelium (RPE) or between the RPE and the photoreceptor layer in the macular region of the retina.\\

				\bottomrule
				\end{longtable}
			}
		}

	\subsection{Fundus Abnormalities}

	Fig.\ref{fig:fundus-abnormalities} shows the fundus abnormalities in the ODADS.
	Table \ref{tb:fundus-ab} lists the description of abnormalities.

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{lp{3.8in}}
				\caption{Fundus Abnormalities}
				\label{tb:fundus-ab}\\
				\toprule
				Abnormality&Description\\
				\toprule

				\multicolumn{1}{l}{Epiretinal membrane (ERM)}
				& Retinal Wrinkling.  Foveal Reflex Changes. Retinal Vessel Distortion\\

				\multicolumn{1}{l}{Macular hole (MH)} & Full-thickness macular hole showing a surrounding cuff of subretinal fluid.\\

				\multicolumn{1}{l}{Retinal nerve fiber layer defect} & A dark stripe or wedge-shaped localized defect in the peripapillary area, parallel to the normal retinal striation, or as a diffuse loss of this striation. \\

				\multicolumn{1}{l}{Glaucomatous disc change} & Cupping.  Cup-to-Disc Asymmetry. Thinning of Neuroretinal Rim. Optic Nerve Head Hemorrhages \\

				\multicolumn{1}{l}{Hard exudate} & Yellow or Yellow-White Deposits.  Hard Borders.  Distribution.  Clustering Around Blood Vessels\\

				\multicolumn{1}{l}{Hemorrhage} & Small dot-like to larger blot.  Fresh hemorrhages typically appear bright red or deep red in color, indicating the presence of oxygenated blood. Over time, as the blood undergoes degradation and clotting, the hemorrhage may change color to darker red, orange, or yellowish hues.\\

				\multicolumn{1}{l}{Cotton wool patch / soft exudate} & White or off-white lesions.  Irregular shapes and margins.\\

				\multicolumn{1}{l}{Fluid accumulation} &  a localized or diffuse elevation of the retina, often with a smooth or dome-shaped contour\\

				\multicolumn{1}{l}{Vascular abnormality} & Retinal Vessel Tortuosity.  Retinal Vessel Caliber Changes.  \\

				\multicolumn{1}{l}{Choroidal lesion} & Flat, well-defined areas of pigmentation ranging from light brown to dark brown. \\

				\multicolumn{1}{l}{Drusen} & Small, round or oval-shaped yellow or white deposits.\\

				\bottomrule
			\end{longtable}
		}
	}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.9\linewidth]{OCT-abnormalities.pdf}
		\caption{OCT Abnormalities}
		\vspace{0.3cm}
		\label{fig:oct-abnormalities}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.9\linewidth]{fundus-ab.pdf}
		\caption{Fundus Abnormalities}
		\vspace{0.3cm}
		\label{fig:fundus-abnormalities}
	\end{figure}

	\subsection{Diseases}
		Table \ref{tb:diseases} lists the diseases in ODADS.

		{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{lp{3.8in}}
				\caption{Diseases}
				\label{tb:diseases}\\
				\toprule
				Abnormality&Description\\
				\toprule

				\multicolumn{1}{l}{Central Serous Chorioretinopathy} & The accumulation of fluid under the retina, specifically in the macular region, leading to vision disturbances.\\

				\multicolumn{1}{l}{Epiretinal Membrane} & Also known as macular pucker or cellophane maculopathy, a condition characterized by the formation of a thin, semitransparent membrane on the surface of the retina, particularly in the macular region. Here's an overview of epiretinal membrane. \\

				\multicolumn{1}{l}{Macular Hole} & A defect or opening in the center of the macula, the central part of the retina responsible for sharp central vision. \\

				\multicolumn{1}{l}{Glaucoma Suspect} & Exhibit one or more risk factors or suspicious findings that suggest they may be at increased risk of developing glaucoma in the future. \\

				\multicolumn{1}{l}{Retinal Detachment} & The retina, the light-sensitive tissue lining the back of the eye, becomes separated from its underlying layers of support\\

				\multicolumn{1}{l}{Stargardt Disease} & Also known as Stargardt macular dystrophy or fundus flavimaculatus, is a genetic eye disorder characterized by progressive degeneration of the macula, the central part of the retina responsible for sharp central vision.\\

				\multicolumn{1}{l}{Mild DR} & Mild diabetic retinopathy (DR) refers to the early stages of retinal damage caused by diabetes. \\

				\multicolumn{1}{l}{Referable DR} & Referable diabetic retinopathy (DR) refers to the presence of diabetic retinopathy that requires referral to an ophthalmologist or retina specialist for further evaluation and management. This designation typically applies to cases of moderate to severe diabetic retinopathy or the presence of sight-threatening complications such as diabetic macular edema (DME). \\

				\multicolumn{1}{l}{Dry AMD} & Dry age-related macular degeneration (AMD) is characterized by the gradual deterioration of the macula due to the accumulation of drusen (yellowish deposits) and the loss of retinal pigment epithelial (RPE) cells, photoreceptors, and other retinal cells. It is the most common form of AMD, accounting for approximately 85-90\% of all cases.\\

				\multicolumn{1}{l}{Wet AMD} & Wet AMD is a more severe form of AMD compared to dry AMD. It is characterized by the growth of abnormal blood vessels (choroidal neovascularization) beneath the macula. These blood vessels are fragile and leak fluid and blood, causing damage to the macula and leading to rapid vision loss if left untreated.\\

				\multicolumn{1}{l}{BRVO / HCRVO} & Branch retinal vein occlusion (BRVO) and hemiretinal vein occlusion (HCRVO) are two types of retinal vein occlusion, which occur when one or more of the veins that carry blood away from the retina become blocked or occluded.\\

				\multicolumn{1}{l}{CRVO} & Central retinal vein occlusion (CRVO) is a serious eye condition that occurs when the main vein that drains blood from the retina becomes blocked or occluded. This blockage leads to a buildup of pressure in the retinal veins, causing hemorrhages, edema (fluid buildup), and ischemia (lack of blood flow) in the retina. \\

				\multicolumn{1}{l}{Retinitis Pigmentosa (RP)} & Retinitis pigmentosa (RP) is a group of inherited retinal disorders characterized by progressive degeneration of the retina, leading to vision loss and, in severe cases, blindness. RP typically affects the rod and cone photoreceptor cells in the retina, which are essential for vision in low light (rods) and daylight and color vision (cones). \\

				\multicolumn{1}{l}{Macular Telangiectasia (Mactel)} & 
				Macular telangiectasia, also known as idiopathic juxtafoveal retinal telangiectasis (IJRT) or idiopathic macular telangiectasia (IMT), is a rare, progressive eye condition characterized by abnormal dilation and leakage of blood vessels in the macula, the central part of the retina responsible for sharp central vision. Macular telangiectasia primarily affects the retinal capillaries in the juxtafoveal region, leading to vision loss and, in severe cases, legal blindness.\\

				\bottomrule
			\end{longtable}
		}
	}

	\section{Back-end Model}

		The back-end model is shown in Fig.\ref{fig:back-end}.

		The model contains $n$ OCT-Models, $m$ Fundus-Models and one Diagnosis Model.  The OCT-Models and Fundus-Models are fed by OCT images and fundus images respectively, and output image features and abnormality probabilities to the Diagnosis-Model where the data is fused and calculated.  Ultimately the diagnosis result is generated and outputted to Front-end UI.

		\vspace{0.5cm}

		\begin{figure}[htbp]
			\centering
			\includegraphics[width=\linewidth]{Back-end.pdf}
			\caption{Back-end Model}
			\label{fig:back-end}
		\end{figure}

	\subsection{Classifier}
		Each OCT-Model and Fundus-Model uses several types of abnormalities with the normal for training, which makes the model a classifier in the ODADS, as shown in Fig.\ref{fig:back-end}.

		We have the following formulas.

		\[
		N = \sum_{i=1}^{n} K_i \qquad M = \sum_{i=1}^{m} L_i
		\]

		Where:

		$n$: the OCT-Model number.

		$m$: the Fundus-Model number.

		$K_i$: the classifying abnormality number in $i^{th}$ OCT-Model.

		$L_i$: the classifying abnormality number in $i^{th}$ fundus-Model.

		$N$: the total abnormality number in OCT images.

		$M$: the total abnormality number in fundus images.

		\vspace{0.3cm}		
		We use the Greedy Algorithm to determining $K_i$, $L_i$, $n$, and $m$.

		Fig.\ref{fig:classifier} is an example to illustrate how OCT-Model 1 is generated.  First we choose the first abnormality and the normal to assemble a bi-classifier and calculate its performance (We will use F1-score as the performance indicator, refer to Section \ref{sec:results} for more information).  Then we introduce the second abnormality to form a new tri-classifier including 2 abnormalities and the normal.  If the performance of tri-classifier is better than the bi-classifier, we adopt the tri-classifier, otherwise we still use bi-classifier.  All the abnormalities are introduced in turn, either adopted or abandoned by the OCT-Model 1, and finally we get the classifier for OCT-Model1 including $K_i$ abnormalities and the normal.  Then we generate other classifiers in the same way as the first one until all the abnormalities belong to specific classifiers.

		\vspace{0.5cm}

		\begin{figure}[htbp]
			\centering
			\includegraphics[width=\linewidth]{Classifier.pdf}
			\caption{Classifiers Generation Algorithm}
			\label{fig:classifier}
		\end{figure}

		\vspace{0.5cm}

		We will set up a threshold for performance comparison.  Even when one classifier with more abnormalities has lower performance than another classifier with less abnormalities but the gap is within the threshold, we still choose the classifier with more abnormalities because we need to minimum classifier number to insure smaller CNN parameter quantities, faster running and easier deployment.

	\subsection{OCT-Model and Fundus-Model}
		The OCT-Model and fundus-Model use ResNet50 as backbones.  We apply transferred learning to train the ResNet50, which includes 2 phases, namely taking the models with the parameters learned with ImageNet and then performing a fine-tuning process.

		Fig.\ref{fig:resnet50} shows the architecture of OCT-Model and Fundus-Model.  We apply a modified ResNet50 and then flatten the data.  With a full-connected (FC) hidden layer, we get feature vector.  Then with another FC layer, we get abnormalities probabilities.  In Diagnosis-Model, we will determine to use whether feature vector or abnormalities probabilities for data fusion.

		\vspace{0.5cm}

		\begin{figure}[htbp]
			\centering
			\includegraphics[width=0.6\linewidth]{ResNet50.pdf}
			\caption{OCT-Model and Fundus-Model Architecture}
			\label{fig:resnet50}
		\end{figure}

	\subsection{Diagnosis-Model}

		The Diagnosis-Model is a neural network which fuses data from OCT-Models and Fundus-Models and then leverages a FC hidden layer to translate abnormalities to diseases.
		Fig.\ref{fig:diagnosis-model} shows 2 solutions for data fusion.  One is to fuse the feature vectors from OCT-Models and fundus-models, and the other is to fuse the probability vectors from those sub-models.  We compare the performance between 2 solutions and choose the better one as our ultimate architecture.
		When we fuse the feature vectors, we concatenate them as a big vector.  And when we fuse the probability vectors, we pick the maximum probability for each abnormality and then normalize the vector to form a new abnormality probability vector.

		\vspace{0.5cm}

		\begin{figure}[htbp]
			\centering
			\includegraphics[width=\linewidth]{Diagnosis-Model.pdf}
			\vspace{0.1cm}
			\caption{Diagnosis Model}
			\label{fig:diagnosis-model}
		\end{figure}

		For training Diagnosis-Model, we need to set up ground truth in terms of converting abnormalities to diseases.  We refer to 3 books for determining the conversion criteria, namely \textit{\citefield{Wolf_Kirchhof_Reim_2006}{title}}\autocite{Wolf_Kirchhof_Reim_2006}, \textit{\citefield{Duker_Waheed_Goldman_2022}{title}}\autocite{Duker_Waheed_Goldman_2022} and \textit{\citefield{Kawasaki_2013}{title}}\autocite{Kawasaki_2013}.

		The conversion criteria is shown in Fig.\ref{fig:abnormality-disease}, where the gray boxes represent OCT abnormalities, orange boxes represent fundus abnormalities, and blue boxes represent diseases.  Refer to Section \ref{sec:ab_di} for more information regarding abnormalities and diseases.

		\vspace{0.3cm}

		\begin{figure}[htbp]
			\centering
			\includegraphics[width=0.95\linewidth]{Abnormality-Disease.pdf}
			\vspace{0.3cm}
			\caption{From Abnormality to Disease}
			\label{fig:abnormality-disease}
		\end{figure}

	\subsection{Training}

		We will train all the OCT-Models and Fundus-Models first and determine all the classifiers.  Then we will freeze those models and train the Diagnoal-Model.  The training images will be labeled, prepossessing, augmented when necessary.  The augmentation includes image rotation, translation, scaling, flipping, brightness adjustment, constrat adjust, and noise addition etc.  If training images are too fewer, we will use CycleGAN to generate some synthetic images for training, but we will try to avoid doing this by looking for more public datasets.

		The trainings are implemented on a desktop computer with Intel® Xeon® Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM.

		\vspace{0.3cm}

		The training images for OCT-Models will come from the following 2 public datasets.
		\begin{enumerate}
			\vspace{-0.2cm}
			\item \textit{Large Dataset of Labeled Optical Coherence Tomography (OCT) and Chest X-Ray Images}\autocite{Kermany_database}.
			\vspace{-0.2cm}
			\item \textit{Data for: Improved accuracy in OCT diagnosis of rare ocular disease using few-shot learning with generative adversarial networks} \autocite{Yoo_2020}.
		\end{enumerate}

		\vspace{0.3cm}

		The training images for Fundus-Models will come from another 5 public datasets.
		\begin{enumerate}
			\vspace{-0.2cm}
			\item \textit{E-ophtha} \autocite{E_ophtha}.
			\vspace{-0.2cm}
			\item \textit{Diabetic Retinopathy Detection} \autocite{DR_dataset}.
			\vspace{-0.2cm}
			\item \textit{Indian Diabetic Retinopathy Image Dataset. (IDRiD)} \autocite{Porwal_2018}.
			\vspace{-0.2cm}
			\item \textit{Messidor} \autocite{Messidor}.
			\vspace{-0.2cm}
			\item \textit{STructured Analysis of the Retina} \autocite{STARE}.
		\end{enumerate}

		\vspace{0.3cm}

		We have not found online open dataset for training Diagnosis-Model.  We will need OCT images and fundus images from the same patients.  Online datasets only contain OCT images or fundus images, which do not meet our requirement.

		There are 2 plans as follow.  \textcolor{magenta}{We would hope to implement plan A.  Using the real data from hospital could make the ODADS more reliable and robust}.  If plan A is not possible, we will do plan B.
		\vspace{0.1cm}
		\begin{enumerate}
			\vspace{-0.2cm}
			\item \textcolor{magenta}{We will use the data from hospital.  The dataset will contain OCT images and fundus images from patients.  For privacy, we do not need any patient identity information, and each piece of data in the dataset could be organized as "Data Number", "OCT images", "Fundus Images" and "Brief Diagnosis".  This may need to be approved by authorities.}
			\vspace{-0.2cm} 
			\item We will make up the training data on our own.  The image data will come from above public database and the diagnosis will be made by ourselves.
		\end{enumerate}

	\subsection{Results} \label{sec:results}

		We will provide the following performance indicators for each model.
		\vspace{0.1cm}
		\begin{itemize}
			\vspace{-0.2cm}
			\item Confusion Matrix, as shown in Fig.\ref{fig:cm}.
			\begin{figure}[htbp]
				\centering
				\includegraphics[width=0.5\linewidth]{ConfusionMatrix.pdf}
				\vspace{0.1cm}
				\caption{Confusion Matrix}
				\label{fig:cm}
			\end{figure}

			\vspace{-0.2cm} 
			\item Accuracy = $\displaystyle \frac{TP+TN}{TP+TN+FP+FN}$.

			\vspace{0.1cm} 
			\item Precision = $\displaystyle \frac{TP}{TP+FP}$.

			\vspace{0.1cm} 
			\item Recall (Sensitivity) = $\displaystyle \frac{TP}{TP+FN}$.

			\vspace{0.1cm} 
			\item Specificity = $\displaystyle \frac{TN}{TN+FP}$.

			\vspace{0.1cm} 
			\item F1-score = $\displaystyle \frac{2\times Precision\times Recall}{Precision+Recall}$.

			\vspace{0.1cm} 
			\item Receiver Operating Characteristic Curve (ROC).
			\vspace{-0.1cm} 
			\item Area Under the ROC (AUC).
			\vspace{-0.1cm} 
			\item t-distributed Stochastic Neighbor Embedding (t-SNE).

		\end{itemize}

	\section{Front-end UI}

		The front-end UI includes one website application and one APP.  They have the following UI elements and functionalities.

		\begin{itemize}
		\vspace{-0.2cm}
		\item Taking photo button (APP only) enables users to take photos as diagnosis images.
		\vspace{-0.2cm} 
		\item Selecting photo button enables user to select photos from disk or mobile phone's gallery.
		\vspace{-0.2cm} 
		\item A list of abnormalities lists all the potential abnormalities by their probabilities.
		\vspace{-0.2cm} 
		\item A probabilities pie graph for diseases.
		\vspace{-0.2cm} 
		\item A diagnosis report.
		\vspace{-0.2cm} 
		\item When user select abnormalities, the abnormalities are highlighted on the image.
		\vspace{-0.2cm} 
		\item Reset button enables user to clear current information and begin a new diagnosis.
		\vspace{-0.2cm} 
		\item Uploading button enables user to upload the images to server to help make the ODADS better.
	\end{itemize}

	\vspace{0.2cm}

	In the front-end UI, users can select up to 10 images for diagnosis.  Each image will go through the back-end model and generate probability vectors.  For evaluating the ultimate probability vector, we will choose the maximum probability for each abnormality and disease, and normalize the vector with maximum values as ultimate result.

	The Front-end UI will leverage Gradient-weighted Class Activation Mapping (Grad-CAM) to visualize the abnormality location.  Grad-CAM is implemented before the last fully connected layer in each OCT-Model and Fundus-Model and passes its result from the back-end model to the front-end UI.

	We also encourage users to upload their images so that the server can train the back-end model periodically to make the ODADS better.

	\section{Innovation}

		\begin{itemize}
			\item The ODADS uses bi-modal architecture and integrates 2 types of ocular images, namely fundus images and OCT images, making the diagnosis more comprehensive.

			\vspace{-0.2cm} 
			\item The ODADS outputs the probabilities of ocular diseases instead of simply naming a single disease. Therefore, the ODADS can reflect the ocular condition more accurately.

			\vspace{-0.2cm} 
			\item The ODADS lists all the abnormalities to break the black box. The diagnosis result could be more flexible, complete, and interpretable.

			\vspace{-0.2cm} 
			\item The ODADS has a front-end UI that implements the back-end model and makes a complete diagnosis system. Also, the ODADS allows users to upload images to better the system.

			\vspace{-0.2cm} 
			\item The ODADS investigates the optimal classifier generation and 2 types of fusion timing, which helps the ODADS achieve better performance.

		\end{itemize}

	\section{Plan}

		\begin{figure}[htbp]
			\centering
			\includegraphics[width=\linewidth]{Plan.pdf}
			\caption{Research Plan}
			\label{fig:plan}
		\end{figure}

		The research process consists of 4 phases, as shown in Fig. \ref{fig:plan}.

		The first phase is from March to June. I will read relevant literature, including deep learning technology and state-of-the-art image detection researches. And I will also study ophthalmology to familiarize myself with ocular diagnosis and learn to read OCT and fundus images to identify abnormalities and diseases. In the meanwhile, I will collect OCT and fundus images from websites and do the prepossessing work, so that they can be used in training models. I will also develop the OCT-models, the Fundus-Models, the Diagnosis-model, and the APP and website in sequence.  \textcolor{magenta}{It is preferable if we can get real data from hospital prior to developing the Diagnosis-Model}.

		The second phase includes July and August. I will complete the first draft of the paper. And I will keep on developing the system.

		The third phase includes September and October. I will keep on improving development and paper.

		The last phase is November. I will finalize the paper and be prepared for the thesis defense.

	\phantomsection
	\addcontentsline{toc}{section}{References}
	\newrefcontext[sorting=nyt]
	\printbibliography

\end{document}

### 2024-08-12 Paper/Paper.tex
Add paper framework to tex doc

@@
 	\pagebreak
+
+	\section{Background}
+
+	\section{Model Overview}
+
+		Fig: OCT abnormities
+		Fig: Fundus abnormities
+		Fig: From Abnormity to Disease
+		Fig: 3 parts
+		Fig: fusion
+
+	\section{Methodology}
+
+		\subsection{Abnormity Models}
+
+			\subsubsection{Data Preparation}
+
+				Table: Data source
+				CycleGAN
+					Fig: Intro
+					Table: selection rates
+					selection criteria
+				Transformations
+
+			\subsubsection{Training}
+
+				intro to five-fold train/valid
+				parameters used
+				Fig: how batchSize, LR, and featureLayerSize affects accuracy
+
+			\subsubsection{Testing}
+
+				numerical results calculation method
+				t-SNE intro
+				GradCAM intro
+
+		\subsection{Diagnosis Model}
+
+			\subsubsection{Data Preparation}
+
+				fusion method
+				how to choose data (with an example)
+
+			\subsubsection{Training}
+
+				parameters used
+				Fig: how batchSize, LR, gradeSize affects accuracy
+
+			\subsubsection{Testing}
+
+				numerical results list
+				t-SNE
+
+	\section{Results and Discussion}
+
+		\subsection{Abnormity Models}
+
+			For both OCT and Fundus:
+				Fig: accuracy and loss over epochs
+				Table: total accuracy and abnormities accuracies
+				Table: numerical results for each abnormity
+				Fig: ROC for each abnormity
+				Fig: GradCAM example
+
+		\subsection{Diagnosis Model}
+
+			Fig: accuracy and loss over epochs
+			Table: total accuracy and abnormities accuracies
+			Table: numerical results for each disease
+			Fig: ROC for each disease
+
+	\section{Appendix}
+
+		Google Image source links
+		Table: OCT abnormities description
+		Table: Fundus abnormities description
 

### 2024-08-12 Paper/Paper.tex
Change folder structures; delete former trials; delete __init__.py

--- 2024-08-12 Paper/Paper.tex
@@
 	\pagebreak
+
+	\section{Background}
+
+	\section{Model Overview}
+
+		Fig: OCT abnormities
+		Fig: Fundus abnormities
+		Fig: From Abnormity to Disease
+		Fig: 3 parts
+		Fig: fusion
+		how to find grade
+
+	\subsection{Abnormity Models}
+
+		\subsubsection{Data Preparation}
+
+			Table: Data source
+			CycleGAN
+				Fig: Intro
+				Table: selection rates
+				selection criteria
+			Transformations
+
+		\subsubsection{Training}
+
+			intro to five-fold train/valid
+			parameters used, hard device parameters
+
+		\subsubsection{Results}
+
+			For both OCT and Fundus:
+				Fig: accuracy and loss over epochs
+				Table: total accuracy and abnormities accuracies
+				Table: numerical results for each abnormity
+				Fig: t-SNE
+				Fig: ROC for each abnormity
+
+				Fig: GradCAM intro
+				Fig: GradCAM example
+
+	\subsection{Diagnosis Model}
+
+		\subsubsection{Data Preparation}
+
+			how to choose data (with an example)
+
+		\subsubsection{Training}
+
+			parameters used
+
+		\subsubsection{Results}
+
+			Do two models increase accuracy?
+			Fig: accuracy and loss over epochs
+			Table: total accuracy and disease accuracies
+			Table: numerical results for each disease
+			Fig: ROC for each disease
+
+	\section{Conclusion}
+
+		Comparison
+		Strengths and weaknesses
+
+	\section{Appendix}
+
+		Google Image source links
+		Table: OCT abnormities description
+		Table: Fundus abnormities description
+		APP/website description
 

### 2024-08-12 ODADS/Code/AbnormityModels/classify.py

@@ -1,6 +1,6 @@
 import os
 import torch
-import abnormityModel
+from AbnormityModels import abnormityModel
 from Utils import utils
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 

### 2024-08-12 ODADS/Code/AbnormityModels/trainClassify.py

@@ -8,7 +8,7 @@ import copy
 import csv
 from datetime import datetime
 from Utils import utils
-import AbnormityModels.abnormityModel as abnormityModel
+from AbnormityModels import abnormityModel
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
 

### 2024-08-12 ODADS/Code/DiagnosisModel/trainDiagnose.py

@@ -10,7 +10,7 @@ import csv
 from datetime import datetime
 from AbnormityModels import abnormityModel
 from Utils import utils
-import diagnosisModel
+from DiagnosisModel import diagnosisModel
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
 def getOutputs(device, diseaseName, oAbnormityNum, fAbnormityNum, grade, dbName, oModel, fModel):

### 2024-08-12 ODADS/Code/main.py

@@ -13,12 +13,12 @@ def main():
           "CUDA not available.")
     device = torch.device("cuda:0" if useGpu else "cpu") # get to know how to use both GPUs
     print(device)
-
+    
     task = 2 # TASK!!!
     numClasses = 2 # CHANGE NUM OF CLASSES!
     numEpochs = 5
     if task == 1: # train single OCT or Fundus
-        dataset = "Fundus-normal-DR-demo/train"
+        dataset = "ODADS/Data/Data/Original"
         batchSize = 16
         epochs = 5
         LR = 1e-3

### 2024-08-12 ODADS/Code/AbnormityModels/classify.py
update all file paths in programs to match new folders

@@ -8,10 +8,10 @@ os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 def classify(img, numClasses, device, featureExtract, modelName, wtsName):
     modelFt, _ = abnormityModel.initializeAbnormityModel(modelName, numClasses, featureExtract)
     modelFt = modelFt.to(device)
-    trainedModel = torch.load(os.path.join(".\\TrainedModel", wtsName + ".pth"))
+    trainedModel = torch.load(f"ODADS/Data/Weights/{wtsName}/{wtsName}.pth")
     modelFt.load_state_dict(trainedModel["state_dict"])
-    #utils.imgShow(img)
-    img = utils.resizeLongEdge(img) # Necessary?
+    # utils.imgShow(img)
+    img = utils.resizeLongEdge(img)
     img = img.unsqueeze(0)
     output = modelFt(img.to(device))
     print(output[0])

### 2024-08-12 ODADS/Code/AbnormityModels/gradcam.py

@@ -165,7 +165,7 @@ def camShow(img, cam, title = ""):
 def highlight(imgPath, numClasses, device, featureExtract, modelName, wtsName):
     modelFt, _ = trainClassify.initializeAbnormityModel(modelName, numClasses, featureExtract)
     modelFt = modelFt.to(device)
-    trainedModel = torch.load(os.path.join(".\\TrainedModel", wtsName + ".pth"))
+    trainedModel = torch.load(f"ODADS/Data/Weights/{wtsName}/{wtsName}.pth")
     modelFt.load_state_dict(trainedModel["state_dict"])
     img = Image.open(imgPath)
     img = classify.processImg(img, customResize = 224)

### 2024-08-12 ODADS/Code/AbnormityModels/trainClassify.py

@@ -13,7 +13,7 @@ os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
 
 
-def trainModel(device, model, criterion, optimizer, scheduler, filename, dbName, crossValid, batchSize, numEpochs, isInception = False):
+def trainModel(device, model, criterion, optimizer, scheduler, filename, dataDir, crossValid, batchSize, numEpochs, isInception = False):
     startTime = time.time()
     bestAcc = 0
     model.to(device)
@@ -25,7 +25,6 @@ def trainModel(device, model, criterion, optimizer, scheduler, filename, dbName,
     
     bestModelWts = copy.deepcopy(model.state_dict())
     
-    dataDir = "./Data/" + dbName
     dataTransforms = transforms.Compose([transforms.Lambda(utils.resizeLongEdge), transforms.ToTensor()])
     if crossValid:
         imageDataset = datasets.ImageFolder(dataDir, dataTransforms)
@@ -98,8 +97,8 @@ def trainModel(device, model, criterion, optimizer, scheduler, filename, dbName,
                     "best_acc": bestAcc,
                     "optimizer": optimizer.state_dict()
                 }
-                torch.save(state, os.path.join(".\\TrainedModel", filename))
-                print(f"Data successfully written into {filename}")
+                torch.save(state, f"ODADS/Data/Weights/{filename}/{filename}.pth")
+                print(f"Data successfully written into {filename}.pth")
                 
             if phase == "valid":
                 validAccHistory.append(epochAcc)
@@ -121,34 +120,34 @@ def trainModel(device, model, criterion, optimizer, scheduler, filename, dbName,
     return model, validAccHistory, trainAccHistory, validLosses, trainLosses, LRs, timeElapsed
 
 def train(device, featureExtract, modelName, numClasses, batchSize, numEpochs, LR, usePretrained, dbName, wtsName, modelType, crossValid = True):
-    modelFt, inputSize = abnormityModel.initializeAbnormityModel(modelName, numClasses, featureExtract, usePretrained = usePretrained) # what does FT stand for?
-    modelFt = modelFt.to(device)
+    model, _ = abnormityModel.initializeAbnormityModel(modelName, numClasses, featureExtract, usePretrained = usePretrained)
+    model = model.to(device)
     if wtsName != "":
[…]

### 2024-08-12 ODADS/Code/DiagnosisModel/diagnose.py

@@ -33,7 +33,7 @@ def diagnose(oImgs, fImgs, diseaseName, device, modelName, dWtsTime, oWts, fWts)
     
     dModel, _ = trainDiagnose.diagnosisModel.SimpleNet(abnormityNum, gradeLevels)
     dModel = dModel.to(device)
-    trainedModel = torch.load(f"./TrainedModel/D {dWtsTime}/D {diseaseName} {dWtsTime}.pth")
+    trainedModel = torch.load(f"ODADS/Data/Weights/D {dWtsTime}/D {diseaseName} {dWtsTime}.pth")
     dModel.load_state_dict(trainedModel["state_dict"])
     
     output = dModel(dInput.to(device))

### 2024-08-12 ODADS/Code/DiagnosisModel/trainDiagnose.py

@@ -163,33 +163,30 @@ def trainModel(device, diseaseName, oModel, fModel, wtsName, dTime, dbName, batc
     
     return dModel, trainAccHistory, validAccHistory, trainLosses, validLosses, LRs, timeElapsed
 
-def train(device, diseaseName, featureExtract, modelName, oWts, fWts, batchSize, gradeSize, numEpochs, LR, dbName, wtsName):
+def train(device, diseaseName, featureExtract, modelName, oWts, fWts, batchSize, gradeSize, numEpochs, LR, dbName, wtsName, dTime):
     criteria = utils.getCriteria()
     oNumClasses = len(criteria["All"]["OCT"])
     fNumClasses = len(criteria["All"]["Fundus"])
     
     oModel, _ = abnormityModel.initializeAbnormityModel(modelName, oNumClasses, featureExtract)
     oModel = oModel.to(device)
-    oTrainedModel = torch.load(os.path.join(".\\TrainedModel", oWts + ".pth"))
+    oTrainedModel = torch.load(f"ODADS/Data/Weights/{oWts}/{oWts}.pth")
     oModel.load_state_dict(oTrainedModel["state_dict"])
     
     fModel, _ = abnormityModel.initializeAbnormityModel(modelName, fNumClasses, featureExtract)
     fModel = fModel.to(device)
-    fTrainedModel = torch.load(os.path.join(".\\TrainedModel", fWts + ".pth"))
+    fTrainedModel = torch.load(f"ODADS/Data/Weights/{fWts}/{fWts}.pth")
     fModel.load_state_dict(fTrainedModel["state_dict"])
     
-    now = datetime.now()
-    dTime = now.strftime("%Y-%m-%d %H-%M-%S")
     filename = f"D {diseaseName} {dTime}"
-    filePath = f"D {dTime}/{filename}"
     
     dModel, validAccHistory, trainAccHistory, trainLosses, validLosses, LRs, timeElapsed = trainModel(device, diseaseName, oModel, fModel, wtsName, dTime, dbName, batchSize, LR, numEpochs, gradeSize)
     
-    with open(os.path.join(".\\Log", filename + ".csv"), "w", newline="") as file:  
+    with open(f"ODADS/Data/Results/D {dTime}/{filename}.csv", "w", newline="") as file:  
         writer = csv.writer(file)  
[…]

### 2024-08-12 ODADS/Code/Utils/crop_imgs.py

@@ -1,8 +1,8 @@
 import os
 from PIL import Image
 
-source_folder = './OCT-Original/Drusen_sel'
-target_folder = './OCT-Original/Drusen'
+source_folder = 'ODADS/Data/Data/Original/OCT/Drusen'
+target_folder = 'ODADS/Data/Data/Transformed/OCT/Drusen'
 
 os.makedirs(target_folder, exist_ok=True)
 

### 2024-08-12 ODADS/Code/Utils/ppm_to_jpeg.py

@@ -14,5 +14,5 @@ def convert_ppm_to_jpg(root_folder):
                 os.remove(ppm_path)
                 print(f'Converted and deleted: {ppm_path}')
 
-root_folder = './Fundus-Original - Copy'
+root_folder = ''
 convert_ppm_to_jpg(root_folder)

### 2024-08-12 ODADS/Code/Utils/split_test_data.py

@@ -1,0 +1,31 @@
+import os
+import shutil
+import random
+
+parent_folder_A = 'ODADS/Data/Data/Transformed/OCT'
+parent_folder_B = 'ODADS/Data/Data/Test/OCT'
+num = 5000
+
+def ensure_subfolder_exists(folder_path):
+    if not os.path.exists(folder_path):
+        os.makedirs(folder_path)
+
+for subfolder_A in os.listdir(parent_folder_A):
+    path_A = os.path.join(parent_folder_A, subfolder_A)
+    
+    if os.path.isdir(path_A):
+        subfolder_B = subfolder_A
+        path_B = os.path.join(parent_folder_B, subfolder_B)
+        ensure_subfolder_exists(path_B)
+
+        all_files = [f for f in os.listdir(path_A) if os.path.isfile(os.path.join(path_A, f))]
+        num_files_to_move = int(0.1 * num)
+        files_to_move = random.sample(all_files, num_files_to_move)
+        
+        for file_name in files_to_move:
+            source_file = os.path.join(path_A, file_name)
+            destination_file = os.path.join(path_B, file_name)
+            shutil.move(source_file, destination_file)
+        print(f"Moved {num_files_to_move} files from '{subfolder_A}' to '{subfolder_B}'")
+
+print("File moving process completed.")

### 2024-08-12 ODADS/Code/Utils/transform.py

@@ -1,113 +1,0 @@
-import os
-from PIL import Image
-import torchvision.transforms as transforms
-import torchvision.datasets as datasets
-import torch
-import math
-import random
-
-def resizeLongEdge(img, longEdgeSize = 0):
-    width, height = img.size
-    if longEdgeSize == 0:
-        longEdgeSize = max(width, height)
-    if width > height:
-        newSize = (longEdgeSize, int(height * longEdgeSize / width))
-        loc = (0, int((longEdgeSize - newSize[1]) / 2))
-    else:
-        newSize = (int(longEdgeSize * width / height), longEdgeSize)
-        width, _ = img.size
-        loc = (int((longEdgeSize - newSize[0]) / 2), 0)
-    img = img.resize(newSize)
-    blackBackground = Image.new("RGB", (longEdgeSize, longEdgeSize), "black")
-    blackBackground.paste(img, loc)
-    return blackBackground
-
-class MultiTransformDataset(torch.utils.data.Dataset):
-    def __init__(self, root_dir, transform, num_transforms=5, exclude_classes=None):
-        self.dataset = datasets.ImageFolder(root=root_dir)
-        self.transform = transform
-        self.num_transforms = num_transforms
-        if exclude_classes is not None:
-            self.exclude_classes = set(exclude_classes)
-            self._filter_classes()
-        
-    def _filter_classes(self):
-        filtered_samples = []
-        for sample in self.dataset.samples:
-            path, class_idx = sample
-            class_name = self.dataset.classes[class_idx]
-            if class_name not in self.exclude_classes:
-                filtered_samples.append(sample)
-        self.dataset.samples = filtered_samples
-        self.dataset.targets = [s[1] for s in filtered_samples]
-
-    def __len__(self):
-        return len(self.dataset)
-
-    def __getitem__(self, idx):
-        img, label = self.dataset[idx]
-        transformed_imgs = [self.transform(img) for _ in range(self.num_transforms)]
-        return transformed_imgs, label
-
-def delete_random_files(directory, num_files_to_delete):
-    files = os.listdir(directory)
-    files_to_delete = random.sample(files, num_files_to_delete)
-    for file in files_to_delete:
-        file_path = os.path.join(directory, file)
-        os.remove(file_path)
-        print(f"Deleted file: {file}")
-
-
-
-if __name__ == '__main__':
-    
-    sideLength = 224
-    
[…]

### 2024-08-12 ODADS/Code/Utils/transform_imgs.py

@@ -1,0 +1,110 @@
+import os
+from PIL import Image
+import torchvision.transforms as transforms
+import torchvision.datasets as datasets
+import torch
+import math
+import random
+
+def resizeLongEdge(img, longEdgeSize = 0):
+    width, height = img.size
+    if longEdgeSize == 0:
+        longEdgeSize = max(width, height)
+    if width > height:
+        newSize = (longEdgeSize, int(height * longEdgeSize / width))
+        loc = (0, int((longEdgeSize - newSize[1]) / 2))
+    else:
+        newSize = (int(longEdgeSize * width / height), longEdgeSize)
+        width, _ = img.size
+        loc = (int((longEdgeSize - newSize[0]) / 2), 0)
+    img = img.resize(newSize)
+    blackBackground = Image.new("RGB", (longEdgeSize, longEdgeSize), "black")
+    blackBackground.paste(img, loc)
+    return blackBackground
+
+class MultiTransformDataset(torch.utils.data.Dataset):
+    def __init__(self, root_dir, transform, num_transforms=5, exclude_classes=None):
+        self.dataset = datasets.ImageFolder(root=root_dir)
+        self.transform = transform
+        self.num_transforms = num_transforms
+        if exclude_classes is not None:
+            self.exclude_classes = set(exclude_classes)
+            self._filter_classes()
+        
+    def _filter_classes(self):
+        filtered_samples = []
+        for sample in self.dataset.samples:
+            path, class_idx = sample
+            class_name = self.dataset.classes[class_idx]
+            if class_name not in self.exclude_classes:
+                filtered_samples.append(sample)
+        self.dataset.samples = filtered_samples
+        self.dataset.targets = [s[1] for s in filtered_samples]
+
+    def __len__(self):
+        return len(self.dataset)
+
+    def __getitem__(self, idx):
+        img, label = self.dataset[idx]
+        transformed_imgs = [self.transform(img) for _ in range(self.num_transforms)]
+        return transformed_imgs, label
+
+def delete_random_files(directory, num_files_to_delete):
+    files = os.listdir(directory)
+    files_to_delete = random.sample(files, num_files_to_delete)
+    for file in files_to_delete:
+        file_path = os.path.join(directory, file)
+        os.remove(file_path)
+        print(f"Deleted file: {file}")
+
+
+sideLength = 224
+
[…]

### 2024-08-12 ODADS/Code/Utils/utils.py

@@ -25,7 +25,7 @@ def resizeLongEdge(img, longEdgeSize = 224):
     blackBackground.paste(img, loc)
     return blackBackground
 
-def curve(validAccHistory, trainAccHistory, validLosses, trainLosses, filename):
+def curve(validAccHistory, trainAccHistory, validLosses, trainLosses, filename, show = False):
     plt.clf()
     x = range(1, len(trainLosses) + 1)
     
@@ -48,8 +48,9 @@ def curve(validAccHistory, trainAccHistory, validLosses, trainLosses, filename):
     plt.legend() 
     
     plt.tight_layout()
-    plt.savefig(os.path.join(".\\Results", filename), format="pdf")
-    plt.show()
+    plt.savefig(filename, format="pdf")
+    if show:
+        plt.show()
 
 def processImg(img, customResize = 224):
     if customResize != 0:

### 2024-08-12 ODADS/Code/main.py

@@ -1,7 +1,9 @@
 from AbnormityModels import classify, trainClassify, gradcam
 from DiagnosisModel import diagnose, trainDiagnose
+from Utils import utils
 import torch
 from PIL import Image
+import datetime
 import os
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
@@ -13,36 +15,47 @@ def main():
           "CUDA not available.")
     device = torch.device("cuda:0" if useGpu else "cpu") # get to know how to use both GPUs
     print(device)
+    criteria = utils.getCriteria()
     
-    task = 2 # TASK!!!
-    numClasses = 2 # CHANGE NUM OF CLASSES!
-    numEpochs = 5
-    if task == 1: # train single OCT or Fundus
-        dataset = "ODADS/Data/Data/Original"
+    task = 1 
+    numClasses = len(criteria["All"]["OCT"])
+    
+    if task == 1: # train OCT or Fundus
+        dbName = "ODADS/Data/Data/Transformed/OCT/"
+        wtsName = ""
         batchSize = 16
-        epochs = 5
+        numEpochs = 200
         LR = 1e-3
-        imgType = "F"
-        trainClassify.train(device, featureExtract, modelName, numClasses, batchSize, epochs, LR, True, dataset, "", imgType, crossValid = True)
+        imgType = "O"
+        trainClassify.train(device, featureExtract, modelName, numClasses, batchSize, numEpochs, LR, True, dbName, wtsName, imgType, crossValid = True)
+        
     elif task == 2: # classify single image with OCT or Fundus
-        string = "./Data/Fundus-normal-DR-selected/train/DR/16_left.jpeg"
-        wts = "F 2024-08-07 16-48-56"
+        string = "ODADS/Data/Data/Original/OCT"
+        wts = ""
         img = Image.open(string)
         classify.classify(img, numClasses, device, featureExtract, modelName, wts)
+        
     elif task == 3: # gradCAM single image with OCT or Fundus
         string = "./Data/OCT-normal-drusen-large/train/drusen/DRUSEN-303435-2.jpeg"
         wts = "O 2024-05-09 22-42-15"
         gradcam.highlight(string, numClasses, device, featureExtract, modelName, wts)
+        
     elif task == 4: # train single disease
-        oModelName = "./Data/Fundus-normal-DR-selected/train/DR/16_left.jpeg"
-        fModelName = "O 2024-05-09 22-42-15"
+        now = datetime.now()
[…]

### 2024-08-12 CycleGAN/additional_code/move_fake.py
Copy CycleGAN to ODADS/CycleGAN. Update LOG and move source.txt to outermost folder

@@ -1,0 +1,34 @@
+import os
+import shutil
+import re
+
+def copy_with_regex(pattern, src_dir, dest_dir):
+    if not os.path.exists(dest_dir):
+        os.makedirs(dest_dir)
+    
+    num_files = 0
+    num_skips = 0
+
+    for root, _, files in os.walk(src_dir):
+        for filename in files:
+            if pattern.search(filename):
+                src_file = os.path.join(root, filename)
+                dest_file = os.path.join(dest_dir, filename)
+                
+                if os.path.exists(dest_file):
+                    print(f"Skipped (exists): {dest_file}")
+                    num_skips += 1
+                else:
+                    shutil.copy(src_file, dest_file)
+                    print(f"Copied: {src_file} to {dest_file}")
+                    num_files += 1
+    
+    print(f"moved {num_files} files to {dest_dir}")
+    print(f"skipped {num_skips} files")
+
+if __name__ == "__main__":
+    pattern = re.compile(r'_fake\.(jpg|jpeg|png)$', re.IGNORECASE)
+    src_directory = "results/Final_Neo_ERM/Transformed_Neo_ERM/maps_cyclegan/test_latest/images"
+    dest_directory = "GAN-imgs/ERM"
+
+    copy_with_regex(pattern, src_directory, dest_directory)

### 2024-08-12 CycleGAN/additional_code/transform_imgs.py

@@ -1,0 +1,115 @@
+import os
+from PIL import Image
+import torchvision.transforms as transforms
+import torchvision.datasets as datasets
+import torch
+
+def resizeLongEdge(img, longEdgeSize = 0):
+    width, height = img.size
+    if longEdgeSize == 0:
+        longEdgeSize = max(width, height)
+    if width > height:
+        newSize = (longEdgeSize, int(height * longEdgeSize / width))
+        loc = (0, int((longEdgeSize - newSize[1]) / 2))
+    else:
+        newSize = (int(longEdgeSize * width / height), longEdgeSize)
+        width, _ = img.size
+        loc = (int((longEdgeSize - newSize[0]) / 2), 0)
+    img = img.resize(newSize)
+    blackBackground = Image.new("RGB", (longEdgeSize, longEdgeSize), "black")
+    blackBackground.paste(img, loc)
+    return blackBackground
+
+"""
+def normalizeBrightness(img, target_mean, target_std):
+       grayscale_img = transforms.Grayscale(num_output_channels=1)(img)
+        grayscale_tensor = transforms.ToTensor()(grayscale_img)
+        current_std = torch.std(grayscale_tensor)
+    
+        if current_std > 0:
+            std_adjustment_factor = target_std / (current_std + 1e-6)
+        else:
+            std_adjustment_factor = 1.0
+        
+        img_tensor = transforms.ToTensor()(img)
+        normalized_img_tensor = (img_tensor - img_tensor.mean(dim=[1,2], keepdim=True)) * std_adjustment_factor + target_mean
+        normalized_img_tensor = torch.clamp(normalized_img_tensor, 0.0, 1.0)
+        
+        grayscale_img = transforms.Grayscale(num_output_channels=1)(img)
+        grayscale_tensor = transforms.ToTensor()(grayscale_img)
+        min_grayscale = torch.min(grayscale_tensor)
+        max_grayscale = torch.max(grayscale_tensor)
+        
+        img = transforms.ToTensor()(img)
+        normalized_img_tensor = (img - min_grayscale) / (max_grayscale - min_grayscale + 1e-6)
+        
+        return normalized_img_tensor
+"""
+
+class MultiTransformDataset(torch.utils.data.Dataset):
+    def __init__(self, root_dir, transform, num_transforms=5, exclude_classes=None):
+        self.dataset = datasets.ImageFolder(root=root_dir)
+        self.transform = transform
+        self.num_transforms = num_transforms
+        if exclude_classes is not None:
[…]

### 2024-08-12 CycleGAN/test.py

@@ -1,0 +1,80 @@
+"""General-purpose test script for image-to-image translation.
+
+Once you have trained your model with train.py, you can use this script to test the model.
+It will load a saved model from '--checkpoints_dir' and save the results to '--results_dir'.
+
+It first creates model and dataset given the option. It will hard-code some parameters.
+It then runs inference for '--num_test' images and save results to an HTML file.
+
+Example (You need to train models first or download pre-trained models from our website):
+    Test a CycleGAN model (both sides):
+        python test.py --dataroot ./datasets/maps --name maps_cyclegan --model cycle_gan
+
+    Test a CycleGAN model (one side only):
+        python test.py --dataroot datasets/horse2zebra/testA --name horse2zebra_pretrained --model test --no_dropout
+
+    The option '--model test' is used for generating CycleGAN results only for one side.
+    This option will automatically set '--dataset_mode single', which only loads the images from one set.
+    On the contrary, using '--model cycle_gan' requires loading and generating results in both directions,
+    which is sometimes unnecessary. The results will be saved at ./results/.
+    Use '--results_dir <directory_path_to_save_result>' to specify the results directory.
+
+    Test a pix2pix model:
+        python test.py --dataroot ./datasets/facades --name facades_pix2pix --model pix2pix --direction BtoA
+
+See options/base_options.py and options/test_options.py for more test options.
+See training and test tips at: https://github.com/junyanz/pytorch-CycleGAN-and-pix2pix/blob/master/docs/tips.md
+See frequently asked questions at: https://github.com/junyanz/pytorch-CycleGAN-and-pix2pix/blob/master/docs/qa.md
+"""
+import os
+from options.test_options import TestOptions
+from data import create_dataset
+from models import create_model
+from util.visualizer import save_images
+from util import html
+
+try:
+    import wandb
+except ImportError:
+    print('Warning: wandb package cannot be found. The option "--use_wandb" will result in error.')
+
+
+if __name__ == '__main__':
+    opt = TestOptions().parse()  # get test options
+    # hard-code some parameters for test
+    opt.num_threads = 0   # test code only supports num_threads = 0
+    opt.batch_size = 1    # test code only supports batch_size = 1
+    opt.serial_batches = True  # disable data shuffling; comment this line if results on randomly chosen images are needed.
[…]

### 2024-08-12 ODADS/Code/Utils/utils.py

@@ -7,7 +7,7 @@ import json
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
 def getCriteria():
-    with open('criteria.json', 'r', encoding='utf-8') as file:
+    with open('Criteria.json', 'r', encoding='utf-8') as file:
         criteria = json.load(file)
     return criteria
 

### 2024-08-12 ODADS/Code/main.py

@@ -19,7 +19,7 @@ def main():
     
     task = 1 
     numClasses = len(criteria["All"]["OCT"])
-    
+        
     if task == 1: # train OCT or Fundus
         dbName = "ODADS/Data/Data/Transformed/OCT/"
         wtsName = ""

### 2024-08-12 ODADS/Code/AbnormityModels/abnormityModel.py
Correct "random_split" to make all classes be split according to proportions 80%:20%.

@@ -10,17 +10,17 @@ def setParameterRequiresGrad(model, featureExtract):
             param.requires_grad = False
 
 def initializeAbnormityModel(modelName, numClasses, featureExtract, usePretrained = True):
-    modelFt = None
+    model = None
     inputSize = 0
     
     if modelName == "resnet":
-        modelFt = models.resnet152(weights = models.ResNet152_Weights.DEFAULT if usePretrained else None)
-        utils.setParameterRequiresGrad(modelFt, featureExtract if usePretrained else False)
-        numFtrs = modelFt.fc.in_features
-        modelFt.fc = nn.Sequential(nn.Linear(numFtrs, numClasses), nn.LogSoftmax(dim = 1))
+        model = models.resnet152(weights = models.ResNet152_Weights.DEFAULT if usePretrained else None)
+        setParameterRequiresGrad(model, featureExtract if usePretrained else False)
+        numFtrs = model.fc.in_features
+        model.fc = nn.Sequential(nn.Linear(numFtrs, numClasses), nn.LogSoftmax(dim = 1))
         inputSize = 224
     else:
         print("Invalid model name.")
         exit()
     
-    return modelFt, inputSize
+    return model, inputSize

### 2024-08-12 ODADS/Code/AbnormityModels/trainClassify.py

@@ -3,17 +3,19 @@ import torch
 from torch import nn
 import torch.optim as optim
 from torchvision import transforms, datasets
+from torch.utils.data import Subset
 import time
 import copy
 import csv
 from datetime import datetime
+import numpy as np
 from Utils import utils
 from AbnormityModels import abnormityModel
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
 
 
-def trainModel(device, model, criterion, optimizer, scheduler, filename, dataDir, crossValid, batchSize, numEpochs, isInception = False):
+def trainModel(device, model, criterion, optimizer, scheduler, filename, dataDir, crossValid, batchSize, numEpochs, numClasses, isInception = False):
     startTime = time.time()
     bestAcc = 0
     model.to(device)
@@ -38,10 +40,17 @@ def trainModel(device, model, criterion, optimizer, scheduler, filename, dataDir
         print("-" * 10)
         
         if crossValid:
-            datasetSize = len(imageDataset)
-            trainSize = int(0.8 * datasetSize)
-            validSize = datasetSize - trainSize
-            trainDataset, validDataset = torch.utils.data.random_split(imageDataset, [trainSize, validSize])
+            labels = np.array(imageDataset.targets)
+            trainIndices = []
+            validIndices = []
+            for classId in range(numClasses):
+                classIndices = np.where(labels == classId)[0]
+                np.random.shuffle(classIndices)
+                splitPoint = int(0.8 * len(classIndices))
+                trainIndices.extend(classIndices[:splitPoint])
+                validIndices.extend(classIndices[splitPoint:])
+            trainDataset = Subset(imageDataset, trainIndices)
+            validDataset = Subset(imageDataset, validIndices)
             dataloaders = {
                 "train": torch.utils.data.DataLoader(trainDataset, batch_size = batchSize, shuffle=True),
                 "valid": torch.utils.data.DataLoader(validDataset, batch_size = batchSize, shuffle=True)
@@ -142,7 +151,7 @@ def train(device, featureExtract, modelName, numClasses, batchSize, numEpochs, L
     now = datetime.now()
     filename = now.strftime(modelType + " %Y-%m-%d %H-%M-%S")
 
[…]

### 2024-08-12 ODADS/Code/main.py

@@ -19,7 +19,7 @@ def main():
     
     task = 1 
     numClasses = len(criteria["All"]["OCT"])
-        
+    
     if task == 1: # train OCT or Fundus
         dbName = "ODADS/Data/Data/Transformed/OCT/"
         wtsName = ""

### 2024-08-12 ODADS/Code/AbnormityModels/trainClassify.py
update file paths; create directories before saving weights and csv

@@ -106,6 +106,7 @@ def trainModel(device, model, criterion, optimizer, scheduler, filename, dataDir
                     "best_acc": bestAcc,
                     "optimizer": optimizer.state_dict()
                 }
+                os.makedirs(f"ODADS/Data/Weights/{filename}/", exist_ok=True)
                 torch.save(state, f"ODADS/Data/Weights/{filename}/{filename}.pth")
                 print(f"Data successfully written into {filename}.pth")
                 
@@ -152,6 +153,8 @@ def train(device, featureExtract, modelName, numClasses, batchSize, numEpochs, L
     filename = now.strftime(modelType + " %Y-%m-%d %H-%M-%S")
 
     model, validAccHistory, trainAccHistory, validLosses, trainLosses, LRs, timeElapsed = trainModel(device, model, criterion, optimizer, scheduler, filename, dbName, crossValid, batchSize, numEpochs, numClasses)
+    
+    os.makedirs(f"ODADS/Data/Results/{filename}/", exist_ok=True)
     with open(f"ODADS/Data/Results/{filename}/{filename}.csv", "w", newline="") as file:  
         writer = csv.writer(file)  
         writer.writerow(["Trained from ResNet152" if wtsName == "" else f"Trained from {wtsName}", f"Data: {dbName}", f"batchSize = {batchSize}", f"LR = {LRs[0]}", f"epochNum = {len(trainLosses)}", f"timeElapsed = {timeElapsed // 60 :.0f}m {timeElapsed % 60: .2f}s"])

### 2024-08-12 ODADS/Code/DiagnosisModel/trainDiagnose.py

@@ -148,8 +148,9 @@ def trainModel(device, diseaseName, oModel, fModel, wtsName, dTime, dbName, batc
                 "best_acc": bestAcc,
                 "optimizer": optimizer.state_dict()
             }
-            torch.save(state, os.path.join(f".\\TrainedModel\\D {dTime}\\D {diseaseName} {dTime}.pth"))
-            print(f"Data successfully written into .\\TrainedModel\\D {dTime}\\D {diseaseName} {dTime}.pth")
+            os.makedirs(f"ODADS/Data/Weights/D {dTime}/", exist_ok=True)
+            torch.save(state, os.path.join(f"ODADS/Data/Weights/D {dTime}/D {diseaseName} {dTime}.pth"))
+            print(f"Data successfully written into ODADS/Data/Weights/D {dTime}/D {diseaseName} {dTime}.pth")
         
         scheduler.step()
         LRs.append(optimizer.param_groups[0]["lr"])
@@ -182,6 +183,7 @@ def train(device, diseaseName, featureExtract, modelName, oWts, fWts, batchSize,
     
     dModel, validAccHistory, trainAccHistory, trainLosses, validLosses, LRs, timeElapsed = trainModel(device, diseaseName, oModel, fModel, wtsName, dTime, dbName, batchSize, LR, numEpochs, gradeSize)
     
+    os.makedirs(f"ODADS/Data/Results/D {dTime}/", exist_ok=True)
     with open(f"ODADS/Data/Results/D {dTime}/{filename}.csv", "w", newline="") as file:  
         writer = csv.writer(file)  
         writer.writerow(["Trained from scratch" if wtsName == "" else f"Trained from {wtsName}", f"Data: {dbName}", f"batchSize = {batchSize}", f"LR = {LRs[0]}", f"epochNum = {len(trainLosses)}", f"gradeSize = {gradeSize}", f"timeElapsed = {timeElapsed // 60 :.0f}m {timeElapsed % 60: .2f}s"])

### 2024-08-12 ODADS/Code/main.py

@@ -24,7 +24,7 @@ def main():
         dbName = "ODADS/Data/Data/Transformed/OCT/"
         wtsName = ""
         batchSize = 16
-        numEpochs = 200
+        numEpochs = 100
         LR = 1e-3
         imgType = "O"
         trainClassify.train(device, featureExtract, modelName, numClasses, batchSize, numEpochs, LR, True, dbName, wtsName, imgType, crossValid = True)

### 2024-08-13 ODADS/Code/Utils/transform_imgs.py
Change to square first and resize to 224x224 last; update fundus source for normal and clear log

@@ -61,10 +61,11 @@ def delete_random_files(directory, num_files_to_delete):
 sideLength = 224
 
 transformAndResize = transforms.Compose([
-    transforms.Lambda(lambda x: resizeLongEdge(x, longEdgeSize = sideLength)),
+    transforms.Lambda(lambda x: resizeLongEdge(x, longEdgeSize = max(x.size[0], x.size[1]))),
     transforms.RandomHorizontalFlip(p=0.5),
     transforms.ColorJitter(brightness=0.1),
     transforms.RandomAffine(degrees = 10, translate = (0.05, 0.05), scale = (0.8, 1.2)),
+    transforms.Lambda(lambda x: resizeLongEdge(x, longEdgeSize = sideLength)),
     transforms.ToTensor(),
 ])
 onlyResize = transforms.Compose([

### 2024-08-14 ODADS/Code/AbnormityModels/classify.py
Use test dataset to check multiple generations of Fundus Model during 100-epoch train

@@ -14,10 +14,10 @@ def classify(img, model, device):
     # print(output)
     return output
 
-def classifyImg(img, numClasses, device, featureExtract, modelName, wtsName):
+def classifyImg(img, numClasses, device, featureExtract, modelName, foldername, wtsName):
     model, _ = abnormityModel.initializeAbnormityModel(modelName, numClasses, featureExtract)
     model = model.to(device)
-    trainedModel = torch.load(f"ODADS/Data/Weights/{wtsName}/{wtsName}.pth")
+    trainedModel = torch.load(f"ODADS/Data/Weights/{foldername}/{wtsName}")
     model.load_state_dict(trainedModel["state_dict"])
     # utils.imgShow(img)
     return classify(img, model, device)

### 2024-08-14 ODADS/Code/AbnormityModels/testClassify.py

@@ -1,15 +1,16 @@
 import os
 import torch
+import csv
 from torchvision import transforms, datasets
 from PIL import Image
 from Utils import utils
 from AbnormityModels import abnormityModel, classify
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
-def testAcc(device, featureExtract, modelName, numClasses, dbName, wtsName):
+def testAcc(device, featureExtract, modelName, numClasses, dbName, foldername, wtsName):
     model, _ = abnormityModel.initializeAbnormityModel(modelName, numClasses, featureExtract)
     model = model.to(device)
-    trainedModel = torch.load(f"ODADS/Data/Weights/{wtsName}/{wtsName}.pth")
+    trainedModel = torch.load(f"ODADS/Data/Weights/{foldername}/{wtsName}")
     model.load_state_dict(trainedModel["state_dict"])
     transform = transforms.Compose([
                     transforms.Lambda(lambda x: utils.resizeLongEdge(x)),
@@ -32,4 +33,15 @@ def testAcc(device, featureExtract, modelName, numClasses, dbName, wtsName):
     accuracy = corrects / total
     print(f"corrects: {corrects}/{total}")
     print(f"accuracy: {accuracy}")
-    return accuracy
+    return corrects, total, accuracy
+
+def testMultipleAcc(device, featureExtract, modelName, numClasses, dbName, foldername):
+    wtsFolder = f"ODADS/Data/Weights/{foldername}" 
+    with open(f"ODADS/Data/Results/{foldername}/{foldername} Test Acc.csv", "w", newline="") as file:  
+        writer = csv.writer(file)
+        writer.writerow(["Filename", "Corrects", "Total", "Accuracy"])
+        for filename in os.listdir(wtsFolder):
+            if os.path.splitext(filename)[1] == ".pth":
+                corrects, total, accuracy = testAcc(device, featureExtract, modelName, numClasses, dbName, foldername, filename)
+            writer.writerow([filename, corrects, total, accuracy])
+    print(f"Data successfully written into {filename}.csv")

### 2024-08-14 ODADS/Code/main.py

@@ -17,7 +17,7 @@ def main():
     print(device)
     criteria = utils.getCriteria()
     
-    task = 2
+    task = 7
     
     if task == 0: # train OCT or Fundus
         numClasses = len(criteria["All"]["Fundus"])
@@ -105,11 +105,11 @@ def main():
         fWts = "F 2024-08-07-16-48-56"
         diagnose.diagnose(oImgs, fImgs, diseaseName, device, modelName, dWtsTime, oWts, fWts)
     
-    elif task == 7: # test total accuracy for abnormity model
-        numClasses = len(criteria["All"]["OCT"])
-        dbName = "ODADS/Data/Data/Test/OCT/"
-        wtsName = "O 2024-08-13 08-59-11"
-        testClassify.testAcc(device, featureExtract, modelName, numClasses, dbName, wtsName)
+    elif task == 7: # test accuracy for a series of abnormity models
+        numClasses = len(criteria["All"]["Fundus"])
+        dbName = "ODADS/Data/Data/Test/Fundus/"
+        wtsName = "F 2024-08-14 14-21-54 Transferred"
+        testClassify.testMultipleAcc(device, featureExtract, modelName, numClasses, dbName, wtsName)
 
     elif task == 8: # classify single image with OCT or Fundus
         numClasses = len(criteria["All"]["OCT"])

### 2024-08-14 Paper/Paper.tex
Include "github repo link" in paper framework

--- 2024-08-12 Paper/Paper.tex
@@
 
-	\section{Purpose}
+	\section{Model Overview}
 
-		We will develop an Ocular Disease Auxiliary Diagnosis System (ODADS).
+		The Optical Disease Auxiliary Diagnosis System (ODADS)
+		Model purpose: recognize abnormities, then diagnose disease; 
+		interpretable findings
 
-		\vspace{0.3cm}
+		Fig: OCT abnormities
+		Fig: Fundus abnormities
 
-		\textbf{First, the ODADS aims to simulate the comprehensive diagnosis process by considering information from both fundus and OCT images.} While both types of images can respectively indicate different diseases, they can also strengthen certain disease discrimination.
-Considering both sources can result in a more comprehensive disease diagnosis.
+		\begin{itemize}
+			\item Branch retinal vein occlusion (BRVO) or hemicentral retinal vein occlusion (HCRVO)
 
-		\vspace{0.1cm}
+			\item Central retinal vein occlusion (CRVO)
 
-		\textbf{Second, the ODADS aims to present more interpretable findings.}  Most studies provide end-to-end systems for classifying diseases as black boxes, which may not be convincing enough when their results are different from ophthalmologists'.
-The ODADS will provide 2 types of results, namely abnormalities and disease.
-We will highlight all the abnormalities and use them to deduce diseases, so that the ODADS could provide as much information as possible.
-Even when the ODADS does not automate diagnosis correctly, the results can still be references for users.
+			\item Central serous chorioretinopathy (CSC)
 
-		\vspace{0.1cm}
+			\item Dry age-related macular dystrophy (dry AMD)
 
-		\textbf{Third, the ODADS aims to provide the probabilities of ocular diseases.}  Most studies only do the classification, which is not enough in some scenarios.
-The symptoms could be complex, where multiple disease could be in the same case.
-Providing diseases probabilities than simple discrimination can enable users to be aware of actual ocular conditions and potentially improve treatment.
+			\item Epiretinal membrane (ERM)
 
-		\vspace{0.1cm}
+			\item Macular hole (MH)
 
-		\textbf{Fourth, The ODADS aims to be accessible to all people.}  While most studies design models dedicated to ophthalmologists, the ODADS will contain a website and a mobile application (APP) to serve people including ophthalmologists, patients and their families, and all others.
+			\item Macular telangiectasia (Mactel)
 
-		\vspace{0.1cm}
+			\item Mild diabetic retinopathy (mild DR)
 
-		\textbf{Last, The ODADS aims to be more flexible by allowing user to input multiple images.}  Most studies only consider limited images.
-In other words, mono-modal systems only work on one fundus image or one OCT image and bi-modal systems only work on 2 images.
-The ODADS will enable user to input more than 2 images, especially for OCT images, which could result in more accurate diagnosis.
+			\item Referable diabetic retinopathy (referable DR)
 
-	\section{Models}
+			\item Retinitis pigmentosa (RP)
 
-		The ODADS will consist of two parts.
+			\item Stargardt disease (Stargardt)
 
-		The first part is a back-end model, which has fundus and OCT images as input and features and probabilities as output.
-The second part is a front-end user interface (UI), including a website and an APP, which implements the back-end model and provides users with diagnosis information.
+			\item Wet age-related macular dystrophy (wet AMD)
+		\end{itemize}
 
-		The back-end model will be built based on multiple sub-models including several OCT-Models, several Fundus-Models and one Diagnosis-Model.
-Each OCT-Model and Fundus-Model will contain a classifier which will be trained separately by a backboned ResNet50.
-Diagnosis-Model will consist of a neural network for determining the deduction from abnormalities to diseases.
-We will study the optimal OCT-Model and Fundus-Model number and compare different fusion timing to determine the best architecture.
-The back-end model will output 2 sets of results to the front-end UI, one containing the probabilities of potential ocular diseases and the other containing abnormalities and their locations in each image.
+		No real data. use the following criteria
 
-		The front-end UI will enable users to upload OCT and fundus images, which can be got by taking photos in the APP or selecting image files from disk on the website.
-The UI will generate a report, including the ocular abnormalities, their locations, and the probabilities of different ocular diseases, etc.
-Ophthalmologists can use the APP or website to assist their diagnosis.
-And if patients and their families can get their OCT and fundus images from the hospital, they can also use the UI to view the report, which can be a supplementary reference to clinical diagnosis.
-The front-end UI will also provide some functionalities like viewing the locations of abnormalities interactively and revising the automated diagnosis results of diseases and abnormalities and upload the revision to server for improving the back-end model in the future.
+		Fig: From Abnormity to Disease
 
-	\pagebreak
-	\section{Abnormalities and Diseases} \label{sec:ab_di}
+		Model consists of 3 parts: OCT-Model, Fundus-Model, and Diagnosis-Model.
+OCT-Model and Fundus-Model are collectively called the Abnormity-Models.
+They use the same architecture (ResNet152, flatten to 2048 features, and fc).
+Diagnosis Model consists of #num submodels, one of which is for normal, and the other ones for each disease.
+each submodel first fuses output from both Abnormity-Models, then uses an fc to get final results for normal or for the disease.
 
-	\subsection{OCT Abnormalities}
+		Fig: 3 parts
 
-		Fig.\ref{fig:oct-abnormalities} shows the OCT abnormalities in the ODADS.
-		Table \ref{tb:oct-abnormalites} lists the description of abnormalities.
+		fusion: max of OCT, max of fundus, concatenate
+
+		Fig: fusion
+
+		how to find grade (number of traits = grade for the disease as label during training), output - calculate expected grade.
+in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1].
+)
+
+	\section{Abnormity Models}
+
+		\subsection{Data Preparation}
+
+			Table: Data source for OCT
+				numbered list of sources
+				columns for source number, final column = total number of imgs
+				rows for abnormities
+
+			CycleGAN
+				Fig: Intro
+				Table: selection rates
+				selection criteria
+
+			transforms for OCT
+				for train: copy, flip, randomcomb1
+				for test: copy, flip, randomcomb2 -> explain truthfulness
+
+			Table: Data source for Fundus - same as OCT
+
+			Why I did not GAN Fundus
+
+			transforms for Fundus
+				similar to OCT
+				explain differences
+
+		\subsection{Training}
+
+			intro to five-fold train/valid (reason for using this?)
+
+			starting point of fine-tuning???????????????????????????????
+			prevent overfitting
+
+			crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
+
+			conda, PyTorch;
+			desktop computer with Intel® Xeon® Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM
+
+		\subsection{Results}
+
+			For both OCT and Fundus:
+
+				Fig: accuracy and loss over epochs
+					trainAcc, validAcc, trainLosses, validLosses
+					testAcc for best weights - align below acc graph
+
+				Table: for each abnormity:
+					accuracy (only present accuracy for TOTAL)
+					precision
+					recall/sensitivity
+					specificity
+					F1
+					AUC
+
+				Table: Confusion matrix
+					analyze which abnormities are commonly confused, and the effect on the numerical results
+				Fig: t-SNE
+					which abnormities are "close"
+
+				Fig: ROC for each abnormity
+
+			"co-dominance"??????????????????????????????
+
+			Fig: GradCAM intro
+			Fig: GradCAM example
+
+	\section{Diagnosis Model}
+
+		\subsection{Data Preparation}
+
+			how to choose data (with an example)
+
+		\subsection{Training}
+
+			parameters used
+
+		\subsection{Results}
+
+			Do two models increase accuracy?
+				how do I compare?????????????????????????????????
+				any math here?
+
+			Fig: accuracy and loss over epochs
+				trainAcc, validAcc, trainLosses, validLosses
+			Table: for each disease:
+				accuracy (only present accuracy for TOTAL)
+				precision
+				recall/sensitivity
+				specificity
+				F1
+				AUC
+			Fig: ROC for each disease
+
+			"co-dominance"???????????????????????????????????
+
+	\section{Conclusion}
+
+		Comparison
+
+		Strengths and weaknesses
+
+	\section{Appendix}
+
+		Google Image source links
+		Add prevalence (1 out of how many people) for abnormities?
 
@@
 				\begin{longtable}{lp{3.8in}}
-				\caption{OCT Abnormalities}
-				\label{tb:oct-abnormalites}\\
+					\caption{OCT Abnormities}
+					\label{tb:oct-abnormites}\\
 					\toprule
@@
 
-				\multicolumn{1}{l}{Retinal detachment}
-				& The separation between the neurosensory retina and the underlying retinal pigment epithelium (RPE) or choroid.\\
-
 					\multicolumn{1}{l}{Stargardt disease}
@@
 
-				\multicolumn{1}{l}{Macular neovascularization}
-				& The abnormal growth of new blood vessels in the macular region of the retina.\\
+					\multicolumn{1}{l}{Choroidal neovascularization}
+					& The abnormal growth of new blood vessels in the choroid layer.\\
 
@@
 
-	\subsection{Fundus Abnormalities}
-
-	Fig.\ref{fig:fundus-abnormalities} shows the fundus abnormalities in the ODADS.
-	Table \ref{tb:fundus-ab} lists the description of abnormalities.
-
 		{
@@
 
-				\multicolumn{1}{l}{Epiretinal membrane (ERM)}
-				& Retinal Wrinkling.  Foveal Reflex Changes. Retinal Vessel Distortion\\
+					\multicolumn{1}{l}{Retinitis pigmentosa (RP)}
+					& Description of RP\\
+
+					\multicolumn{1}{l}{Microaneurysm}
+					& Description of microaneurysm\\
 
 					\multicolumn{1}{l}{Macular hole (MH)} & Full-thickness macular hole showing a surrounding cuff of subretinal fluid.\\
-
-				\multicolumn{1}{l}{Retinal nerve fiber layer defect} & A dark stripe or wedge-shaped localized defect in the peripapillary area, parallel to the normal retinal striation, or as a diffuse loss of this striation.
-\\
-
-				\multicolumn{1}{l}{Glaucomatous disc change} & Cupping.  Cup-to-Disc Asymmetry. Thinning of Neuroretinal Rim. Optic Nerve Head Hemorrhages \\
 
@@
 
-				\multicolumn{1}{l}{Fluid accumulation} &  a localized or diffuse elevation of the retina, often with a smooth or dome-shaped contour\\
-
 					\multicolumn{1}{l}{Vascular abnormality} & Retinal Vessel Tortuosity.  Retinal Vessel Caliber Changes.  \\
-
-				\multicolumn{1}{l}{Choroidal lesion} & Flat, well-defined areas of pigmentation ranging from light brown to dark brown. \\
 
@@
 
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.9\linewidth]{OCT-abnormalities.pdf}
-		\caption{OCT Abnormalities}
-		\vspace{0.3cm}
-		\label{fig:oct-abnormalities}
-	\end{figure}
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.9\linewidth]{fundus-ab.pdf}
-		\caption{Fundus Abnormalities}
-		\vspace{0.3cm}
-		\label{fig:fundus-abnormalities}
-	\end{figure}
-
-	\subsection{Diseases}
-		Table \ref{tb:diseases} lists the diseases in ODADS.
-
-		{
-		\fontsize{9}{12}\selectfont
-		{
-			\begin{longtable}{lp{3.8in}}
-				\caption{Diseases}
-				\label{tb:diseases}\\
-				\toprule
-				Abnormality&Description\\
-				\toprule
-
-				\multicolumn{1}{l}{Central Serous Chorioretinopathy} & The accumulation of fluid under the retina, specifically in the macular region, leading to vision disturbances.\\
-
-				\multicolumn{1}{l}{Epiretinal Membrane} & Also known as macular pucker or cellophane maculopathy, a condition characterized by the formation of a thin, semitransparent membrane on the surface of the retina, particularly in the macular region.
-Here's an overview of epiretinal membrane.
-\\
-
-				\multicolumn{1}{l}{Macular Hole} & A defect or opening in the center of the macula, the central part of the retina responsible for sharp central vision. \\
-
-				\multicolumn{1}{l}{Glaucoma Suspect} & Exhibit one or more risk factors or suspicious findings that suggest they may be at increased risk of developing glaucoma in the future. \\
-
-				\multicolumn{1}{l}{Retinal Detachment} & The retina, the light-sensitive tissue lining the back of the eye, becomes separated from its underlying layers of support\\
-
-				\multicolumn{1}{l}{Stargardt Disease} & Also known as Stargardt macular dystrophy or fundus flavimaculatus, is a genetic eye disorder characterized by progressive degeneration of the macula, the central part of the retina responsible for sharp central vision.\\
-
-				\multicolumn{1}{l}{Mild DR} & Mild diabetic retinopathy (DR) refers to the early stages of retinal damage caused by diabetes. \\
-
-				\multicolumn{1}{l}{Referable DR} & Referable diabetic retinopathy (DR) refers to the presence of diabetic retinopathy that requires referral to an ophthalmologist or retina specialist for further evaluation and management.
-This designation typically applies to cases of moderate to severe diabetic retinopathy or the presence of sight-threatening complications such as diabetic macular edema (DME).
-\\
-
-				\multicolumn{1}{l}{Dry AMD} & Dry age-related macular degeneration (AMD) is characterized by the gradual deterioration of the macula due to the accumulation of drusen (yellowish deposits) and the loss of retinal pigment epithelial (RPE) cells, photoreceptors, and other retinal cells.
-It is the most common form of AMD, accounting for approximately 85-90\% of all cases.\\
-
-				\multicolumn{1}{l}{Wet AMD} & Wet AMD is a more severe form of AMD compared to dry AMD.
-It is characterized by the growth of abnormal blood vessels (choroidal neovascularization) beneath the macula.
-These blood vessels are fragile and leak fluid and blood, causing damage to the macula and leading to rapid vision loss if left untreated.\\
-
-				\multicolumn{1}{l}{BRVO / HCRVO} & Branch retinal vein occlusion (BRVO) and hemiretinal vein occlusion (HCRVO) are two types of retinal vein occlusion, which occur when one or more of the veins that carry blood away from the retina become blocked or occluded.\\
-
-				\multicolumn{1}{l}{CRVO} & Central retinal vein occlusion (CRVO) is a serious eye condition that occurs when the main vein that drains blood from the retina becomes blocked or occluded.
-This blockage leads to a buildup of pressure in the retinal veins, causing hemorrhages, edema (fluid buildup), and ischemia (lack of blood flow) in the retina.
-\\
-
-				\multicolumn{1}{l}{Retinitis Pigmentosa (RP)} & Retinitis pigmentosa (RP) is a group of inherited retinal disorders characterized by progressive degeneration of the retina, leading to vision loss and, in severe cases, blindness.
-RP typically affects the rod and cone photoreceptor cells in the retina, which are essential for vision in low light (rods) and daylight and color vision (cones).
-\\
-
-				\multicolumn{1}{l}{Macular Telangiectasia (Mactel)} & 
-				Macular telangiectasia, also known as idiopathic juxtafoveal retinal telangiectasis (IJRT) or idiopathic macular telangiectasia (IMT), is a rare, progressive eye condition characterized by abnormal dilation and leakage of blood vessels in the macula, the central part of the retina responsible for sharp central vision.
-Macular telangiectasia primarily affects the retinal capillaries in the juxtafoveal region, leading to vision loss and, in severe cases, legal blindness.\\
-
-				\bottomrule
-			\end{longtable}
-		}
-	}
-
-	\section{Back-end Model}
-
-		The back-end model is shown in Fig.\ref{fig:back-end}.
-
-		The model contains $n$ OCT-Models, $m$ Fundus-Models and one Diagnosis Model.
-The OCT-Models and Fundus-Models are fed by OCT images and fundus images respectively, and output image features and abnormality probabilities to the Diagnosis-Model where the data is fused and calculated.
-Ultimately the diagnosis result is generated and outputted to Front-end UI.
-
-		\vspace{0.5cm}
-
-		\begin{figure}[htbp]
-			\centering
-			\includegraphics[width=\linewidth]{Back-end.pdf}
-			\caption{Back-end Model}
-			\label{fig:back-end}
-		\end{figure}
-
-	\subsection{Classifier}
-		Each OCT-Model and Fundus-Model uses several types of abnormalities with the normal for training, which makes the model a classifier in the ODADS, as shown in Fig.\ref{fig:back-end}.
-
-		We have the following formulas.
-
-		\[
-		N = \sum_{i=1}^{n} K_i \qquad M = \sum_{i=1}^{m} L_i
-		\]
-
-		Where:
-
-		$n$: the OCT-Model number.
-
-		$m$: the Fundus-Model number.
-
-		$K_i$: the classifying abnormality number in $i^{th}$ OCT-Model.
-
-		$L_i$: the classifying abnormality number in $i^{th}$ fundus-Model.
-
-		$N$: the total abnormality number in OCT images.
-
-		$M$: the total abnormality number in fundus images.
-
-		\vspace{0.3cm}		
-		We use the Greedy Algorithm to determining $K_i$, $L_i$, $n$, and $m$.
-
-		Fig.\ref{fig:classifier} is an example to illustrate how OCT-Model 1 is generated.
-First we choose the first abnormality and the normal to assemble a bi-classifier and calculate its performance (We will use F1-score as the performance indicator, refer to Section \ref{sec:results} for more information).
-Then we introduce the second abnormality to form a new tri-classifier including 2 abnormalities and the normal.
-If the performance of tri-classifier is better than the bi-classifier, we adopt the tri-classifier, otherwise we still use bi-classifier.
-All the abnormalities are introduced in turn, either adopted or abandoned by the OCT-Model 1, and finally we get the classifier for OCT-Model1 including $K_i$ abnormalities and the normal.
-Then we generate other classifiers in the same way as the first one until all the abnormalities belong to specific classifiers.
-
-		\vspace{0.5cm}
-
-		\begin{figure}[htbp]
-			\centering
-			\includegraphics[width=\linewidth]{Classifier.pdf}
-			\caption{Classifiers Generation Algorithm}
-			\label{fig:classifier}
-		\end{figure}
-
-		\vspace{0.5cm}
-
-		We will set up a threshold for performance comparison.
-Even when one classifier with more abnormalities has lower performance than another classifier with less abnormalities but the gap is within the threshold, we still choose the classifier with more abnormalities because we need to minimum classifier number to insure smaller CNN parameter quantities, faster running and easier deployment.
-
-	\subsection{OCT-Model and Fundus-Model}
-		The OCT-Model and fundus-Model use ResNet50 as backbones.
-We apply transferred learning to train the ResNet50, which includes 2 phases, namely taking the models with the parameters learned with ImageNet and then performing a fine-tuning process.
-
-		Fig.\ref{fig:resnet50} shows the architecture of OCT-Model and Fundus-Model.
-We apply a modified ResNet50 and then flatten the data.
-With a full-connected (FC) hidden layer, we get feature vector.
-Then with another FC layer, we get abnormalities probabilities.
-In Diagnosis-Model, we will determine to use whether feature vector or abnormalities probabilities for data fusion.
-
-		\vspace{0.5cm}
-
-		\begin{figure}[htbp]
-			\centering
-			\includegraphics[width=0.6\linewidth]{ResNet50.pdf}
-			\caption{OCT-Model and Fundus-Model Architecture}
-			\label{fig:resnet50}
-		\end{figure}
-
-	\subsection{Diagnosis-Model}
-
-		The Diagnosis-Model is a neural network which fuses data from OCT-Models and Fundus-Models and then leverages a FC hidden layer to translate abnormalities to diseases.
-		Fig.\ref{fig:diagnosis-model} shows 2 solutions for data fusion.
-One is to fuse the feature vectors from OCT-Models and fundus-models, and the other is to fuse the probability vectors from those sub-models.
-We compare the performance between 2 solutions and choose the better one as our ultimate architecture.
-		When we fuse the feature vectors, we concatenate them as a big vector.
-And when we fuse the probability vectors, we pick the maximum probability for each abnormality and then normalize the vector to form a new abnormality probability vector.
-
-		\vspace{0.5cm}
-
-		\begin{figure}[htbp]
-			\centering
-			\includegraphics[width=\linewidth]{Diagnosis-Model.pdf}
-			\vspace{0.1cm}
-			\caption{Diagnosis Model}
-			\label{fig:diagnosis-model}
-		\end{figure}
-
-		For training Diagnosis-Model, we need to set up ground truth in terms of converting abnormalities to diseases.
-We refer to 3 books for determining the conversion criteria, namely \textit{\citefield{Wolf_Kirchhof_Reim_2006}{title}}\autocite{Wolf_Kirchhof_Reim_2006}, \textit{\citefield{Duker_Waheed_Goldman_2022}{title}}\autocite{Duker_Waheed_Goldman_2022} and \textit{\citefield{Kawasaki_2013}{title}}\autocite{Kawasaki_2013}.
-
-		The conversion criteria is shown in Fig.\ref{fig:abnormality-disease}, where the gray boxes represent OCT abnormalities, orange boxes represent fundus abnormalities, and blue boxes represent diseases.
-Refer to Section \ref{sec:ab_di} for more information regarding abnormalities and diseases.
-
-		\vspace{0.3cm}
-
-		\begin{figure}[htbp]
-			\centering
-			\includegraphics[width=0.95\linewidth]{Abnormality-Disease.pdf}
-			\vspace{0.3cm}
-			\caption{From Abnormality to Disease}
-			\label{fig:abnormality-disease}
-		\end{figure}
-
-	\subsection{Training}
-
-		We will train all the OCT-Models and Fundus-Models first and determine all the classifiers.
-Then we will freeze those models and train the Diagnoal-Model.
-The training images will be labeled, prepossessing, augmented when necessary.
-The augmentation includes image rotation, translation, scaling, flipping, brightness adjustment, constrat adjust, and noise addition etc.
-If training images are too fewer, we will use CycleGAN to generate some synthetic images for training, but we will try to avoid doing this by looking for more public datasets.
-
-		The trainings are implemented on a desktop computer with Intel® Xeon® Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM.
-
-		\vspace{0.3cm}
-
-		The training images for OCT-Models will come from the following 2 public datasets.
-		\begin{enumerate}
-			\vspace{-0.2cm}
-			\item \textit{Large Dataset of Labeled Optical Coherence Tomography (OCT) and Chest X-Ray Images}\autocite{Kermany_database}.
-			\vspace{-0.2cm}
-			\item \textit{Data for: Improved accuracy in OCT diagnosis of rare ocular disease using few-shot learning with generative adversarial networks} \autocite{Yoo_2020}.
-		\end{enumerate}
-
-		\vspace{0.3cm}
-
-		The training images for Fundus-Models will come from another 5 public datasets.
-		\begin{enumerate}
-			\vspace{-0.2cm}
-			\item \textit{E-ophtha} \autocite{E_ophtha}.
-			\vspace{-0.2cm}
-			\item \textit{Diabetic Retinopathy Detection} \autocite{DR_dataset}.
-			\vspace{-0.2cm}
-			\item \textit{Indian Diabetic Retinopathy Image Dataset. (IDRiD)} \autocite{Porwal_2018}.
-			\vspace{-0.2cm}
-			\item \textit{Messidor} \autocite{Messidor}.
-			\vspace{-0.2cm}
-			\item \textit{STructured Analysis of the Retina} \autocite{STARE}.
-		\end{enumerate}
-
-		\vspace{0.3cm}
-
-		We have not found online open dataset for training Diagnosis-Model.
-We will need OCT images and fundus images from the same patients.
-Online datasets only contain OCT images or fundus images, which do not meet our requirement.
-
-		There are 2 plans as follow.
-\textcolor{magenta}{We would hope to implement plan A.
-Using the real data from hospital could make the ODADS more reliable and robust}.
-If plan A is not possible, we will do plan B.
-		\vspace{0.1cm}
-		\begin{enumerate}
-			\vspace{-0.2cm}
-			\item \textcolor{magenta}{We will use the data from hospital.
-The dataset will contain OCT images and fundus images from patients.
-For privacy, we do not need any patient identity information, and each piece of data in the dataset could be organized as "Data Number", "OCT images", "Fundus Images" and "Brief Diagnosis".
-This may need to be approved by authorities.}
-			\vspace{-0.2cm} 
-			\item We will make up the training data on our own.  The image data will come from above public database and the diagnosis will be made by ourselves.
-		\end{enumerate}
-
-	\subsection{Results} \label{sec:results}
-
-		We will provide the following performance indicators for each model.
-		\vspace{0.1cm}
-		\begin{itemize}
-			\vspace{-0.2cm}
-			\item Confusion Matrix, as shown in Fig.\ref{fig:cm}.
-			\begin{figure}[htbp]
-				\centering
-				\includegraphics[width=0.5\linewidth]{ConfusionMatrix.pdf}
-				\vspace{0.1cm}
-				\caption{Confusion Matrix}
-				\label{fig:cm}
-			\end{figure}
-
-			\vspace{-0.2cm} 
-			\item Accuracy = $\displaystyle \frac{TP+TN}{TP+TN+FP+FN}$.
-
-			\vspace{0.1cm} 
-			\item Precision = $\displaystyle \frac{TP}{TP+FP}$.
-
-			\vspace{0.1cm} 
-			\item Recall (Sensitivity) = $\displaystyle \frac{TP}{TP+FN}$.
-
-			\vspace{0.1cm} 
-			\item Specificity = $\displaystyle \frac{TN}{TN+FP}$.
-
-			\vspace{0.1cm} 
-			\item F1-score = $\displaystyle \frac{2\times Precision\times Recall}{Precision+Recall}$.
-
-			\vspace{0.1cm} 
-			\item Receiver Operating Characteristic Curve (ROC).
-			\vspace{-0.1cm} 
-			\item Area Under the ROC (AUC).
-			\vspace{-0.1cm} 
-			\item t-distributed Stochastic Neighbor Embedding (t-SNE).
-
-		\end{itemize}
-
-	\section{Front-end UI}
-
-		The front-end UI includes one website application and one APP.  They have the following UI elements and functionalities.
-
-		\begin{itemize}
-		\vspace{-0.2cm}
-		\item Taking photo button (APP only) enables users to take photos as diagnosis images.
-		\vspace{-0.2cm} 
-		\item Selecting photo button enables user to select photos from disk or mobile phone's gallery.
-		\vspace{-0.2cm} 
-		\item A list of abnormalities lists all the potential abnormalities by their probabilities.
-		\vspace{-0.2cm} 
-		\item A probabilities pie graph for diseases.
-		\vspace{-0.2cm} 
-		\item A diagnosis report.
-		\vspace{-0.2cm} 
-		\item When user select abnormalities, the abnormalities are highlighted on the image.
-		\vspace{-0.2cm} 
-		\item Reset button enables user to clear current information and begin a new diagnosis.
-		\vspace{-0.2cm} 
-		\item Uploading button enables user to upload the images to server to help make the ODADS better.
-	\end{itemize}
-
-	\vspace{0.2cm}
-
-	In the front-end UI, users can select up to 10 images for diagnosis.
-Each image will go through the back-end model and generate probability vectors.
-For evaluating the ultimate probability vector, we will choose the maximum probability for each abnormality and disease, and normalize the vector with maximum values as ultimate result.
-
-	The Front-end UI will leverage Gradient-weighted Class Activation Mapping (Grad-CAM) to visualize the abnormality location.
-Grad-CAM is implemented before the last fully connected layer in each OCT-Model and Fundus-Model and passes its result from the back-end model to the front-end UI.
-
-	We also encourage users to upload their images so that the server can train the back-end model periodically to make the ODADS better.
-
-	\section{Innovation}
-
-		\begin{itemize}
-			\item The ODADS uses bi-modal architecture and integrates 2 types of ocular images, namely fundus images and OCT images, making the diagnosis more comprehensive.
-
-			\vspace{-0.2cm} 
-			\item The ODADS outputs the probabilities of ocular diseases instead of simply naming a single disease. Therefore, the ODADS can reflect the ocular condition more accurately.
-
-			\vspace{-0.2cm} 
-			\item The ODADS lists all the abnormalities to break the black box. The diagnosis result could be more flexible, complete, and interpretable.
-
-			\vspace{-0.2cm} 
-			\item The ODADS has a front-end UI that implements the back-end model and makes a complete diagnosis system. Also, the ODADS allows users to upload images to better the system.
-
-			\vspace{-0.2cm} 
-			\item The ODADS investigates the optimal classifier generation and 2 types of fusion timing, which helps the ODADS achieve better performance.
-
-		\end{itemize}
-
-	\section{Plan}
-
-		\begin{figure}[htbp]
-			\centering
-			\includegraphics[width=\linewidth]{Plan.pdf}
-			\caption{Research Plan}
-			\label{fig:plan}
-		\end{figure}
-
-		The research process consists of 4 phases, as shown in Fig. \ref{fig:plan}.
-
-		The first phase is from March to June.
-I will read relevant literature, including deep learning technology and state-of-the-art image detection researches.
-And I will also study ophthalmology to familiarize myself with ocular diagnosis and learn to read OCT and fundus images to identify abnormalities and diseases.
-In the meanwhile, I will collect OCT and fundus images from websites and do the prepossessing work, so that they can be used in training models.
-I will also develop the OCT-models, the Fundus-Models, the Diagnosis-model, and the APP and website in sequence.
-\textcolor{magenta}{It is preferable if we can get real data from hospital prior to developing the Diagnosis-Model}.
-
-		The second phase includes July and August. I will complete the first draft of the paper. And I will keep on developing the system.
-
-		The third phase includes September and October. I will keep on improving development and paper.
-
-		The last phase is November. I will finalize the paper and be prepared for the thesis defense.
+		APP/website description
+		GitHub repo
 

### 2024-08-14 ODADS/Code/AbnormityModels/classify.py
Test Fundus data

@@ -10,7 +10,7 @@ def classify(img, model, device):
     img = transforms.ToTensor()(img)
     img = img.unsqueeze(0)
     output = model(img.to(device))
-    output = torch.exp(output[0])
+    output = torch.nn.functional.softmax(output[0], dim=0)
     # print(output)
     return output
 
@@ -19,5 +19,6 @@ def classifyImg(img, numClasses, device, featureExtract, modelName, foldername, 
     model = model.to(device)
     trainedModel = torch.load(f"ODADS/Data/Weights/{foldername}/{wtsName}")
     model.load_state_dict(trainedModel["state_dict"])
+    model.eval()
     # utils.imgShow(img)
     return classify(img, model, device)

### 2024-08-14 ODADS/Code/AbnormityModels/testClassify.py

@@ -30,6 +30,7 @@ def testAcc(device, featureExtract, modelName, numClasses, dbName, foldername, w
             _, pred = torch.max(output, dim=0)
             corrects += pred == classToIdx[className]
             total += 1
+        print(f"completed {className}")
     accuracy = corrects / total
     print(f"corrects: {corrects}/{total}")
     print(f"accuracy: {accuracy}")

### 2024-08-14 ODADS/Code/main.py

@@ -17,7 +17,7 @@ def main():
     print(device)
     criteria = utils.getCriteria()
     
-    task = 7
+    task = 8
     
     if task == 0: # train OCT or Fundus
         numClasses = len(criteria["All"]["Fundus"])
@@ -108,15 +108,16 @@ def main():
     elif task == 7: # test accuracy for a series of abnormity models
         numClasses = len(criteria["All"]["Fundus"])
         dbName = "ODADS/Data/Data/Test/Fundus/"
-        wtsName = "F 2024-08-14 14-21-54 Transferred"
-        testClassify.testMultipleAcc(device, featureExtract, modelName, numClasses, dbName, wtsName)
+        foldername = "F 2024-08-14 14-21-54 Transferred"
+        testClassify.testMultipleAcc(device, featureExtract, modelName, numClasses, dbName, foldername)
 
     elif task == 8: # classify single image with OCT or Fundus
-        numClasses = len(criteria["All"]["OCT"])
-        string = "ODADS/Data/Data/Original/OCT"
-        wts = ""
-        img = Image.open(string)
-        classify.classifyImg(img, numClasses, device, featureExtract, modelName, wts)
+        numClasses = len(criteria["All"]["Fundus"])
+        dbName = "ODADS/Data/Data/Small_test/Fundus/"
+        foldername = "F 2024-08-14 14-21-54 Transferred"
+        wtsName = "F 2024-08-14 14-21-54 Transferred Best Epoch in 81 to 90.pth"
+        testClassify.testAcc(device, featureExtract, modelName, numClasses, dbName, foldername, wtsName)
     
 if __name__ == "__main__":
     main()
+    

### 2024-08-14 Paper/Paper.tex

@@
 
+	\section*{Abstract}
+
+	\pagebreak
 	\vspace{0.5cm}
 	\tableofcontents
-
 	\pagebreak
@@
 
-	\section{Model Overview}
+	\section{Overview}
 
@@
 
-		\begin{itemize}
-			\item Branch retinal vein occlusion (BRVO) or hemicentral retinal vein occlusion (HCRVO)
-
-			\item Central retinal vein occlusion (CRVO)
-
-			\item Central serous chorioretinopathy (CSC)
-
-			\item Dry age-related macular dystrophy (dry AMD)
-
-			\item Epiretinal membrane (ERM)
-
-			\item Macular hole (MH)
-
-			\item Macular telangiectasia (Mactel)
-
-			\item Mild diabetic retinopathy (mild DR)
-
-			\item Referable diabetic retinopathy (referable DR)
-
-			\item Retinitis pigmentosa (RP)
-
-			\item Stargardt disease (Stargardt)
-
-			\item Wet age-related macular dystrophy (wet AMD)
-		\end{itemize}
-
-		No real data. use the following criteria
+		No real data. use the following criteria. source for criteria
 
 		Fig: From Abnormity to Disease
+
+		Fig: 3 parts
 
@@
 They use the same architecture (ResNet152, flatten to 2048 features, and fc).
-Diagnosis Model consists of #num submodels, one of which is for normal, and the other ones for each disease.
+Diagnosis Model consists of num submodels, one of which is for normal, and the other ones for each disease.
 each submodel first fuses output from both Abnormity-Models, then uses an fc to get final results for normal or for the disease.
-
-		Fig: 3 parts
 
@@
 
-		how to find grade (number of traits = grade for the disease as label during training), output - calculate expected grade.
-in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1].
-)
+		output
 
@@
 
-			Table: Data source for OCT
+			Fig: overall flowchart
+
+			Table: Data source for OCT and Fundus
 				numbered list of sources
@@
 				selection criteria
+				Why I did not GAN Fundus
 
@@
 				for test: copy, flip, randomcomb2 -> explain truthfulness
+				explain differences between train and test, OCT and fundus
 
-			Table: Data source for Fundus - same as OCT
-
-			Why I did not GAN Fundus
-
-			transforms for Fundus
-				similar to OCT
-				explain differences
+			Table: all data source
 
@@
 			crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
+			running time
+
+			Fig: accuracy and loss over epochs
+				trainAcc, validAcc, trainLosses, validLosses
+				testAcc for best weights - align below acc graph
 
@@
 
+			time per image
+
 			For both OCT and Fundus:
-
-				Fig: accuracy and loss over epochs
-					trainAcc, validAcc, trainLosses, validLosses
-					testAcc for best weights - align below acc graph
 
@@
 
+				comparison to other studies
+
 			"co-dominance"??????????????????????????????
@@
 			how to choose data (with an example)
+			how to find grade (number of traits = grade for the disease as label during training)
 
@@
 			parameters used
+			running time
+			Fig: accuracy and loss over epochs
+				trainAcc, validAcc, trainLosses, validLosses
 
@@
 
-			Do two models increase accuracy?
-				how do I compare?????????????????????????????????
-				any math here?
+			output - calculate expected grade. in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1].
 
-			Fig: accuracy and loss over epochs
-				trainAcc, validAcc, trainLosses, validLosses
 			Table: for each disease:
@@
 				AUC
+			Fig: confusion matrix (is it suitable?)
 			Fig: ROC for each disease
@@
 
-	\section{Conclusion}
+	\section{Discussion}
+
+		Do two models increase accuracy?
+			how do I compare?????????????????????????????????
+			any math here?
 
@@
 		Strengths and weaknesses
+		how to improve
+
+	\section{Conclusion}
 

### 2024-08-27 Paper/Paper.tex
Draw GradCAM highlighted figures; plot OCT acc and loss

@@
 	\maketitle
+	\vspace{0.5cm}
 
@@
 
+	TEXT: abstract
+
 	\pagebreak
-	\vspace{0.5cm}
 	\tableofcontents
@@
 	\section{Background}
+
+		TEXT: Edit background
 
@@
 
-		Fig: OCT abnormities
-		Fig: Fundus abnormities
+		Fig: OCT abnormities and Fundus abnormities
 
-		No real data. use the following criteria. source for criteria
+		TEXT: No real data. use the following criteria. source for criteria
 
@@
 
-		Model consists of 3 parts: OCT-Model, Fundus-Model, and Diagnosis-Model.
+		TEXT: Model consists of 3 parts: OCT-Model, Fundus-Model, and Diagnosis-Model.
 OCT-Model and Fundus-Model are collectively called the Abnormity-Models.
@@
 
-		fusion: max of OCT, max of fundus, concatenate
+		TEXT: max of OCT, max of fundus, concatenate; concatenate D1 outputs
 
@@
 
-		output
+		TEXT: output
 
@@
 
-			Fig: overall flowchart
+			Fig: preparation flowchart (include cycleGAN)
 
@@
 
-			CycleGAN
-				Fig: Intro
+			TEXT: CycleGAN
 				Table: selection rates
@@
 
-			transforms for OCT
+			TEXT: transforms for OCT
 				for train: copy, flip, randomcomb1
@@
 
-			intro to five-fold train/valid (reason for using this?)
+			TEXT: intro to five-fold train/valid (reason for using this?)
 
-			starting point of fine-tuning???????????????????????????????
+			TEXT: starting point of fine-tuning???????????????????????????????
 			prevent overfitting
 
-			crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
-			running time
-
-			Fig: accuracy and loss over epochs
-				trainAcc, validAcc, trainLosses, validLosses
-				testAcc for best weights - align below acc graph
-
+			TEXT: crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
 			conda, PyTorch;
@@
 
+			Graph: accuracy and loss over epochs
+			TEXT: comments
+
 		\subsection{Results}
-
-			time per image
 
@@
 
+				TEXT: accuracy; explain top-probs method
+
 				Table: for each abnormity:
-					accuracy (only present accuracy for TOTAL)
 					precision
@@
 
-				Table: Confusion matrix
-					analyze which abnormities are commonly confused, and the effect on the numerical results
-				Fig: t-SNE
-					which abnormities are "close"
+				Graph: Confusion matrix
+				TEXT: analyze which abnormities are commonly confused, and the effect on the numerical results
+				Graph: t-SNE
+				TEXT: which abnormities are "close"
 
-				Fig: ROC for each abnormity
+				Graph: ROC for each abnormity
 
-				comparison to other studies
+				TEXT: comparison to other studies
 
-			"co-dominance"??????????????????????????????
-
-			Fig: GradCAM intro
 			Fig: GradCAM example
@@
 
-			how to choose data (with an example)
-			how to find grade (number of traits = grade for the disease as label during training)
+			TEXT: how to choose data (with an example)
+			how to find level (number of traits = level for the disease as label during training)
 
@@
 
-			parameters used
-			running time
-			Fig: accuracy and loss over epochs
-				trainAcc, validAcc, trainLosses, validLosses
+			TEXT: hyperparameters, software, hardware
+
+			Graph: accuracy and loss over epochs
+			TEXT: comments
 
@@
 
-			output - calculate expected grade. in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1].
+			TEXT: D1 output - calculate expected grade. in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1]. 
+			used for checking number of abnormities associated to the disease
+
+			TEXT: top-probs method
 
 			Table: for each disease:
-				accuracy (only present accuracy for TOTAL)
 				precision
@@
 				AUC
-			Fig: confusion matrix (is it suitable?)
-			Fig: ROC for each disease
+			Graph: D1 acc bar chart (with D2 no use-top-probs and D2 use-top-probs)
+			Graph: D1 confusion matrix
+			TEXT: comments
 
-			"co-dominance"???????????????????????????????????
+			Graph: D2 confusion matrix
+			Graph: D2 tSNE
+			TEXT: comments
+
+			Graph: D2 ROC for each disease
+			TEXT: comparison and comments
 
@@
 
-		Do two models increase accuracy?
-			how do I compare?????????????????????????????????
-			any math here?
+		TEXT: Do two models increase accuracy? How?
 
-		Comparison
+		TEXT: Comparison to other studies
 
-		Strengths and weaknesses
+		TEXT: Strengths and weaknesses
 		how to improve
@@
 
-	\section{Appendix}
+		TEXT: conclusion
 
-		Google Image source links
-		Add prevalence (1 out of how many people) for abnormities?
+	\phantomsection
+	\addcontentsline{toc}{section}{References}
+	\newrefcontext[sorting=nyt]
+	\printbibliography
+
+	\pagebreak
+	\section*{Appendix}
+
+	List: Google Image source links
+
+	Table: abnormities with description (edit the two tables below)
 
@@
 
-		APP/website description
-		GitHub repo
+	Fig: website
+	TEXT: APP/website description
 
-	\phantomsection
-	\addcontentsline{toc}{section}{References}
-	\newrefcontext[sorting=nyt]
-	\printbibliography
+	Link: GitHub repo
 

### 2024-08-27 ODADS/Code/Results/abnormity_gradCAM.py

@@ -3,12 +3,19 @@ import numpy as np
 from PIL import Image
 from Abnormity_Models import abnormity_models
 from Utils import utils
+from torchvision import transforms
+import os
+from Abnormity_Models import classify_abnormity
 import matplotlib.pyplot as plt
 from matplotlib.colors import LinearSegmentedColormap
 
-# small utilities. refactor later!
-
 # from https://blog.csdn.net/sjhKevin/article/details/121747933
+
+custom_cmap = [
+        LinearSegmentedColormap.from_list('red_outline', [(0, 'black'), (0.6, 'black'), (0.7, 'red'), (0.8, 'black'), (1, 'black')]),
+        LinearSegmentedColormap.from_list('red_yellow_green_blue', [(0, 'blue'), (0.4, 'green'), (0.6, 'yellow'), (0.8, 'orange'), (1, 'red')]),
+        LinearSegmentedColormap.from_list('red_blue_black', [(0, 'black'), (0.5, 'blue'), (1, 'red')])
+    ]
 
 class Cam_Extractor():
     def __init__(self, model):
@@ -54,23 +61,19 @@ class Cam_Extractor():
         x = self.model.fc(x)
         return conv_output, x
 
-
-
-
-
-class GradCam():
+class GradCAM():
     def __init__(self, model):
         self.model = model
         self.model.eval()
         self.extractor = Cam_Extractor(self.model)
 
-    def generate_cam(self, input_image, target_layer, device, model, target_class=None):
+    def generate_cam(self, input_image, target_layer, device, model, target_class_idx=None, img_size = (224, 224)):
 
         # Full forward pass
         # conv_output is the output of convolutions at specified layer
         # model_output is the final output of the model (1, 1000)
         conv_output, model_output = self.extractor.forward_pass(input_image)
-        if target_class is None:
+        if target_class_idx is None:
             target_class_idx = 0
             for idx in range(len(model_output[0])):
                 if model_output[0][idx] > model_output[0][target_class_idx]:
@@ -97,33 +100,26 @@ class GradCam():
         weights = torch.mean(guided_gradients, axis=(1, 2))  # Take averages for each gradient
 
         # Create empty numpy array for cam
[…]

### 2024-08-27 ODADS/Code/Results/abnormity_loss_and_acc.py

@@ -126,16 +126,6 @@ def plot_loss_and_acc_alt(): # (2x1) x (2x2) x (2x1)
 def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
     setting = utils.get_setting()
     fig_folder = setting.fig_folder
-    fig_file = "abnormity_loss_and_acc.pdf"
-    fig_path = os.path.join(fig_folder, fig_file)
-    
-    fig = plt.figure(figsize=(8, 13))
-    grid = gridspec.GridSpec(4, 1, wspace = 0, hspace = 0.2)
-    plt.axis(False)
-    
-    type = "AF" # "AO"
-    best_net = "152" # "050"
-
     net_list = [
         ("152", 0), 
         ("050", 1),
@@ -143,38 +133,46 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
         ("016", 3)
     ]
     
-    plt.title("Fundus" if type == "AF" else "OCT")
-    
-    for net_name, pos in net_list:
-        sub_ax = fig.add_subplot(grid[pos, 0])
-        sub_ax.set_title(net_name)
-        sub_ax.set_axis_off()
-        sub_grid = gridspec.GridSpecFromSubplotSpec(2, 1, subplot_spec = grid[pos, 0], wspace = 0, hspace = 0.05)
+    for type in ["AF", "AO"]:
+        best_net = setting.best_f_net if type == "AF" else setting.best_o_net
+        fig_file = "abnormity_Fundus_loss_and_acc.pdf" if type == "AF" else "abnormity_OCT_loss_and_acc.pdf"
+        fig_path = os.path.join(fig_folder, fig_file)
         
-        rst = get_loss_and_acc(net_name, type) # ReSults from Transferred learning
-        rsf = get_loss_and_acc(net_name, type, starting_epoch = rst["best epoch"]) # ReSults from Finetuning
-        continuation_epoch = rst["best epoch"]
-        rsf["epoch train"].insert(0, continuation_epoch)
-        rsf["train acc"].insert(0, rst["train acc"][continuation_epoch - 1])
-        rsf["train losses"].insert(0, rst["train losses"][continuation_epoch - 1])
-        rsf["valid acc"].insert(0, rst["valid acc"][continuation_epoch - 1])
-        rsf["valid losses"].insert(0, rst["valid losses"][continuation_epoch - 1])
-        rsf["epoch test"].insert(0, continuation_epoch)
[…]

### 2024-08-27 ODADS/Code/Utils/utils.py

@@ -172,3 +172,18 @@ def calc_expected_abnormity_num(abnormity_num_vector):
         sum += i * abnormity_num_vector[i]
     sum /= len(abnormity_num_vector)
     return sum
+
+# turn array into img, then resize and crop it to fit img_shape
+def resize_array_to_img_size(array, img_shape):
+    long_edge = max(img_shape)
+    short_edge = min(img_shape)
+    x = (long_edge - short_edge) / 2
+    y = x + short_edge
+    img = Image.fromarray(array).resize((long_edge, long_edge), Image.LANCZOS)
+    
+    if img_shape[0] < img_shape[1]:
+        img = img.crop((0, x, img_shape[1], y))
+    elif img_shape[0] > img_shape[1]:
+        img = img.crop((x, 0, y, img_shape[0]))
+        
+    return img

### 2024-08-27 ODADS/Code/main.py

@@ -30,7 +30,7 @@ if task == "get results":
     elif name == "A: confusion matrix":
         abnormity_confusion_matrix.plot_all_conf_mat()
     elif name == "A: gradCAM":
-        pass
+        abnormity_gradCAM.highlight(device, sys.argv[4], sys.argv[5])
     elif name == "D1: Acc barchart":
         diagnosis1_acc_barchart.plot_acc_barchart()
     elif name == "D1: confusion matrix":

### 2024-08-27 ODADS/Code/setting.py

@@ -280,3 +280,10 @@ class Setting:
             return (self.O_train_class_size, self.O_test_class_size)
         else:
             return (self.F_train_class_size, self.F_test_class_size)
+        
+    def img_path_is_OCT(self, img_path: str) -> bool:
+        match = re.search(r"(OCT)", img_path)
+        if match:
+            return True
+        else:
+            return False

### 2024-08-27 Paper/Paper.tex
Import tables into latex

@@
 \usepackage{tikz}
+\usepackage{pgfplotstable}
 \usepackage{pgfplots}
-\usepackage{mhchem}
 \pgfplotsset{compat=1.18}
@@
 
+				\begin{table}[htbp]
+					\centering
+					\caption{OCT Test}
+					\label{tb:OCT_test}
+					\pgfplotstabletypeset[
+						multicolumn names,
+						col sep=comma,
+						columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
+						columns/Abnormity/.style={string type, column name=Abnormities},
+						columns/Precision/.style={string type, column name=Precision},
+						columns/Sensitivity/.style={string type, column name=Sensitivity},
+						columns/Specificity/.style={string type, column name=Specificity},
+						columns/FOne/.style={string type, column name={F1 Score}},
+						columns/AUC/.style={string type, column name=AUC},
+						every head row/.style={before row=\toprule, after row=\midrule},
+						every last row/.style={ after row=\bottomrule}
+					]{Tables/abnormity_o_test.csv}
+				\end{table}
+
+				\begin{table}[htbp]
+					\centering
+					\caption{Fundus Test}
+					\label{tb:Fundus_test}
+					\pgfplotstabletypeset[
+					multicolumn names,
+					col sep=comma,
+					columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
+					columns/Abnormity/.style={string type, column name=Abnormities},
+					columns/Precision/.style={string type, column name=Precision},
+					columns/Sensitivity/.style={string type, column name=Sensitivity},
+					columns/Specificity/.style={string type, column name=Specificity},
+					columns/FOne/.style={string type, column name={F1 Score}},
+					columns/AUC/.style={string type, column name=AUC},
+					every head row/.style={before row=\toprule, after row=\midrule},
+					every last row/.style={after row=\bottomrule}
+					]{Tables/abnormity_f_test.csv}
+				\end{table}
+
 				Table: for each abnormity:
@@
 
-			Table: for each disease:
-				precision
-				recall/sensitivity
-				specificity
-				F1
-				AUC
+			\begin{table}[htbp]
+				\centering
+				\caption{Diagnosis Test}
+				\label{tb:diagnosis_test}
+				\pgfplotstabletypeset[
+				multicolumn names,
+				col sep=comma,
+				columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
+				columns/Abnormity/.style={string type, column name=Abnormities},
+				columns/Precision/.style={string type, column name=Precision},
+				columns/Sensitivity/.style={string type, column name=Sensitivity},
+				columns/Specificity/.style={string type, column name=Specificity},
+				columns/FOne/.style={string type, column name={F1 Score}},
+				columns/AUC/.style={string type, column name=AUC},
+				every head row/.style={before row=\toprule, after row=\midrule},
+				every last row/.style={ after row=\bottomrule}
+				]{Tables/diagnosis2.csv}
+			\end{table}
+
 			Graph: D1 acc bar chart (with D2 no use-top-probs and D2 use-top-probs)

### 2024-08-27 ODADS/Code/Results/abnormity_confusion_matrix.py

@@ -40,6 +40,14 @@ def calc_and_save_numerical_results(csv_filename, type, source, conf_mat):
     abnormities = setting.get_abnormities("OCT Abnormities") if type == "OCT" else setting.get_abnormities("Fundus Abnormities")
     with open(table_path, 'w', newline = "") as file:
         writer = csv.writer(file)
+        writer.writerow([
+                "Abnormity",
+                "Precision",
+                "Sensitivity",
+                "Specificity",
+                "FOne", 
+                "AUC"
+            ])
         for i in range(len(abnormities)):
             auc = abnormity_ROC.plot_single_roc(type, abnormities[i][1], draw_roc = False)[source]
             disease_conf_mat = get_single_conf_mat(conf_mat, i)
@@ -53,11 +61,11 @@ def calc_and_save_numerical_results(csv_filename, type, source, conf_mat):
             f1 = 2 * precision * sensitivity / (precision + sensitivity)
             writer.writerow([
                 abnormities[i][1],
-                precision,
-                sensitivity,
-                specificity,
-                f1, 
-                auc
+                f"{precision:.3f}",
+                f"{sensitivity:.3f}",
+                f"{specificity:.3f}",
+                f"{f1:.3f}", 
+                f"{auc:.3f}"
             ])
 
 def plot_all_conf_mat():

### 2024-08-27 ODADS/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py

@@ -148,6 +148,14 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
     
     with open(os.path.join(setting.table_folder, "diagnosis2.csv"), "w", newline="") as file:
         writer = csv.writer(file)
+        writer.writerow([
+                "Abnormity",
+                "Precision",
+                "Sensitivity",
+                "Specificity",
+                "FOne", 
+                "AUC"
+            ])
         for i in range(len(diseases_including_normal)):
             disease_conf_mat = get_single_conf_mat(conf_mat, i)
             tp = disease_conf_mat[0][0]
@@ -160,9 +168,9 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
             f1 = 2 * precision * sensitivity / (precision + sensitivity)
             writer.writerow([
                 diseases_including_normal[i],
-                precision,
-                sensitivity,
-                specificity,
-                f1, 
-                aucs[i]
+                f"{precision:.3f}",
+                f"{sensitivity:.3f}",
+                f"{specificity:.3f}",
+                f"{f1:.3f}", 
+                f"{aucs[i]:.3f}"
             ])

### 2024-08-27 ODADS/Code/main.py
Fix Mactel and MH order problem; rerun diagnosis1 and 2; replot all graphs

@@ -19,7 +19,7 @@ use_gpu = torch.cuda.is_available()
 device = torch.device(cuda_device if use_gpu else "cpu")
 print(device)
 
-# get results commands
+
 if task == "get results":
     if name == "A: Loss and Acc":
         abnormity_loss_and_acc.plot_loss_and_acc()
@@ -37,8 +37,18 @@ if task == "get results":
         diagnosis1_confusion_matrix.plot_conf_mat()
     elif name == "D2: tSNE, ROC, confusion matrix":
         diagnosis2_tSNE_ROC_confusion_matrix.plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
+    elif task == "graph all":
+        abnormity_confusion_matrix.plot_all_conf_mat()
+        diagnosis1_confusion_matrix.plot_conf_mat()
+        
+        abnormity_loss_and_acc.plot_loss_and_acc()
+        abnormity_ROC.plot_roc()
+        abnormity_tSNE.plot_tsne()
+        diagnosis1_acc_barchart.plot_acc_barchart()
+        diagnosis1_confusion_matrix.plot_conf_mat()
 
-# multi-task commands
+
+
 elif task == "abnormity all":
     train_abnormity.train(device, name + "TRRS - T")
     test_abnormity.test_multiple(device, name + "TORS - T")
@@ -52,12 +62,12 @@ elif task == "abnormity all":
 
 elif task == "diagnosis all":
     names = name.split(", ")
-    #train_diagnosis.train(device, [name + "D1TRRS" for name in names])
-    #train_diagnosis.train(device, [name + "D2TRRS" for name in names])
+    train_diagnosis.train(device, [name + "D1TRRS" for name in names])
+    train_diagnosis.train(device, [name + "D2TRRS" for name in names])
     test_diagnosis.test(device, [name + "D1TORS" for name in names])
     test_diagnosis.test(device,[name + "D2TORS" for name in names])
 
-# single-task commands
+
 else:
     if setting.is_abnormity(name):
         if task == "train":

### 2024-08-28 Paper/Paper.tex
Fix Mactel and MH order problem; rerun diagnosis1 and 2; replot all graphs
Remove colorbar of conf mats; write model overview draft

@@
 
-		The Optical Disease Auxiliary Diagnosis System (ODADS)
-		Model purpose: recognize abnormities, then diagnose disease; 
-			interpretable findings
+		The Optical Disease Auxiliary Diagnosis System (ODADS) is developed to aid doctors in diagnosing optical diseases.
+It simulates the decision-making process of doctors when they examine patients with optical diseases, i.e., first identifying the abnormities, and then deducing the disease.
+By doing so, the ODADS partly opens up the ``black box'' of DL and presents more interpretable conclusions.
+In addition, it is multi-modal and considers both OCT and color fundus image inputs.
 
-		Fig: OCT abnormities and Fundus abnormities
+		The ODADS is trained to identify 12 OCT abnormities (including normal) and 9 Fundus abnormities (including normal), as shown in Fig.~\ref{fig:abnormities}.
 
-		TEXT: No real data. use the following criteria. source for criteria
+		\begin{figure}[htbp]
+			\centering
+			\includegraphics[width=\linewidth]{Figs/Temp.png}
+			\caption{Abnormities}
+			\vspace{0.3cm}
+			\label{fig:abnormities}
+		\end{figure}
 
-		Fig: From Abnormity to Disease
+		Most of the data we acquire are only labeled with abnormities (sometimes called ``findings'' in other studies).
+Therefore, we compose the following abnormity-disease conversion criteria and use these criteria to generate data for training (see Fig.~\ref{fig:criteria}).
 
-		Fig: 3 parts
+		\begin{figure}[htbp]
+			\centering
+			\includegraphics[width=\linewidth]{Figs/Temp.png}
+			\caption{Criteria}
+			\vspace{0.3cm}
+			\label{fig:criteria}
+		\end{figure}
 
-		TEXT: Model consists of 3 parts: OCT-Model, Fundus-Model, and Diagnosis-Model.
-OCT-Model and Fundus-Model are collectively called the Abnormity-Models.
-They use the same architecture (ResNet152, flatten to 2048 features, and fc).
-Diagnosis Model consists of num submodels, one of which is for normal, and the other ones for each disease.
-each submodel first fuses output from both Abnormity-Models, then uses an fc to get final results for normal or for the disease.
+		The structure of the ODADS is shown in Fig.~\ref{fig:3_parts}. The ODADS constitutes of 2 parts: the Abnormity Models and the Diagnosis Model.
 
-		TEXT: max of OCT, max of fundus, concatenate; concatenate D1 outputs
+		The Abnormity Models consists of the OCT Model and the Fundus Model, which identify OCT and Fundus abnormities, respectively.
+Both of the Abnormity Models are a CNN with a modified final FC layer.
+Four CNN structures (ResNet152, ResNet50, ResNet18, and VGG16) are tried and the best is chosen for each of the Abnormity Models.
+The final FC layers are modified so that the size of their output vectors is equal to the number of OCT or Fundus abnormities, and a softmax layer is added.
+After an image is inputted into one of the Abnormity Models, the model returns a probability vector containing the probabilities of different abnormities.
 
-		Fig: fusion
+		The Diagnosis Model consists of two stages: the Abnormity Number Stage (Stage D1) and the Disease Probability Stage (Stage D2).
+In Stage D1, there is a small NN for each of the diseases.
+Each NN takes input from the OCT and Fundus Models, passes the input through a FC layer and a softmax layer, and determines how many abnormities that are related to the specific disease (as in Fig.~\ref{fig:criteria}) are present in an image.
+Then, in Stage D2, an NN takes input from all the NNs in Stage D1, passes the input through a FC layer and a softmax layer, and returns the probability vector containing the probabilities of being normal and having different diseases.
 
-		TEXT: output
+		\begin{figure}[htbp]
+			\centering
+			\includegraphics[width=\linewidth]{Figs/Temp.png}
+			\caption{3 Parts}
+			\vspace{0.3cm}
+			\label{fig:3_parts}
+		\end{figure}
+
+		Fig.~\ref{fig:fusion} shows how the different parts of the ODADS are connected.
+
+		When multiple OCT and Fundus images are inputted, they are passed through the Abnormity Models, resulting in multiple OCT and Fundus probability vectors.
+For each OCT abnormity, we choose the maximum probability  from the OCT probability vectors.
+Thus, we can get a final OCT probability vector with all the maximum probabilities.
+We do this for Fundus as well, and then concatenate the final OCT and Fundus vectors as an input to the Diagnosis Model.
+
+		Stage D1 then takes the input and generates multiple abnormity number vectors. All these vectors are concatenated and inputted into Stage D2, which finally yields the probability vector of diseases.
+
+		The results are then given to a user interface and shown to the user.
+
+		\begin{figure}[htbp]
+			\centering
+			\includegraphics[width=\linewidth]{Figs/Temp.png}
+			\caption{Fusion}
+			\vspace{0.3cm}
+			\label{fig:fusion}
+		\end{figure}
 
@@
 
-			Fig: preparation flowchart (include cycleGAN)
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/Temp.png}
+				\caption{Data preparation for abnormity models}
+				\vspace{0.3cm}
+				\label{fig:A_data_prep}
+			\end{figure}
 
@@
 
-			TEXT: starting point of fine-tuning???????????????????????????????
+			TEXT: starting point of fine-tuning
 			prevent overfitting
@@
 			conda, PyTorch;
-			desktop computer with Intel® Xeon® Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM
+			desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM
 
-			Graph: accuracy and loss over epochs
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
+				\caption{AO train}
+				\vspace{0.3cm}
+				\label{fig:AO_train}
+			\end{figure}
+
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
+				\caption{AF train}
+				\vspace{0.3cm}
+				\label{fig:AF_train}
+			\end{figure}
+
+			Graph bar chart for comparison?
+
 			TEXT: comments
@@
 		\subsection{Results}
-
-			For both OCT and Fundus:
 
@@
 
-				Table: for each abnormity:
-					precision
-					recall/sensitivity
-					specificity
-					F1
-					AUC
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=0.8\linewidth]{Figs/abnormity_confusion_matrix.pdf}
+				\caption{A Conf Mat}
+				\vspace{0.3cm}
+				\label{fig:A_conf_mat}
+			\end{figure}
 
-				Graph: Confusion matrix
 			TEXT: analyze which abnormities are commonly confused, and the effect on the numerical results
-				Graph: t-SNE
+
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/abnormity_tSNE.pdf}
+				\caption{A ROC}
+				\vspace{0.3cm}
+				\label{fig:A_tSNE}
+			\end{figure}
+
 			TEXT: which abnormities are "close"
 
-				Graph: ROC for each abnormity
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/abnormity_ROC.pdf}
+				\caption{A ROC}
+				\vspace{0.3cm}
+				\label{fig:A_ROC}
+			\end{figure}
 
@@
 
-			Fig: GradCAM example
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.png}
+				\caption{GradCAM}
+				\vspace{0.3cm}
+				\label{fig:gradCAM}
+			\end{figure}
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.png}
+				\caption{GradCAM with multiple abnormities}
+				\vspace{0.3cm}
+				\label{fig:gradCAM_multi_abnormity}
+			\end{figure}
 
@@
 
-			Graph: accuracy and loss over epochs
 			TEXT: comments
@@
 
-			Graph: D1 acc bar chart (with D2 no use-top-probs and D2 use-top-probs)
-			Graph: D1 confusion matrix
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
+				\caption{D1 Acc Bar}
+				\vspace{0.3cm}
+				\label{fig:D1_acc_bar}
+			\end{figure}
+
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.pdf}
+				\caption{D1 Conf Mat}
+				\vspace{0.3cm}
+				\label{fig:D1_conf_mat}
+			\end{figure}
 			TEXT: comments
 
-			Graph: D2 confusion matrix
-			Graph: D2 tSNE
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/diagnosis2_confusion_matrix.pdf}
+				\caption{D2 Conf Mat}
+				\vspace{0.3cm}
+				\label{fig:D2_conf_mat}
+			\end{figure}
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/diagnosis2_tSNE.pdf}
+				\caption{D2 tSNE}
+				\vspace{0.3cm}
+				\label{fig:D2_tSNE}
+			\end{figure}
 			TEXT: comments
 
-			Graph: D2 ROC for each disease
+			\begin{figure}[htbp]
+				\centering
+				\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
+				\caption{D2 ROC}
+				\vspace{0.3cm}
+				\label{fig:D2_ROC}
+			\end{figure}
 			TEXT: comparison and comments
@@
 
-	Fig: website
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\linewidth]{Figs/Temp.png}
+		\caption{Result Page}
+		\vspace{0.3cm}
+		\label{fig:result_page}
+	\end{figure}
+
 	TEXT: APP/website description

### 2024-08-28 ODADS/Code/Results/abnormity_confusion_matrix.py

@@ -31,7 +31,6 @@ def plot_complete_conf_mat(ax, complete_conf_mat, abnormities):
     for i in range(complete_conf_mat.shape[0]):
         for j in range(complete_conf_mat.shape[1]):
             ax.text(j, i, complete_conf_mat[i, j], ha='center', va='center', color='black' if complete_conf_mat[i, j] < max / 2 else 'white')
-    plt.colorbar(mat)
 
 def calc_and_save_numerical_results(csv_filename, type, source, conf_mat):
     setting = utils.get_setting()

### 2024-08-28 ODADS/Code/Results/diagnosis1_confusion_matrix.py

@@ -111,7 +111,6 @@ def plot_conf_mat():
             for i in range(conf_mat.shape[0]):
                 for j in range(conf_mat.shape[1]):
                     axs[row, col].text(j, i, conf_mat[i, j], ha='center', va='center', color='black' if conf_mat[i, j] < max / 2 else 'white')
-            plt.colorbar(mat)
             if col == 3:
                 col = 0
                 row += 1

### 2024-08-28 ODADS/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py

@@ -85,7 +85,6 @@ def plot_conf_mat(conf_mat, diseases):
     for i in range(conf_mat.shape[0]):
         for j in range(conf_mat.shape[1]):
             plt.text(j, i, conf_mat[i, j], ha='center', va='center', color='black' if conf_mat[i, j] < max / 2 else 'white')
-    plt.colorbar(mat)
     
     plt.savefig(fig_path)
     plt.show()

### 2024-08-28 ODADS/Code/main.py

@@ -37,15 +37,15 @@ if task == "get results":
         diagnosis1_confusion_matrix.plot_conf_mat()
     elif name == "D2: tSNE, ROC, confusion matrix":
         diagnosis2_tSNE_ROC_confusion_matrix.plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
-    elif task == "graph all":
+    elif name == "graph all":
         abnormity_confusion_matrix.plot_all_conf_mat()
         diagnosis1_confusion_matrix.plot_conf_mat()
+        diagnosis2_tSNE_ROC_confusion_matrix.plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
         
         abnormity_loss_and_acc.plot_loss_and_acc()
         abnormity_ROC.plot_roc()
         abnormity_tSNE.plot_tsne()
         diagnosis1_acc_barchart.plot_acc_barchart()
-        diagnosis1_confusion_matrix.plot_conf_mat()
 
 
 

### 2024-08-28 Paper/Paper.tex
Update .gitignore to include png and jpg needed by Paper.tex

@@
 \begin{document}
-	\title{\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System}
-	\author{Jerry Pan}
+	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
+	\author{Siqi Pan}
 	\date{}
 	\maketitle
-	\vspace{0.5cm}
 
@@
 Many studies use convolutional neural network (CNN) to analyze ocular images.
-Some commonly used CNNs are VGG16, ResNet50, and Inception \autocite{daich2023artificial}.
+Some commonly used CNNs are VGG, ResNet, and Inception \autocite{daich2023artificial}.
 And for segmenting images and finding abnormalities, U-net is widely used \autocite{Ronneberger_Fischer_Brox_2015}.
@@
 
-		The Optical Disease Auxiliary Diagnosis System (ODADS) is developed to aid doctors in diagnosing optical diseases.
-It simulates the decision-making process of doctors when they examine patients with optical diseases, i.e., first identifying the abnormities, and then deducing the disease.
-By doing so, the ODADS partly opens up the ``black box'' of DL and presents more interpretable conclusions.
-In addition, it is multi-modal and considers both OCT and color fundus image inputs.
+		We develop a multimodal abnormity-aware model to aid doctors in diagnosing ocular diseases.
+It is a multimodal model and considers both OCT and color fundus image inputs.
+In addition, tt simulates the decision-making process of doctors when they examine patients with ocular diseases, i.e., first identifying the abnormities, and then deducing the disease.
+By doing so, it partly opens up the ``black box'' of DL and presents more interpretable conclusions.
+
+		The structure of the model is shown in Fig.~\ref{fig:3_parts}. The model constitutes of 2 parts: the Abnormity Models and the Diagnosis Model.
+
+		The Abnormity Models consists of the OCT Model and the Fundus Model, which identify OCT and Fundus abnormities, respectively.
+Both of the Abnormity Models are CNNs with modified final FC layer.
+All CNNs that are used for classification tasks can be used.
+In this study, we consider ResNet152, ResNet50, ResNet18, and VGG16, tried and the best is chosen for each of the Abnormity Models.
+The final FC layers are modified so that the size of their output vectors is equal to the number of OCT or Fundus abnormities, and a softmax layer is added.
+After an image is inputted into one of the Abnormity Models, the model returns a probability vector containing the probabilities of different abnormities.
+
+		The Diagnosis Model consists of two stages: the Abnormity Number Stage (Stage D1) and the Disease Probability Stage (Stage D2).
+In Stage D1, there is a small NN for each of the diseases.
+Each NN takes input from the OCT and Fundus Models, passes the input through a FC layer and a softmax layer, and determines how many abnormities that are related to the specific disease (as in Fig.~\ref{fig:criteria}) are present in an image.
+Then, in Stage D2, an NN takes input from all the NNs in Stage D1, passes the input through a FC layer and a softmax layer, and returns the probability vector containing the probabilities of being normal and having different diseases.
 
@@
 
-		Most of the data we acquire are only labeled with abnormities (sometimes called ``findings'' in other studies).
+		Most of the data we acquire are only labeled with abnormities, which are symptoms that can be directly observed in the images.
 Therefore, we compose the following abnormity-disease conversion criteria and use these criteria to generate data for training (see Fig.~\ref{fig:criteria}).
@@
 		\end{figure}
-
-		The structure of the ODADS is shown in Fig.~\ref{fig:3_parts}. The ODADS constitutes of 2 parts: the Abnormity Models and the Diagnosis Model.
-
-		The Abnormity Models consists of the OCT Model and the Fundus Model, which identify OCT and Fundus abnormities, respectively.
-Both of the Abnormity Models are a CNN with a modified final FC layer.
-Four CNN structures (ResNet152, ResNet50, ResNet18, and VGG16) are tried and the best is chosen for each of the Abnormity Models.
-The final FC layers are modified so that the size of their output vectors is equal to the number of OCT or Fundus abnormities, and a softmax layer is added.
-After an image is inputted into one of the Abnormity Models, the model returns a probability vector containing the probabilities of different abnormities.
-
-		The Diagnosis Model consists of two stages: the Abnormity Number Stage (Stage D1) and the Disease Probability Stage (Stage D2).
-In Stage D1, there is a small NN for each of the diseases.
-Each NN takes input from the OCT and Fundus Models, passes the input through a FC layer and a softmax layer, and determines how many abnormities that are related to the specific disease (as in Fig.~\ref{fig:criteria}) are present in an image.
-Then, in Stage D2, an NN takes input from all the NNs in Stage D1, passes the input through a FC layer and a softmax layer, and returns the probability vector containing the probabilities of being normal and having different diseases.
 

### 2024-08-28 Paper/Paper.tex
Reorder model overview part.

@@
 In addition, tt simulates the decision-making process of doctors when they examine patients with ocular diseases, i.e., first identifying the abnormities, and then deducing the disease.
-By doing so, it partly opens up the ``black box'' of DL and presents more interpretable conclusions.
+Thus, it partly opens up the ``black box'' of DL and presents more interpretable conclusions.
+
+		\begin{figure}[htbp]
+			\centering
+			\includegraphics[width=\linewidth]{Figs/Temp.png}
+			\caption{Model Overview}
+			\vspace{0.3cm}
+			\label{fig:3_parts}
+		\end{figure}
 
@@
 		The Abnormity Models consists of the OCT Model and the Fundus Model, which identify OCT and Fundus abnormities, respectively.
-Both of the Abnormity Models are CNNs with modified final FC layer.
+Both of the Abnormity Models are CNNs with modified final FC layers.
 All CNNs that are used for classification tasks can be used.
-In this study, we consider ResNet152, ResNet50, ResNet18, and VGG16, tried and the best is chosen for each of the Abnormity Models.
-The final FC layers are modified so that the size of their output vectors is equal to the number of OCT or Fundus abnormities, and a softmax layer is added.
+In this study, we consider ResNet152, ResNet50, ResNet18 and VGG16, and choose the best CNN for both Abnormity Models.
+The final FC layers are modified so that the size of their output vectors is equal to the number of OCT or Fundus abnormities.
+We also add a softmax layer after it.
 After an image is inputted into one of the Abnormity Models, the model returns a probability vector containing the probabilities of different abnormities.
@@
 		The Diagnosis Model consists of two stages: the Abnormity Number Stage (Stage D1) and the Disease Probability Stage (Stage D2).
-In Stage D1, there is a small NN for each of the diseases.
-Each NN takes input from the OCT and Fundus Models, passes the input through a FC layer and a softmax layer, and determines how many abnormities that are related to the specific disease (as in Fig.~\ref{fig:criteria}) are present in an image.
-Then, in Stage D2, an NN takes input from all the NNs in Stage D1, passes the input through a FC layer and a softmax layer, and returns the probability vector containing the probabilities of being normal and having different diseases.
-
-		The ODADS is trained to identify 12 OCT abnormities (including normal) and 9 Fundus abnormities (including normal), as shown in Fig.~\ref{fig:abnormities}.
+In Stage D1, there is a submodel for each of the diseases.
+Each submodel takes input from the OCT and Fundus Models, passes the input through a FC layer and a softmax layer, and determines how many abnormities that are related to the specific disease (as in Fig.~\ref{fig:criteria}) are present in an image.
+Then, in Stage D2, the output of all the submodels in Stage D1 passes through a FC layer and a softmax layer, and returns a disease probability vector.
 
@@
 			\includegraphics[width=\linewidth]{Figs/Temp.png}
-			\caption{Abnormities}
+			\caption{OCT and Fundus abnormities}
 			\vspace{0.3cm}
@@
 
-		Most of the data we acquire are only labeled with abnormities, which are symptoms that can be directly observed in the images.
-Therefore, we compose the following abnormity-disease conversion criteria and use these criteria to generate data for training (see Fig.~\ref{fig:criteria}).
+		Abnormities are symptoms that can be directly observed in the images.
+The model is trained to identify 12 OCT abnormities (including normal) and 9 Fundus abnormities (including normal), as shown in Fig.~\ref{fig:abnormities}.
 
@@
 			\includegraphics[width=\linewidth]{Figs/Temp.png}
-			\caption{Criteria}
+			\caption{Abnormity-to-disease conversion criteria}
 			\vspace{0.3cm}
@@
 
+		Most of the data we acquire are only labeled with abnormities.
+Therefore, we compose the following abnormity-to-disease conversion criteria and use these criteria to generate data for training the Diagnosis Model (see Fig.~\ref{fig:criteria}).
+
 		\begin{figure}[htbp]
@@
 			\includegraphics[width=\linewidth]{Figs/Temp.png}
-			\caption{3 Parts}
+			\caption{Fusion}
 			\vspace{0.3cm}
-			\label{fig:3_parts}
+			\label{fig:fusion}
 		\end{figure}
@@
 		The results are then given to a user interface and shown to the user.
-
-		\begin{figure}[htbp]
-			\centering
-			\includegraphics[width=\linewidth]{Figs/Temp.png}
-			\caption{Fusion}
-			\vspace{0.3cm}
-			\label{fig:fusion}
-		\end{figure}
 

### 2024-08-28 Paper/Paper.tex
add OCT image sources (not complete yet)
overview.

@@
 	\pagebreak
-	\tableofcontents
-	\pagebreak
 
@@
 With the widespread application of artificial intelligence (AI), deep learning (DL) has made great contributions in providing support to patients in remote areas by sharing expert knowledge \autocite{Ichhpujani_Thakur_2021}.
-By leveraging DL, researchers have developed auxiliary diagnosis programs to help doctors in the process.
+By leveraging DL, researchers have developed auxiliary diagnosis programs to help ophthalmologists in the process.
 Many studies use convolutional neural network (CNN) to analyze ocular images.
@@
 
-		We develop a multimodal abnormity-aware model to aid doctors in diagnosing ocular diseases.
-It is a multimodal model and considers both OCT and color fundus image inputs.
-In addition, tt simulates the decision-making process of doctors when they examine patients with ocular diseases, i.e., first identifying the abnormities, and then deducing the disease.
-Thus, it partly opens up the ``black box'' of DL and presents more interpretable conclusions.
+	We develop the Multimodal Abnormity-Aware Model (MAAM) to aid ophthalmologists in diagnosing ocular diseases.
+It considers both OCT and color fundus image inputs.
+In addition, it simulates the decision-making process of ophthalmologists when they examine patients, i.e., first identifying the abnormities, and then deducing the disease.
+The model is designed in a way that partly opens up the ``black box'' of DL and presents more interpretable information for the reference of the ophthalmologists.
 
@@
 
-		The structure of the model is shown in Fig.~\ref{fig:3_parts}. The model constitutes of 2 parts: the Abnormity Models and the Diagnosis Model.
+	The structure of the MAAM is shown in Fig.~\ref{fig:3_parts}.
+It consists of 2 submodels: the Abnormity Models and the Diagnosis Model.
+We input multiple OCT and fundus images to Abnormity Models, and output the classification of abnormities as inputs to Diagnosis Model, which generates disease probabilities as final result.
 
-		The Abnormity Models consists of the OCT Model and the Fundus Model, which identify OCT and Fundus abnormities, respectively.
-Both of the Abnormity Models are CNNs with modified final FC layers.
-All CNNs that are used for classification tasks can be used.
-In this study, we consider ResNet152, ResNet50, ResNet18 and VGG16, and choose the best CNN for both Abnormity Models.
-The final FC layers are modified so that the size of their output vectors is equal to the number of OCT or Fundus abnormities.
-We also add a softmax layer after it.
-After an image is inputted into one of the Abnormity Models, the model returns a probability vector containing the probabilities of different abnormities.
+	\vspace{0.5cm}
 
-		The Diagnosis Model consists of two stages: the Abnormity Number Stage (Stage D1) and the Disease Probability Stage (Stage D2).
-In Stage D1, there is a submodel for each of the diseases.
-Each submodel takes input from the OCT and Fundus Models, passes the input through a FC layer and a softmax layer, and determines how many abnormities that are related to the specific disease (as in Fig.~\ref{fig:criteria}) are present in an image.
-Then, in Stage D2, the output of all the submodels in Stage D1 passes through a FC layer and a softmax layer, and returns a disease probability vector.
+	The Abnormity Models are classifiers for abnormities, which are symptoms that can be directly observed in the images.
+The MAAM identifies 11 OCT abnormities and 8 Fundus abnormities, as shown in Fig.~\ref{fig:abnormities}.
+Also refer to ``Appendix'' for more details.
 
@@
 		\includegraphics[width=\linewidth]{Figs/Temp.png}
-			\caption{OCT and Fundus abnormities}
+		\caption{OCT and Fundus Abnormities}
 		\vspace{0.3cm}
@@
 
-		Abnormities are symptoms that can be directly observed in the images.
-The model is trained to identify 12 OCT abnormities (including normal) and 9 Fundus abnormities (including normal), as shown in Fig.~\ref{fig:abnormities}.
+	The Abnormity Models also contains 2 submodels: the OCT Model and the Fundus Model, which identify OCT and fundus abnormities, respectively.
+Both of the submodels leverage CNNs with modified final full-connected (FC) layers.
+We compare the performances of 4 commonly used CNN, ResNet152, ResNet50, ResNet18 and VGG16, and choose the best one for each submodel.
+The final FC layers in each CNN are modified so that the size of their output vectors is equal to the number of OCT or fundus abnormities.
+In order to do normalization, we perform softmax operation for the FC layer.
+After an image is inputted into one of the submodels, the submodel returns a probability vector for all the abnormities.
+
+	\vspace{0.5cm}
+
+	And the Diagnosis Model consists of two stages: the Stage D1 and Stage D2.
+
+	\vspace{0.2cm}
+
+	In Stage D1, we determine the severity level for each disease from the probability vectors from the Abnormity Models.
+We use Abnormity to Disease Deduction Criteria (shown in Fig.~\ref{fig:criteria}) as ground truth.
+There are multiple submodels in Stage D1 and each one corresponds to one disease.
+From the deduction criteria, we determine the number of abnormities for one disease and use the number to define the severity levels.
+For example, there are totally 5 abnormities that are present in disease ``Referable DR'', i.e., OCT abnormity ``DME'' and Fundus abnormities ``Hemorrhage'', ``Vascular Abnormity'', ``Microaneurysm'', and ``Cotton Wool Patch''.
+Therefore, when taking account of healthy status, we end up with 6 severity levels for disease ``Referable DR''.
+
+	We use fused vector as an input for each submodels in Stage D1, and have the vector pass a FC layer with softmax operation to generate severity level probability vectors.
 
@@
 		\includegraphics[width=\linewidth]{Figs/Temp.png}
-			\caption{Abnormity-to-disease conversion criteria}
+		\caption{Abnormity-to-disease Deduction Criteria}
 		\vspace{0.3cm}
@@
 
-		Most of the data we acquire are only labeled with abnormities.
-Therefore, we compose the following abnormity-to-disease conversion criteria and use these criteria to generate data for training the Diagnosis Model (see Fig.~\ref{fig:criteria}).
+	\vspace{0.2cm}
+
+	In Stage D2, we determine the final disease probability vector.
+Similarly we use a fused vector from the output of submodels in Stage D1, and have the vector pass a FC layer with softmax operation.
+The result presents potential diseases that can be referenced by ophthalmologist.
+
+	\vspace{0.5cm}
+
+	In MAAM, we leverage the fusion operation to incorporate all the results from different submodels.  As shown in Fig.~\ref{fig:fusion}, there are 3 fusion operations in MAAM.
 
@@
 
-		Fig.~\ref{fig:fusion} shows how the different parts of the ODADS are connected.
+	The first fusion occurs at the output of OCT Models or Fundus Models.
+In reality, multiple OCT images and Fundus images can be used for ocular disease diagnosis.
+Each image goes through one of the Abnormity Models and generates a probability vector.
+To use the probability results from all the images, a maximization fusion is implemented for all the vectors so that the fusion yeilds one OCT abnormity probability vector and one Fundus abnormity probability vector with maximum values.
 
-		When multiple OCT and Fundus images are inputted, they are passed through the Abnormity Models, resulting in multiple OCT and Fundus probability vectors.
-For each OCT abnormity, we choose the maximum probability  from the OCT probability vectors.
-Thus, we can get a final OCT probability vector with all the maximum probabilities.
-We do this for Fundus as well, and then concatenate the final OCT and Fundus vectors as an input to the Diagnosis Model.
+	The second fusion occurs at the interface between Abnormity Model and Stage D1.
+A concatenation fusion is implemented for OCT abnormality probability vector and Fundus abnormality probability vector.
+The fused vector works as an input to all the submodels in Stage D1.
 
-		Stage D1 then takes the input and generates multiple abnormity number vectors. All these vectors are concatenated and inputted into Stage D2, which finally yields the probability vector of diseases.
-
-		The results are then given to a user interface and shown to the user.
+	The third fusion occurs at the interface between Stage D1 and Stage D2.
+We concatenation all the severity level vectors to feed the model in Stage D2.
+The fused vector goes through the FC layer and does a softmax operation to yield the final result.
 

### 2024-08-28 Paper/Paper.tex
Get illustration PPT out; draw OCT and Fundus source tables

@@
 In addition, it simulates the decision-making process of ophthalmologists when they examine patients, i.e., first identifying the abnormities, and then deducing the disease.
-The model is designed in a way that partly opens up the ``black box'' of DL and presents more interpretable information for the reference of the ophthalmologists.
+The model is designed in a way that partly opens up the ``black box'' of DL and presents more interpretable information for the reference of ophthalmologists.
 
@@
 It consists of 2 submodels: the Abnormity Models and the Diagnosis Model.
-We input multiple OCT and fundus images to Abnormity Models, and output the classification of abnormities as inputs to Diagnosis Model, which generates disease probabilities as final result.
+We input multiple OCT and fundus images to the Abnormity Models, and output the classification of abnormities as inputs to the Diagnosis Model, which generates disease probabilities as the final result.
 
@@
 
-	The Abnormity Models also contains 2 submodels: the OCT Model and the Fundus Model, which identify OCT and fundus abnormities, respectively.
-Both of the submodels leverage CNNs with modified final full-connected (FC) layers.
-We compare the performances of 4 commonly used CNN, ResNet152, ResNet50, ResNet18 and VGG16, and choose the best one for each submodel.
-The final FC layers in each CNN are modified so that the size of their output vectors is equal to the number of OCT or fundus abnormities.
-In order to do normalization, we perform softmax operation for the FC layer.
+	The Abnormity Models also contain 2 submodels: the OCT Model and the Fundus Model, which identify OCT and fundus abnormities, respectively.
+Both of the submodels leverage CNNs with modified final fully-connected (FC) layers.
+We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18 and VGG16, and choose the best one for each submodel.
+The final FC layer in each CNN is modified so that the size of its output vector is equal to the number of OCT or fundus abnormities.
+In order to normalize the output vector, we perform the softmax operation.
 After an image is inputted into one of the submodels, the submodel returns a probability vector for all the abnormities.
@@
 
-	And the Diagnosis Model consists of two stages: the Stage D1 and Stage D2.
+	The Diagnosis Model consists of two stages: Stage D1 and Stage D2.
 
@@
 	In Stage D1, we determine the severity level for each disease from the probability vectors from the Abnormity Models.
-We use Abnormity to Disease Deduction Criteria (shown in Fig.~\ref{fig:criteria}) as ground truth.
+We use Abnormity-to-Disease Deduction Criteria (shown in Fig.~\ref{fig:criteria}) as ground truth.
 There are multiple submodels in Stage D1 and each one corresponds to one disease.
 From the deduction criteria, we determine the number of abnormities for one disease and use the number to define the severity levels.
-For example, there are totally 5 abnormities that are present in disease ``Referable DR'', i.e., OCT abnormity ``DME'' and Fundus abnormities ``Hemorrhage'', ``Vascular Abnormity'', ``Microaneurysm'', and ``Cotton Wool Patch''.
-Therefore, when taking account of healthy status, we end up with 6 severity levels for disease ``Referable DR''.
+For example, there are totally 5 abnormities that are present in the disease ``Referable DR'': OCT abnormity ``DME'' and Fundus abnormities ``Hemorrhage'', ``Vascular Abnormity'', ``Microaneurysm'', and ``Cotton Wool Patch''.
+Therefore, taking into account the healthy status, we end up with 6 severity levels for disease ``Referable DR''.
 
-	We use fused vector as an input for each submodels in Stage D1, and have the vector pass a FC layer with softmax operation to generate severity level probability vectors.
+	We use the fused vector as an input for each submodels in Stage D1, and have the vector pass a FC layer with softmax operation to generate severity level probability vectors.
 
@@
 	In Stage D2, we determine the final disease probability vector.
-Similarly we use a fused vector from the output of submodels in Stage D1, and have the vector pass a FC layer with softmax operation.
-The result presents potential diseases that can be referenced by ophthalmologist.
+Similarly we use a fused vector from the outputs of submodels in Stage D1, and have the vector pass a FC layer with softmax operation.
+The result presents potential diseases that can be referenced by ophthalmologists.
 
@@
 
-	In MAAM, we leverage the fusion operation to incorporate all the results from different submodels.  As shown in Fig.~\ref{fig:fusion}, there are 3 fusion operations in MAAM.
+	In the MAAM, we leverage the fusion operation to incorporate all the results from different submodels. As shown in Fig.~\ref{fig:fusion}, there are 3 fusion operations in MAAM.
 
@@
 
-	The first fusion occurs at the output of OCT Models or Fundus Models.
-In reality, multiple OCT images and Fundus images can be used for ocular disease diagnosis.
+	The first fusion occurs at the output of OCT Model or Fundus Model.
+In real cases, multiple OCT and Fundus images can be used for ocular disease diagnosis.
 Each image goes through one of the Abnormity Models and generates a probability vector.
-To use the probability results from all the images, a maximization fusion is implemented for all the vectors so that the fusion yeilds one OCT abnormity probability vector and one Fundus abnormity probability vector with maximum values.
+To use the probability results from all the images, a maximization fusion is implemented for all the vectors so that the fusion yields one OCT abnormity probability vector and one Fundus abnormity probability vector with maximum values.
 
 	The second fusion occurs at the interface between Abnormity Model and Stage D1.
-A concatenation fusion is implemented for OCT abnormality probability vector and Fundus abnormality probability vector.
+A concatenation fusion is implemented for OCT abnormity probability vector and Fundus abnormity probability vector.
 The fused vector works as an input to all the submodels in Stage D1.
@@
 We concatenation all the severity level vectors to feed the model in Stage D2.
-The fused vector goes through the FC layer and does a softmax operation to yield the final result.
+The fused vector goes through the FC layer and undergoes a softmax operation to yield the final result.
 
@@
 
-	Table: Data source for OCT and Fundus
-	numbered list of sources
-	columns for source number, final column = total number of imgs
-	rows for abnormities
+	The data preparation process is shown in Fig.~\ref{fig:A_data_prep}. First,
+
+	\begin{minipage}[t]{0.4\linewidth}
+		{
+			\fontsize{9}{12}\selectfont
+			{
+				\begin{longtable}{cccccc}
+					\caption{OCT abnormities}
+					\label{tb:OCT_source}\\
+					\toprule
+					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
+					&1&2&3&4&\\
+					\midrule
+					CNV               &2984&/  &/ &/ &2984\\
+					CSC               &/   &102&32&/ &134 \\
+					DME               &2500&/  &/ &/ &2500\\
+					Drusen            &2500&/  &/ &/ &2500\\
+					ERM               &/   &/  &/ &19&19  \\
+					Intraretinal&1097&/  &/ &/ &1097\\
+					MH                &/   &99 &31&/ &130 \\
+					Mactel            &/   &/  &29&/ &29  \\
+					Normal            &5000&/  &/ &/ &5000\\
+					RP                &/   &102&31&/ &133 \\
+					Stargardt         &/   &/  &23&/ &23  \\
+					Subretinal  &1083&/  &/ &/ &1083\\
+					\bottomrule
+				\end{longtable}
+
+				\vspace{0.5cm}
+				\begin{enumerate}
+					\item Normal Disease Database
+					\vspace{-0.2cm}
+
+					\item OpenICPSR
+					\vspace{-0.2cm}
+
+					\item Few-shot
+					\vspace{-0.2cm}
+
+					\item Google Image
+					\vspace{-0.2cm}
+				\end{enumerate}
+
+				\vspace{0.5cm}
+			}
+		}
+	\end{minipage}
+	\begin{minipage}[t]{0.6\linewidth}
+		{
+			\fontsize{9}{12}\selectfont
+			{
+				\begin{longtable}{cccccccc}
+					\caption{Fundus abnormities}
+					\label{tb:Fundus_source}\\
+					\toprule
+					\multirow{2}{*}{Abnormity}&\multicolumn{6}{c}{Source}&\multirow{2}{*}{Total}\\
+					&1&2&3&4&5&6&\\
+					\midrule
+					Cotton  &/  &/ &/ &33 &205&/ &238\\
+					Drusen            &/  &/ &/ &50 &/  &/ &50 \\     
+					Hard    &20 &/ &/ &75 &284&/ &379\\ 
+					Hemorrhage        &13 &66&/ &105&278&/ &462\\     
+					MH                &/  &/ &/ &/  &/  &34&34 \\        
+					Micro   &55 &/ &/ &1  &219&/ &275\\
+					Normal            &100&37&15&/  &/  &/ &152\\      
+					RP                &/  &22&/ &/  &/  &44&66 \\         
+					Vascular&/  &64&/ &14 &/  &/ &78 \\
+
+					\bottomrule
+				\end{longtable}
+
+				\vspace{1cm}
+				\begin{enumerate}
+
+					\item E-ophtha
+					\vspace{-0.2cm}
+
+					\item Kaggle1000
+					\vspace{-0.2cm}
+
+					\item HRF
+					\vspace{-0.2cm}
+
+					\item STARE
+					\vspace{-0.2cm}
+
+					\item EyePACS
+					\vspace{-0.2cm}
+
+					\item Google Image
+					\vspace{-0.2cm}
+
+				\end{enumerate}
+
+				\vspace{0.5cm}
+			}
+		}
+	\end{minipage}
+
+	{
+		\fontsize{9}{12}\selectfont
+		{
+			\begin{longtable}{ccccc}
+				\caption{OCT images CycleGAN selection rate}
+				\label{tb:cycleGAN_selection_rate}\\
+				\toprule
+				Abnormity&Original&Generated&Selected&Selection Rate\\
+				\midrule
+				CSC      &134&1730&3000&57.667\% \\
+				ERM      &19 &1931&3000&64.367\% \\
+				MH       &130&1811&3000&60.367\% \\
+				Mactel   &29 &1900&3000&63.333\% \\
+				RP       &133&1923&3000&64.100\% \\
+				Stargardt&23 &2582&3000&86.067\% \\
+				\bottomrule
+			\end{longtable}
+		}
+	}
 
 	TEXT: CycleGAN
-	Table: selection rates
 	selection criteria
@@
 	explain differences between train and test, OCT and fundus
-
-	Table: all data source
 
@@
 				\toprule
-				Abnormality&Description\\
+				Abnormity&Description\\
 				\toprule
@@
 
-				\multicolumn{1}{l}{Vascular abnormality} & Retinal Vessel Tortuosity.  Retinal Vessel Caliber Changes.  \\
+				\multicolumn{1}{l}{Vascular abnormity} & Retinal Vessel Tortuosity. Retinal Vessel Caliber Changes. \\
 

### 2024-08-28 Paper/Paper.tex
Write data preparation

@@
 
-	The data preparation process is shown in Fig.~\ref{fig:A_data_prep}. First,
+	The data preparation process is shown in Fig.~\ref{fig:A_data_prep}.
+
+	First, we acquire data from publicly available online datasets.
+For abnormities that we have no data of, we search for images on Google Image.
+The numbers of images acquired from each data source are shown in Tables \ref{tb:OCT_source} and \ref{tb:Fundus_source}.
 
@@
 					ERM    &/   &/  &/ &19&19  \\
-					Intraretinal&1097&/  &/ &/ &1097\\
+					IF     &1097&/  &/ &/ &1097\\
 					MH     &/   &99 &31&/ &130 \\
 					Mactel &/   &/  &29&/ &29  \\
-					Normal            &5000&/  &/ &/ &5000\\
+					Healthy&5000&/  &/ &/ &5000\\
 					RP     &/   &102&31&/ &133 \\
-					Stargardt         &/   &/  &23&/ &23  \\
-					Subretinal  &1083&/  &/ &/ &1083\\
+					ST     &/   &/  &23&/ &23  \\
+					SF     &1083&/  &/ &/ &1083\\
 					\bottomrule
@@
 					\midrule
-					Cotton  &/  &/ &/ &33 &205&/ &238\\
+					CWP    &/  &/ &/ &33 &205&/ &238\\
 					Drusen &/  &/ &/ &50 &/  &/ &50 \\     
-					Hard    &20 &/ &/ &75 &284&/ &379\\ 
-					Hemorrhage        &13 &66&/ &105&278&/ &462\\     
+					HE     &20 &/ &/ &75 &284&/ &379\\ 
+					HM     &13 &66&/ &105&278&/ &462\\     
 					MH     &/  &/ &/ &/  &/  &34&34 \\        
-					Micro   &55 &/ &/ &1  &219&/ &275\\
-					Normal            &100&37&15&/  &/  &/ &152\\      
+					MA     &55 &/ &/ &1  &219&/ &275\\
+					Healthy&100&37&15&/  &/  &/ &152\\      
 					RP     &/  &22&/ &/  &/  &44&66 \\         
-					Vascular&/  &64&/ &14 &/  &/ &78 \\
+					VA     &/  &64&/ &14 &/  &/ &78 \\
 
@@
 
+	Then, for OCT images that have less than 1000 images, we use Cycle-GAN to generate new images.
+We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy images to abnormity images, and use it to generate new abnormity images.
+We manually eliminate generated images that look obviously wrong.
+The elimination rate is shown in Table~\ref{tb:cycleGAN_number}.
+We only used Cycle-GAN to generate OCT images because generated fundus images are too blurry and do not display the target abnormities.
+
 	{
@@
 			\begin{longtable}{ccccc}
-				\caption{OCT images CycleGAN selection rate}
-				\label{tb:cycleGAN_selection_rate}\\
+				\caption{OCT images CycleGAN elimination rate}
+				\label{tb:cycleGAN_number}\\
 				\toprule
-				Abnormity&Original&Generated&Selected&Selection Rate\\
+				Abnormity&Original&Generated&Eliminated&Elimination Rate\\
 				\midrule
-				CSC      &134&1730&3000&57.667\% \\
-				ERM      &19 &1931&3000&64.367\% \\
-				MH       &130&1811&3000&60.367\% \\
-				Mactel   &29 &1900&3000&63.333\% \\
-				RP       &133&1923&3000&64.100\% \\
-				Stargardt&23 &2582&3000&86.067\% \\
+				CSC   &134&3000&1270&42.333\% \\
+				ERM   &19 &3000&1069&35.633\% \\
+				MH    &130&3000&1189&39.633\% \\
+				Mactel&29 &3000&1100&36.667\% \\
+				RP    &133&3000&1077&36.900\% \\
+				ST    &23 &3000&418 &13.933\% \\
 				\bottomrule
@@
 	}
-
-	TEXT: CycleGAN
-	selection criteria
-	Why I did not GAN Fundus
 
@@
 
-	Table: abnormities with description (edit the two tables below)
+	Table: abnormities with description (edit the two tables below; ALPHABETICAL ORDER!!!)
 

### 2024-08-28 Paper/Paper.tex
add OCT_Abnormities.png

@@
 	The Abnormity Models are classifiers for abnormities, which are symptoms that can be directly observed in the images.
-The MAAM identifies 11 OCT abnormities and 8 Fundus abnormities, as shown in Fig.~\ref{fig:abnormities}.
+The MAAM identifies 11 OCT abnormities and 8 Fundus abnormities, as shown in Fig.~\ref{fig:OCT_abnormities} and Fig.~\ref{fig:fundus_abnormities}.
 Also refer to ``Appendix'' for more details.
@@
 		\centering
+		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.png}
+		\caption{OCT Abnormities}
+		\vspace{0.3cm}
+		\label{fig:OCT_abnormities}
+	\end{figure}
+
+	\begin{figure}[htbp]
+		\centering
 		\includegraphics[width=\linewidth]{Figs/Temp.png}
-		\caption{OCT and Fundus Abnormities}
+		\caption{Fundus Abnormities}
 		\vspace{0.3cm}
-		\label{fig:abnormities}
+		\label{fig:fundus_abnormities}
 	\end{figure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.png}
+		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.png}
 		\caption{GradCAM with multiple abnormities}

### 2024-08-28 Paper/Paper.tex
write abnormity data prep

@@
 	TEXT: abstract
-
-	\pagebreak
 
@@
 The numbers of images acquired from each data source are shown in Tables \ref{tb:OCT_source} and \ref{tb:Fundus_source}.
+For the links if the images from Google Image, please refer to ``Appendix''.
 
@@
 
-	TEXT: transforms for OCT
-	for train: copy, flip, randomcomb1
-	for test: copy, flip, randomcomb2 -> explain truthfulness
-	explain differences between train and test, OCT and fundus
+	We separate the images, including generated images, into two datasets, one training and the other for testing.
+We implement a set of transformations on the images, including a horizontal flip, a random brightness change from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and a random rotation, which is between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for Fundus images.
+The rotation is only applied for images in the train dataset.
+Eventually, we get 5000 train images and 500 test images for each OCT abnormity, and 3000 train images and 300 test images for each fundus abnormity.
 

### 2024-08-29 Paper/Paper.tex
Update criteria to include abbr.s; edit data prep section

--- 2024-08-28 Paper/Paper.tex
@@
 	First, we acquire data from publicly available online datasets.
-For abnormities that we have no data of, we search for images on Google Image.
-The numbers of images acquired from each data source are shown in Tables \ref{tb:OCT_source} and \ref{tb:Fundus_source}.
+For abnormities with no data found, we search for images on Google Image.
+The numbers of images acquired from each data source are shown in Table~\ref{tb:OCT_source} and Table~\ref{tb:Fundus_source}.
+For the links of the images from Google Image, please refer to ``Appendix''.
 
@@
 
-	Then, for OCT images that have less than 1000 images, we use Cycle-GAN to generate new images.
-We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy images to abnormity images, and use it to generate new abnormity images.
+	Then, for OCT abnormities with less than 1000 images, we use Cycle-GAN to generate new images.
+We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.
 We manually eliminate generated images that look obviously wrong.
-The elimination rate is shown in Table~\ref{tb:cycleGAN_number}.
-We only used Cycle-GAN to generate OCT images because generated fundus images are too blurry and do not display the target abnormities.
+The elimination rates are shown in Table~\ref{tb:cycleGAN_number}.
+We did not use Cycle-GAN to generate fundus images because generated fundus images are too blurry and do not display the desired abnormities.
 
@@
 			\begin{longtable}{ccccc}
-				\caption{OCT images CycleGAN elimination rate}
+				\caption{OCT images CycleGAN elimination rates}
 				\label{tb:cycleGAN_number}\\
@@
 
-	TEXT: transforms for OCT
-	for train: copy, flip, randomcomb1
-	for test: copy, flip, randomcomb2 -> explain truthfulness
-	explain differences between train and test, OCT and fundus
+	We separate the images, including generated images, into training and testing datasets.
+We implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images.
+The rotation is only applied to images in the train dataset.
+Eventually, we get 5000 train images and 500 test images for each OCT abnormity, and 3000 train images and 300 test images for each fundus abnormity.
 
@@
 
+	We
+
 	TEXT: intro to five-fold train/valid (reason for using this?)
-
-	TEXT: starting point of fine-tuning
-	prevent overfitting
-
 	TEXT: crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...

### 2024-08-29 Paper/Paper.tex
add Fundus_Abnormities.png
write abnormity model training

@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/Temp.png}
+		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.png}
 		\caption{Fundus Abnormities}
@@
 From the deduction criteria, we determine the number of abnormities for one disease and use the number to define the severity levels.
-For example, there are totally 5 abnormities that are present in the disease ``Referable DR'': OCT abnormity ``DME'' and Fundus abnormities ``Hemorrhage'', ``Vascular Abnormity'', ``Microaneurysm'', and ``Cotton Wool Patch''.
+For example, there are totally 5 abnormities that are present in the disease ``rDR'': OCT abnormity ``DME'' and Fundus abnormities ``HM'', ``VA'', ``MA'', and ``CWP''.
 Therefore, taking into account the healthy status, we end up with 6 severity levels for disease ``Referable DR''.
@@
 
-	We
+	We train the models on a desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM.
+The code is written with PyTorch in an Anaconda environment.
+For the link to the GitHub repository, please refer to ``Appendix''.
+We use cross entropy loss, ADAM optimizer with learning rate 0.001, and a batch size of 32.
+We perform five-fold cross-validation during training.
 
-	TEXT: intro to five-fold train/valid (reason for using this?)
-	TEXT: crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
-	conda, PyTorch;
-	desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM
+	For both OCT and Fundus Models, we employ a strategy of transfer learning to finetuning.
+
+	In the transfer learning phase, we use pretrained weights from ImageNet.
+We freeze the weights in all the convolutional layers and only allow the weights in the final FC layer to learn.
+We train the model for 100 epochs.
+Every 10 epochs, we save the weights of the model with the best validation accuracy.
+Of all the saved models, we find the model with the best overall performance on the validation and testing datasets, and start finetuning based on this model.
+
+	In the finetuning phase, we start on the best model in the transfer learning phase, unfreezing all weights in the model.
+We train the model for 30 epochs.
+Similarly, we save the weights of the model with the best validation accuracy every 10 epochs, and find the model with the best overall performance.
+Finally, we compare the performance of the best model in the transfer learning phase and the best one in the finetuning phase to determine the final model.
+
+	For OCT
+
+	The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train}.
 

### 2024-08-29 Paper/Paper.tex
add model_overview.png
plot combined acc; continue writing training section

@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/Temp.png}
+		\includegraphics[width=\linewidth]{Figs/model_overview.png}
 		\caption{Model Overview}
@@
 We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.
-We manually eliminate generated images that look obviously wrong.
-The elimination rates are shown in Table~\ref{tb:cycleGAN_number}.
-We did not use Cycle-GAN to generate fundus images because generated fundus images are too blurry and do not display the desired abnormities.
+We go through all generated images and adopt those that clearly display only the desired abnormities.
+The adoption rates are shown in Table~\ref{tb:cycleGAN_number}.
+We did not use Cycle-GAN to generate fundus images because generated fundus images are too blurry and do not show the desired abnormities.
 
@@
 			\begin{longtable}{ccccc}
-				\caption{OCT images CycleGAN elimination rates}
+				\caption{OCT images CycleGAN adoption rates}
 				\label{tb:cycleGAN_number}\\
 				\toprule
-				Abnormity&Original&Generated&Eliminated&Elimination Rate\\
+				Abnormity&Original&Generated&Adopted&Adoption Rate\\
 				\midrule
-				CSC   &134&3000&1270&42.333\% \\
-				ERM   &19 &3000&1069&35.633\% \\
-				MH    &130&3000&1189&39.633\% \\
-				Mactel&29 &3000&1100&36.667\% \\
-				RP    &133&3000&1077&36.900\% \\
-				ST    &23 &3000&418 &13.933\% \\
+				CSC   &134&3000&1730&58.667\% \\
+				ERM   &19 &3000&1931&64.367\% \\
+				MH    &130&3000&1811&60.367\% \\
+				Mactel&29 &3000&1900&63.333\% \\
+				RP    &133&3000&1923&63.100\% \\
+				ST    &23 &3000&2572&86.067\% \\
 				\bottomrule
@@
 
-	We separate the images, including generated images, into training and testing datasets.
+	We separate the images, including generated images, into training and test datasets.
 We implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images.
@@
 
-	For both OCT and Fundus Models, we employ a strategy of transfer learning to finetuning.
+	For the Abnormity Models, we employ a strategy of transfer learning to finetuning.
 
@@
 Every 10 epochs, we save the weights of the model with the best validation accuracy.
-Of all the saved models, we find the model with the best overall performance on the validation and testing datasets, and start finetuning based on this model.
+For all the saved models, we calculate a overall accuracy, which is the weighted average of validation and test accuracy, to find the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.
 
@@
 We train the model for 30 epochs.
-Similarly, we save the weights of the model with the best validation accuracy every 10 epochs, and find the model with the best overall performance.
-Finally, we compare the performance of the best model in the transfer learning phase and the best one in the finetuning phase to determine the final model.
+Similarly, we save the weights of the model with the best validation accuracy every 10 epochs, and find the model with the highest overall accuracy.
+Finally, we compare the overall accuracies of the best model in the transfer learning phase and the finetuning phase to determine the final model.
 
-	For OCT
-
-	The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train}.
+	For both OCT and Fundus Models, we trained 4 commonly used CNNs: ResNet152, ResNet50, ResNet18, and VGG16.
+The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train} for all of the CNNs.
 
@@
 
-	Graph bar chart for comparison?
-
-	TEXT: comments
+	{
+		\fontsize{9}{12}\selectfont
+		{
+			\begin{table}
+				\centering
+				\caption{Validation accuracies}
+				\label{tb:A_accuracies}
+				\begin{tabular}{ccccc}
+					\toprule
+					Model&ResNet152&ResNet50&ResNet18&VGG16\\
+					\midrule
+					OCT Model   &91.906\%&\textbf{92.183\%}&91.011\%&89.744\% \\
+					Fundus Model&\textbf{89.111\%}&88.926\%&86.605\%&79.185\% \\
+					\bottomrule
+				\end{tabular}
+			\end{table}
+		}
+	}
 

### 2024-08-29 ODADS/Code/Results/abnormity_loss_and_acc.py

@@ -41,6 +41,7 @@ def get_loss_and_acc(net_name, type, starting_epoch = 0):
     train_losses = [float(row[4]) for row in train_rs]
     epoch_test = [int(row[0]) + starting_epoch for row in test_rs]
     test_acc = [float(row[3]) for row in test_rs]
+    combined_acc = [(test_acc[i] + 2 * valid_acc[epoch_train.index(epoch_test[i])]) / 3 for i in range(len(epoch_test))]
     
     return {
         "epoch train": epoch_train,
@@ -51,7 +52,8 @@ def get_loss_and_acc(net_name, type, starting_epoch = 0):
         "epoch test": epoch_test,
         "test acc": test_acc,
         "best epoch": best_epoch,
-        "best acc": best_acc
+        "best acc": best_acc,
+        "combined acc": combined_acc
     }
 
 def plot_loss_and_acc_alt(): # (2x1) x (2x2) x (2x1)

### 2024-08-29 Paper/Paper.tex
add criteria.png
Finish training section draft

@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/Temp.png}
+		\includegraphics[width=0.8\linewidth]{Figs/criteria.png}
 		\caption{Abnormity-to-disease Deduction Criteria}
@@
 Every 10 epochs, we save the weights of the model with the best validation accuracy.
-For all the saved models, we calculate a overall accuracy, which is the weighted average of validation and test accuracy, to find the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.
+In order to prevent overfitting on the train dataset, we introduce a measure called overall accuracy, which is the weighted average of validation and test accuracy.
+For all the saved models, we calculate the overall accuracy to find the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.
 
@@
 	\end{figure}
+
+	We can observe that finetuning can significantly increase the model accuracy and, therefore, all the final models are finetuned models.
+As shown in Table~\ref{tb:A_accuracies}, the best CNN for OCT Model is ResNet50 and the best for Fundus Model is ResNet152.
+ResNet50 may have performed better than ResNet152 on OCT because it has fewer parameters and is less likely to overfit on OCT images, which has fewer and clearer traits; on the other hand, ResNet152 is better on fundus possibly because it has more parameters and can better discern the complex traits in fundus images.
+ResNet18 may have too few parameters, so it performs less well over all; and VGG16 sometimes experiences large dips in accuracy, possibly due to gradient vanishing, and this impairs its performance.
+Therefore, we will use ResNet50 for OCT Model and ResNet152 for Fundus Model.
 

### 2024-08-29 ODADS/Code/Results/abnormity_loss_and_acc.py

@@ -161,14 +161,17 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
             rsf["valid losses"].insert(0, rst["valid losses"][continuation_epoch - 1])
             rsf["epoch test"].insert(0, continuation_epoch)
             rsf["test acc"].insert(0, rst["test acc"][rst["epoch test"].index(continuation_epoch)])
+            rsf["combined acc"].insert(0, rst["combined acc"][rst["epoch test"].index(continuation_epoch)])
             
             acc_ax = fig.add_subplot(sub_grid[0, 0])
             acc_ax.plot(rst["epoch train"], rst["train acc"], color='blue')
             acc_ax.plot(rsf["epoch train"], rsf["train acc"], color='blue')
             acc_ax.plot(rst["epoch train"], rst["valid acc"], color='red')
             acc_ax.plot(rsf["epoch train"], rsf["valid acc"], color='red')
-            acc_ax.plot(rst["epoch test"], rst["test acc"], color='green')
-            acc_ax.plot(rsf["epoch test"], rsf["test acc"], color='green')
+            #acc_ax.plot(rst["epoch test"], rst["test acc"], color='green')
+            #acc_ax.plot(rsf["epoch test"], rsf["test acc"], color='green')
+            acc_ax.plot(rst["epoch test"], rst["combined acc"], color='green')
+            acc_ax.plot(rsf["epoch test"], rsf["combined acc"], color='green')
             
             loss_ax = fig.add_subplot(sub_grid[1, 0])
             loss_ax.plot(rst["epoch train"], rst["train losses"], color='blue')

### 2024-08-29 Paper/Paper.tex
use pdf instead of png image.
Delete fig for data prep
edit data prep

@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/model_overview.png}
+		\includegraphics[width=\linewidth]{Figs/model_overview.pdf}
 		\caption{Model Overview}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.png}
+		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
 		\caption{OCT Abnormities}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.png}
+		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
 		\caption{Fundus Abnormities}
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{Figs/criteria.png}
+		\includegraphics[width=0.8\linewidth]{Figs/criteria.pdf}
 		\caption{Abnormity-to-disease Deduction Criteria}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/Temp.png}
+		\includegraphics[width=\linewidth]{Figs/fusion.pdf}
 		\caption{Fusion}
@@
 
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/Temp.png}
-		\caption{Data preparation for abnormity models}
-		\vspace{0.3cm}
-		\label{fig:A_data_prep}
-	\end{figure}
-
-	The data preparation process is shown in Fig.~\ref{fig:A_data_prep}.
-
-	First, we acquire data from publicly available online datasets.
-For abnormities with no data found, we search for images on Google Image.
+	The images and labels used for training are mainly downloaded from public databases, but some abnormities are not included in these databases.
+For those abnormities, we use the search engine as an additional data source and search for images.
 The numbers of images acquired from each data source are shown in Table~\ref{tb:OCT_source} and Table~\ref{tb:Fundus_source}.
-For the links of the images from Google Image, please refer to ``Appendix''.
+As to the links of the images from the search engine, refer to ``Appendix''.
 
@@
 
-					\item Google Image
+					\item Search engine
 					\vspace{-0.2cm}
@@
 
-	Then, for OCT abnormities with less than 1000 images, we use Cycle-GAN to generate new images.
+	For OCT abnormities with less than 1000 images, we use Cycle-GAN to generate new images.
 We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.
-We go through all generated images and adopt those that clearly display only the desired abnormities.
+We go through all generated images and adopt those that clearly display only the abnormity of interest.
 The adoption rates are shown in Table~\ref{tb:cycleGAN_number}.
-We did not use Cycle-GAN to generate fundus images because generated fundus images are too blurry and do not show the desired abnormities.
+Fundus images are not generated using Cycle-GAN because generated fundus images are too blurry; in addition, fundus abnormities are usually less salient than OCT ones and cannot be properly learned by Cycle-GAN, given that we only have a small number of fundus images.
 
@@
 
-	We separate the images, including generated images, into training and test datasets.
-We implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images.
+	We separate the images, including generated images, into training and test datasets, and implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images.
 The rotation is only applied to images in the train dataset.
@@
 The code is written with PyTorch in an Anaconda environment.
-For the link to the GitHub repository, please refer to ``Appendix''.
+For the link to the GitHub repository, refer to ``Appendix''.
 We use cross entropy loss, ADAM optimizer with learning rate 0.001, and a batch size of 32.
@@
 
-	We can observe that finetuning can significantly increase the model accuracy and, therefore, all the final models are finetuned models.
+	We can observe that finetuning significantly increases the model accuracy and, therefore, all the final models are finetuned models.
 As shown in Table~\ref{tb:A_accuracies}, the best CNN for OCT Model is ResNet50 and the best for Fundus Model is ResNet152.
-ResNet50 may have performed better than ResNet152 on OCT because it has fewer parameters and is less likely to overfit on OCT images, which has fewer and clearer traits; on the other hand, ResNet152 is better on fundus possibly because it has more parameters and can better discern the complex traits in fundus images.
+ResNet50 performed better than ResNet152 on OCT, possibly because it has fewer parameters and is less likely to overfit on OCT images, which has fewer and clearer traits; on the other hand, ResNet152 is better on fundus possibly because it has more parameters and can better discern the complex traits in fundus images.
 ResNet18 may have too few parameters, so it performs less well over all; and VGG16 sometimes experiences large dips in accuracy, possibly due to gradient vanishing, and this impairs its performance.
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.png}
+		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.pdf}
 		\caption{GradCAM}
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.png}
+		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
 		\caption{GradCAM with multiple abnormities}

### 2024-08-29 Paper/Paper.tex
revise background and overview.

@@
 	\section{Background}
-
-	TEXT: Edit background
-
 	Ocular diseases can be diagnosed through various methods, including using optical coherence tomography (OCT) and color fundus images.
@@
 And for segmenting images and finding abnormalities, U-net is widely used \autocite{Ronneberger_Fischer_Brox_2015}.
-In training CNNs, most studies use transferred learning, which consists of three steps: learning, fine-tuning, and validation.
+With regards to training CNNs, most studies use transferred learning, which consists of three steps: learning, fine-tuning, and validation.
 
 	Some studies directly predict the disease from OCT images.
-	\authyear{li2019deep} used ResNet to analyze OCT images and distinguish between choroidal neovascularization (CNV), diabetic macular edema (DME), drusen, and normal eyes.
+	\authyear{li2019deep} used ResNet to analyze OCT images and distinguish between choroidal neovascularization (CNV), diabetic macular edema (DME), drusen, and healthy eyes.
 In addition, they performed occlusion testing to find out the regions that are the most important in diagnosis \autocite{li2019deep}.
 	\authyear{yoo2021feasibility} used generative adversarial network (GAN) and Inception-v3 together with a few-shot dataset to investigate the feasibility of improving OCT diagnosis of rare ocular diseases \autocite{yoo2021feasibility}.
-They cleverly handled the issues of training image shortage and data imbalance by creating ocular disease OCT images from healthy OCT images.
+They handled the issues of training image shortage and data imbalance by creating ocular disease OCT images from healthy OCT images.
 \authyear{Kermany2018} conducts medical diagnosis and identifies treatable diseases by image-based deep learning.
@@
 It considers both OCT and color fundus image inputs.
-In addition, it simulates the decision-making process of ophthalmologists when they examine patients, i.e., first identifying the abnormities, and then deducing the disease.
-The model is designed in a way that partly opens up the ``black box'' of DL and presents more interpretable information for the reference of ophthalmologists.
+In addition, it simulates the decision-making process of ophthalmologists when they examine patients, namely, first identifying the abnormities, and then deducing the disease.
+The model is designed in a way that partly opens up the ``black box'' of DL and presents more interpretable information to ophthalmologists for the reference.
 
@@
 	The structure of the MAAM is shown in Fig.~\ref{fig:3_parts}.
-It consists of 2 submodels: the Abnormity Models and the Diagnosis Model.
-We input multiple OCT and fundus images to the Abnormity Models, and output the classification of abnormities as inputs to the Diagnosis Model, which generates disease probabilities as the final result.
+It consists of 2 submodels: the Abnormity Model and the Diagnosis Model.
+We input multiple OCT and fundus images to the Abnormity Models, and output the classification of abnormities as an input to the Diagnosis Model, which yields disease probabilities as the final result.
 
@@
 
-	The Abnormity Models are classifiers for abnormities, which are symptoms that can be directly observed in the images.
+	The Abnormity Models are de facto classifiers for abnormities, which are symptoms that can be directly observed in the images.
 The MAAM identifies 11 OCT abnormities and 8 Fundus abnormities, as shown in Fig.~\ref{fig:OCT_abnormities} and Fig.~\ref{fig:fundus_abnormities}.
-Also refer to ``Appendix'' for more details.
+The abbreviations and detail information of abnormities and diseases are tabulated in ``Appendix''.
 
@@
 
-	The Abnormity Models also contain 2 submodels: the OCT Model and the Fundus Model, which identify OCT and fundus abnormities, respectively.
+	The Abnormity Models also contain 2 submodels: the OCT Model and the Fundus Model, which classify OCT and fundus abnormities, respectively.
 Both of the submodels leverage CNNs with modified final fully-connected (FC) layers.
@@
 In order to normalize the output vector, we perform the softmax operation.
-After an image is inputted into one of the submodels, the submodel returns a probability vector for all the abnormities.
+Each submodel outputs a probability vector for all the abnormities.
 
@@
 There are multiple submodels in Stage D1 and each one corresponds to one disease.
-From the deduction criteria, we determine the number of abnormities for one disease and use the number to define the severity levels.
+Based on the deduction criteria, we determine the number of abnormities for one disease and use the number to define the severity levels.
 For example, there are totally 5 abnormities that are present in the disease ``rDR'': OCT abnormity ``DME'' and Fundus abnormities ``HM'', ``VA'', ``MA'', and ``CWP''.
-Therefore, taking into account the healthy status, we end up with 6 severity levels for disease ``Referable DR''.
+Therefore, taking into account the healthy status, we end up with 6 severity levels for disease ``rDR''.
 
-	We use the fused vector as an input for each submodels in Stage D1, and have the vector pass a FC layer with softmax operation to generate severity level probability vectors.
+	We use the fused vector as an input for each submodels in Stage D1, and have the vector go through a FC layer with softmax operation to yield severity level probability vectors.
 
@@
 	In Stage D2, we determine the final disease probability vector.
-Similarly we use a fused vector from the outputs of submodels in Stage D1, and have the vector pass a FC layer with softmax operation.
+Similarly, we use a fused vector from the outputs of submodels in Stage D1, and have the vector go through a FC layer with softmax operation.
 The result presents potential diseases that can be referenced by ophthalmologists.
@@
 
-	In the MAAM, we leverage the fusion operation to incorporate all the results from different submodels. As shown in Fig.~\ref{fig:fusion}, there are 3 fusion operations in MAAM.
+	In the MAAM, we leverage the fusion operation to incorporate all the results from different submodels. As shown in Fig.~\ref{fig:fusion}, there are totally 3 fusion operations in MAAM.
 
@@
 	The first fusion occurs at the output of OCT Model or Fundus Model.
-In real cases, multiple OCT and Fundus images can be used for ocular disease diagnosis.
-Each image goes through one of the Abnormity Models and generates a probability vector.
+In real scenarios, multiple OCT and Fundus images can be used for ocular disease diagnosis.
+Each image goes through either the OCT Model or the Fundus Model to yield a probability vector.
 To use the probability results from all the images, a maximization fusion is implemented for all the vectors so that the fusion yields one OCT abnormity probability vector and one Fundus abnormity probability vector with maximum values.

### 2024-08-29 Paper/Paper.tex
write gradcam

--- 2024-08-29 Paper/Paper.tex
@@
 
-	TEXT: accuracy; explain top-probs method
+	Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values obtained when the Abnormity Models are tested on the test dataset.
+Fig.~\ref{fig:A_ROC} shows the ROCs of each abnormity.
+From the tables and the figure, we can see that the performance of the OCT Model is significantly better than that of the Fundus Model, likely because fundus abnormities tend to be subtler and there are more fundus images that have multiple abnormities.
 
@@
 		\centering
+		\includegraphics[width=\linewidth]{Figs/abnormity_ROC.pdf}
+		\caption{A ROC}
+		\vspace{0.3cm}
+		\label{fig:A_ROC}
+	\end{figure}
+
+	We can further confirm that overlapping abnormities have a large impact by looking at the confusion matrices (Fig.~\ref{fig:A_conf_mat}) and the t-SNE graphs (Fig.~\ref{fig:A_tSNE}).
+During training, most of the abnormities are well-separated.
+However, this is not the case during testing.
+On the t-SNE graph, the OCT Model still shows clear separation of clusters, many of which, however, are mingled with data points that do not belong to the cluster.
+This may be because some OCT abnormities resemble each other.
+For example, ``IF'', ``DME'' and ``Mactel'' may look very similar.
+As to the Fundus Model, there are fewer small distinct clusters and there is a large cluster instead.
+This is likely due to the fact that many fundus images contain multiple abnormities.
+For example, a patient with the disease ``rDR'' shows the abnormities ``CWP'', ``HE'', ``HM'' and ``VA''.
+Therefore, many abnormities tend to appear together, impeding classification of abnormities.
+
+	\begin{figure}[htbp]
+		\centering
 		\includegraphics[width=0.8\linewidth]{Figs/abnormity_confusion_matrix.pdf}
@@
 	\end{figure}
-
-	TEXT: analyze which abnormities are commonly confused, and the effect on the numerical results
 
@@
 
-	TEXT: which abnormities are "close"
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/abnormity_ROC.pdf}
-		\caption{A ROC}
-		\vspace{0.3cm}
-		\label{fig:A_ROC}
-	\end{figure}
-
-	TEXT: comparison to other studies
-
 	\begin{figure}[htbp]
@@
 	\end{figure}
+
 	\begin{figure}[htbp]
@@
 	\end{figure}
+
+	Considering that one image 050AO78.017\%, 152AF71.889\%
 

### 2024-08-29 Paper/Paper.tex
add bib ref.

@@
 Both of the submodels leverage CNNs with modified final fully-connected (FC) layers.
-We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18 and VGG16, and choose the best one for each submodel.
+We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18\autocite{He_Zhang_Ren_Sun_2016} and VGG16\autocite{Simonyan_Zisserman_2015}, and choose the best one for each submodel.
 The final FC layer in each CNN is modified so that the size of its output vector is equal to the number of OCT or fundus abnormities.
@@
 
-	For OCT abnormities with less than 1000 images, we use Cycle-GAN to generate new images.
+	For OCT abnormities with less than 1000 images, we use Cycle-GAN\autocite{Zhu_Park_Isola_Efros_2020} to generate new images.
 We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.

### 2024-08-29 Paper/Paper.tex
write about gradcam

@@
 
+	We can use Grad-CAM to highlight areas on the image that make a large contribution to the final classification.
+If the model had been trained correctly, this would be equivalent to highlighting the abnormity.
+Fig.~\ref{fig:gradCAM} shows some examples.
+Furthermore, Grad-CAM can highlight a designated abnormity, so it may be able to highlight multiple abnormities on one image, as shown in Fig.~\ref{fig:gradCAM_multi_abnormity}.
+
 	\begin{figure}[htbp]
@@
 
-	Considering that one image 050AO78.017\%, 152AF71.889\%
+	Fig.~\ref{fig:gradCAM_multi_abnormity} demonstrates that the Abnormity Models may be able to correctly identify multiple abnormities on an image.
+Knowning that OCT and fundus images often do include more than one abnormities, we employ a method to determine the codominant abnormities.
+We input an image to the Abnormity Models and get the abnormity probabilities vector, and we take the highest probability.
+050AO78.017\%, 152AF71.889\%
 

### 2024-08-29 Paper/Paper.tex
Write about dominant-probs method

@@
 
-	We can use Grad-CAM to highlight areas on the image that make a large contribution to the final classification.
+	We can use Grad-CAM to highlight areas on the image that make a large contribution to the final classification \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra}.
 If the model had been trained correctly, this would be equivalent to highlighting the abnormity.
@@
 	Fig.~\ref{fig:gradCAM_multi_abnormity} demonstrates that the Abnormity Models may be able to correctly identify multiple abnormities on an image.
-Knowning that OCT and fundus images often do include more than one abnormities, we employ a method to determine the codominant abnormities.
-We input an image to the Abnormity Models and get the abnormity probabilities vector, and we take the highest probability.
+Knowing that OCT and fundus images often do include more than one abnormity, we employ a method to determine the dominant abnormities.
+We input an image to the Abnormity Models and get the abnormity probabilities vector.
+If the abnormity with the highest probability has probability greater than 0.9, then we regard it as dominant; if not, we take the abnormity with the second high probability, and if the sum of the two probabilities is greater than 0.9, we regard them as codominant; we continue taking the abnormity with the next high probability until either the sum of probabilities reaches 0.9, or the number of abnormities reaches the maximum, which is 4.
 050AO78.017\%, 152AF71.889\%

### 2024-08-29 Paper/Paper.tex
add autocite.

@@
 \usepackage{algpseudocode}
+\usepackage{enumitem}
 \usepackage[style=ieee,sorting=nyt]{biblatex}
@@
 Both of the submodels leverage CNNs with modified final fully-connected (FC) layers.
-We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18\autocite{He_Zhang_Ren_Sun_2016} and VGG16\autocite{Simonyan_Zisserman_2015}, and choose the best one for each submodel.
+We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18 \autocite{He_Zhang_Ren_Sun_2016} and VGG16 \autocite{Simonyan_Zisserman_2015}, and choose the best one for each submodel.
 The final FC layer in each CNN is modified so that the size of its output vector is equal to the number of OCT or fundus abnormities.
@@
 	The images and labels used for training are mainly downloaded from public databases, but some abnormities are not included in these databases.
-For those abnormities, we use the search engine as an additional data source and search for images.
+For those abnormities, we use the search engine as an additional data source to get images.
 The numbers of images acquired from each data source are shown in Table~\ref{tb:OCT_source} and Table~\ref{tb:Fundus_source}.
@@
 				\begin{enumerate}
-					\item Normal Disease Database
+					\item Normal Disease Database \autocite{Kermany_database}
 					\vspace{-0.2cm}
 
-					\item OpenICPSR
+					\item OCTID \autocite{Gholami_Roy_Parthasarathy_Lakshminarayanan_2020}
 					\vspace{-0.2cm}
 
-					\item Few-shot
+					\item Few-shot \autocite{Yoo_2020}
 					\vspace{-0.2cm}
@@
 				\vspace{1cm}
-				\begin{enumerate}
+				\begin{enumerate}[left=1.5cm]
 
-					\item E-ophtha
+					\item E-ophtha \autocite{E_ophtha}.
 					\vspace{-0.2cm}
 
-					\item Kaggle1000
+					\item Kaggle1000 \autocite{1000Fundus_Pytorch_TransferLearning}
 					\vspace{-0.2cm}
 
-					\item HRF
+					\item HRF \autocite{HRF_2013}
 					\vspace{-0.2cm}
 
-					\item STARE
+					\item STARE \autocite{STARE}
 					\vspace{-0.2cm}
 
-					\item EyePACS
+					\item EyePACS \autocite{DR_dataset}
 					\vspace{-0.2cm}
@@
 
-	For OCT abnormities with less than 1000 images, we use Cycle-GAN\autocite{Zhu_Park_Isola_Efros_2020} to generate new images.
+	For OCT abnormities with less than 1000 images, we use Cycle-GAN \autocite{Zhu_Park_Isola_Efros_2020} to generate new images.
 We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.

### 2024-08-29 Paper/Paper.tex
add Grad-CAM's autocite.

@@
 
-	We can use Grad-CAM to highlight areas on the image that make a large contribution to the final classification \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra}.
+	We can use Grad-CAM \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra} to highlight areas on the image that make a large contribution to the final classification.
 If the model had been trained correctly, this would be equivalent to highlighting the abnormity.

### 2024-08-29 Paper/Paper.tex
finish abnormity models results draft

--- 2024-08-29 Paper/Paper.tex
@@
 	Fig.~\ref{fig:gradCAM_multi_abnormity} demonstrates that the Abnormity Models may be able to correctly identify multiple abnormities on an image.
-Knowing that OCT and fundus images often do include more than one abnormity, we employ a method to determine the dominant abnormities.
+Knowing that OCT and fundus images often do include more than one abnormity, we employ a method to determine the codominant abnormities.
 We input an image to the Abnormity Models and get the abnormity probabilities vector.
-If the abnormity with the highest probability has probability greater than 0.9, then we regard it as dominant; if not, we take the abnormity with the second high probability, and if the sum of the two probabilities is greater than 0.9, we regard them as codominant; we continue taking the abnormity with the next high probability until either the sum of probabilities reaches 0.9, or the number of abnormities reaches the maximum, which is 4.
-050AO78.017\%, 152AF71.889\%
+If the abnormity with the highest probability has probability greater than 0.9, it is regarded as dominant; if not, we continue taking the abnormity with the next high probability until either the sum of the probabilities of the chosen abnormities reaches 0.9, or the number of abnormities reaches the maximum, which is 4, and all the chosen abnormities are regarded as codominant.
+
+	This codominant abnormities method allows the Abnormity Models to identify multiple abnormities.
+For example, the fundus image in Fig.~\ref{fig:gradCAM_multi_abnormity} only has ground truth label ``HE'', but the Fundus Model correctly predicts that it has codominant abnormities ``HE'' and ``HM''.
 

### 2024-08-29 Paper/Paper.tex
revise Section training.

@@
 
-	We separate the images, including generated images, into training and test datasets, and implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images.
+	We split the images, including generated images, into training and test datasets, and implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images.
 The rotation is only applied to images in the train dataset.
@@
 
-	We train the models on a desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256G of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48 VRAM.
+	The model training is on a desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256GB of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48GB VRAM.
+The training uses cross entropy loss, ADAM optimizer with learning rate 0.001, a batch size of 32 and five-fold cross-validation.
 The code is written with PyTorch in an Anaconda environment.
-For the link to the GitHub repository, refer to ``Appendix''.
-We use cross entropy loss, ADAM optimizer with learning rate 0.001, and a batch size of 32.
-We perform five-fold cross-validation during training.
+Refer to ``Appendix'' for the link to the code repository on GitHub.
+
+	\vspace{0.3cm}
 
@@
 
-	In the transfer learning phase, we use pretrained weights from ImageNet.
-We freeze the weights in all the convolutional layers and only allow the weights in the final FC layer to learn.
-We train the model for 100 epochs.
-Every 10 epochs, we save the weights of the model with the best validation accuracy.
+	In the transfer learning phase, pretrained weights from ImageNet \autocite{Krizhevsky_Sutskever_Hinton_2017} are used.
+We freeze the weights in all the convolutional layers and only vary the weights in the final FC layer.
+The training lasts for 100 epochs.
+Every 10 epochs, weights of the model with the best validation accuracy are saved.
 In order to prevent overfitting on the train dataset, we introduce a measure called overall accuracy, which is the weighted average of validation and test accuracy.
-For all the saved models, we calculate the overall accuracy to find the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.
+For all the saved models, we calculate the overall accuracy to select the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.
 
-	In the finetuning phase, we start on the best model in the transfer learning phase, unfreezing all weights in the model.
+	In the finetuning phase, we start from the best model in the transfer learning phase, unfreezing all weights in the model.
 We train the model for 30 epochs.
 Similarly, we save the weights of the model with the best validation accuracy every 10 epochs, and find the model with the highest overall accuracy.
-Finally, we compare the overall accuracies of the best model in the transfer learning phase and the finetuning phase to determine the final model.
+Finally, we compare the overall accuracies of the best model in the transfer learning phase and the finetuning phase to determine the best model of all.
 
 	For both OCT and Fundus Models, we trained 4 commonly used CNNs: ResNet152, ResNet50, ResNet18, and VGG16.
-The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train} for all of the CNNs.
+The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train}.
 
@@
 
+	\vspace{0.3cm}
+
 	We can observe that finetuning significantly increases the model accuracy and, therefore, all the final models are finetuned models.
@@
 ResNet18 may have too few parameters, so it performs less well over all; and VGG16 sometimes experiences large dips in accuracy, possibly due to gradient vanishing, and this impairs its performance.
-Therefore, we will use ResNet50 for OCT Model and ResNet152 for Fundus Model.
+
+	\vspace{0.2cm}
+
+	After all the training and comparisons, we determine to use a finetuned model with ResNet50 for OCT Model and a finetuned model with ResNet152 for Fundus Model.
 

### 2024-08-29 Paper/Paper.tex
write diagnosis model
revise test.

@@
 
-	Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values obtained when the Abnormity Models are tested on the test dataset.
+	Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values on the test dataset.
 Fig.~\ref{fig:A_ROC} shows the ROCs of each abnormity.
-From the tables and the figure, we can see that the performance of the OCT Model is significantly better than that of the Fundus Model, likely because fundus abnormities tend to be subtler and there are more fundus images that have multiple abnormities.
+The results show that the performance of the OCT Model is significantly better than that of the Fundus Model.
+Fundus abnormities tend to be less prominent, since the abnormity on fundus image are usually quite small and scattered.
+Moreover, one fundus image usually contains more than one abnormities, while most OCT images contain only one abnormity on each image.
+Also given that we have less fundus images than OCT ones, the difficulties for fundus classification increases.
 
@@
 
-	We can further confirm that overlapping abnormities have a large impact by looking at the confusion matrices (Fig.~\ref{fig:A_conf_mat}) and the t-SNE graphs (Fig.~\ref{fig:A_tSNE}).
+	The confusion matrices are shown in Fig.~\ref{fig:A_conf_mat}) and the t-SNE graphs are shown in Fig.~\ref{fig:A_tSNE}.
 During training, most of the abnormities are well-separated.
@@
 On the t-SNE graph, the OCT Model still shows clear separation of clusters, many of which, however, are mingled with data points that do not belong to the cluster.
-This may be because some OCT abnormities resemble each other.
+This is because some OCT abnormities resemble each other.
 For example, ``IF'', ``DME'' and ``Mactel'' may look very similar.
@@
 
+	In Stage D1, we prepare data
+
 	TEXT: how to choose data (with an example)
@@
 
-	TEXT: hyperparameters, software, hardware
+	%The model training is on a desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256GB of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48GB VRAM.
+The training uses cross entropy loss, ADAM optimizer with learning rate 0.001, a batch size of 32 and five-fold cross-validation.
+The code is written with PyTorch in an Anaconda environment.
+Refer to ``Appendix'' for the link to the code repository on GitHub.
 

### 2024-08-29 Paper/Paper.tex
again
cont.

@@
 	Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values on the test dataset.
-Fig.~\ref{fig:A_ROC} shows the ROCs of each abnormity.
-The results show that the performance of the OCT Model is significantly better than that of the Fundus Model.
-Fundus abnormities tend to be less prominent, since the abnormity on fundus image are usually quite small and scattered.
-Moreover, one fundus image usually contains more than one abnormities, while most OCT images contain only one abnormity on each image.
+Fig.~\ref{fig:A_ROC} shows the ROCs, Fig.~\ref{fig:A_conf_mat} shows the confusion matrices and Fig.~\ref{fig:A_tSNE} shows the t-SNE graphs for each abnormity.
+
+	The OCT Model tends to be overfitting, while the Fundus Model cannot reach a satisfying level in terms of DL.
+Overall, the performance of the OCT Model is significantly better than that of the Fundus Model.
+
+	Fundus abnormities tend to be less prominent than those of OCT, since the abnormity in fundus image are usually quite small and scattered.
+Moreover, one fundus image usually contains more than one abnormity, while most OCT images contain only one abnormity on each image.
 Also given that we have less fundus images than OCT ones, the difficulties for fundus classification increases.
@@
 	\end{figure}
-
-	The confusion matrices are shown in Fig.~\ref{fig:A_conf_mat}) and the t-SNE graphs are shown in Fig.~\ref{fig:A_tSNE}.
-During training, most of the abnormities are well-separated.
-However, this is not the case during testing.
-On the t-SNE graph, the OCT Model still shows clear separation of clusters, many of which, however, are mingled with data points that do not belong to the cluster.
-This is because some OCT abnormities resemble each other.
-For example, ``IF'', ``DME'' and ``Mactel'' may look very similar.
-As to the Fundus Model, there are fewer small distinct clusters and there is a large cluster instead.
-This is likely due to the fact that many fundus images contain multiple abnormities.
-For example, a patient with the disease ``rDR'' shows the abnormities ``CWP'', ``HE'', ``HM'' and ``VA''.
-Therefore, many abnormities tend to appear together, impeding classification of abnormities.
 

### 2024-08-29 Paper/Paper.tex
revise abnormity results

@@
 By leveraging DL, researchers have developed auxiliary diagnosis programs to help ophthalmologists in the process.
-Many studies use convolutional neural network (CNN) to analyze ocular images.
+Many studies use convolutional neural networks (CNNs) to analyze ocular images.
 Some commonly used CNNs are VGG, ResNet, and Inception \autocite{daich2023artificial}.
@@
 
-	The OCT Model tends to be overfitting, while the Fundus Model cannot reach a satisfying level in terms of DL.
-Overall, the performance of the OCT Model is significantly better than that of the Fundus Model.
+	The OCT Model tends to overfit, while the Fundus Model cannot reach a satisfying level in terms of DL. Overall, the performance of the OCT Model is significantly better than that of the Fundus Model.
 
 	Fundus abnormities tend to be less prominent than those of OCT, since the abnormity in fundus image are usually quite small and scattered.
-Moreover, one fundus image usually contains more than one abnormity, while most OCT images contain only one abnormity on each image.
-Also given that we have less fundus images than OCT ones, the difficulties for fundus classification increases.
+Moreover, one fundus image usually contains more than one abnormity, while most OCT images contain only one abnormity per image.
+Also, given that we have fewer fundus images than OCT ones, the difficulties for fundus classification increases.
+
+	In order to allow the Abnormity Models to identify multiple abnormities in one image, we employ a method to determine the codominant abnormities.
+We input an image to the Abnormity Models and get the abnormity probabilities vector.
+If the abnormity with the highest probability has probability greater than 0.9, it is regarded as dominant; if not, we continue taking the abnormity with the next high probability until either the sum of the probabilities of the chosen abnormities reaches 0.9, or the number of abnormities reaches the maximum, which is 4, and all the chosen abnormities are regarded as codominant.
 
@@
 If the model had been trained correctly, this would be equivalent to highlighting the abnormity.
-Fig.~\ref{fig:gradCAM} shows some examples.
-Furthermore, Grad-CAM can highlight a designated abnormity, so it may be able to highlight multiple abnormities on one image, as shown in Fig.~\ref{fig:gradCAM_multi_abnormity}.
+In Fig.~\ref{fig:gradCAM}, the left image in each pair of images is the original OCT or Fundus image, and the right one is the image with the abnormity correctly highlighted with Grad-CAM.
+
+	Furthermore, Grad-CAM can highlight any designated abnormity, so it can be used to highlight codominant abnormities.
+In Fig.~\ref{fig:gradCAM_multi_abnormity}, the middle images are the original OCT and fundus images.
+In the images on the left and right, respectively, the ground truth abnormity and its codominant abnormity are highlighted with Grad-CAM.
 
@@
 	\end{figure}
-
-	Fig.~\ref{fig:gradCAM_multi_abnormity} demonstrates that the Abnormity Models may be able to correctly identify multiple abnormities on an image.
-Knowing that OCT and fundus images often do include more than one abnormity, we employ a method to determine the codominant abnormities.
-We input an image to the Abnormity Models and get the abnormity probabilities vector.
-If the abnormity with the highest probability has probability greater than 0.9, it is regarded as dominant; if not, we continue taking the abnormity with the next high probability until either the sum of the probabilities of the chosen abnormities reaches 0.9, or the number of abnormities reaches the maximum, which is 4, and all the chosen abnormities are regarded as codominant.
-
-	This codominant abnormities method allows the Abnormity Models to identify multiple abnormities.
-For example, the fundus image in Fig.~\ref{fig:gradCAM_multi_abnormity} only has ground truth label ``HE'', but the Fundus Model correctly predicts that it has codominant abnormities ``HE'' and ``HM''.
 

### 2024-08-29 Paper/Paper.tex
Revise Grad-CAM paragraph

@@
 By leveraging DL, researchers have developed auxiliary diagnosis programs to help ophthalmologists in the process.
-Many studies use convolutional neural networks (CNNs) to analyze ocular images.
+Many studies use convolutional neural networks (CNN) to analyze ocular images.
 Some commonly used CNNs are VGG, ResNet, and Inception \autocite{daich2023artificial}.
@@
 
+	\vspace{0.3cm}
+
 	We can use Grad-CAM \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra} to highlight areas on the image that make a large contribution to the final classification.
@@
 In Fig.~\ref{fig:gradCAM_multi_abnormity}, the middle images are the original OCT and fundus images.
-In the images on the left and right, respectively, the ground truth abnormity and its codominant abnormity are highlighted with Grad-CAM.
+In the images on the left and right, we use Grad-CAM to highlight the codominant abnormities.
 

### 2024-08-30 ODADS/Code/Results/diagnosis1_acc_barchart.py
record add acc bar for D2

@@ -3,6 +3,8 @@ import os
 import matplotlib.pyplot as plt
 from Utils import utils
 
+# Add D2 accuracy with codominant method
+
 def plot_acc_barchart():
     setting = utils.get_setting()
     csv_file_path = os.path.join(setting.D1_folder, "000D1TORS.csv")

### 2024-08-31 Paper/Paper.tex
record add acc bar for D2
write diagnosis model data prep, train, and results

@@
 	\section{Overview}
+	\label{sec:overview}
 
@@
 	\subsection{Training}
+	\label{sec:a_training}
 
@@
 
-	In Stage D1, we prepare data
+	The purpose of Stage D1 is to determine the severity level for all diseases, each of which has a corresponding submodel.
+We prepare data for each submodel according to the Abnormity-to-Disease Deduction Criteria (shown in Fig.~\ref{fig:criteria}).
+As stated in Section~\ref{sec:overview}, we determine the target abnormities for one disease and use the number of target abnormities to define the severity levels.
+If a disease has 5 target abnormities, then, taking into account the healthy status, we get 6 severity levels, namely 0 to 5.
+We use sets of images as inputs to the submodel, and the severity level label for one set is equal to the number of target abnormities that appear in the set.
+We randomly choose sets of images from the OCT and fundus images and determine the severity level for each set.
+In the end, we get 10000 inputs for training and 10000 inputs for testing for each severity level.
 
-	TEXT: how to choose data (with an example)
-	how to find level (number of traits = level for the disease as label during training)
+	The purpose of Stage D2 is to output the disease probability vectors.
+For each disease, we use the Abnormity-to-Disease Deduction Criteria to find the target abnormities, randomly choose sets of images that are composed of one image for each of the target abnormities, and label the sets of images with the disease.
+We get 10000 sets of images for training and 10000 sets of images for testing for each of the disease.
 
@@
 
-	%The model training is on a desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256GB of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48GB VRAM.
-The training uses cross entropy loss, ADAM optimizer with learning rate 0.001, a batch size of 32 and five-fold cross-validation.
-The code is written with PyTorch in an Anaconda environment.
-Refer to ``Appendix'' for the link to the code repository on GitHub.
+	The Diagnosis Model is trained with the same hardware as the Abnormity Models.
+Stage D1 submodels are trained for 10 epochs and Stage D2 model is trained for 30 epochs, and all the other hyperparameters are identical to those of the Abnormity Models.
+Refer to Section~\ref{sec:a_training} for details.
 
-	TEXT: comments
+	Submodels in Stage D1 and the model in Stage D2 quickly reach very high accuracies during training and validation because they only consists of a FC layer.
 
@@
 
-	TEXT: D1 output - calculate expected grade. in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1]. 
-	used for checking number of abnormities associated to the disease
+	Fig.~\ref{fig:D1_conf_mat} shows the confusion matrices for Stage D1 and Fig.~\ref{fig:D1_conf_mat} shows the accuracies of the submodels of Stage D1.
+Table~\ref{tb:diagnosis_test} shows the predictive values of Stage D2, Fig.~\ref{fig:D2_ROC} shows the ROCs, Fig.~\ref{fig:D2_conf_mat} shows the confusion matrix and Fig~\ref{fig:D2_tSNE} shows the t-SNE graph.
 
-	TEXT: top-probs method
+	The submodels of Stage D1 tend to yield results one severity level higher or lower than the label.
+This impairs the accuracies of the submodels of Stage D1.
+However, Stage D2 partly solves this problem, as the model in Stage D2 has a higher accuracy than the average accuracy of the Stage D1 submodels.
+
+	Stage D2 performs quite well on classifying the diseases.
+Furthermore, considering that some diseases may look alike each other, we employ a method similar to the codominant abnormities method to allow Stage D2 to give up to 3 codominant diseases.
+As shown in Fig.~\ref{fig:D1_acc_bar}, if the codominant diseases method is used, the accuracy of Stage D2 further increases.
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.pdf}
+		\caption{D1 Conf Mat}
+		\vspace{0.3cm}
+		\label{fig:D1_conf_mat}
+	\end{figure}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
+		\caption{D1 Acc Bar}
+		\vspace{0.3cm}
+		\label{fig:D1_acc_bar}
+	\end{figure}
 
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
-		\caption{D1 Acc Bar}
+		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
+		\caption{D2 ROC}
 		\vspace{0.3cm}
-		\label{fig:D1_acc_bar}
+		\label{fig:D2_ROC}
 	\end{figure}
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.pdf}
-		\caption{D1 Conf Mat}
-		\vspace{0.3cm}
-		\label{fig:D1_conf_mat}
-	\end{figure}
-	TEXT: comments
 
@@
 	\end{figure}
-	TEXT: comments
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
-		\caption{D2 ROC}
-		\vspace{0.3cm}
-		\label{fig:D2_ROC}
-	\end{figure}
-	TEXT: comparison and comments
 

### 2024-08-31 Paper/Paper.tex
revise diagnosis model

@@
 	The purpose of Stage D2 is to output the disease probability vectors.
-For each disease, we use the Abnormity-to-Disease Deduction Criteria to find the target abnormities, randomly choose sets of images that are composed of one image for each of the target abnormities, and label the sets of images with the disease.
+For each disease, we use the Abnormity-to-Disease Deduction Criteria to find the target abnormities, randomly choose sets of images where each of them is from one target abnormitiy, and label the sets of images with the disease.
 We get 10000 sets of images for training and 10000 sets of images for testing for each of the disease.
@@
 
-	Submodels in Stage D1 and the model in Stage D2 quickly reach very high accuracies during training and validation because they only consists of a FC layer.
+	Submodels in Stage D1 and the model in Stage D2 quickly reach very high accuracies during training and validation because there are plenty of training data and the models leverage relatively simpler networks.
 
@@
 
-	Fig.~\ref{fig:D1_conf_mat} shows the confusion matrices for Stage D1 and Fig.~\ref{fig:D1_conf_mat} shows the accuracies of the submodels of Stage D1.
+	Fig.~\ref{fig:D1_conf_mat} shows the confusion matrices for Stage D1 and Fig.~\ref{fig:D1_acc_bar} shows the accuracies of the submodels of Stage D1.
 Table~\ref{tb:diagnosis_test} shows the predictive values of Stage D2, Fig.~\ref{fig:D2_ROC} shows the ROCs, Fig.~\ref{fig:D2_conf_mat} shows the confusion matrix and Fig~\ref{fig:D2_tSNE} shows the t-SNE graph.
 
-	The submodels of Stage D1 tend to yield results one severity level higher or lower than the label.
+	The submodels of Stage D1 tend to yield results where the predicted severity level is 1 level offset from the label.
 This impairs the accuracies of the submodels of Stage D1.

### 2024-08-31 Paper/Paper.tex
write discussion of increase accuracy

@@
 					\midrule
-					CNV    &2984&/  &/ &/ &2984\\
-					CSC    &/   &102&32&/ &134 \\
-					DME    &2500&/  &/ &/ &2500\\
-					Drusen &2500&/  &/ &/ &2500\\
-					ERM    &/   &/  &/ &19&19  \\
-					IF     &1097&/  &/ &/ &1097\\
-					MH     &/   &99 &31&/ &130 \\
-					Mactel &/   &/  &29&/ &29  \\
-					Healthy&5000&/  &/ &/ &5000\\
-					RP     &/   &102&31&/ &133 \\
-					ST     &/   &/  &23&/ &23  \\
-					SF     &1083&/  &/ &/ &1083\\
+					CNV    &2984&-  &- &- &2984\\
+					CSC    &-   &102&32&- &134 \\
+					DME    &2500&-  &- &- &2500\\
+					Drusen &2500&-  &- &- &2500\\
+					ERM    &-   &-  &- &19&19  \\
+					IF     &1097&-  &- &- &1097\\
+					MH     &-   &99 &31&- &130 \\
+					Mactel &-   &-  &29&- &29  \\
+					Healthy&5000&-  &- &- &5000\\
+					RP     &-   &102&31&- &133 \\
+					ST     &-   &-  &23&- &23  \\
+					SF     &1083&-  &- &- &1083\\
 					\bottomrule
@@
 					\midrule
-					CWP    &/  &/ &/ &33 &205&/ &238\\
-					Drusen &/  &/ &/ &50 &/  &/ &50 \\     
-					HE     &20 &/ &/ &75 &284&/ &379\\ 
-					HM     &13 &66&/ &105&278&/ &462\\     
-					MH     &/  &/ &/ &/  &/  &34&34 \\        
-					MA     &55 &/ &/ &1  &219&/ &275\\
-					Healthy&100&37&15&/  &/  &/ &152\\      
-					RP     &/  &22&/ &/  &/  &44&66 \\         
-					VA     &/  &64&/ &14 &/  &/ &78 \\
+					CWP    &-  &- &- &33 &205&- &238\\
+					Drusen &-  &- &- &50 &-  &- &50 \\     
+					HE     &20 &- &- &75 &284&- &379\\ 
+					HM     &13 &66&- &105&278&- &462\\     
+					MH     &-  &- &- &-  &-  &34&34 \\        
+					MA     &55 &- &- &1  &219&- &275\\
+					Healthy&100&37&15&-  &-  &- &152\\      
+					RP     &-  &22&- &-  &-  &44&66 \\         
+					VA     &-  &64&- &14 &-  &- &78 \\
 
@@
 				\centering
-				\caption{Validation accuracies}
+				\caption{Overall accuracies}
 				\label{tb:A_accuracies}
@@
 
-	TEXT: Do two models increase accuracy? How?
+	The combination of the Abnormity Models and the Diagnosis Model successfully improve the performance of the MAAM.
+The OCT Model and Fundus Model only have accuracies between 70\% and 80\% with the codominant abnormities method, with the Fundus Model having lower accuracy.
+The average accuracy of submodels in Stage D1 is still slightly lower than the OCT Model's accuracy, but it is already higher than the Fundus Model.
+Stage D2 makes the accuracy increase even further, with a 82\% accuracy without the codominant diseases method and a 89\% accuracy with the method.
 
-	TEXT: Comparison to other studies
+	\vspace{0.2cm}
+
+	The Abnormity Models does not perform very well due to several reasons.
+
+	There are often multiple abnormities on one image, and this is especially true for fundus images.
+Multiple abnormities increase the difficulty for the model to correctly extract and identify the abnormities.
+
+	Also, the data used for training are collected from various online sources.
+The labeling criteria are different for different sources, so our data lack a uniform standard.
+Furthermore, some of the data selection are done by ourselves, but we do not have the expertise of ophthalmologists.
+As a result, our data is not very reliable.
+
+	In addition, the size of our dataset is quite small and there is an imbalance between the number of images of different abnormities.
+In the OCT Model, the imbalance is partly neutralized by using Cycle-GAN to generate images.
+However, in the Fundus Model, we could only perform transformations to get more images, which may increase the model's tendency of being overfitting or make it hard for the model to extract the correct abnormities.
+
+	\vspace{0.2cm}
+
+	The Diagnosis Model can increase the accuracy of the diagnosis for the following reasons.
+
+	The Diagnosis Model performs two additional feature extracts based on the outputs of the Abnormity Models.
+In Stage D1, the severity levels of the diseases are extracted; and in Stage D2, the probabilities of diseases are extracted.
+Even though the Abnormity Models are not very accurate, for example, in discriminating similar abnormities, the Diagnosis Model can still extract key features and make a correct diagnosis.
+
+	Additionally, in training the Diagnosis Model, we use the Abnormity-to-Disease Deduction Criteria to generate a new set of inputs and labels, which are reliable as long as the Criteria is correct.
+The Diagnosis Model is therefore trained on a relatively reliable set of data compared to the Abnormity Model.
+
+	\vspace{0.3cm}
+
+	Fundus 103262 imgs, 15 abnormities, 8 diseases \autocite{Son2023}
 

### 2024-08-31 Paper/Paper.tex
write comparison with other studies

@@
 
-	Fundus 103262 imgs, 15 abnormities, 8 diseases \autocite{Son2023}
+	The MAAM, or specifically the abnormity models, does not have a very satisfactory performance.
 
-	TEXT: Strengths and weaknesses
-	how to improve
+	In terms of classifying OCT abnormities, \citeauthor{leandro2023oct}'s model is trained on 10770 images, classifies 8 abnormities, and has overall accuracy between 93\% and 99\% \autocite{leandro2023oct}.
+\citeauthor{li2019deep}'s model is trained on 21357 images, classifies 4 abnormities, and has overall accuracy 97.3\% \autocite{li2019deep}.
+In comparison, our OCT Model is trained on 15632 images, classifies 11 abnormities, and has overall accuracy less than 80\%.
+\citeauthor{leandro2023oct}'s and \citeauthor{li2019deep}'s model perform better than ours because ophthalmologists labeled their data and they have more images per abnormity than ours.
+
+	In terms of the classifying fundus abnormities, \citeauthor{Son2023}'s model is trained on 103262 images, classifies 15 abnormities, and has a mean AUC of 0.980 \autocite{Son2023}.
+In comparison, our Fundus Model is trained on 1734 images, classifies 8 abnormities, and has a mean AUC of 0.909, which is much lower than \citeauthor{Son2023}'s because they have much more data with professional labeling.
+
+	\citeauthor{Son2023} also have diagnosis model, which classifies 8 diseases and has mean AUC 0.992.
+Our Diagnosis Model classifies 12 diseases and has mean AUC of 0.984, which is quite close to \citeauthor{Son2023}'s value.
 

### 2024-08-31 Paper/Paper.tex
Revise discussion

--- 2024-08-31 Paper/Paper.tex
@@
 
-	The combination of the Abnormity Models and the Diagnosis Model successfully improve the performance of the MAAM.
-The OCT Model and Fundus Model only have accuracies between 70\% and 80\% with the codominant abnormities method, with the Fundus Model having lower accuracy.
+	The Abnormity Models do not have a very satisfactory performance.
+
+	In terms of classifying OCT abnormities, \citeauthor{leandro2023oct}'s model is trained on 10770 images (most images belong to multiple classes), classifies 8 abnormities, and has overall accuracy between 93\% and 99\% \autocite{leandro2023oct}.
+\citeauthor{li2019deep}'s model is trained on 21357 images, classifies 4 abnormities, and has overall accuracy 97.3\% \autocite{li2019deep}.
+In comparison, our OCT Model is trained on 15632 images, classifies 11 abnormities, and has overall accuracy less than 80\%.
+
+	In terms of the classifying fundus abnormities, \citeauthor{Son2023}'s model is trained on 103262 images, classifies 15 abnormities, and has a mean AUC of 0.980 \autocite{Son2023}.
+In comparison, our Fundus Model is trained on 1734 images, classifies 8 abnormities, and has a mean AUC of 0.909.
+
+	All three models mentioned above perform better than ours. The Abnormity Models do not perform very well due to several factors:
+
+	Our data are collected from various online sources and therefore lack a uniform standard.
+Furthermore, some of the data selection are done by ourselves, but we do not have the expertise of ophthalmologists.
+In contrast, in all the three studies, the data are labeled by ophthalmologists and are more reliable.
+
+	The size of our dataset is quite small.
+There is also an imbalance between the number of images of different abnormities.
+In the OCT Model, the imbalance is partly neutralized by using Cycle-GAN to generate images.
+However, in the Fundus Model, we could only perform transformations to get more images, which may increase the model's tendency of being overfitting or make it hard for the model to extract the correct abnormities.
+In comparison, two of the studies have more images than ours, and all three have datasets that are more balanced.
+
+	In addition, there are often multiple abnormities on one image, which increase the difficulty for the models to correctly extract and identify the abnormities.
+
+	\vspace{0.3cm}
+
+	However, the addition the Diagnosis Model successfully improves the performance of the MAAM.
+
+	\citeauthor{Son2023}'s study also has a diagnosis model, which classifies 8 diseases and has mean AUC 0.992.
+Our Diagnosis Model classifies 12 diseases and has mean AUC of 0.984 \autocite{Son2023}.
+The diagnosis model has helped narrow the gap between the MAAM and \citeauthor{Son2023}'s model.
+
+	with the codominant abnormities method, with the Fundus Model having lower accuracy.
 The average accuracy of submodels in Stage D1 is still slightly lower than the OCT Model's accuracy, but it is already higher than the Fundus Model.
@@
 
-	\vspace{0.2cm}
+	The Diagnosis Model can increase the accuracy of diagnosis for the following factors:
 
-	The Abnormity Models does not perform very well due to several reasons.
-
-	There are often multiple abnormities on one image, and this is especially true for fundus images.
-Multiple abnormities increase the difficulty for the model to correctly extract and identify the abnormities.
-
-	Also, the data used for training are collected from various online sources.
-The labeling criteria are different for different sources, so our data lack a uniform standard.
-Furthermore, some of the data selection are done by ourselves, but we do not have the expertise of ophthalmologists.
-As a result, our data is not very reliable.
-
-	In addition, the size of our dataset is quite small and there is an imbalance between the number of images of different abnormities.
-In the OCT Model, the imbalance is partly neutralized by using Cycle-GAN to generate images.
-However, in the Fundus Model, we could only perform transformations to get more images, which may increase the model's tendency of being overfitting or make it hard for the model to extract the correct abnormities.
-
-	\vspace{0.2cm}
-
-	The Diagnosis Model can increase the accuracy of the diagnosis for the following reasons.
-
-	The Diagnosis Model performs two additional feature extracts based on the outputs of the Abnormity Models.
-In Stage D1, the severity levels of the diseases are extracted; and in Stage D2, the probabilities of diseases are extracted.
-Even though the Abnormity Models are not very accurate, for example, in discriminating similar abnormities, the Diagnosis Model can still extract key features and make a correct diagnosis.
+	The Diagnosis Model performs two additional feature extractions based on the outputs of the Abnormity Models.
+The Abnormity Models only have accuracies between 70\% and 80\%.
+After the severity levels of diseases are extracted Stage D1, the average accuracy of the submodels of Stage D1 is still slightly lower than the OCT Model's accuracy, but is already higher than the Fundus Model.
+And after the disease probabilities are extracted in Stage D2, accuracy increases even further to 89\%.
+These two extractions can help correct some mistakes made by the Abnormity Models and make the features of the diseases more distinct.
 
@@
 The Diagnosis Model is therefore trained on a relatively reliable set of data compared to the Abnormity Model.
-
-	\vspace{0.3cm}
-
-	Fundus 103262 imgs, 15 abnormities, 8 diseases \autocite{Son2023}
-
-	TEXT: Strengths and weaknesses
-	how to improve
 

### 2024-08-31 Paper/Paper.tex
revise discussion.

--- 2024-08-31 Paper/Paper.tex
@@
 
-	The combination of the Abnormity Models and the Diagnosis Model successfully improve the performance of the MAAM.
-The OCT Model and Fundus Model only have accuracies between 70\% and 80\% with the codominant abnormities method, with the Fundus Model having lower accuracy.
-The average accuracy of submodels in Stage D1 is still slightly lower than the OCT Model's accuracy, but it is already higher than the Fundus Model.
-Stage D2 makes the accuracy increase even further, with a 82\% accuracy without the codominant diseases method and a 89\% accuracy with the method.
+	There are some studies working on classifying OCT abnormities.
+For examples, \citeauthor{leandro2023oct}'s model is trained on 10770 images (most images belong to multiple classes), classifies 8 abnormities, and has overall accuracy between 93\% and 99\% \autocite{leandro2023oct}.
+\citeauthor{li2019deep}'s model is trained on 21357 images, classifies 4 abnormities, and has overall accuracy 97.3\% \autocite{li2019deep}.
+And there are some studies working on classifying fundus abnormities.
+For example,  	\citeauthor{Son2023}'s model is trained on 103262 images, classifies 15 abnormities, and has a mean AUC of 0.980 \autocite{Son2023}.
+In comparison, our OCT Model is trained on 15632 images, classifies 11 abnormities, and has overall accuracy less than 80\%.
+And our Fundus Model is trained on 1734 images, classifies 8 abnormities, and has a mean AUC of 0.909.
+As a matter of fact, our Abnormity Models are not satisfying in terms of performance.
 
-	\vspace{0.2cm}
-
-	The Abnormity Models does not perform very well due to several reasons.
-
-	There are often multiple abnormities on one image, and this is especially true for fundus images.
-Multiple abnormities increase the difficulty for the model to correctly extract and identify the abnormities.
-
-	Also, the data used for training are collected from various online sources.
-The labeling criteria are different for different sources, so our data lack a uniform standard.
-Furthermore, some of the data selection are done by ourselves, but we do not have the expertise of ophthalmologists.
-As a result, our data is not very reliable.
-
-	In addition, the size of our dataset is quite small and there is an imbalance between the number of images of different abnormities.
-In the OCT Model, the imbalance is partly neutralized by using Cycle-GAN to generate images.
-However, in the Fundus Model, we could only perform transformations to get more images, which may increase the model's tendency of being overfitting or make it hard for the model to extract the correct abnormities.
-
-	\vspace{0.2cm}
-
-	The Diagnosis Model can increase the accuracy of the diagnosis for the following reasons.
-
-	The Diagnosis Model performs two additional feature extracts based on the outputs of the Abnormity Models.
-In Stage D1, the severity levels of the diseases are extracted; and in Stage D2, the probabilities of diseases are extracted.
-Even though the Abnormity Models are not very accurate, for example, in discriminating similar abnormities, the Diagnosis Model can still extract key features and make a correct diagnosis.
-
-	Additionally, in training the Diagnosis Model, we use the Abnormity-to-Disease Deduction Criteria to generate a new set of inputs and labels, which are reliable as long as the Criteria is correct.
-The Diagnosis Model is therefore trained on a relatively reliable set of data compared to the Abnormity Model.
+	Our data are collected from various online sources and therefore lack a uniform standard.
+Furthermore, some of the data are labeled by ourselves, while we do not have the expertise of ophthalmologists.
+Moreover, our data is not sufficient.
+There is also an imbalance between the number of images of different abnormities.
+In the OCT Model, the imbalance is partly neutralized by using Cycle-GAN.
+However, in the Fundus Model, we could only perform transformations to generate more images, which may increase the model's tendency of being overfitting and make it hard for the model to extract the correct features.
+Also as mentioned before, in our model, there are often multiple abnormities on one image, which increase the difficulty to identify one specific abnormity correctly.
 
@@
 
-	Fundus 103262 imgs, 15 abnormities, 8 diseases \autocite{Son2023}
+	In MAAM, the Diagnosis Model improves the overall performance successfully.
+There are also some studies using similar framework.
+For example, \citeauthor{Son2023}'s diagnosis model classifies 8 diseases and has mean AUC 0.992\autocite{Son2023}.
+In comparison, our Diagnosis Model classifies 12 diseases and has mean AUC of 0.984 which is close to other studies.
 
-	TEXT: Strengths and weaknesses
-	how to improve
+	It is noted that the goal of MAAM is not to identify one specific disease.
+It is developed for identifying all the potential diseases, which is different from other studies mentioned in this paper.
+Therefore, we introduced codominant abnormities and codominant diseases, which buff up the performances.
+Moreover, the Diagnosis Model performs two additional feature extractions.
+While the Abnormity Models only have accuracies between 70\% and 80\%, after we extracted the features of severity levels of diseases in Stage D1, the average accuracy increases.
+And after we extracted the features of disease in Stage D2, the accuracy keep on increasing up to a satisfying level.
+These two stages enhance the performance of the Abnormity Models and make the features of the diseases more distinct.	Also, in training the Diagnosis Model, we use the Abnormity-to-Disease Deduction Criteria to generate ground truth, which is reliable even without involving ophthalmologists.
 

### 2024-08-31 Paper/Paper.tex
write conclusion

@@
 
-	TEXT: abstract
+	We develop a novel model called the Multimodal Abnormity-Aware Model, which uses optical coherence tomography (OCT) and color fundus images to diagnose ocular diseases.
+The model is composed of the Abnormity Models, which use OCT images to identify 11 abnormities and fundus images to identify 8 abnormities, and the Diagnosis Model, which diagnoses 12 diseases by integrating information from the Abnormity Models.
+We use an abnormity-to-disease approach and simulate the decision-making process of ophthalmologists.
+Information integration is achieved through employing a fusion mechanism.
+We also introduced codominant abnormities and diseases, providing more information for reference.
 
@@
 
-	TEXT: conclusion
+	We developed the Multimodal Abnormity-Aware Model, which takes both OCT and fundus images as input.
+We integrate information from different sources by employing the fusion mechanism.
+Moreover, we use an abnormity-to-disease approach and simulate the decision-making process of ophthalmologists.
+We also introduced codominant abnormities and diseases, providing more information for reference.
+
+	The main goal of this study is to devise a novel model and verify its feasibility.
+The MAAM still has room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model.
 

### 2024-08-31 Paper/Paper.tex
Write abstract

--- 2024-08-31 Paper/Paper.tex
@@
 
-	TEXT: abstract
+	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), and verify its feasibility.
+The MAAM uses optical coherence tomography (OCT) and color fundus images to diagnose ocular diseases.
+It simulates the decision-making process of ophthalmologists by deducing the disease from abnormities.
+The model is composed of the Abnormity Models, which identify 11 abnormities from OCT images and 8 abnormities from fundus images, and the Diagnosis Model, which diagnoses 12 diseases by integrating information from the Abnormity Models through a fusion mechanism.
+We also introduce the concept of codominant abnormities and diseases, providing more information for reference.
+The final model has a diagnosis accuracy of 89\%.
 
@@
 
-	TEXT: conclusion
+	The main goal of this study is to devise a novel model and verify its feasibility.
+The MAAM takes both OCT and fundus images as input.
+We integrate information from different sources by employing the fusion mechanism.
+Moreover, we use an abnormity-to-disease approach and simulate the decision-making process of ophthalmologists.
+We also introduced codominant abnormities and diseases, providing more information for reference.
+There is some room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model, etc.
 

### 2024-08-31 Paper/Paper.tex
update softmax code; add appendix

@@
 					Drusen &2500&-  &- &- &2500\\
-					ERM    &-   &-  &- &19&19  \\
+					ERM    &-   &-  &- &16&16  \\
 					IF     &1097&-  &- &- &1097\\
@@
 
-	List: Google Image source links
+	\subsection*{Code}
 
-	Table: abnormities with description (edit the two tables below; ALPHABETICAL ORDER!!!)
+	The link for the GitHub repository is \url{https://github.com/SiqiPan2008/MAAM/}.
+
+	\subsection*{Results Page}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\linewidth]{Figs/Temp.png}
+		\caption{Result Page}
+		\vspace{0.3cm}
+		\label{fig:result_page}
+	\end{figure}
+
+	\subsection*{Abnormities and Diseases}
 
@@
 		{
-			\begin{longtable}{lp{3.8in}}
+			\begin{longtable}{llp{9.5cm}}
 				\caption{OCT Abnormities}
@@
 				\toprule
-				Abnormity&Description\\
+				Abnormity&Abbr.&Description\\
 				\toprule
 
-				\multicolumn{1}{l}{Central serous chorioretinopathy (CSC)}
-				& \multicolumn{1}{l}{The accumulation of fluid underneath the retina.}\\
+				Choroidal neovascularization
+				& CNV
+				& The abnormal growth of new blood vessels in the choroid layer.\\
 
-				\multicolumn{1}{l}{Epiretinal membrane (ERM)}
+				Central serous chorioretinopathy
+				& CSC
+				& The accumulation of fluid underneath the retina.\\
+
+				Diabetic macular edema
+				& DME
+				& The accumulation of fluid in the macula associated with diabetic retinopathy. \\
+
+				Drusen
+				& Drusen
+				& Small deposits of extracellular material that accumulate beneath the retinal pigment epithelium (RPE) or between the RPE and the photoreceptor layer in the macular region of the retina.\\
+
+				Epiretinal membrane
+				& ERM
 				& A thin layer of fibrous tissue forms on the surface of the retina, particularly the macula.\\
 
-				\multicolumn{1}{l}{Macular hole (MH)}
+				Intraretinal fluid
+				& IF
+				& The accumulation of fluid within the layers of the retina.\\
+
+				Macular hole
+				& MH
 				& Disruption or discontinuity in the normal retinal layers surrounding the macular hole.\\
 
-				\multicolumn{1}{l}{Stargardt disease}
+				Macular telangiectasia
+				& Mactel
+				& Abnormities in the macular blood vessels, leading to changes in the macular structure and function.\\
+
+				Retinitis pigmentosa
+				& RP
+				& Thinning of the retinal layers. Disruption of photoreceptor layers. Attenuation of retinal vasculature.\\
+
+				Stargardt disease
+				& ST
 				& Thinning and atrophy of the retina. Disruption of photoreceptor layers. Presence of subretinal deposits.\\
 
-				\multicolumn{1}{l}{Retinitis pigmentosa (RP)}
-				& Thinning of the Retinal Layers. Disruption of Photoreceptor Layers. Attenuation of Retinal Vasculature.\\
-
-				\multicolumn{1}{l}{Macular telangiectasia (Mactel)}
-				& Abnormalities in the macular blood vessels, leading to changes in the macular structure and function\\
-
-				\multicolumn{1}{l}{Diabetic macular edema (DME)}
-				& The accumulation of fluid in the macula. \\
-
-				\multicolumn{1}{l}{Choroidal neovascularization}
-				& The abnormal growth of new blood vessels in the choroid layer.\\
-
-				\multicolumn{1}{l}{Subretinal fluid}
+				Subretinal fluid
+				& SF
 				& The accumulation of fluid between the neurosensory retina and the retinal pigment epithelium (RPE)\\
-
-				\multicolumn{1}{l}{Intraretinal fluid}
-				& The accumulation of fluid within the layers of the retina.\\
-
-				\multicolumn{1}{l}{Drusen}
-				& Small deposits of extracellular material that accumulate beneath the retinal pigment epithelium (RPE) or between the RPE and the photoreceptor layer in the macular region of the retina.\\
 
@@
 		{
-			\begin{longtable}{lp{3.8in}}
+			\begin{longtable}{llp{11.2cm}}
 				\caption{Fundus Abnormalities}
@@
 				\toprule
-				Abnormity&Description\\
+				Abnormity&Abbr.&Description\\
 				\toprule
 
-				\multicolumn{1}{l}{Retinitis pigmentosa (RP)}
-				& Description of RP\\
+				Cotton wool patch
+				& CWP
+				& White or off-white lesions. Irregular shapes and margins. Also called soft exudates. \\
 
-				\multicolumn{1}{l}{Microaneurysm}
-				& Description of microaneurysm\\
+				Drusen
+				& Drusen
+				& Small, round or oval-shaped yellow or white deposits.\\
 
-				\multicolumn{1}{l}{Macular hole (MH)} & Full-thickness macular hole showing a surrounding cuff of subretinal fluid.\\
+				Hard exudate
+				& HE
+				& Yellow or Yellow-White Deposits. Hard Borders. Distribution. Clustering Around Blood Vessels\\
 
-				\multicolumn{1}{l}{Hard exudate} & Yellow or Yellow-White Deposits. Hard Borders. Distribution. Clustering Around Blood Vessels\\
-
-				\multicolumn{1}{l}{Hemorrhage} & Small dot-like to larger blot.
+				Hemorrhage
+				& HM
+				& Small dot-like to larger blot.
 Fresh hemorrhages typically appear bright red or deep red in color, indicating the presence of oxygenated blood.
@@
 
-				\multicolumn{1}{l}{Cotton wool patch / soft exudate} & White or off-white lesions. Irregular shapes and margins.\\
+				Macular hole
+				& MH
+				& Full-thickness macular hole showing a surrounding cuff of subretinal fluid.\\
 
-				\multicolumn{1}{l}{Vascular abnormity} & Retinal Vessel Tortuosity. Retinal Vessel Caliber Changes. \\
+				Microaneurysm
+				& MA
+				& Small vascular dilatations observed in retinal blood vessels, visible as tiny red dots scattered in the retina posteriorly.\\
 
-				\multicolumn{1}{l}{Drusen} & Small, round or oval-shaped yellow or white deposits.\\
+				Retinitis pigmentosa
+				& RP
+				& Arteriolar attenuation. Retinal pigmentary changes (either hypopigmentation and/or hyperpigmentation in the form of bone-spicule and pigment clumpings). Waxy disc pallor.\\
+
+				Vascular abnormity
+				& VA
+				& Retinal Vessel Tortuosity. Retinal Vessel Caliber Changes. \\
 
@@
 
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/Temp.png}
-		\caption{Result Page}
-		\vspace{0.3cm}
-		\label{fig:result_page}
-	\end{figure}
+	{
+		\fontsize{9}{12}\selectfont
+		{
+			\begin{longtable}{cc}
+				\caption{Diseases}
+				\label{tb:diseases}\\
+				\toprule
+				Disease&Abbr.\\
+				\toprule
 
-	TEXT: APP/website description
+				Branch or hemi-central retinal vein occlusion&BRVO\\
+				Central retinal vein occlusion&CRVO\\
+				Central serous chorioretinopathy&CSC\\
+				Dry age-related macular degeneration&dAMD\\
+				Epiretinal membrane&ERM\\
+				Macular telangiectasia&Mactel\\
+				Macular hole&MH\\
+				Mild diabetic retinopathy&mDR\\
+				Referable diabetic retinopathy&rDR\\
+				Retinitis pigmentosa&RP\\
+				Stargardt disease&ST\\
+				Wet age-related macular degeneration&wAMD\\
+				\bottomrule
+			\end{longtable}
+		}
+	}
 
-	Link: GitHub repo
+	\subsection*{Image Sources}
+
+	\subsubsection*{OCT -- ERM}
+	\vspace{0.5cm}
+
+	\fontsize{6}{0}\selectfont{
+	\begin{enumerate}
+		\item \url{https://qers.com.au/eye-conditions/epiretinal-membrane-erm/}
+
+		\item \url{https://www.asrs.org/patients/retinal-diseases/19/epiretinal-membranes}
+
+		\item \url{https://theretinagroup.com/epiretinal-membrane/}
+
+		\item \url{https://www.istanbulretina.com/en-diseases-epiretinal-membrane.php}
+
+		\item \url{https://www.mdfoundation.com.au/about-macular-disease/other-macular-conditions/epiretinal-membrane-macular-pucker/}
+
+		\item \url{https://www.researchgate.net/figure/Grading-of-epiretinal-membrane-ERM-by-spectral-domain-optical-coherence-tomography_fig1_351426760}
+
+		\item \url{https://www.singhealth.com.sg/patient-care/conditions-treatments/epiretinal-membrane}
+
+		\item \url{https://www.windycityretina.com/epiretinal-membrane/}
+
+		\item \url{https://retinacentertx.com/conditions/macular-pucker}
+
+		\item \url{https://www.rvscny.com/patient-eduction/conditions-we-treat/epiretinal-membrane/}
+
+		\item \url{https://www.lyneye.co.za/epiretinal-membrane-erm/}
+
+		\item \url{https://rehmansiddiqui.com/epi-retinal-membrane-erm/}
+
+		\item \url{https://www.reviewofophthalmology.com/article/when-and-how-to-peel-an-epiretinal-membrane}
+
+		\item \url{https://www.janigianretina.com/retina-conditions/epiretinal-membrane}
+
+		\item \url{https://www.researchgate.net/figure/6-months-later-ERM-with-partial-attachment-to-the-retina_fig2_309566437}
+
+		\item \url{https://www.capefearretina.com/epiretinal-membrane/}
+	\end{enumerate}
+	}
+
+	\subsubsection*{Fundus -- MH}
+	\vspace{0.5cm}
+
+	\fontsize{6}{0}\selectfont{
+	\begin{enumerate}
+			\item \url{https://emedicine.medscape.com/article/1224320-overview}
+
+			\item \url{https://www.chatswoodeye.com/macular-hole-specialists/}
+
+			\item \url{https://swretina.com/macular-hole/}
+
+			\item \url{https://www.ophthalmologyexpertservices.com/blog/2019/macular-hole}
+
+			\item \url{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}
+
+			\item \url{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}
+
+			\item \url{https://www.reviewofoptometry.com/article/facedown-showdown}
+
+			\item \url{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}
+
+			\item \url{https://www.researchgate.net/figure/Fundus-image-of-the-right-eye-of-case-1-a-shows-a-macular-hole-with-associated-retinal_fig1_324657341}
+
+			\item \url{https://www.girayersoz.com.tr/en/macular-hole/}
+
+			\item \url{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}
+
+			\item \url{https://www.gotzaridis.gr/en/conhttps://www.willseye.org/macular-hole/ditions/macula/full-thickness-macular-hole}
+
+			\item \url{https://www.willseye.org/macular-hole/}
+
+			\item \url{http://www.oculist.net/downaton502/prof/ebook/duanes/pages/v3/ch031/013f.html}
+
+			\item \url{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#11}
+
+			\item \url{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#12}
+
+			\item \url{https://www.jaypeedigital.com/book/9788180616532/chapter/ch7}
+
+			\item \url{https://emedicine.medscape.com/article/1224320-clinical?form=fpf}
+
+			\item \url{https://www.jaafarelannanmd.com/macular-hole}
+
+			\item \url{https://asiaeyecentre.com.sg/eye-conditions/the-ageing-eye/macular-hole/}
+
+			\item \url{https://retinaandeye.com.au/eye-conditions/full-thickness-macular-holes/}
+
+			\item \url{https://retinahi.com/interesting-cases/}
+
+			\item \url{https://imagebank.asrs.org/file/2858/traumatic-macular-hole}
+
+			\item \url{https://www.semanticscholar.org/paper/Giant-macular-hole-as-an-atypical-consequence-of-a-Blaise-Comhaire/5c9a60375d904323eb5fbcd52b6bd03b735f6951}
+
+			\item \url{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/Macular-hole-commotio-retinae-choroidal-rupture.htm#gsc.tab=0}
+
+			\item \url{https://areaoftalmologica.com/en/terms-of-ophthalmology/macular-hole/}
+
+			\item \url{https://www.reviewofoptometry.com/article/facedown-showdown}
+
+			\item \url{https://montanaretinaconsultants.com/portfolio/macular-holes/}
+
+			\item \url{https://ccteyes.com/2019/09/30/what-is-a-macular-hole-and-how-does-it-affect-your-vision/}
+
+			\item \url{https://www.backoftheeyemd.com/retina-services/macular-holes/}
+
+			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
+
+			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
+
+			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
+
+			\item \url{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/extrafoveal-macular-hole/emh-1.jpg}
+	\end{enumerate}
+	}
+
+	\subsubsection*{Fundus -- RP}
+	\vspace{0.5cm}
+
+	\fontsize{6}{0}\selectfont{
+		\begin{enumerate}
+			\item \url{https://imagebank.asrs.org/file/93471/retinitis-pigmentosa}
+
+			\item \url{https://educate.choroida.com/2021/07/05/retinitis-pigmentosa/}
+
+			\item \url{https://decisionmakerplus.net/dg-post/h35-52-retinitis-pigmentosa/}
+
+			\item \url{https://basicmedicalkey.com/retinitis-pigmentosa/}
+
+			\item \url{https://www.news-medical.net/health/What-is-Retinitis-Pigmentosa.aspx}
+
+			\item \url{https://www.researchgate.net/figure/Fundus-photograph-of-an-individual-affected-with-retinitis-pigmentosa-The-fundus_fig3_40447070}
+
+			\item \url{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F15/}
+
+			\item \url{https://www.brainkart.com/article/Retinal-Dystrophies--Retinitis-Pigmentosa_26087/}
+
+			\item \url{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}
+
+			\item \url{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}
+
+			\item \url{https://retinography.org/sector-retinitis-pigmentosa/}
+
+			\item \url{https://retinography.org/sector-retinitis-pigmentosa/}
+
+			\item \url{https://www.linkedin.com/posts/stevenlevymd_blindness-from-retinitis-pigmentosa-reversed-activity-7047214648877608960-ar4h}
+
+			\item \url{https://atlas-1-elastic.atlasoph.com/photo.jsf;jsessionid=94EF0B6B067E676E8BCB3F2AD7B9885A?node=6475&locale=en}
+
+			\item \url{https://dizziness-and-balance.com/disorders/visual/retinopathy/RP.html}
+
+			\item \url{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}
+
+			\item \url{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}
+
+			\item \url{https://eyeandear.org/2020/07/a-new-era-in-retinal-research/}
+
+			\item \url{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F14/}
+
+			\item \url{https://commons.wikimedia.org/wiki/File:Fundus_of_patient_with_retinitis_pigmentosa,_end_stage.jpg}
+
+			\item \url{https://healthjade.net/retinitis-pigmentosa/}
+
+			\item \url{https://www.reviewofoptometry.com/article/night-spots}
+
+			\item \url{https://www.visualsurgery.com/eye-conditions/retinal-diseases/other-retinal-diseases/retinitis-pigmentosa/}
+
+			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
+
+			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
+
+			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
+
+			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
+
+			\item \url{https://emedicine.medscape.com/article/1227488-overview?form=basic}
+
+			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
+
+			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
+
+			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
+
+			\item \url{https://webvision.med.utah.edu/book/electrophysiology/the-electroretinogram-clinical-applications/}
+
+			\item \url{https://www.retinarevealed.com/retinitis-pigmentosa-page-34-of-49/}
+
+			\item \url{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}
+
+			\item \url{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}
+
+			\item \url{https://www.nyp.org/advances/article/ophthalmology/retinitis-pigmentosa-mitigating-retinal-degeneration-with-crispr-technology}
+
+			\item \url{https://www.ehu.eus/en/-/pacientes-con-retinosis-pigmentaria-en-la-pole}
+
+			\item \url{https://en.wikipedia.org/wiki/Retinal_degeneration_%28rhodopsin_mutation%29}
+
+			\item \url{https://imagebank.asrs.org/file/29807/x-linked-retinitis-pigmentosa}
+
+			\item \url{https://educate.choroida.com/2023/04/07/choroideremia-unveiling-what-you-need-to-know/}
+
+			\item \url{https://retinography.org/retinitis-pigmentosa-2/}
+
+			\item \url{https://retinography.org/retinitis-pigmentosa-2/}
+
+			\item \url{https://retinography.org/retinitis-pigmentosa/}
+
+			\item \url{https://retinography.org/retinitis-pigmentosa/}
+		\end{enumerate}
+	}
 

### 2024-08-31 ODADS/Code/Results/diagnosis1_confusion_matrix.py

@@ -86,7 +86,7 @@ def get_conf_mat(device, disease):
 def plot_conf_mat():
     setting = utils.get_setting()
     diseases = setting.get_diseases(include_normal = False)
-    folder_path = setting.D2_folder
+    folder_path = setting.D1_folder
     fig_folder = setting.fig_folder
     fig_file = "diagnosis1_confusion_matrix.pdf"
     fig_path = os.path.join(fig_folder, fig_file)
@@ -97,7 +97,7 @@ def plot_conf_mat():
     row = 0
     col = 0
     
-    with open(os.path.join(folder_path, "00D1TORS.csv"), "w", newline="") as file:  
+    with open(os.path.join(folder_path, "000D1TORS.csv"), "w", newline="") as file:  
         writer = csv.writer(file)
         for i in range(len(diseases)):
             disease = diseases[i]

### 2024-08-31 ODADS/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py

@@ -106,6 +106,7 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
     
     start_time = time.time()
     corrects = 0
+    corrects_codominant = 0
     total = 0
     shape = mr.shape
     for i in range(shape[0]):
@@ -113,6 +114,8 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
             output = mr[i][j]
             predicted = np.argmax(np.array(output))
             corrects += (predicted == i).item()
+            output = torch.nn.functional.softmax(torch.Tensor(output))
+            corrects_codominant += i in utils.get_top_prob_indices(output, setting.D2_top_probs_max_num, setting.D2_top_probs_min_prob)
             total += 1
             
             conf_mat[i][predicted] += 1
@@ -122,9 +125,11 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
                 roc_probs[disease].append(output[k])
             
     acc = corrects / total
+    acc_codominant = corrects_codominant / total
     time_elapsed = time.time() - start_time
     print(f"Time elapsed {time_elapsed // 60 :.0f}m {time_elapsed % 60 :.2f}s")
     print(f"acc: {corrects}/{total} = {acc :.4f}")
+    print(f"acc: {corrects_codominant}/{total} = {acc_codominant :.4f}")
     
     tSNE_features = [[] for _ in range(disease_num_including_normal)]
     for i in range(len(tSNE_features)):
@@ -143,7 +148,7 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
     
     with open(os.path.join(setting.D2_folder, "000D2TORS.csv"), "w", newline="") as file:
         writer = csv.writer(file)
-        writer.writerow([corrects, total, acc])
+        writer.writerow([corrects, corrects_codominant, total, acc, acc_codominant])
     
     with open(os.path.join(setting.table_folder, "diagnosis2.csv"), "w", newline="") as file:
         writer = csv.writer(file)

### 2024-08-31 Paper/Paper.tex
revise abstract.

@@
 
-	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), and verify its feasibility.
-The MAAM uses optical coherence tomography (OCT) and color fundus images to diagnose ocular diseases.
-It simulates the decision-making process of ophthalmologists by deducing the disease from abnormities.
-The model is composed of the Abnormity Models, which identify 11 abnormities from OCT images and 8 abnormities from fundus images, and the Diagnosis Model, which diagnoses 12 diseases by integrating information from the Abnormity Models through a fusion mechanism.
-We also introduce the concept of codominant abnormities and diseases, providing more information for reference.
-The final model has a diagnosis accuracy of 89\%.
+	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis.
+The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities.
+The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model.
+In MAAM, we introduce the fusion mechanics, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.
+The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists.
+And it gets the overall accuracy of 89\% and thus the feasibility is verified.
 
@@
 		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
-		\caption{OCT Abnormities}
+		\caption{OCT Abnormities \autocite{Duker_Waheed_Goldman_2022}}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
-		\caption{Fundus Abnormities}
+		\caption{Fundus Abnormities \autocite{Wolf_Kirchhof_Reim_2006}}
 		\vspace{0.3cm}
@@
 We integrate information from different sources by employing the fusion mechanism.
-Moreover, we use an abnormity-to-disease approach and simulate the decision-making process of ophthalmologists.
+Moreover, we deduce disease from abnormities and simulate the decision-making process of ophthalmologists.
 We also introduced codominant abnormities and diseases, providing more information for reference.
-There is some room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model, etc.
+As a result, the model breaks the black box of complex neural network and exposes more information.
+On the other hand, there is some room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model, etc.
 

### 2024-08-31 Paper/Paper.tex
use nolinkurl; cancel table numbering

@@
 \usepackage{longtable}
+\usepackage{xurl}
 \usepackage{booktabs}
@@
 
-	\subsection*{Results Page}
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/Temp.png}
-		\caption{Result Page}
-		\vspace{0.3cm}
-		\label{fig:result_page}
-	\end{figure}
-
 	\subsection*{Abnormities and Diseases}
@@
 			\begin{longtable}{llp{9.5cm}}
-				\caption{OCT Abnormities}
+				\caption*{OCT Abnormities}
 				\label{tb:oct-abnormites}\\
@@
 			\begin{longtable}{llp{11.2cm}}
-				\caption{Fundus Abnormalities}
+				\caption*{Fundus Abnormalities}
 				\label{tb:fundus-ab}\\
@@
 			\begin{longtable}{cc}
-				\caption{Diseases}
+				\caption*{Diseases}
 				\label{tb:diseases}\\
@@
 
-	\fontsize{6}{0}\selectfont{
 	\begin{enumerate}
-		\item \url{https://qers.com.au/eye-conditions/epiretinal-membrane-erm/}
-
-		\item \url{https://www.asrs.org/patients/retinal-diseases/19/epiretinal-membranes}
-
-		\item \url{https://theretinagroup.com/epiretinal-membrane/}
-
-		\item \url{https://www.istanbulretina.com/en-diseases-epiretinal-membrane.php}
-
-		\item \url{https://www.mdfoundation.com.au/about-macular-disease/other-macular-conditions/epiretinal-membrane-macular-pucker/}
-
-		\item \url{https://www.researchgate.net/figure/Grading-of-epiretinal-membrane-ERM-by-spectral-domain-optical-coherence-tomography_fig1_351426760}
-
-		\item \url{https://www.singhealth.com.sg/patient-care/conditions-treatments/epiretinal-membrane}
-
-		\item \url{https://www.windycityretina.com/epiretinal-membrane/}
-
-		\item \url{https://retinacentertx.com/conditions/macular-pucker}
-
-		\item \url{https://www.rvscny.com/patient-eduction/conditions-we-treat/epiretinal-membrane/}
-
-		\item \url{https://www.lyneye.co.za/epiretinal-membrane-erm/}
-
-		\item \url{https://rehmansiddiqui.com/epi-retinal-membrane-erm/}
-
-		\item \url{https://www.reviewofophthalmology.com/article/when-and-how-to-peel-an-epiretinal-membrane}
-
-		\item \url{https://www.janigianretina.com/retina-conditions/epiretinal-membrane}
-
-		\item \url{https://www.researchgate.net/figure/6-months-later-ERM-with-partial-attachment-to-the-retina_fig2_309566437}
-
-		\item \url{https://www.capefearretina.com/epiretinal-membrane/}
+		\item \nolinkurl{https://qers.com.au/eye-conditions/epiretinal-membrane-erm/}
+
+		\item \nolinkurl{https://www.asrs.org/patients/retinal-diseases/19/epiretinal-membranes}
+
+		\item \nolinkurl{https://theretinagroup.com/epiretinal-membrane/}
+
+		\item \nolinkurl{https://www.istanbulretina.com/en-diseases-epiretinal-membrane.php}
+
+		\item \nolinkurl{https://www.mdfoundation.com.au/about-macular-disease/other-macular-conditions/epiretinal-membrane-macular-pucker/}
+
+		\item \nolinkurl{https://www.researchgate.net/figure/Grading-of-epiretinal-membrane-ERM-by-spectral-domain-optical-coherence-tomography_fig1_351426760}
+
+		\item \nolinkurl{https://www.singhealth.com.sg/patient-care/conditions-treatments/epiretinal-membrane}
+
+		\item \nolinkurl{https://www.windycityretina.com/epiretinal-membrane/}
+
+		\item \nolinkurl{https://retinacentertx.com/conditions/macular-pucker}
+
+		\item \nolinkurl{https://www.rvscny.com/patient-eduction/conditions-we-treat/epiretinal-membrane/}
+
+		\item \nolinkurl{https://www.lyneye.co.za/epiretinal-membrane-erm/}
+
+		\item \nolinkurl{https://rehmansiddiqui.com/epi-retinal-membrane-erm/}
+
+		\item \nolinkurl{https://www.reviewofophthalmology.com/article/when-and-how-to-peel-an-epiretinal-membrane}
+
+		\item \nolinkurl{https://www.janigianretina.com/retina-conditions/epiretinal-membrane}
+
+		\item \nolinkurl{https://www.researchgate.net/figure/6-months-later-ERM-with-partial-attachment-to-the-retina_fig2_309566437}
+
+		\item \nolinkurl{https://www.capefearretina.com/epiretinal-membrane/}
 	\end{enumerate}
-	}
 
@@
 
-	\fontsize{6}{0}\selectfont{
 	\begin{enumerate}
-			\item \url{https://emedicine.medscape.com/article/1224320-overview}
-
-			\item \url{https://www.chatswoodeye.com/macular-hole-specialists/}
-
-			\item \url{https://swretina.com/macular-hole/}
-
-			\item \url{https://www.ophthalmologyexpertservices.com/blog/2019/macular-hole}
-
-			\item \url{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}
-
-			\item \url{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}
-
-			\item \url{https://www.reviewofoptometry.com/article/facedown-showdown}
-
-			\item \url{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}
-
-			\item \url{https://www.researchgate.net/figure/Fundus-image-of-the-right-eye-of-case-1-a-shows-a-macular-hole-with-associated-retinal_fig1_324657341}
-
-			\item \url{https://www.girayersoz.com.tr/en/macular-hole/}
-
-			\item \url{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}
-
-			\item \url{https://www.gotzaridis.gr/en/conhttps://www.willseye.org/macular-hole/ditions/macula/full-thickness-macular-hole}
-
-			\item \url{https://www.willseye.org/macular-hole/}
-
-			\item \url{http://www.oculist.net/downaton502/prof/ebook/duanes/pages/v3/ch031/013f.html}
-
-			\item \url{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#11}
-
-			\item \url{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#12}
-
-			\item \url{https://www.jaypeedigital.com/book/9788180616532/chapter/ch7}
-
-			\item \url{https://emedicine.medscape.com/article/1224320-clinical?form=fpf}
-
-			\item \url{https://www.jaafarelannanmd.com/macular-hole}
-
-			\item \url{https://asiaeyecentre.com.sg/eye-conditions/the-ageing-eye/macular-hole/}
-
-			\item \url{https://retinaandeye.com.au/eye-conditions/full-thickness-macular-holes/}
-
-			\item \url{https://retinahi.com/interesting-cases/}
-
-			\item \url{https://imagebank.asrs.org/file/2858/traumatic-macular-hole}
-
-			\item \url{https://www.semanticscholar.org/paper/Giant-macular-hole-as-an-atypical-consequence-of-a-Blaise-Comhaire/5c9a60375d904323eb5fbcd52b6bd03b735f6951}
-
-			\item \url{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/Macular-hole-commotio-retinae-choroidal-rupture.htm#gsc.tab=0}
-
-			\item \url{https://areaoftalmologica.com/en/terms-of-ophthalmology/macular-hole/}
-
-			\item \url{https://www.reviewofoptometry.com/article/facedown-showdown}
-
-			\item \url{https://montanaretinaconsultants.com/portfolio/macular-holes/}
-
-			\item \url{https://ccteyes.com/2019/09/30/what-is-a-macular-hole-and-how-does-it-affect-your-vision/}
-
-			\item \url{https://www.backoftheeyemd.com/retina-services/macular-holes/}
-
-			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
-
-			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
-
-			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
-
-			\item \url{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/extrafoveal-macular-hole/emh-1.jpg}
+			\item \nolinkurl{https://emedicine.medscape.com/article/1224320-overview}
+
+			\item \nolinkurl{https://www.chatswoodeye.com/macular-hole-specialists/}
+
+			\item \nolinkurl{https://swretina.com/macular-hole/}
+
+			\item \nolinkurl{https://www.ophthalmologyexpertservices.com/blog/2019/macular-hole}
+
+			\item \nolinkurl{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}
+
+			\item \nolinkurl{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}
+
+			\item \nolinkurl{https://www.reviewofoptometry.com/article/facedown-showdown}
+
+			\item \nolinkurl{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}
+
+			\item \nolinkurl{https://www.researchgate.net/figure/Fundus-image-of-the-right-eye-of-case-1-a-shows-a-macular-hole-with-associated-retinal_fig1_324657341}
+
+			\item \nolinkurl{https://www.girayersoz.com.tr/en/macular-hole/}
+
+			\item \nolinkurl{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}
+
+			\item \nolinkurl{https://www.gotzaridis.gr/en/conhttps://www.willseye.org/macular-hole/ditions/macula/full-thickness-macular-hole}
+
+			\item \nolinkurl{https://www.willseye.org/macular-hole/}
+
+			\item \nolinkurl{http://www.oculist.net/downaton502/prof/ebook/duanes/pages/v3/ch031/013f.html}
+
+			\item \nolinkurl{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#11}
+
+			\item \nolinkurl{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#12}
+
+			\item \nolinkurl{https://www.jaypeedigital.com/book/9788180616532/chapter/ch7}
+
+			\item \nolinkurl{https://emedicine.medscape.com/article/1224320-clinical?form=fpf}
+
+			\item \nolinkurl{https://www.jaafarelannanmd.com/macular-hole}
+
+			\item \nolinkurl{https://asiaeyecentre.com.sg/eye-conditions/the-ageing-eye/macular-hole/}
+
+			\item \nolinkurl{https://retinaandeye.com.au/eye-conditions/full-thickness-macular-holes/}
+
+			\item \nolinkurl{https://retinahi.com/interesting-cases/}
+
+			\item \nolinkurl{https://imagebank.asrs.org/file/2858/traumatic-macular-hole}
+
+			\item \nolinkurl{https://www.semanticscholar.org/paper/Giant-macular-hole-as-an-atypical-consequence-of-a-Blaise-Comhaire/5c9a60375d904323eb5fbcd52b6bd03b735f6951}
+
+			\item \nolinkurl{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/Macular-hole-commotio-retinae-choroidal-rupture.htm#gsc.tab=0}
+
+			\item \nolinkurl{https://areaoftalmologica.com/en/terms-of-ophthalmology/macular-hole/}
+
+			\item \nolinkurl{https://www.reviewofoptometry.com/article/facedown-showdown}
+
+			\item \nolinkurl{https://montanaretinaconsultants.com/portfolio/macular-holes/}
+
+			\item \nolinkurl{https://ccteyes.com/2019/09/30/what-is-a-macular-hole-and-how-does-it-affect-your-vision/}
+
+			\item \nolinkurl{https://www.backoftheeyemd.com/retina-services/macular-holes/}
+
+			\item \nolinkurl{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
+
+			\item \nolinkurl{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
+
+			\item \nolinkurl{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}
+
+			\item \nolinkurl{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/extrafoveal-macular-hole/emh-1.jpg}
 	\end{enumerate}
-	}
 
@@
 
-	\fontsize{6}{0}\selectfont{
 	\begin{enumerate}
-			\item \url{https://imagebank.asrs.org/file/93471/retinitis-pigmentosa}
-
-			\item \url{https://educate.choroida.com/2021/07/05/retinitis-pigmentosa/}
-
-			\item \url{https://decisionmakerplus.net/dg-post/h35-52-retinitis-pigmentosa/}
-
-			\item \url{https://basicmedicalkey.com/retinitis-pigmentosa/}
-
-			\item \url{https://www.news-medical.net/health/What-is-Retinitis-Pigmentosa.aspx}
-
-			\item \url{https://www.researchgate.net/figure/Fundus-photograph-of-an-individual-affected-with-retinitis-pigmentosa-The-fundus_fig3_40447070}
-
-			\item \url{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F15/}
-
-			\item \url{https://www.brainkart.com/article/Retinal-Dystrophies--Retinitis-Pigmentosa_26087/}
-
-			\item \url{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}
-
-			\item \url{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}
-
-			\item \url{https://retinography.org/sector-retinitis-pigmentosa/}
-
-			\item \url{https://retinography.org/sector-retinitis-pigmentosa/}
-
-			\item \url{https://www.linkedin.com/posts/stevenlevymd_blindness-from-retinitis-pigmentosa-reversed-activity-7047214648877608960-ar4h}
-
-			\item \url{https://atlas-1-elastic.atlasoph.com/photo.jsf;jsessionid=94EF0B6B067E676E8BCB3F2AD7B9885A?node=6475&locale=en}
-
-			\item \url{https://dizziness-and-balance.com/disorders/visual/retinopathy/RP.html}
-
-			\item \url{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}
-
-			\item \url{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}
-
-			\item \url{https://eyeandear.org/2020/07/a-new-era-in-retinal-research/}
-
-			\item \url{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F14/}
-
-			\item \url{https://commons.wikimedia.org/wiki/File:Fundus_of_patient_with_retinitis_pigmentosa,_end_stage.jpg}
-
-			\item \url{https://healthjade.net/retinitis-pigmentosa/}
-
-			\item \url{https://www.reviewofoptometry.com/article/night-spots}
-
-			\item \url{https://www.visualsurgery.com/eye-conditions/retinal-diseases/other-retinal-diseases/retinitis-pigmentosa/}
-
-			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
-
-			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
-
-			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
-
-			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
-
-			\item \url{https://emedicine.medscape.com/article/1227488-overview?form=basic}
-
-			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
-
-			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
-
-			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
-
-			\item \url{https://webvision.med.utah.edu/book/electrophysiology/the-electroretinogram-clinical-applications/}
-
-			\item \url{https://www.retinarevealed.com/retinitis-pigmentosa-page-34-of-49/}
-
-			\item \url{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}
-
-			\item \url{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}
-
-			\item \url{https://www.nyp.org/advances/article/ophthalmology/retinitis-pigmentosa-mitigating-retinal-degeneration-with-crispr-technology}
-
-			\item \url{https://www.ehu.eus/en/-/pacientes-con-retinosis-pigmentaria-en-la-pole}
-
-			\item \url{https://en.wikipedia.org/wiki/Retinal_degeneration_%28rhodopsin_mutation%29}
-
-			\item \url{https://imagebank.asrs.org/file/29807/x-linked-retinitis-pigmentosa}
-
-			\item \url{https://educate.choroida.com/2023/04/07/choroideremia-unveiling-what-you-need-to-know/}
-
-			\item \url{https://retinography.org/retinitis-pigmentosa-2/}
-
-			\item \url{https://retinography.org/retinitis-pigmentosa-2/}
-
-			\item \url{https://retinography.org/retinitis-pigmentosa/}
-
-			\item \url{https://retinography.org/retinitis-pigmentosa/}
+		\item \nolinkurl{https://imagebank.asrs.org/file/93471/retinitis-pigmentosa}
+
+		\item \nolinkurl{https://educate.choroida.com/2021/07/05/retinitis-pigmentosa/}
+
+		\item \nolinkurl{https://decisionmakerplus.net/dg-post/h35-52-retinitis-pigmentosa/}
+
+		\item \nolinkurl{https://basicmedicalkey.com/retinitis-pigmentosa/}
+
+		\item \nolinkurl{https://www.news-medical.net/health/What-is-Retinitis-Pigmentosa.aspx}
+
+		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-photograph-of-an-individual-affected-with-retinitis-pigmentosa-The-fundus_fig3_40447070}
+
+		\item \nolinkurl{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F15/}
+
+		\item \nolinkurl{https://www.brainkart.com/article/Retinal-Dystrophies--Retinitis-Pigmentosa_26087/}
+
+		\item \nolinkurl{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}
+
+		\item \nolinkurl{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}
+
+		\item \nolinkurl{https://retinography.org/sector-retinitis-pigmentosa/}
+
+		\item \nolinkurl{https://retinography.org/sector-retinitis-pigmentosa/}
+
+		\item \nolinkurl{https://www.linkedin.com/posts/stevenlevymd_blindness-from-retinitis-pigmentosa-reversed-activity-7047214648877608960-ar4h}
+
+		\item \nolinkurl{https://atlas-1-elastic.atlasoph.com/photo.jsf;jsessionid=94EF0B6B067E676E8BCB3F2AD7B9885A?node=6475&locale=en}
+
+		\item \nolinkurl{https://dizziness-and-balance.com/disorders/visual/retinopathy/RP.html}
+
+		\item \nolinkurl{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}
+
+		\item \nolinkurl{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}
+
+		\item \nolinkurl{https://eyeandear.org/2020/07/a-new-era-in-retinal-research/}
+
+		\item \nolinkurl{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F14/}
+
+		\item \nolinkurl{https://commons.wikimedia.org/wiki/File:Fundus_of_patient_with_retinitis_pigmentosa,_end_stage.jpg}
+
+		\item \nolinkurl{https://healthjade.net/retinitis-pigmentosa/}
+
+		\item \nolinkurl{https://www.reviewofoptometry.com/article/night-spots}
+
+		\item \nolinkurl{https://www.visualsurgery.com/eye-conditions/retinal-diseases/other-retinal-diseases/retinitis-pigmentosa/}
+
+		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
+
+		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
+
+		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
+
+		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}
+
+		\item \nolinkurl{https://emedicine.medscape.com/article/1227488-overview?form=basic}
+
+		\item \nolinkurl{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
+
+		\item \nolinkurl{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
+
+		\item \nolinkurl{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}
+
+		\item \nolinkurl{https://webvision.med.utah.edu/book/electrophysiology/the-electroretinogram-clinical-applications/}
+
+		\item \nolinkurl{https://www.retinarevealed.com/retinitis-pigmentosa-page-34-of-49/}
+
+		\item \nolinkurl{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}
+
+		\item \nolinkurl{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}
+
+		\item \nolinkurl{https://www.nyp.org/advances/article/ophthalmology/retinitis-pigmentosa-mitigating-retinal-degeneration-with-crispr-technology}
+
+		\item \nolinkurl{https://www.ehu.eus/en/-/pacientes-con-retinosis-pigmentaria-en-la-pole}
+
+		\item \nolinkurl{https://en.wikipedia.org/wiki/Retinal_degeneration_%28rhodopsin_mutation%29}
+
+		\item \nolinkurl{https://imagebank.asrs.org/file/29807/x-linked-retinitis-pigmentosa}
+
+		\item \nolinkurl{https://educate.choroida.com/2023/04/07/choroideremia-unveiling-what-you-need-to-know/}
+
+		\item \nolinkurl{https://retinography.org/retinitis-pigmentosa-2/}
+
+		\item \nolinkurl{https://retinography.org/retinitis-pigmentosa-2/}
+
+		\item \nolinkurl{https://retinography.org/retinitis-pigmentosa/}
+
+		\item \nolinkurl{https://retinography.org/retinitis-pigmentosa/}
 	\end{enumerate}
-	}
 

### 2024-08-31 Paper/Paper.tex
rename ODADS in code to MAAM; change table headers to abbr.

@@
 				\centering
+				\fontsize{9}{12}\selectfont{
 				\caption{OCT Test}
@@
 				every last row/.style={ after row=\bottomrule}
-		]{Tables/abnormity_o_test.csv}
+				]{Tables/abnormity_o_test.csv}}
 			\end{table}
@@
 				\centering
+				\fontsize{9}{12}\selectfont{
 				\caption{Fundus Test}
@@
 				every last row/.style={after row=\bottomrule}
-		]{Tables/abnormity_f_test.csv}
+				]{Tables/abnormity_f_test.csv}}
 			\end{table}
@@
 		\centering
+		\fontsize{9}{12}\selectfont{
 		\caption{Diagnosis Test}
@@
 		every last row/.style={ after row=\bottomrule}
-		]{Tables/diagnosis2.csv}
+		]{Tables/diagnosis2.csv}}
 	\end{table}

### 2024-08-31 MAAM/Code/Abnormity_Models/classify_abnormity.py

@@ -14,11 +14,3 @@ def get_abnormities_probs(img, model, device):
     output = torch.nn.functional.softmax(output[0], dim=0)
     # print(output)
     return output
-
-def get_abnormity_probs_from_img(img, numClasses, device, featureExtract, modelName, foldername, wtsName):
-    model = abnormity_models.initialize_abnormity_model(modelName, numClasses, featureExtract)
-    model = model.to(device)
-    trainedModel = torch.load(f"ODADS/Data/Weights/{foldername}/{wtsName}")
-    model.load_state_dict(trainedModel["state_dict"])
-    utils.img_show(img)
-    return get_abnormities_probs(img, model, device)

### 2024-08-31 MAAM/Code/Diagnosis_Model/diagnose_disease.py

@@ -1,49 +1,0 @@
-import os
-import torch
-from Abnormity_Models import classify_abnormity
-from Diagnosis_Model import diagnosis_model
-from Utils import utils
-os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
-
-# small utilities. refactor later!
-# OUTDATED! rewrite
-
-def diagnose(oImgs, fImgs, diseaseName, device, modelName, dWtsTime, oWts, fWts):
-    criteria = utils.get_criteria()
-    oNumClasses = len(criteria["All"]["OCT"])
-    fNumClasses = len(criteria["All"]["Fundus"])
-    oAbnormityNum = len(criteria[diseaseName]["OCT"])
-    fAbnormityNum = len(criteria[diseaseName]["Fundus"])
-    abnormityNum = oAbnormityNum + fAbnormityNum
-    gradeLevels = abnormityNum + 1
-    
-    if oAbnormityNum != 0:
-        lenO = len(oImgs)
-        oOutputs = torch.empty([lenO, oNumClasses])
-        for i in range(lenO):
-            img = oImgs[i]
-            output = classify_abnormity.get_abnormity_probs_from_img(img, oNumClasses, device, True, modelName, oWts)
-            oOutputs[i] = output
-        oOutput, _ = torch.max(oOutputs, dim = 0)
-    if oAbnormityNum != 0:
-        lenF = len(fImgs)
-        fOutputs = torch.empty([lenF, fNumClasses])
-        for i in range(lenF):
-            img = fImgs[i]
-            output = classify_abnormity.get_abnormity_probs_from_img(img, fNumClasses, device, True, modelName, fWts)
-            fOutputs[i] = output
-        fOutput, _ = torch.max(fOutputs, dim = 0)
-    dInput = torch.concat((oOutput, fOutput), dim = 0)
-    
-    dModel, _ = diagnosis_model.Simple_Net(abnormityNum, gradeLevels)
-    dModel = dModel.to(device)
-    trainedModel = torch.load(f"ODADS/Data/Weights/D {dWtsTime}/D {diseaseName} {dWtsTime}.pth")
-    dModel.load_state_dict(trainedModel["state_dict"])
-    
-    output = dModel(dInput.to(device))[0]
-    print(output)
-    expectedVal = 0
-    for grade in range(len(output)):
-        expectedVal += grade * output[grade]
-    print(expectedVal)
-    return output, expectedVal

### 2024-08-31 MAAM/Code/Results/abnormity_confusion_matrix.py

@@ -37,6 +37,7 @@ def calc_and_save_numerical_results(csv_filename, type, source, conf_mat):
     table_folder = setting.table_folder
     table_path = os.path.join(table_folder, csv_filename + ".csv")
     abnormities = setting.get_abnormities("OCT Abnormities") if type == "OCT" else setting.get_abnormities("Fundus Abnormities")
+    abbr_abnormities = setting.get_abbr_abnormities("OCT Abnormities") if type == "OCT" else setting.get_abbr_abnormities("Fundus Abnormities")
     with open(table_path, 'w', newline = "") as file:
         writer = csv.writer(file)
         writer.writerow([
@@ -59,7 +60,7 @@ def calc_and_save_numerical_results(csv_filename, type, source, conf_mat):
             sensitivity = tp / (tp + fn)
             f1 = 2 * precision * sensitivity / (precision + sensitivity)
             writer.writerow([
-                abnormities[i][1],
+                abbr_abnormities[i][1],
                 f"{precision:.3f}",
                 f"{sensitivity:.3f}",
                 f"{specificity:.3f}",

### 2024-08-31 MAAM/Code/Results/abnormity_loss_and_acc.py

@@ -140,7 +140,7 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
         fig_file = "abnormity_Fundus_loss_and_acc.pdf" if type == "AF" else "abnormity_OCT_loss_and_acc.pdf"
         fig_path = os.path.join(fig_folder, fig_file)
         
-        fig = plt.figure(figsize=(8, 13))
+        fig = plt.figure(figsize=(4, 13))
         grid = gridspec.GridSpec(4, 1, wspace = 0, hspace = 0.2)
         plt.axis(False)
         plt.title("Fundus" if type == "AF" else "OCT")

### 2024-08-31 MAAM/Code/Utils/crop_imgs.py

@@ -1,39 +1,0 @@
-import os
-from PIL import Image
-
-# Crop white borders of images in source folder and save to target folder 
-
-source_folder = 'ODADS/Data/Data/Original/OCT/Drusen'
-target_folder = 'ODADS/Data/Data/Transformed/OCT/Drusen'
-
-os.makedirs(target_folder, exist_ok=True)
-
-number = 0
-for filename in os.listdir(source_folder):
-    file_path = os.path.join(source_folder, filename)
-    
-    with Image.open(file_path) as img:  
-        width, height = img.size
-        aspect_ratio = width / height
-        
-        if 0.9 <= aspect_ratio <= 1.1:  
-            top_prop = 0.06
-            bottom_prop = 0.9
-            horizontal_prop = 0.03
-        else:
-            top_prop = 0
-            bottom_prop = 1
-            horizontal_prop = 0
-        top_crop = int(height * top_prop)
-        bottom_crop = int(height * bottom_prop)
-        left_crop = int(width * horizontal_prop)
-        right_crop = width - left_crop
-        cropped_img = img.crop((left_crop, top_crop, right_crop, bottom_crop))
-        save_path = os.path.join(target_folder, filename)
-        cropped_img.save(save_path)
-
-    number += 1
-    if number % 5 == 0:
-        print(f"{number} imgs processed")
-
-print("Processing complete")

### 2024-08-31 MAAM/Code/Utils/get_TI.py

@@ -1,53 +1,0 @@
-import os
-import random
-import shutil
-from PIL import Image
-
-# randomly select images from each class in a folder and copy to another folder
-# alternatively, resize all images in each class in a folder to 224*224 and save to another folder  
-
-def resize_long_edge(img, long_edge_size = 224):
-    width, height = img.size
-    if width > height:
-        new_size = (long_edge_size, int(height * long_edge_size / width))
-        loc = (0, int((long_edge_size - new_size[1]) / 2))
-    else:
-        new_size = (int(long_edge_size * width / height), long_edge_size)
-        loc = (int((long_edge_size - new_size[0]) / 2), 0)
-    img = img.resize(new_size)
-    black_background = Image.new("RGB", (long_edge_size, long_edge_size), "black")
-    black_background.paste(img, loc)
-    return black_background
-
-def copy_images(image_list, src_folder, dest_folder):
-    for img_name in image_list:
-        shutil.copy(os.path.join(src_folder, img_name), os.path.join(dest_folder, img_name))
-
-def resize_and_save_images(image_list, src_folder, dest_folder):
-    for img_name in image_list:
-        src_path = os.path.join(src_folder, img_name)
-        dest_path = os.path.join(dest_folder, img_name)
-        img = Image.open(src_path)
-        img = resize_long_edge(img)
-        img.save(dest_path)
-
-
-resize_only = True
-choose_and_copy = False
-source_folder = "ODADS/Data/Images/TO_Original/Fundus/"
-target_folder = "ODADS/Data/Images/TO/Fundus/"
-os.makedirs(target_folder, exist_ok=True)
-all_classes = [f.name for f in os.scandir(source_folder) if f.is_dir()]
-for class_name in all_classes:
-    class_source_folder = f'{source_folder}{class_name}'
-    class_target_folder = f'{target_folder}{class_name}'
-    all_images = os.listdir(class_source_folder)
-    os.makedirs(class_target_folder, exist_ok=True)
-    if resize_only:
-        resize_and_save_images(all_images, class_source_folder, class_target_folder)
-    elif choose_and_copy:
-        m = 300
-        random.shuffle(all_images)
-        all_images = all_images[:m]
-        copy_images(all_images, class_source_folder, class_target_folder)
-    print(class_name)

### 2024-08-31 MAAM/Code/Utils/get_TR_and_TO.py

@@ -1,143 +1,0 @@
-import os
-import random
-import shutil
-from PIL import Image
-import torchvision.transforms as transforms
-
-# read from Original images
-# split non-GAN images into test and train
-# add GAN images to train
-
-# transform and save test images to test folder
-# resize and save train images to temp_train folder
-# transform and save train images from temp_train to train folder
-
-def resize_long_edge(img, longEdgeSize = 224):
-    width, height = img.size
-    if longEdgeSize == 0:
-        longEdgeSize = max(width, height)
-    if width > height:
-        newSize = (longEdgeSize, int(height * longEdgeSize / width))
-        loc = (0, int((longEdgeSize - newSize[1]) / 2))
-    else:
-        newSize = (int(longEdgeSize * width / height), longEdgeSize)
-        width, _ = img.size
-        loc = (int((longEdgeSize - newSize[0]) / 2), 0)
-    img = img.resize(newSize)
-    blackBackground = Image.new("RGB", (longEdgeSize, longEdgeSize), "black")
-    blackBackground.paste(img, loc)
-    return blackBackground
-
-def copy_images(image_list, src_folder, dest_folder, resize, add_prefix = True):
-    for img_name in image_list:
-        img_path = os.path.join(src_folder, img_name)
-        image = Image.open(img_path)
-        if resize:
-            image = resize_long_edge(image, longEdgeSize=resize)
-        save_image(image, f"original_{img_name}" if add_prefix else img_name, dest_folder)
-
-def save_image(image, img_name, folder):
-    image.save(os.path.join(folder, img_name))
-
-def filter_images(images):
-    ignore_suffixes = ['_fake.jpg', '_fake.jpeg', '_fake.JPG', '_fake.JPEG', '_fake.png', '_fake.PNG']
-    return [img for img in images if not any(img.endswith(suffix) for suffix in ignore_suffixes)]
-
-def flip_and_save(images, src_folder, dest_folder, resize):
-    flip_transform = transforms.RandomHorizontalFlip(p=1.0)
-    for img_name in images:
-        img_path = os.path.join(src_folder, img_name)
-        flipped_image = flip_transform(Image.open(img_path))
-        if resize:
-            flipped_image = resize_long_edge(flipped_image, longEdgeSize=resize)
[…]

### 2024-08-31 MAAM/Code/Utils/ppm_to_jpeg.py

@@ -1,20 +1,0 @@
-import os
-from PIL import Image
-
-# convert all images within root_folder from .ppm to .jpg
-
-def convert_ppm_to_jpg(root_folder):
-    for root, _, files in os.walk(root_folder):
-        for file in files:
-            if file.lower().endswith('.ppm'):
-                ppm_path = os.path.join(root, file)
-
-                with Image.open(ppm_path) as img:
-                    jpg_path = os.path.splitext(ppm_path)[0] + '.jpg'
-                    img.save(jpg_path, 'JPEG')
-                
-                os.remove(ppm_path)
-                print(f'Converted and deleted: {ppm_path}')
-
-root_folder = ''
-convert_ppm_to_jpg(root_folder)

### 2024-08-31 MAAM/Code/Utils/utils.py

@@ -13,7 +13,7 @@ os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
 # read Criteria.json and get criteria
 def get_criteria():
-    with open('ODADS/Code/criteria.json', 'r', encoding='utf-8') as file:
+    with open('MAAM/Code/criteria.json', 'r', encoding='utf-8') as file:
         criteria = json.load(file)
     return criteria
 
@@ -24,7 +24,7 @@ def load_json(filename: str) -> Dict:
 
 # read Setting.json
 def get_setting():
-    json_data = load_json('ODADS/CODE/Setting.json')
+    json_data = load_json('MAAM/Code/Setting.json')
     return setting.Setting.from_dict(json_data)
 
 # resize the image so that its longer edge has length "longEdgeSize"

### 2024-08-31 MAAM/Code/setting.py

@@ -170,6 +170,17 @@ class Setting:
             return oct_abnormities
         else:
             return fundus_abnormities
+        
+    def get_abbr_abnormities(self, name: str = "All Abnormities") -> list:
+        criteria = utils.get_criteria()
+        oct_abnormities = [("OCT", abnormity) for abnormity in criteria["All"]["OCT Abbr"]]
+        fundus_abnormities = [("Fundus", abnormity) for abnormity in criteria["All"]["Fundus Abbr"]]
+        if name == "All Abnormities":
+            return  oct_abnormities + fundus_abnormities
+        elif self.is_OCT(name) or name == "OCT Abnormities":
+            return oct_abnormities
+        else:
+            return fundus_abnormities
     
     def get_correct_abnormities(self, name: str) -> list:
         criteria = utils.get_criteria()
@@ -270,6 +281,14 @@ class Setting:
             diseases = [disease for disease in criteria.keys() if disease != "All"]
         else:
             diseases = [disease for disease in criteria.keys() if disease != "All" and disease != "Normal"]
+        return diseases
+    
+    def get_abbr_diseases(self, include_normal: bool = True) -> list:
+        criteria = utils.get_criteria()
+        if include_normal:
+            diseases = criteria["All"]["Disease Abbr"]
+        else:
+            diseases = [disease for disease in criteria["All"]["Disease Abbr"] if disease != "Healthy"]
         return diseases
     
     def get_epoch_num(self, filename: str) -> int:

### 2024-08-31 MAAM/Code/Results/abnormity_loss_and_acc.py
refine acc and loss graph

@@ -116,23 +116,17 @@ def plot_loss_and_acc_alt(): # (2x1) x (2x2) x (2x1)
             loss_ax.plot(rsf["epoch train"], rsf["valid losses"], color='red')
     
     plt.show()
-    plt.save(fig_path)
-    
-    
-    
-    
-    
-    
-    
-    
+    plt.savefig(fig_path)
+
+
 def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
     setting = utils.get_setting()
     fig_folder = setting.fig_folder
     net_list = [
-        ("152", 0), 
-        ("050", 1),
-        ("018", 2),
-        ("016", 3)
+        ("152", (0, 0)), 
+        ("050", (0, 1)),
+        ("018", (1, 0)),
+        ("016", (1, 1))
     ]
     
     for type in ["AF", "AO"]:
@@ -140,16 +134,16 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
         fig_file = "abnormity_Fundus_loss_and_acc.pdf" if type == "AF" else "abnormity_OCT_loss_and_acc.pdf"
         fig_path = os.path.join(fig_folder, fig_file)
         
-        fig = plt.figure(figsize=(4, 13))
-        grid = gridspec.GridSpec(4, 1, wspace = 0, hspace = 0.2)
+        fig = plt.figure(figsize=(8, 6))
+        grid = gridspec.GridSpec(2, 2, wspace = 0, hspace = 0.2)
         plt.axis(False)
         plt.title("Fundus" if type == "AF" else "OCT")
         
         for net_name, pos in net_list:
-            sub_ax = fig.add_subplot(grid[pos, 0])
+            sub_ax = fig.add_subplot(grid[pos])
             sub_ax.set_title(net_name)
             sub_ax.set_axis_off()
-            sub_grid = gridspec.GridSpecFromSubplotSpec(2, 1, subplot_spec = grid[pos, 0], wspace = 0, hspace = 0.05)
+            sub_grid = gridspec.GridSpecFromSubplotSpec(2, 1, subplot_spec = grid[pos], wspace = 0, hspace = 0.05)
             
             rst = get_loss_and_acc(net_name, type) # ReSults from Transferred learning
             rsf = get_loss_and_acc(net_name, type, starting_epoch = rst["best epoch"]) # ReSults from Finetuning

### 2024-08-31 MAAM/Code/Results/abnormity_loss_and_acc.py
continue refining acc and loss graph

@@ -3,7 +3,7 @@ import os
 import numpy as np
 from Utils import utils
 import matplotlib.pyplot as plt
-import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
 import matplotlib.gridspec as gridspec
 
 def read_csv(path):
@@ -129,13 +129,18 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
         ("016", (1, 1))
     ]
     
+    plt.rcParams['axes.titlesize'] = 12
+    plt.rcParams['axes.labelsize'] = 9
+    plt.rcParams['xtick.labelsize'] = 9
+    plt.rcParams['ytick.labelsize'] = 9
+    
     for type in ["AF", "AO"]:
         best_net = setting.best_f_net if type == "AF" else setting.best_o_net
         fig_file = "abnormity_Fundus_loss_and_acc.pdf" if type == "AF" else "abnormity_OCT_loss_and_acc.pdf"
         fig_path = os.path.join(fig_folder, fig_file)
         
         fig = plt.figure(figsize=(8, 6))
-        grid = gridspec.GridSpec(2, 2, wspace = 0, hspace = 0.2)
+        grid = gridspec.GridSpec(2, 2, wspace = 0.05, hspace = 0.25)
         plt.axis(False)
         plt.title("Fundus" if type == "AF" else "OCT")
         
@@ -143,7 +148,7 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
             sub_ax = fig.add_subplot(grid[pos])
             sub_ax.set_title(net_name)
             sub_ax.set_axis_off()
-            sub_grid = gridspec.GridSpecFromSubplotSpec(2, 1, subplot_spec = grid[pos], wspace = 0, hspace = 0.05)
+            sub_grid = gridspec.GridSpecFromSubplotSpec(2, 1, subplot_spec = grid[pos], wspace = 0, hspace = 0.025)
             
             rst = get_loss_and_acc(net_name, type) # ReSults from Transferred learning
             rsf = get_loss_and_acc(net_name, type, starting_epoch = rst["best epoch"]) # ReSults from Finetuning
@@ -172,6 +177,22 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
             loss_ax.plot(rsf["epoch train"], rsf["train losses"], color='blue')
             loss_ax.plot(rst["epoch train"], rst["valid losses"], color='red')
[…]

### 2024-09-01 Paper/Paper.tex
change layout
Complete refining acc and loss graph

@@
 
+	\vspace{-0.2cm}
+	\hrule
+	\vspace{-0.1cm}
 	\section*{Abstract}
-
+	\hrule
+	\vspace{0.4cm}
 	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis.
@@
 And it gets the overall accuracy of 89\% and thus the feasibility is verified.
-
+	\vspace{0.4cm}
+	\hrule
+	\vspace{1cm}
+
+	\begin{multicols}{2}
 	\section{Background}
@@
 
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/model_overview.pdf}
-		\caption{Model Overview}
-		\vspace{0.3cm}
-		\label{fig:3_parts}
-	\end{figure}
-
 	The structure of the MAAM is shown in Fig.~\ref{fig:3_parts}.
@@
 
+	\end{multicols}
+
+	\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figs/model_overview.pdf}
+	\caption{Model Overview}
+	\vspace{0.3cm}
+	\label{fig:3_parts}
+	\end{figure}
+
 	\begin{figure}[htbp]
@@
 	\end{figure}
+
+	\begin{multicols}{2}
 
@@
 	We use the fused vector as an input for each submodels in Stage D1, and have the vector go through a FC layer with softmax operation to yield severity level probability vectors.
+
+	\end{multicols}
 
@@
 	For both OCT and Fundus Models, we trained 4 commonly used CNNs: ResNet152, ResNet50, ResNet18, and VGG16.
-The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train}.
+The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:A_train}.
 
@@
 		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
-		\caption{AO train}
-		\vspace{0.3cm}
-		\label{fig:AO_train}
-	\end{figure}
-
-	\begin{figure}[htbp]
-		\centering
+	\end{figure}
+	\begin{figure}[htbp]
+		\centering
+		\vspace{-1cm}
 		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
-		\caption{AF train}
-		\vspace{0.3cm}
-		\label{fig:AF_train}
+		\caption{Abnormity training}
+		\vspace{0.3cm}
+		\label{fig:A_train}
 	\end{figure}

### 2024-09-01 MAAM/Code/Results/abnormity_loss_and_acc.py

@@ -31,7 +31,7 @@ def get_loss_and_acc(net_name, type, starting_epoch = 0):
     test_rs_file = os.path.join(A_folder, setting.get_testing_rs_name(name))
     train_rs = read_csv(train_rs_file)
     test_rs, best_epoch, best_acc = read_csv(test_rs_file)
-    best_epoch = int(best_epoch)
+    best_epoch = int(best_epoch) + starting_epoch
     best_acc = float(best_acc)
     
     epoch_train = [int(row[0]) + starting_epoch for row in train_rs]
@@ -133,14 +133,17 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
     plt.rcParams['axes.labelsize'] = 9
     plt.rcParams['xtick.labelsize'] = 9
     plt.rcParams['ytick.labelsize'] = 9
+    plt.rcParams['legend.fontsize'] = 9
+    plt.rcParams['lines.linewidth'] = 1
     
     for type in ["AF", "AO"]:
         best_net = setting.best_f_net if type == "AF" else setting.best_o_net
         fig_file = "abnormity_Fundus_loss_and_acc.pdf" if type == "AF" else "abnormity_OCT_loss_and_acc.pdf"
         fig_path = os.path.join(fig_folder, fig_file)
         
-        fig = plt.figure(figsize=(8, 6))
+        fig = plt.figure(figsize=(8, 5) if type == "AO" else (8, 5.4))
         grid = gridspec.GridSpec(2, 2, wspace = 0.05, hspace = 0.25)
+        plt.subplots_adjust(left=0.1, right=0.9, top=0.9 if type == "AO" else 0.95, bottom=0.1 if type == "AO" else 0.2092592592592593)
         plt.axis(False)
         plt.title("Fundus" if type == "AF" else "OCT")
         
@@ -153,6 +156,7 @@ def plot_loss_and_acc(): # 2 x (4x1) x (2x2)
             rst = get_loss_and_acc(net_name, type) # ReSults from Transferred learning
             rsf = get_loss_and_acc(net_name, type, starting_epoch = rst["best epoch"]) # ReSults from Finetuning
             continuation_epoch = rst["best epoch"]
+            best_epoch = rst["best epoch"] if rst["best acc"] > rsf["best acc"] else rsf["best epoch"]
             rsf["epoch train"].insert(0, continuation_epoch)
             rsf["train acc"].insert(0, rst["train acc"][continuation_epoch - 1])
[…]

### 2024-09-01 MAAM/Code/Results/abnormity_loss_and_acc.py
Rename acc plot titles

@@ -56,80 +56,17 @@ def get_loss_and_acc(net_name, type, starting_epoch = 0):
         "combined acc": combined_acc
     }
 
-def plot_loss_and_acc_alt(): # (2x1) x (2x2) x (2x1)
-    setting = utils.get_setting()
-    fig_folder = setting.fig_folder
-    fig_file = "abnormity_loss_and_acc.pdf"
-    fig_path = os.path.join(fig_folder, fig_file)
-    
-    fig = plt.figure(figsize=(8, 12))
-    grid = gridspec.GridSpec(2, 1, wspace = 0, hspace = 0.3)
-    plt.axis(False)
-
-    model_list = [
-        ("AF", 0, "152"), 
-        ("AO", 1, "050")
-    ]
-
-    net_list = [
-        ("152", 0, 0), 
-        ("050", 0, 1),
-        ("018", 1, 0),
-        ("016", 1, 1)
-    ]
-    
-    for type, pos, best_net in model_list:
-        sub_ax = fig.add_subplot(grid[pos, 0])
-        sub_ax.set_title("Fundus" if type == "AF" else "OCT")
-        sub_ax.set_axis_off()
-        sub_grid = gridspec.GridSpecFromSubplotSpec(2, 2, subplot_spec = grid[pos, 0], wspace = 0.3, hspace = 0.3)
-        
-        for net_name, pos_x, pos_y in net_list:
-            subsub_ax = fig.add_subplot(sub_grid[pos_x, pos_y])
-            subsub_ax.set_title(net_name)
-            subsub_ax.set_axis_off()
-            subsub_grid = gridspec.GridSpecFromSubplotSpec(2, 1, subplot_spec = sub_grid[pos_x, pos_y], wspace = 0, hspace = 0.1)
-            
-            rst = get_loss_and_acc(net_name, type) # ReSults from Transferred learning
-            rsf = get_loss_and_acc(net_name, type, starting_epoch = rst["best epoch"]) # ReSults from Finetuning
-            continuation_epoch = rst["best epoch"]
-            rsf["epoch train"].insert(0, continuation_epoch)
-            rsf["train acc"].insert(0, rst["train acc"][continuation_epoch - 1])
-            rsf["train losses"].insert(0, rst["train losses"][continuation_epoch - 1])
-            rsf["valid acc"].insert(0, rst["valid acc"][continuation_epoch - 1])
[…]

### 2024-09-01 MAAM/Code/Results/abnormity_ROC.py
Complete refining abnormity ROC

@@ -1,15 +1,18 @@
 import csv
 import os
 import numpy as np
+from matplotlib.lines import Line2D
 from Utils import utils
 from sklearn.metrics import roc_curve, auc
 import matplotlib.pyplot as plt
-import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
 
-def plot_single_roc(type, abnormity, draw_roc = True, ax = None):
-    colors = {"TR": "red", "TO": "green"}
+def plot_single_roc(type, abnormity, draw_roc = True, ax = None, row = 0, col = 0):
+    colors = {"TR": "#FF0000", "TO": "#00BB00"}
+    linewidths = {"TR": 1.2, "TO": 1.2}
     
     setting = utils.get_setting()
+    abbr = setting.convert_abnormity_to_abbr(abnormity, type)
     abnormities = setting.get_abnormities("OCT Abnormities") if type == "OCT" else setting.get_abnormities("Fundus Abnormities")
     abnormity_index = abnormities.index((type, abnormity))
     abnormity_folder_path = setting.A_folder
@@ -41,11 +44,24 @@ def plot_single_roc(type, abnormity, draw_roc = True, ax = None):
         fpr, tpr, _ = roc_curve(labels, probs)
         aucs[source] = auc(fpr, tpr)
         if draw_roc:
-            ax.plot(fpr, tpr, color = colors[source])
+            ax.plot(fpr, tpr, color = colors[source], linewidth = linewidths[source])
             ax.set_xlim([0.0, 1.0])
             ax.set_ylim([0.0, 1.0])
     if draw_roc:
-        ax.plot([0, 1], [0, 1], color = "black")
+        ax.plot([0, 1], [0, 1], color = "gray", linewidth = 0.6)
+        ax.text(0.95, 0.05, abbr, verticalalignment='bottom', horizontalalignment='right', fontsize=9)
+        ax.set_xticks([0, 0.25, 0.5, 0.75, 1])
+        ax.xaxis.set_ticks_position('top')
+        ax.set_yticks([0, 0.25, 0.5, 0.75, 1])
+        ax.xaxis.set_tick_params(labelbottom=False, labeltop=True)
+        if row == 0 or row == 3:
+            ax.set_xticklabels(["0", "", "0.5", "", "1"])
+        else:
+            ax.set_xticks([])
+        if col == 0:
+            ax.set_yticklabels(["0", "", "0.5", "", "1"])
+        else:
[…]

### 2024-09-01 MAAM/Code/setting.py

@@ -182,6 +182,11 @@ class Setting:
         else:
             return fundus_abnormities
     
+    def convert_abnormity_to_abbr(self, abnormity: str, type: str) -> str:
+        abnormities = self.get_abnormities("OCT Abnormities" if type == "AO" or type == "OCT" else "Fundus Abnormities")
+        abbr_abnormities = self.get_abbr_abnormities("OCT Abnormities" if type == "AO" or type == "OCT" else "Fundus Abnormities")
+        return abbr_abnormities[abnormities.index(("OCT" if type == "AO" or type == "OCT" else "Fundus", abnormity))][1]
+    
     def get_correct_abnormities(self, name: str) -> list:
         criteria = utils.get_criteria()
         disease_name = self.get_disease_name(name)

### 2024-09-01 MAAM/Code/Results/abnormity_loss_and_acc.py
Update loss and acc graph to include axis titles

@@ -78,15 +78,18 @@ def plot_loss_and_acc():
         fig_file = "abnormity_Fundus_loss_and_acc.pdf" if type == "AF" else "abnormity_OCT_loss_and_acc.pdf"
         fig_path = os.path.join(fig_folder, fig_file)
         
-        fig = plt.figure(figsize=(8, 5) if type == "AO" else (8, 5.4))
+        fig = plt.figure(figsize=(8, 5) if type == "AO" else (8, 5.6))
         grid = gridspec.GridSpec(2, 2, wspace = 0.05, hspace = 0.25)
-        plt.subplots_adjust(left=0.1, right=0.9, top=0.9 if type == "AO" else 0.95, bottom=0.1 if type == "AO" else 0.2092592592592593)
+        plt.subplots_adjust(left=0.1, right=0.9, top=0.9 if type == "AO" else 0.95, bottom=0.1 if type == "AO" else 0.2357142857142857)
         plt.axis(False)
         plt.title("Fundus" if type == "AF" else "OCT", fontsize = 12)
         
         for net_name, net_name_title, pos in net_list:
             sub_ax = fig.add_subplot(grid[pos])
-            sub_ax.set_title(net_name_title)
+            if pos[0] == 1:
+                sub_ax.set_title(net_name_title, pad = 3.5)
+            else:
+                sub_ax.text(0.5, -0.03, net_name_title,ha='center', va='top', fontsize=9)
             sub_ax.set_axis_off()
             sub_grid = gridspec.GridSpecFromSubplotSpec(2, 1, subplot_spec = grid[pos], wspace = 0, hspace = 0.025)
             
@@ -123,12 +126,20 @@ def plot_loss_and_acc():
             loss_ax.axvline(x=continuation_epoch, linewidth = 0.7, color='gray', linestyle='--')
             loss_ax.axvline(x=best_epoch, linewidth = 0.5, color='gray', linestyle='-')
 
+            
             acc_ax.xaxis.set_ticks([])
             if pos[1] == 1:
                 acc_ax.yaxis.tick_right()
                 acc_ax.yaxis.set_label_position('right')
                 loss_ax.yaxis.tick_right()
                 loss_ax.yaxis.set_label_position('right')
+            else:
+                acc_ax.set_ylabel("Accuracy")
+                loss_ax.set_ylabel("Loss")
+            if pos[0] == 0:
+                loss_ax.xaxis.set_ticks([])
+            else:
[…]

### 2024-09-01 MAAM/Code/Results/abnormity_ROC.py
Complete refining all ROCs

@@ -110,9 +110,10 @@ def plot_roc():
     legend_lines = [
         Line2D([0], [0], color=colors["TR"], linewidth = 1.2, linestyle='-', label='ROC for training'),
         Line2D([0], [0], color=colors["TO"], linewidth = 1.2,linestyle='-', label='ROC for testing'),
+        Line2D([0], [0], color="gray", linewidth = 0.6,linestyle='-', label='y = x'),
     ]
     fig.legend(handles=legend_lines, ncols = 2, loc = "lower right", bbox_to_anchor = (0.91,0.1))
-    fig.text(0.898, 0.17, "Horizontal axes: specificity\nVertical axes: sensitivity", fontsize=9, 
+    fig.text(0.898, 0.2, "Horizontal axes: specificity\nVertical axes: sensitivity", fontsize=9, 
         verticalalignment='bottom', horizontalalignment='right', bbox=dict(facecolor='white', edgecolor='#D1D1D1', boxstyle='round,pad=0.25'))
     plt.savefig(fig_path)
     plt.show()

### 2024-09-01 MAAM/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py

@@ -8,6 +8,7 @@ import csv
 from sklearn.manifold import TSNE
 from sklearn.metrics import roc_curve, auc
 import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
 from Diagnosis_Model import diagnosis_model
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
@@ -31,14 +32,21 @@ def plot_tSNE(features, labels, diseases):
     plt.show()
 
 def plot_all_ROC(labels, probs, diseases, draw_roc = True):
+    plt.rcParams['axes.titlesize'] = 9
+    plt.rcParams['axes.labelsize'] = 9
+    plt.rcParams['xtick.labelsize'] = 9
+    plt.rcParams['ytick.labelsize'] = 9
+    plt.rcParams['legend.fontsize'] = 9
+    
     setting = utils.get_setting()
     fig_folder = setting.fig_folder
     fig_file = "diagnosis2_ROC.pdf"
     fig_path = os.path.join(fig_folder, fig_file)
     
     if draw_roc:
-        fig = plt.figure(figsize = (8, 8))
-        axs = fig.subplots(4, 4)
+        fig = plt.figure(figsize = (8, 5))
+        axs = fig.subplots(3, 5)
+        plt.subplots_adjust(wspace=0.1, hspace=0.125)
     
     row = 0
     col = 0
@@ -48,20 +56,42 @@ def plot_all_ROC(labels, probs, diseases, draw_roc = True):
         fpr, tpr, _ = roc_curve(labels[disease], probs[disease])
         aucs.append(auc(fpr, tpr))
         if draw_roc:
-            axs[row, col].plot(fpr, tpr, color = "red")
-            axs[row, col].set_xlim([0.0, 1.0])
-            axs[row, col].set_ylim([0.0, 1.0])
-            axs[row, col].plot([0, 1], [0, 1], color = "black")
-        if col == 3:
+            ax = axs[row, col]
+            abbr = setting.convert_disease_to_abbr(disease)
+            ax.plot(fpr, tpr, color = "#FF0000", linewidth = 1.2)
+            ax.set_xlim([0.0, 1.0])
+            ax.set_ylim([0.0, 1.0])
+            ax.plot([0, 1], [0, 1], color = "gray", linewidth = 0.6)
+            ax.text(0.95, 0.05, abbr, verticalalignment='bottom', horizontalalignment='right', fontsize=9)
[…]

### 2024-09-01 MAAM/Code/setting.py

@@ -187,6 +187,11 @@ class Setting:
         abbr_abnormities = self.get_abbr_abnormities("OCT Abnormities" if type == "AO" or type == "OCT" else "Fundus Abnormities")
         return abbr_abnormities[abnormities.index(("OCT" if type == "AO" or type == "OCT" else "Fundus", abnormity))][1]
     
+    def convert_disease_to_abbr(self, disease: str) -> str:
+        diseases = self.get_diseases()
+        abbr_diseases = self.get_abbr_diseases()
+        return abbr_diseases[diseases.index(disease)]
+    
     def get_correct_abnormities(self, name: str) -> list:
         criteria = utils.get_criteria()
         disease_name = self.get_disease_name(name)

### 2024-09-01 MAAM/Code/Results/abnormity_ROC.py
Refine D1 confusion matrix

@@ -115,5 +115,5 @@ def plot_roc():
     fig.legend(handles=legend_lines, ncols = 2, loc = "lower right", bbox_to_anchor = (0.91,0.1))
     fig.text(0.898, 0.2, "Horizontal axes: specificity\nVertical axes: sensitivity", fontsize=9, 
         verticalalignment='bottom', horizontalalignment='right', bbox=dict(facecolor='white', edgecolor='#D1D1D1', boxstyle='round,pad=0.25'))
-    plt.savefig(fig_path)
+    plt.savefig(fig_path, bbox_inches = "tight")
     plt.show()

### 2024-09-01 MAAM/Code/Results/abnormity_confusion_matrix.py

@@ -31,6 +31,10 @@ def plot_complete_conf_mat(ax, complete_conf_mat, abnormities):
     for i in range(complete_conf_mat.shape[0]):
         for j in range(complete_conf_mat.shape[1]):
             ax.text(j, i, complete_conf_mat[i, j], ha='center', va='center', color='black' if complete_conf_mat[i, j] < max / 2 else 'white')
+    ax.set_xticks(np.arange(len(abnormities)))
+    ax.set_yticks(np.arange(len(abnormities)))
+    ax.set_xticklabels(abnormities)
+    ax.set_yticklabels(abnormities)
 
 def calc_and_save_numerical_results(csv_filename, type, source, conf_mat):
     setting = utils.get_setting()
@@ -82,8 +86,10 @@ def plot_all_conf_mat():
     f_test_mr_name = setting.get_f_tomr_name(setting.best_f_net)
     o_train_mr_name = setting.get_o_trmr_name(setting.best_o_net)
     f_train_mr_name = setting.get_f_trmr_name(setting.best_f_net)
-    o_abnormities = setting.get_abnormities("OCT Abnormities")
-    f_abnormities = setting.get_abnormities("Fundus Abnormities")
+    o_abbr_abnormities = setting.get_abbr_abnormities("OCT Abnormities")
+    o_abbr_abnormities = [abnormity[1] for abnormity in o_abbr_abnormities]
+    f_abbr_abnormities = setting.get_abbr_abnormities("Fundus Abnormities")
+    f_abbr_abnormities = [abnormity[1] for abnormity in f_abbr_abnormities]
     o_abnormity_num = setting.get_abnormity_num("OCT Abnormities")
     f_abnormity_num = setting.get_abnormity_num("Fundus Abnormities")
     
@@ -93,25 +99,25 @@ def plot_all_conf_mat():
     o_train_mr_path = os.path.join(abnormity_folder_path, o_train_mr_name + ".bin")
     o_train_mr = np.fromfile(o_train_mr_path, dtype = np.float64).reshape((o_abnormity_num, o_train_class_size, o_abnormity_num))
     o_train_conf_mat = get_complete_conf_mat(o_train_mr, o_abnormity_num)
-    plot_complete_conf_mat(axs[0, 0], o_train_conf_mat, o_abnormities)
+    plot_complete_conf_mat(axs[0, 0], o_train_conf_mat, o_abbr_abnormities)
[…]

### 2024-09-01 MAAM/Code/Results/diagnosis1_confusion_matrix.py

@@ -23,65 +23,6 @@ def get_conf_mat(disease):
             probs = mr[i][j]
             conf_mat[i][np.argmax(probs)] += 1
     return conf_mat
-'''
-def get_conf_mat(device, disease):
-    setting = utils.get_setting()
-    name = "000D1---- - " + disease
-    batch_size = setting.test_batch_size
-    class_size = setting.D1_test_class_size
-    abnormity_folder_path = setting.A_folder
-    o_class_size = setting.O_test_class_size
-    f_class_size = setting.F_test_class_size
-    wt_name = setting.get_d_wt_file_name(name)
-    o_mr_name = setting.get_o_tomr_name(setting.best_o_net)
-    f_mr_name = setting.get_f_tomr_name(setting.best_f_net)
-    folder_path = setting.get_folder_path(name)
-    o_abnormity_num = setting.get_abnormity_num("OCT Abnormities")
-    f_abnormity_num = setting.get_abnormity_num("Fundus Abnormities")
-    all_abnormity_num = setting.get_abnormity_num("All Abnormities")
-    label_levels = setting.get_disease_abnormity_num(disease, "All Abnormities") + 1
-    
-    o_mr_path = os.path.join(abnormity_folder_path, o_mr_name + ".bin")
-    o_mr = np.fromfile(o_mr_path, dtype = np.float64).reshape((o_abnormity_num, o_class_size, o_abnormity_num))
-    f_mr_path = os.path.join(abnormity_folder_path, f_mr_name + ".bin")
-    f_mr = np.fromfile(f_mr_path, dtype = np.float64).reshape((f_abnormity_num, f_class_size, f_abnormity_num))
-    
-    test_data = torch.zeros(label_levels * class_size, all_abnormity_num)
-    test_label = torch.zeros(label_levels * class_size, dtype=torch.long)
-    
-    model = diagnosis_model.Simple_Net(all_abnormity_num, label_levels).to(device)
-    trained_model = torch.load(os.path.join(folder_path, wt_name + ".pth"))
-    model.load_state_dict(trained_model["state_dict"])
-    
-    start_time = time.time()
-    
-    for label in range(label_levels):
-        for i in range(class_size):
-            output = utils.get_mr(device, disease, label, o_mr, f_mr)
-            test_data[label * class_size + i] = output
-            test_label[label * class_size + i] = label
-    test_dataset = torch.utils.data.TensorDataset(test_data, test_label)
[…]

### 2024-09-01 MAAM/Code/Results/abnormity_confusion_matrix.py
Refine Abnormities confusion matrices

@@ -25,16 +25,18 @@ def get_complete_conf_mat(mr, abnormity_num):
             conf_mat[i][np.argmax(probs)] += 1
     return conf_mat
 
-def plot_complete_conf_mat(ax, complete_conf_mat, abnormities):
+def plot_complete_conf_mat(ax, complete_conf_mat, abnormities, fontsize, title):
     mat = ax.matshow(complete_conf_mat, cmap='Blues')
     max = np.max(complete_conf_mat)
     for i in range(complete_conf_mat.shape[0]):
         for j in range(complete_conf_mat.shape[1]):
-            ax.text(j, i, complete_conf_mat[i, j], ha='center', va='center', color='black' if complete_conf_mat[i, j] < max / 2 else 'white')
+            ax.text(j, i, complete_conf_mat[i, j], ha='center', va='center', color='black' if complete_conf_mat[i, j] < max / 2 else 'white', fontsize = fontsize)
     ax.set_xticks(np.arange(len(abnormities)))
     ax.set_yticks(np.arange(len(abnormities)))
-    ax.set_xticklabels(abnormities)
+    ax.set_xticklabels(abnormities, rotation=-90)
     ax.set_yticklabels(abnormities)
+    ax.tick_params(axis='x', which='both', bottom=False)
+    ax.set_title(title, fontsize = 12)
 
 def calc_and_save_numerical_results(csv_filename, type, source, conf_mat):
     setting = utils.get_setting()
@@ -93,32 +95,37 @@ def plot_all_conf_mat():
     o_abnormity_num = setting.get_abnormity_num("OCT Abnormities")
     f_abnormity_num = setting.get_abnormity_num("Fundus Abnormities")
     
-    fig = plt.figure(figsize=(9, 8))
+    plt.rcParams['font.size'] = 9
+    plt.rcParams['xtick.labelsize'] = 9
+    plt.rcParams['ytick.labelsize'] = 9
+    
+    fig = plt.figure(figsize=(8, 8))
     axs = fig.subplots(2, 2)
+    fig.subplots_adjust(hspace = 0.35, wspace = 0.2)
     
     o_train_mr_path = os.path.join(abnormity_folder_path, o_train_mr_name + ".bin")
     o_train_mr = np.fromfile(o_train_mr_path, dtype = np.float64).reshape((o_abnormity_num, o_train_class_size, o_abnormity_num))
[…]

### 2024-09-01 MAAM/Code/Results/abnormity_confusion_matrix.py
Complete refining abnormity Confusion matrices

@@ -36,7 +36,7 @@ def plot_complete_conf_mat(ax, complete_conf_mat, abnormities, fontsize, title):
     ax.set_xticklabels(abnormities, rotation=-90)
     ax.set_yticklabels(abnormities)
     ax.tick_params(axis='x', which='both', bottom=False)
-    ax.set_title(title, fontsize = 12)
+    ax.set_title(title, fontsize = 12, pad = 20)
 
 def calc_and_save_numerical_results(csv_filename, type, source, conf_mat):
     setting = utils.get_setting()
@@ -99,9 +99,9 @@ def plot_all_conf_mat():
     plt.rcParams['xtick.labelsize'] = 9
     plt.rcParams['ytick.labelsize'] = 9
     
-    fig = plt.figure(figsize=(8, 8))
+    fig = plt.figure(figsize=(8, 9.5))
     axs = fig.subplots(2, 2)
-    fig.subplots_adjust(hspace = 0.35, wspace = 0.2)
+    fig.subplots_adjust(hspace = 0.55, wspace = 0.25)
     
     o_train_mr_path = os.path.join(abnormity_folder_path, o_train_mr_name + ".bin")
     o_train_mr = np.fromfile(o_train_mr_path, dtype = np.float64).reshape((o_abnormity_num, o_train_class_size, o_abnormity_num))

### 2024-09-01 MAAM/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py

@@ -171,10 +171,10 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
     
     #if plt_tSNE:
     #    plot_tSNE(tSNE_features, tSNE_labels, diseases_including_normal)
-    if plt_ROC:
-        aucs = plot_all_ROC(roc_labels, roc_probs, diseases_including_normal)
-    #if plt_conf_mat:
-    #    plot_conf_mat(conf_mat, diseases_including_normal)
+    #if plt_ROC:
+    #    aucs = plot_all_ROC(roc_labels, roc_probs, diseases_including_normal)
+    if plt_conf_mat:
+        plot_conf_mat(conf_mat, diseases_including_normal)
     
     with open(os.path.join(setting.D2_folder, "000D2TORS.csv"), "w", newline="") as file:
         writer = csv.writer(file)
@@ -190,7 +190,7 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
                 "FOne", 
                 "AUC"
             ])
-        for i in range(len(diseases_including_normal)):
+        '''for i in range(len(diseases_including_normal)):
             disease_conf_mat = get_single_conf_mat(conf_mat, i)
             tp = disease_conf_mat[0][0]
             fn = disease_conf_mat[0][1]
@@ -207,4 +207,4 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
                 f"{specificity:.3f}",
                 f"{f1:.3f}", 
                 f"{aucs[i]:.3f}"
-            ])
+            ])'''

### 2024-09-01 MAAM/Code/Results/abnormity_confusion_matrix.py
Refine D2 confusion matrix

@@ -33,7 +33,7 @@ def plot_complete_conf_mat(ax, complete_conf_mat, abnormities, fontsize, title):
             ax.text(j, i, complete_conf_mat[i, j], ha='center', va='center', color='black' if complete_conf_mat[i, j] < max / 2 else 'white', fontsize = fontsize)
     ax.set_xticks(np.arange(len(abnormities)))
     ax.set_yticks(np.arange(len(abnormities)))
-    ax.set_xticklabels(abnormities, rotation=-90)
+    ax.set_xticklabels(abnormities, rotation=90)
     ax.set_yticklabels(abnormities)
     ax.tick_params(axis='x', which='both', bottom=False)
     ax.set_title(title, fontsize = 12, pad = 20)

### 2024-09-01 MAAM/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py

@@ -105,17 +105,26 @@ def get_single_conf_mat(complete_conf_mat, index):
     return conf_mat
 
 def plot_conf_mat(conf_mat, diseases):
+    plt.rcParams['axes.titlesize'] = 9
+    plt.rcParams['axes.labelsize'] = 9
+    plt.rcParams['xtick.labelsize'] = 9
+    plt.rcParams['ytick.labelsize'] = 9
+    plt.rcParams['legend.fontsize'] = 9
+    
     setting = utils.get_setting()
     fig_folder = setting.fig_folder
     fig_file = "diagnosis2_confusion_matrix.pdf"
     fig_path = os.path.join(fig_folder, fig_file)
     
+
     mat = plt.matshow(conf_mat, cmap='Blues')
     max = np.max(conf_mat)
     for i in range(conf_mat.shape[0]):
         for j in range(conf_mat.shape[1]):
-            plt.text(j, i, conf_mat[i, j], ha='center', va='center', color='black' if conf_mat[i, j] < max / 2 else 'white')
-    
+            plt.text(j, i, conf_mat[i, j], ha='center', va='center', color='black' if conf_mat[i, j] < max / 2 else 'white', fontsize=7)
+    plt.xticks(np.arange(len(diseases)), labels=diseases, rotation=-90)
+    plt.yticks(np.arange(len(diseases)), labels=diseases)
+    plt.tick_params(axis='x', which='both', bottom=False)
     plt.savefig(fig_path)
     plt.show()
 
@@ -125,6 +134,7 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
     name = "000D2TOMR"
     tSNE_point_num = setting.tSNE_point_num
     diseases_including_normal = setting.get_diseases(include_normal = True)
+    abbr_diseases = setting.get_abbr_diseases(include_normal = True)
     disease_num_including_normal = setting.get_disease_num(include_normal = True)
     mr_path = os.path.join(setting.D2_folder, name + ".bin")
     mr = np.fromfile(mr_path, dtype = np.float64).reshape((disease_num_including_normal, setting.D2_test_class_size, disease_num_including_normal))
@@ -174,13 +184,13 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
     #if plt_ROC:
     #    aucs = plot_all_ROC(roc_labels, roc_probs, diseases_including_normal)
     if plt_conf_mat:
[…]

### 2024-09-01 MAAM/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py
Refine D2 tSNE

@@ -13,21 +13,32 @@ from Diagnosis_Model import diagnosis_model
 os.environ["KMP_DUPLICATE_LIB_OK"] = "TRUE"
 
 def plot_tSNE(features, labels, diseases):
+    plt.rcParams['axes.titlesize'] = 9
+    plt.rcParams['axes.labelsize'] = 9
+    plt.rcParams['xtick.labelsize'] = 9
+    plt.rcParams['ytick.labelsize'] = 9
+    plt.rcParams['legend.fontsize'] = 9
+    
     setting = utils.get_setting()
     fig_folder = setting.fig_folder
     fig_file = "diagnosis2_tSNE.pdf"
     fig_path = os.path.join(fig_folder, fig_file)
     
-    fig = plt.figure(figsize = (9, 8))
+    fig = plt.figure(figsize = (4, 3))
     
     tsne = TSNE(n_components=2)
     features_tsne = tsne.fit_transform(np.array(features))
-    
-    scatter = plt.scatter(features_tsne[:, 0], features_tsne[:, 1], c=labels, cmap='jet', alpha=0.5)
-    plt.colorbar(scatter)
+    s = 2
+    plt.scatter(features_tsne[:, 0], features_tsne[:, 1], c=labels, cmap='jet', marker='o', s=s)
     plt.xlabel('t-SNE Component 1')
     plt.ylabel('t-SNE Component 2')
     
+    handles = []
+    for i, disease in enumerate(diseases):
+        handle = Line2D([], [], color=plt.get_cmap('jet')(i / len(diseases)), marker='o', linestyle='None', markersize=s, label=disease)
+        handles.append(handle)
+    plt.legend(handles=handles, bbox_to_anchor=(1, 0.5), loc='center left')
+    plt.tight_layout()
     plt.savefig(fig_path)
     plt.show()
 
@@ -179,12 +190,12 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
     tSNE_features = np.concatenate(tSNE_features)
     tSNE_labels = np.concatenate(tSNE_labels)
     
-    #if plt_tSNE:
-    #    plot_tSNE(tSNE_features, tSNE_labels, diseases_including_normal)
+    if plt_tSNE:
+        plot_tSNE(tSNE_features, tSNE_labels, abbr_diseases)
     #if plt_ROC:
[…]

### 2024-09-01 MAAM/Code/Results/abnormity_tSNE.py
refine D2 tSNE

@@ -7,7 +7,7 @@ from sklearn.manifold import TSNE
 import matplotlib.pyplot as plt
 import matplotlib.pyplot as plt
 
-def plot_single_tsne(ax, mr, abnormities, tSNE_point_num, color_bar_on = True):
+def plot_single_tsne(ax, mr, abnormities, tSNE_point_num):
     shape = mr.shape
     features = []
     labels = []
@@ -25,11 +25,14 @@ def plot_single_tsne(ax, mr, abnormities, tSNE_point_num, color_bar_on = True):
     tsne = TSNE(n_components=2)
     features_tsne = tsne.fit_transform(np.array(features))
     
-    scatter = ax.scatter(features_tsne[:, 0], features_tsne[:, 1], c=labels, cmap='jet', alpha=0.5)
-    if color_bar_on:
-        plt.colorbar(scatter)
-    ax.set_xlabel('t-SNE Component 1')
-    ax.set_ylabel('t-SNE Component 2')
+    s=2
+    scatter = ax.scatter(features_tsne[:, 0], features_tsne[:, 1], c=labels, cmap='jet', marker='o', s=s)
+    for i, disease in enumerate(diseases):
+        handle = Line2D([], [], color=plt.get_cmap('jet')(i / len(diseases)), marker='o', linestyle='None', markersize=s, label=disease)
+        handles.append(handle)
+    plt.legend(handles=handles, bbox_to_anchor=(1, 0.5), loc='center left')
+    ax.set_xticks([])
+    ax.set_yticks([])
 
 def plot_tsne():
     setting = utils.get_setting()

### 2024-09-01 MAAM/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py

@@ -24,14 +24,14 @@ def plot_tSNE(features, labels, diseases):
     fig_file = "diagnosis2_tSNE.pdf"
     fig_path = os.path.join(fig_folder, fig_file)
     
-    fig = plt.figure(figsize = (4, 3))
+    fig = plt.figure(figsize = (4, 3.01))
     
     tsne = TSNE(n_components=2)
     features_tsne = tsne.fit_transform(np.array(features))
     s = 2
     plt.scatter(features_tsne[:, 0], features_tsne[:, 1], c=labels, cmap='jet', marker='o', s=s)
-    plt.xlabel('t-SNE Component 1')
-    plt.ylabel('t-SNE Component 2')
+    plt.xticks([])
+    plt.yticks([])
     
     handles = []
     for i, disease in enumerate(diseases):

### 2024-09-01 MAAM/Code/Results/abnormity_tSNE.py
Refine abnormitise tSNE

@@ -5,9 +5,9 @@ from Utils import utils
 import random
 from sklearn.manifold import TSNE
 import matplotlib.pyplot as plt
-import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
 
-def plot_single_tsne(ax, mr, abnormities, tSNE_point_num):
+def plot_single_tsne(ax, mr, abnormities, tSNE_point_num, add_legends, title):
     shape = mr.shape
     features = []
     labels = []
@@ -27,12 +27,15 @@ def plot_single_tsne(ax, mr, abnormities, tSNE_point_num):
     
     s=2
     scatter = ax.scatter(features_tsne[:, 0], features_tsne[:, 1], c=labels, cmap='jet', marker='o', s=s)
-    for i, disease in enumerate(diseases):
-        handle = Line2D([], [], color=plt.get_cmap('jet')(i / len(diseases)), marker='o', linestyle='None', markersize=s, label=disease)
-        handles.append(handle)
-    plt.legend(handles=handles, bbox_to_anchor=(1, 0.5), loc='center left')
+    if add_legends:
+        handles = []
+        for i, disease in enumerate(abnormities):
+            handle = Line2D([], [], color=plt.get_cmap('jet')(i / len(abnormities)), marker='o', linestyle='None', markersize=s, label=disease)
+            handles.append(handle)
+        ax.legend(handles=handles, bbox_to_anchor=(1.025, 0.5), loc='center left')
     ax.set_xticks([])
     ax.set_yticks([])
+    ax.set_title(title, pad = 10)
 
 def plot_tsne():
     setting = utils.get_setting()
@@ -49,29 +52,33 @@ def plot_tsne():
     f_test_mr_name = setting.get_f_tomr_name(setting.best_f_net)
     o_train_mr_name = setting.get_o_trmr_name(setting.best_o_net)
     f_train_mr_name = setting.get_f_trmr_name(setting.best_f_net)
-    o_abnormities = setting.get_abnormities("OCT Abnormities")
-    f_abnormities = setting.get_abnormities("Fundus Abnormities")
+    o_abnormities = setting.get_abbr_abnormities("OCT Abnormities")
+    o_abnormities = [abnormity[1] for abnormity in o_abnormities]
+    f_abnormities = setting.get_abbr_abnormities("Fundus Abnormities")
[…]

### 2024-09-01 MAAM/Code/Results/diagnosis1_acc_barchart.py
Refine D1 acc bar graph

@@ -2,6 +2,7 @@ import csv
 import os
 import matplotlib.pyplot as plt
 from Utils import utils
+import numpy as np
 
 # Add D2 accuracy with codominant method
 
@@ -12,28 +13,42 @@ def plot_acc_barchart():
     fig_file = "diagnosis1_acc_barchart.pdf"
     fig_path = os.path.join(fig_folder, fig_file)
     
+    plt.rcParams["font.size"] = 9
     diseases = []
     accs = []
     with open(csv_file_path, mode='r', newline='') as file:
         reader = csv.reader(file)
         for row in reader:
-            diseases.append(row[0])
+            diseases.append(setting.convert_disease_to_abbr(row[0]))
             accs.append(float(row[3]))
 
-    
+    fig = plt.figure(figsize=(8,3))
     plt.ylim(0.0, 1.0)
     plt.axhline(y = sum(accs) / len(accs), color='gray', linestyle='--')
     
     diseases.append("")
-    diseases.append("D2")
+    diseases.append("*")
+    diseases.append("**")
     accs.append(0.0)
     csv_file_path = os.path.join(setting.D2_folder, "000D2TORS.csv")
     with open(csv_file_path, mode='r', newline='') as file:
         reader = csv.reader(file)
         for row in reader:
-            accs.append(float(row[2]))
+            accs.append(float(row[3]))
+            accs.append(float(row[4]))
             break
-    plt.bar(diseases, accs)
+    plt.bar(diseases, accs, width = 0.6)
+    current_ticks = plt.xticks()[0]
+    current_labels = plt.xticks()[1]
+    new_ticks = [tick for tick, label in zip(current_ticks, current_labels) if tick != 12]
+    new_labels = [label for tick, label in zip(current_ticks, current_labels) if tick != 12]
+    plt.xticks(ticks=new_ticks, labels=new_labels)
+    plt.ylim([0, 1.1])
+    plt.yticks(ticks=[0,0.2,0.4,0.6,0.8,1.0])
+    plt.text(-0.9, 0.79, "Stage D1 Average", color = "gray")
+    plt.text(4.75, -0.25, "Stage D1", fontsize = 12)
+    plt.text(12.75, -0.25, "Stage D2", fontsize = 12)
     
+    plt.tight_layout()
     plt.savefig(fig_path)
     plt.show()

### 2024-09-01 Paper/Paper.tex
Complete refining abnormity ROC
Refine D1 confusion matrix
Refine Abnormities confusion matrices
Refine D2 confusion matrix
Refine D2 tSNE
adjust layout.

@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{Figs/criteria.pdf}
+		\includegraphics[width=0.7\linewidth]{Figs/criteria.pdf}
 		\caption{Abnormity-to-disease Deduction Criteria}
@@
 
+	\begin{multicols}{2}	
 	In Stage D2, we determine the final disease probability vector.
@@
 	In the MAAM, we leverage the fusion operation to incorporate all the results from different submodels. As shown in Fig.~\ref{fig:fusion}, there are totally 3 fusion operations in MAAM.
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/fusion.pdf}
-		\caption{Fusion}
-		\vspace{0.3cm}
-		\label{fig:fusion}
-	\end{figure}
 
@@
 
+	\end{multicols}
+
+	\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figs/fusion.pdf}
+	\caption{Fusion}
+	\vspace{0.3cm}
+	\label{fig:fusion}
+	\end{figure}
+
+	\begin{multicols}{2}
+
 	\section{Abnormity Models}
@@
 
+	For OCT abnormities with less than 1000 images, we use Cycle-GAN \autocite{Zhu_Park_Isola_Efros_2020} to generate new images.
+We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.
+We go through all generated images and adopt those that clearly display only the abnormity of interest.
+The adoption rates are shown in Table~\ref{tb:cycleGAN_number}.
+Fundus images are not generated using Cycle-GAN because generated fundus images are too blurry; in addition, fundus abnormities are usually less salient than OCT ones and cannot be properly learned by Cycle-GAN, given that we only have a small number of fundus images.
+	\end{multicols}
+
+	\vspace{-0.5cm}
 	\begin{minipage}[t]{0.4\linewidth}
@@
 
-	For OCT abnormities with less than 1000 images, we use Cycle-GAN \autocite{Zhu_Park_Isola_Efros_2020} to generate new images.
-We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.
-We go through all generated images and adopt those that clearly display only the abnormity of interest.
-The adoption rates are shown in Table~\ref{tb:cycleGAN_number}.
-Fundus images are not generated using Cycle-GAN because generated fundus images are too blurry; in addition, fundus abnormities are usually less salient than OCT ones and cannot be properly learned by Cycle-GAN, given that we only have a small number of fundus images.
-
 	{
@@
 
+	\begin{multicols}{2}
 	We split the images, including generated images, into training and test datasets, and implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images.
@@
 
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
-	\end{figure}
-	\begin{figure}[htbp]
-		\centering
-		\vspace{-1cm}
-		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
-		\caption{Abnormity training}
-		\vspace{0.3cm}
-		\label{fig:A_train}
-	\end{figure}
-
 	\vspace{0.3cm}
@@
 	After all the training and comparisons, we determine to use a finetuned model with ResNet50 for OCT Model and a finetuned model with ResNet152 for Fundus Model.
+
+	\end{multicols}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
+		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
+		\caption{Abnormity training}
+		\label{fig:A_train}
+	\end{figure}
 
@@
 	}
-
-	\subsection{Results}
-
-	Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values on the test dataset.
-Fig.~\ref{fig:A_ROC} shows the ROCs, Fig.~\ref{fig:A_conf_mat} shows the confusion matrices and Fig.~\ref{fig:A_tSNE} shows the t-SNE graphs for each abnormity.
-
-	The OCT Model tends to overfit, while the Fundus Model cannot reach a satisfying level in terms of DL. Overall, the performance of the OCT Model is significantly better than that of the Fundus Model.
-
-	Fundus abnormities tend to be less prominent than those of OCT, since the abnormity in fundus image are usually quite small and scattered.
-Moreover, one fundus image usually contains more than one abnormity, while most OCT images contain only one abnormity per image.
-Also, given that we have fewer fundus images than OCT ones, the difficulties for fundus classification increases.
-
-	In order to allow the Abnormity Models to identify multiple abnormities in one image, we employ a method to determine the codominant abnormities.
-We input an image to the Abnormity Models and get the abnormity probabilities vector.
-If the abnormity with the highest probability has probability greater than 0.9, it is regarded as dominant; if not, we continue taking the abnormity with the next high probability until either the sum of the probabilities of the chosen abnormities reaches 0.9, or the number of abnormities reaches the maximum, which is 4, and all the chosen abnormities are regarded as codominant.
 
@@
 	\end{table}
-
-			\begin{table}[htbp]
+	\begin{table}[H]
 		\centering
@@
 
+	\pagebreak
+
 	\begin{figure}[htbp]
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{Figs/abnormity_confusion_matrix.pdf}
+		\includegraphics[width=\linewidth]{Figs/abnormity_confusion_matrix.pdf}
 		\caption{A Conf Mat}
@@
 	\end{figure}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.pdf}
+		\caption{GradCAM}
+		\vspace{0.3cm}
+		\label{fig:gradCAM}
+	\end{figure}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
+		\caption{GradCAM with multiple abnormities}
+		\vspace{0.3cm}
+		\label{fig:gradCAM_multi_abnormity}
+	\end{figure}
+
+		\vspace{1.5cm}
+
+	\begin{multicols}{2}
+
+		\subsection{Results}
+
+		Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values on the test dataset.
+Fig.~\ref{fig:A_ROC} shows the ROCs, Fig.~\ref{fig:A_conf_mat} shows the confusion matrices and Fig.~\ref{fig:A_tSNE} shows the t-SNE graphs for each abnormity.
+
+		The OCT Model tends to overfit, while the Fundus Model cannot reach a satisfying level in terms of DL.
+Overall, the performance of the OCT Model is significantly better than that of the Fundus Model.
+
+		Fundus abnormities tend to be less prominent than those of OCT, since the abnormity in fundus image are usually quite small and scattered.
+Moreover, one fundus image usually contains more than one abnormity, while most OCT images contain only one abnormity per image.
+Also, given that we have fewer fundus images than OCT ones, the difficulties for fundus classification increases.
+
+		In order to allow the Abnormity Models to identify multiple abnormities in one image, we employ a method to determine the codominant abnormities.
+We input an image to the Abnormity Models and get the abnormity probabilities vector.
+If the abnormity with the highest probability has probability greater than 0.9, it is regarded as dominant; if not, we continue taking the abnormity with the next high probability until either the sum of the probabilities of the chosen abnormities reaches 0.9, or the number of abnormities reaches the maximum, which is 4, and all the chosen abnormities are regarded as codominant.
 
@@
 In the images on the left and right, we use Grad-CAM to highlight the codominant abnormities.
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.pdf}
-		\caption{GradCAM}
-		\vspace{0.3cm}
-		\label{fig:gradCAM}
-	\end{figure}
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
-		\caption{GradCAM with multiple abnormities}
-		\vspace{0.3cm}
-		\label{fig:gradCAM_multi_abnormity}
-	\end{figure}
 
@@
 
+	\end{multicols}
+
 	\begin{figure}[htbp]
@@
 
-	\begin{table}[htbp]
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
+		\caption{D2 ROC}
+		\vspace{0.3cm}
+		\label{fig:D2_ROC}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.7\linewidth]{Figs/diagnosis2_confusion_matrix.pdf}
+		\vspace{-0.8cm}
+		\caption{D2 Conf Mat}
+		\label{fig:D2_conf_mat}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.65\linewidth]{Figs/diagnosis2_tSNE.pdf}
+		\vspace{-0.3cm}
+		\caption{D2 tSNE}
+		\label{fig:D2_tSNE}
+	\end{figure}
+
+		\begin{table}[H]
 		\centering
@@
 
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
-		\caption{D2 ROC}
-		\vspace{0.3cm}
-		\label{fig:D2_ROC}
-	\end{figure}
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis2_confusion_matrix.pdf}
-		\caption{D2 Conf Mat}
-		\vspace{0.3cm}
-		\label{fig:D2_conf_mat}
-	\end{figure}
-
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis2_tSNE.pdf}
-		\caption{D2 tSNE}
-		\vspace{0.3cm}
-		\label{fig:D2_tSNE}
-	\end{figure}
-
+	\vspace{1cm}
+
+	\begin{multicols}{2}
 	\section{Discussion}
@@
 	\printbibliography
+
+	\end{multicols}
 

### 2024-09-01 Paper/Paper.tex
revise fig and table captions

@@
 The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model.
-In MAAM, we introduce the fusion mechanics, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.
+In MAAM, we introduce the fusion mechanism, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.
 The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists.
@@
 	\includegraphics[width=\linewidth]{Figs/model_overview.pdf}
-	\caption{Model Overview}
+	\caption{Model overview}
 	\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
-		\caption{OCT Abnormities \autocite{Duker_Waheed_Goldman_2022}}
+		\caption{OCT abnormities \autocite{Duker_Waheed_Goldman_2022}}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
-		\caption{Fundus Abnormities \autocite{Wolf_Kirchhof_Reim_2006}}
+		\caption{Fundus abnormities \autocite{Wolf_Kirchhof_Reim_2006}}
 		\vspace{0.3cm}
@@
 	\includegraphics[width=\linewidth]{Figs/fusion.pdf}
-	\caption{Fusion}
+	\caption{Fusion mechanism}
 	\vspace{0.3cm}
@@
 				\begin{longtable}{cccccc}
-					\caption{OCT abnormities}
+					\caption{Data sources of OCT abnormities}
 					\label{tb:OCT_source}\\
@@
 				\begin{longtable}{cccccccc}
-					\caption{Fundus abnormities}
+					\caption{Data sources of fundus abnormities}
 					\label{tb:Fundus_source}\\
@@
 			\begin{longtable}{ccccc}
-				\caption{OCT images CycleGAN adoption rates}
+				\caption{Adoption rates of Cycle-GAN-generated OCT images}
 				\label{tb:cycleGAN_number}\\
@@
 		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
-		\caption{Abnormity training}
+		\caption{Abnormity Models training }
 		\label{fig:A_train}
@@
 			\centering
-			\caption{Overall accuracies}
+			\caption{Overall accuracies using different CNNs}
 			\label{tb:A_accuracies}
@@
 		\fontsize{9}{12}\selectfont{
-		\caption{OCT Test}
+		\caption{Test results of the OCT Model}
 		\label{tb:OCT_test}
@@
 		\fontsize{9}{12}\selectfont{
-		\caption{Fundus Test}
+		\caption{Test results of the Fundus Model}
 		\label{tb:Fundus_test}
@@
 		\includegraphics[width=\linewidth]{Figs/abnormity_ROC.pdf}
-		\caption{A ROC}
+		\caption{ROCs of the Abnormity Models}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/abnormity_confusion_matrix.pdf}
-		\caption{A Conf Mat}
+		\caption{Confusion matrices of the Abnormity Models}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/abnormity_tSNE.pdf}
-		\caption{A ROC}
+		\caption{t-SNE graph of the Abnormity Models}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.pdf}
-		\caption{GradCAM}
+		\caption{Grad-CAM highlighting of abnormities}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
-		\caption{GradCAM with multiple abnormities}
+		\caption{GradCAM highlighting of multiple abnormities}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.pdf}
-		\caption{D1 Conf Mat}
+		\caption{Confusion matrices of Stage D1}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
-		\caption{D1 Acc Bar}
+		\caption{Accuracies of the Diagnosis Model (*: accuracy in terms of the disease with highest probability; **: accuracy in terms of codominant diseases)}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
-		\caption{D2 ROC}
+		\caption{ROCs of Stage D2}
 		\vspace{0.3cm}
@@
 		\vspace{-0.8cm}
-		\caption{D2 Conf Mat}
+		\caption{Confusion matrix of Stage D2}
 		\label{fig:D2_conf_mat}
@@
 		\vspace{-0.3cm}
-		\caption{D2 tSNE}
+		\caption{t-SNE graph of Stage D2}
 		\label{fig:D2_tSNE}
@@
 		\fontsize{9}{12}\selectfont{
-			\caption{Diagnosis Test}
+			\caption{Test results of Stage D2}
 			\label{tb:diagnosis_test}

### 2024-09-01 MAAM/Code/Results/diagnosis2_tSNE_ROC_confusion_matrix.py

@@ -192,16 +192,16 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
     
     if plt_tSNE:
         plot_tSNE(tSNE_features, tSNE_labels, abbr_diseases)
-    #if plt_ROC:
-    #    aucs = plot_all_ROC(roc_labels, roc_probs, diseases_including_normal)
-    #if plt_conf_mat:
-    #    plot_conf_mat(conf_mat, abbr_diseases)
+    if plt_ROC:
+        aucs = plot_all_ROC(roc_labels, roc_probs, diseases_including_normal)
+    if plt_conf_mat:
+        plot_conf_mat(conf_mat, abbr_diseases)
     
     with open(os.path.join(setting.D2_folder, "000D2TORS.csv"), "w", newline="") as file:
         writer = csv.writer(file)
         writer.writerow([corrects, corrects_codominant, total, acc, acc_codominant])
     
-    '''with open(os.path.join(setting.table_folder, "diagnosis2.csv"), "w", newline="") as file:
+    with open(os.path.join(setting.table_folder, "diagnosis2.csv"), "w", newline="") as file:
         writer = csv.writer(file)
         writer.writerow([
                 "Abnormity",
@@ -222,10 +222,10 @@ def plot_tSNE_ROC_conf_mat(plt_tSNE = True, plt_ROC = True, plt_conf_mat = True)
             sensitivity = tp / (tp + fn)
             f1 = 2 * precision * sensitivity / (precision + sensitivity)
             writer.writerow([
-                diseases_including_normal[i],
+                abbr_diseases[i],
                 f"{precision:.3f}",
                 f"{sensitivity:.3f}",
                 f"{specificity:.3f}",
                 f"{f1:.3f}", 
                 f"{aucs[i]:.3f}"
-            ])'''
+            ])

### 2024-09-07 Paper/Paper.tex
small revision
add front page

@@
 \begin{document}
+	\vspace{5cm}
+
+	{\fontsize{20pt}{20pt}\selectfont 参赛学生姓名： 潘思齐\\}
+
+	\vspace{0.6cm}
+	{\fontsize{20pt}{20pt}\selectfont 中学： 上海市世外中学}
+
+	\vspace{1cm}
+	{\fontsize{20pt}{20pt}\selectfont 省份： 上海}
+
+	\vspace{1cm}
+	{\fontsize{20pt}{20pt}\selectfont 国家/地区： 中国}
+
+	\vspace{1cm}
+	{\fontsize{20pt}{20pt}\selectfont 指导老师姓名： 徐庆林}
+
+	\vspace{1cm}
+	{\fontsize{20pt}{20pt}\selectfont 指导老师单位： 上海市世外中学}
+
+	\vspace{1cm}
+	{\fontsize{20pt}{20pt}\selectfont 论文题目： }
+	{\fontsize{16pt}{16pt}\selectfont Multimodal Abnormity-Aware Model}
+
+	\vspace{0.2cm}
+	{\fontsize{16pt}{16pt}\selectfont \hspace{3.7cm} for Ocular Disease Diagnosis}
+
+	\pagebreak
+
 	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
@@
 				\begin{longtable}{cccccc}
-					\caption{Data sources of OCT abnormities}
+					\caption{OCT Data sources}
 					\label{tb:OCT_source}\\
@@
 				\begin{longtable}{cccccccc}
-					\caption{Data sources of fundus abnormities}
+					\caption{Fundus Data sources}
 					\label{tb:Fundus_source}\\
@@
 		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
-		\caption{GradCAM highlighting of multiple abnormities}
+		\caption{Grad-CAM highlighting of multiple abnormities}
 		\vspace{0.3cm}

### 2024-09-07 Paper/Paper.tex
add keywords
add table of content

@@
 	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
+	\vspace{-0.5cm}
 	\author{Siqi Pan}
+	\vspace{-0.5cm}
 	\date{}
@@
 
-	\vspace{-0.2cm}
+	\vspace{-0.7cm}
 	\hrule
-	\vspace{-0.1cm}
+	\vspace{-0.3cm}
 	\section*{Abstract}
 	\hrule
-	\vspace{0.4cm}
+	\vspace{0.3cm}
 	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis.
@@
 And it gets the overall accuracy of 89\% and thus the feasibility is verified.
-	\vspace{0.4cm}
+
+	\vspace{0.2cm}
+	{\fontsize{12pt}{12pt}\selectfont \hspace{-0.8cm}\textbf{Keywords: }Multimodal, Deep Learning, Abnormity-Aware, Ocular Diagnosis}
+	\vspace{0.3cm}
 	\hrule
-	\vspace{1cm}
+
+	\tableofcontents
 
@@
 	\section*{Appendix}
+	\addcontentsline{toc}{section}{Appendix}
 

### 2024-09-07 Paper/Paper.tex
adjust layout
add acknowledgement.

@@
 \usepackage{enumitem}
+\usepackage{setspace}
 \usepackage[style=ieee,sorting=nyt]{biblatex}
@@
 
-	\vspace{-0.7cm}
 	\hrule
@@
 
-	\vspace{0.2cm}
+	\vspace{0.3cm}
+	\hrule
+
+	\vspace{0.5cm}
 	{\fontsize{12pt}{12pt}\selectfont \hspace{-0.8cm}\textbf{Keywords: }Multimodal, Deep Learning, Abnormity-Aware, Ocular Diagnosis}
-	\vspace{0.3cm}
-	\hrule
+
+	\pagebreak
 
 	\tableofcontents
+
+	\vspace{0.4cm}
 
@@
 
+	\pagebreak
+
 	\phantomsection
@@
 
+	\pagebreak
+
+	\section*{Acknowledgement}
+
+	{\setstretch{1.7}
+
+	{\fontsize{12pt}{12pt}\selectfont
+
+	\vspace{0.2cm}
+
+	I would like to express my gratitude to my mathematics teacher Mr.
+Qinglin Xu (徐庆林) for his unrequited guidance and support throughout this research.
+Mr.
+Xu's insightful advice on selecting the research topic was invaluable and helped me navigate the initial stages of my work.
+His constructive feedback on my writing significantly improved the quality and clarity of the paper.
+Mr.
+Xu's encouragement and thoughtful suggestions were instrumental in overcoming challenges and refining the direction of this research.
+His dedication and expertise provided a strong foundation for my work, and I am deeply appreciative of his mentorship and commitment.
+
+	\vspace{0.2cm}
+
+	I have been studying one of the ocular diseases, retinitis pigmentosa (RP), for about 2 years since my family folks have this genetic disease.
+I had decided 3 to 4 directions on researching the RP, including studying the relationship between the genomes of patients and their symptoms, investigating how genetic factors influence the misfolding of RP-related proteins, and modeling retinal structural damage, etc.
+Due to lack of laboratory environment in our middle school, Mr.
+Xu suggested me to pivot my focus onto deep learning area, which can be achieved with certain knowledge and appropriate hardware.
+After having sufficient discussion with Mr.
+Xu., I decided to investigate the model for ocular disease diagnosis.
+
+	When I began to do the study, the first obstacle was that we could not get enough real clinical data.
+We communicated with hospitals and institutions, but it was not easy to get approved by authorities at the level of our study.
+Therefore, Mr.
+Xu suggested I use the data from public database and try to build model and verify its feasibility.
+I believe this was a key step to make progress and finally I was able to complete this paper.
+
+	Regarding paper writing, Mr.
+Xu is very experienced and he gave me a lot of suggestions and instructions.
+I got a lot of help from Mr.
+Xu when I had difficulties on how to use terminologies, organize the contents and do the background research.
+I have been so lucky that I always have Mr.
+Xu at my side.
+
+	\vspace{0.2cm}
+	Again, thank you, Mr. Xu, for your unwavering support and for investing your time and effort in helping me complete this paper.
+
+	}
+	}
+
 \end{document}

### 2024-10-26 Paper/Paper.tex
Update D2 table title

--- 2024-09-07 Paper/Paper.tex
@@
 \begin{document}
-	\vspace{5cm}
-
-	{\fontsize{20pt}{20pt}\selectfont 参赛学生姓名： 潘思齐\\}
-
-	\vspace{0.6cm}
-	{\fontsize{20pt}{20pt}\selectfont 中学： 上海市世外中学}
-
-	\vspace{1cm}
-	{\fontsize{20pt}{20pt}\selectfont 省份： 上海}
-
-	\vspace{1cm}
-	{\fontsize{20pt}{20pt}\selectfont 国家/地区： 中国}
-
-	\vspace{1cm}
-	{\fontsize{20pt}{20pt}\selectfont 指导老师姓名： 徐庆林}
-
-	\vspace{1cm}
-	{\fontsize{20pt}{20pt}\selectfont 指导老师单位： 上海市世外中学}
-
-	\vspace{1cm}
-	{\fontsize{20pt}{20pt}\selectfont 论文题目： }
-	{\fontsize{16pt}{16pt}\selectfont Multimodal Abnormity-Aware Model}
-
-	\vspace{0.2cm}
-	{\fontsize{16pt}{16pt}\selectfont \hspace{3.7cm} for Ocular Disease Diagnosis}
-
-	\pagebreak
-
 	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
@@
 			columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
-			columns/Abnormity/.style={string type, column name=Abnormities},
+			columns/Abnormity/.style={string type, column name=Diseases},
 			columns/Precision/.style={string type, column name=Precision},

### 2024-10-26 Paper-Translated/Paper.tex
Translate paper.

--- 2024-10-26 Paper/Paper.tex
@@
 \usepackage[style=ieee,sorting=nyt]{biblatex}
+\DefineBibliographyStrings{english}{
+	references = {参考文献}
+}
 \assignrefcontextentries[]{*}
@@
 \captionsetup{justification=centering}
-\captionsetup[figure]{name={Fig.},labelsep=space,labelfont=bf}
-\captionsetup[table]{name={Table},labelsep=space,labelfont=bf}
+\captionsetup[figure]{name={图},labelsep=space,labelfont=bf}
+\captionsetup[table]{name={表},labelsep=space,labelfont=bf}
 \CTEXoptions[today=old, contentsname=Contents]
@@
 \begin{document}
-	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
-	\author{Siqi Pan}
+	\title{\vspace{-2.25cm} 眼科疾病诊断的多模态异常感知模型}
+	\author{潘思齐}
 	\date{}
@@
 	\vspace{-0.1cm}
-	\section*{Abstract}
+	\section*{摘要}
 	\hrule
 	\vspace{0.4cm}
-	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis.
-The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities.
-The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model.
-In MAAM, we introduce the fusion mechanism, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.
-The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists.
-And it gets the overall accuracy of 89\% and thus the feasibility is verified.
+	我们设计了一种新颖的模型，即多模态异常感知模型（MAAM），用于辅助眼科疾病的诊断。该模型允许输入两类眼科图像，分别是光学相干断层扫描（OCT）图像和彩色眼底图像，并基于异常来推导疾病，模拟眼科医生的决策过程。该模型由两个子模型组成，分别是异常模型和诊断模型。异常模型识别11种OCT异常和8种眼底异常；诊断模型通过整合异常模型的特征识别出12种疾病。在MAAM中，我们引入了融合机制、共显异常和疾病的概念、以及异常-疾病推导标准。该模型打破了复杂神经网络的“黑箱”，为眼科医生提供了更具可解释性的信息以供参考。模型的总体准确率为89\%，验证了其可行性。
+
 	\vspace{0.4cm}
@@
 	\begin{multicols}{2}
-	\section{Background}
-	Ocular diseases can be diagnosed through various methods, including using optical coherence tomography (OCT) and color fundus images.
-Ophthalmologists usually identify ocular abnormalities to deduce the disease.
-Traditionally, the diagnosis primarily depends on the professional experience and knowledge of the ophthalmologists, which may result in high misdiagnosis rate and under-utilization of medical data.
-With the widespread application of artificial intelligence (AI), deep learning (DL) has made great contributions in providing support to patients in remote areas by sharing expert knowledge \autocite{Ichhpujani_Thakur_2021}.
-By leveraging DL, researchers have developed auxiliary diagnosis programs to help ophthalmologists in the process.
-Many studies use convolutional neural networks (CNN) to analyze ocular images.
-Some commonly used CNNs are VGG, ResNet, and Inception \autocite{daich2023artificial}.
-And for segmenting images and finding abnormalities, U-net is widely used \autocite{Ronneberger_Fischer_Brox_2015}.
-With regards to training CNNs, most studies use transferred learning, which consists of three steps: learning, fine-tuning, and validation.
 
-	Some studies directly predict the disease from OCT images.
-	\authyear{li2019deep} used ResNet to analyze OCT images and distinguish between choroidal neovascularization (CNV), diabetic macular edema (DME), drusen, and healthy eyes.
-In addition, they performed occlusion testing to find out the regions that are the most important in diagnosis \autocite{li2019deep}.
-	\authyear{yoo2021feasibility} used generative adversarial network (GAN) and Inception-v3 together with a few-shot dataset to investigate the feasibility of improving OCT diagnosis of rare ocular diseases \autocite{yoo2021feasibility}.
-They handled the issues of training image shortage and data imbalance by creating ocular disease OCT images from healthy OCT images.
-\authyear{Kermany2018} conducts medical diagnosis and identifies treatable diseases by image-based deep learning.
-They also provided a widely used database including more than one hundred thousand OCT labeled images for 3 diseases \autocite{Kermany2018}.
+	\section{背景}
 
-	Some other studies can identify ocular abnormalities from annotated OCT images.
-	\authyear{camino2018deep} used DL to identify the region of preserved photoreceptors on \textit{en face} OCT in choroideremia and retinitis pigmentosa (RP) \autocite{camino2018deep}. 
-	\authyear{srinivasan2014fully} detected DME and dry age-related macular degeneration (dry AMD) from OCT images by flattening the image and using support vector machine (SVM) to extract the thickness information of the retinal layers \autocite{srinivasan2014fully}.
-	\authyear{leandro2023oct} implemented VGG to identify up to 8 kinds of key abnormalities and hence detect multiple diseases by using central fovea cross-section OCT \autocite{leandro2023oct}.
-\authyear{Fang_Wang2019} developed a novel lesion-aware CNN, called LACNN, to simulate the ophthalmologists' diagnosis that focuses on ocular abnormalities.
-The LACNN is a U-net-like CNN which incorporates VGG16 as the baseline, and the result is impressive \autocite{Fang_Wang2019}.
+	眼科疾病可以通过多种方法诊断，包括使用光学相干断层扫描（OCT）和彩色眼底图像。眼科医生通常通过识别眼部异常来推导疾病。传统上，诊断主要依赖于眼科医生的专业经验和知识，这可能导致高误诊率和医疗数据的利用不足。随着人工智能（AI）的广泛应用，深度学习（DL）共享专家知识，为偏远地区的患者提供支持方面做出了巨大贡献 \autocite{Ichhpujani_Thakur_2021}。通过利用深度学习，研究人员开发了辅助诊断程序，以帮助眼科医生进行诊断。许多研究都使用卷积神经网络（CNN）来分析眼科图像。一些常用的 CNN 包括 VGG、ResNet 和 Inception \autocite{daich2023artificial}。在图像分割和寻找异常中，U-net 被广泛应用 \autocite{Ronneberger_Fischer_Brox_2015}。大多数研究在训练CNN时使用迁移学习，包括三个步骤：学习、微调和验证。
 
-	Other studies use fundus images to predict ocular diseases.
-	\authyear{masumoto2019accuracy} trained deep CNN with ultrawide-field fundus images to make the CNN capable of diagnosing RP \autocite{masumoto2019accuracy}. 
-	\authyear{chen2021artificial} uses color fundus photographs and multiple types of CNN (Inception V3, Inception Resnet V2, and Xception) to develop a method of early detection of RP \autocite{chen2021artificial}.
-	\authyear{li2022development} uses CNN to detect up to 12 fundus diseases based on colour fundus photography \autocite{li2022development}.
-\authyear{Son2023} presented a novel architectural and algorithmic design to comprehensively identify 15 abnormalities and diagnose 8 major ocular diseases from macula-centered fundus images.
-They defined a notion of counterfactual attribution ratio (CAR) to interpret the system's diagnostic reason and disclose the relationship between abnormalities and diseases \autocite{Son2023}.
+	一些研究直接从OCT图像预测疾病。\citeauthor{li2019deep} 使用ResNet分析OCT图像，并区分脉络膜新生血管（CNV）、糖尿病性黄斑水肿（DME）、玻璃疣（Drusen）和健康人眼。此外，他们还进行了遮挡测试，以找出对于诊断最重要的区域 \autocite{li2019deep}。\citeauthor{yoo2021feasibility} 使用生成对抗网络（GAN）和Inception-v3，结合少量数据集，探讨了改善罕见眼科疾病OCT诊断的可行性 \autocite{yoo2021feasibility}。他们通过从健康OCT图像中生成眼科疾病的OCT图像来解决图像数量不足和数据不平衡的问题。\citeauthor{Kermany2018} 通过基于图像的深度学习进行医学诊断，并识别可治疗的疾病。他们还提供了一个广为使用的数据库，其中包含超过十万张用于三种疾病的OCT的有标注图像 \autocite{Kermany2018}。
 
-	In recent years, more and more DL systems began to use multi-modal information to predict ocular diseases.
-For automated detection system, retrieving features from both OCT images and fundus images can effectively keep the diagnosis away from bias and incompleteness.
-It is not always necessary to yield a better automated diagnosis result, but it does help ophthalmologist to make more accurate and holistic clinical decisions.
-For instance, \authyear{liu2023prediction} combined OCT and fundus images to evaluate visual impairment in RP in terms of best-corrected visual acuity(BCVA) \autocite{liu2023prediction}.
-\authyear{Xu2021} leveraged a bi-modal CNN to diagnose AMD and polypoidal choroidal vasculopathy (PCV), where the architecture uses fundus and OCT images as input for transferred learning CNN and concatenates the retrieved features to classify 3 diseases including dry AMD, wet AMD and PCV \autocite{Xu2021}.
-And \author{Andrearczyk2018} ingeniously combined medical images and biomedical textual information to discriminate different diseases, which is a novel method for the usage of multi-modal application \autocite{Andrearczyk2018}.
+	其他研究可以从带注释的OCT图像中识别眼科异常。\citeauthor{camino2018deep} 利用深度学习在面部OCT中识别未凋亡的的光感受器区域，用于脉络膜疾病和视网膜色素变性（RP） \autocite{camino2018deep}。\citeauthor{srinivasan2014fully} 通过展平图像，使用支持向量机（SVM）提取视网膜层的厚度信息，检测 DME 和干性年龄相关性黄斑变性（干性AMD） \autocite{srinivasan2014fully}。\citeauthor{leandro2023oct} 使用VGG，用中央黄斑横截面OCT检测多达8种关键异常并由此检测多种疾病 \autocite{leandro2023oct}。\citeauthor{Fang_Wang2019} 开发了一种新的病灶感知 CNN，称为 LACNN，用于模拟集中于眼科异常的眼科医生诊断 \autocite{Fang_Wang2019}。
 
-	The key technical problem of multi-modal diagnosis is how to fuse the results from multifarious sources.
-There are three types of fusion, namely early, late, and hybrid fusion.
-Deciding on the optimal type of fusion is part of the exploratory process in the application of DL methods \autocite{Ichhpujani_Thakur_2021}.
+	另一些研究使用眼底图像来预测眼科疾病。\citeauthor{masumoto2019accuracy} 使用超宽视野眼底图像训练深度 CNN 以诊断 RP \autocite{masumoto2019accuracy}。\citeauthor{chen2021artificial} 使用彩色眼底照片和多种 CNN（如 Inception V3、Inception Resnet V2 和 Xception），开发了 RP 的早期检测方法 \autocite{chen2021artificial}。\citeauthor{li2022development} 使用 CNN 基于彩色眼底摄影检测多达 12 种眼底疾病 \autocite{li2022development}。\citeauthor{Son2023} 提出了一种新颖的架构和算法设计，从黄斑中心的眼底图像中综合识别 15 种异常和诊断 8 种主要眼科疾病。他们定义了反事实归因比（CAR）的概念，以解释系统的诊断原因，并揭示异常与疾病之间的关系 \autocite{Son2023}。
 
-	\section{Overview}
+	近年来，越来越多的深度学习系统开始使用多模态信息来预测眼科疾病。对于自动化检测系统，从 OCT 图像和眼底图像中提取特征可以有效避免诊断偏差和不完整性。虽然并不总是能带来更好的自动诊断结果，但它确实有助于眼科医生做出更准确和全面的临床决策。例如，\citeauthor{liu2023prediction} 结合 OCT 和眼底图像，评估视网膜色素变性患者的视力损害 \autocite{liu2023prediction}。\citeauthor{Xu2021} 利用双模态 CNN 诊断 AMD 和脉络膜息肉样血管病变（PCV），其中架构使用眼底和 OCT 图像作为迁移学习 CNN 的输入，并将提取的特征拼接以分类干性 AMD、湿性 AMD 和 PCV 三种疾病 \autocite{Xu2021}。\citeauthor{Andrearczyk2018} 将医学图像与生物医学文本信息结合起来，以区分不同的疾病，这是多模态应用的一种创新方法 \autocite{Andrearczyk2018}。
+
+	多模态诊断的关键技术问题在于如何融合来自多种来源的结果。融合有三种类型，即早期融合、后期融合和混合融合。决定最佳融合类型是应用深度学习方法探索过程的一部分 \autocite{Ichhpujani_Thakur_2021}。
+
+	\section{概述}
 	\label{sec:overview}
 
-	We develop the Multimodal Abnormity-Aware Model (MAAM) to aid ophthalmologists in diagnosing ocular diseases.
-It considers both OCT and color fundus image inputs.
-In addition, it simulates the decision-making process of ophthalmologists when they examine patients, namely, first identifying the abnormities, and then deducing the disease.
-The model is designed in a way that partly opens up the ``black box'' of DL and presents more interpretable information to ophthalmologists for the reference.
+	我们开发了多模态异常感知模型（MAAM）来协助眼科医生诊断眼科疾病。该模型同时考虑 OCT 和彩色眼底图像输入。此外，它模拟了眼科医生在检查患者时的决策过程，即首先识别异常，然后推导疾病。该模型设计部分打开了深度学习的“黑箱”，并为眼科医生提供了更多可解释的信息参考。
 
-	The structure of the MAAM is shown in Fig.~\ref{fig:3_parts}.
-It consists of 2 submodels: the Abnormity Model and the Diagnosis Model.
-We input multiple OCT and fundus images to the Abnormity Models, and output the classification of abnormities as an input to the Diagnosis Model, which yields disease probabilities as the final result.
+	MAAM 的结构如图~\ref{fig:3_parts} 所示。模型由两个子模型组成：异常模型和诊断模型。我们将多个 OCT 和眼底图像输入到异常模型中，并将异常分类结果作为诊断模型的输入，诊断模型最终输出疾病概率。
 
@@
 
-	The Abnormity Models are de facto classifiers for abnormities, which are symptoms that can be directly observed in the images.
-The MAAM identifies 11 OCT abnormities and 8 Fundus abnormities, as shown in Fig.~\ref{fig:OCT_abnormities} and Fig.~\ref{fig:fundus_abnormities}.
-The abbreviations and detail information of abnormities and diseases are tabulated in ``Appendix''.
+	异常模型实际上是异常分类器，即图像中可直接观察到的症状。MAAM 能识别 11 种 OCT 异常和 8 种眼底异常，如图~\ref{fig:OCT_abnormities} 和图~\ref{fig:fundus_abnormities} 所示。“附录”中列出了异常和疾病的缩写及详细信息。
+
+	异常模型还包括两个子模型：OCT 模型和眼底模型，分别对 OCT 和眼底异常进行分类。两个子模型都使用 CNN，并修改了最终的全连接层（FC 层）。我们比较了四种常用 CNN 的性能：ResNet152、ResNet50、ResNet18 \autocite{He_Zhang_Ren_Sun_2016}和 VGG16 \autocite{Simonyan_Zisserman_2015}，并为每个子模型选择了最佳模型。每个 CNN 的最终 FC 层被修改，使其输出向量的大小等于 OCT 或眼底异常的数量。为了对输出向量进行归一化，我们对其进行了 softmax 操作。每个子模型输出所有异常的概率向量。
+
+	\vspace{0.5cm}
+
+	诊断模型包括两个阶段：阶段 D1 和阶段 D2。
+
+	\vspace{0.2cm}
+
+	在阶段 D1 中，我们根据异常模型的概率向量确定每种疾病的严重程度。我们使用异常到疾病推导标准（见图~\ref{fig:criteria}）作为判断依据。阶段 D1 中有多个子模型，每个子模型对应一种疾病。根据推导标准，我们确定一种疾病的异常数量，并以此来定义严重程度。例如，疾病“rDR”中共有 5 种异常：OCT 异常“DME”以及眼底异常“HM”、“VA”、“MA”和“CWP”。因此，考虑到健康状态，我们将“rDR”定义为 6 个严重程度级别。
+
+	我们使用融合后的向量作为阶段 D1 中每个子模型的输入，让向量通过一个 FC 层和 softmax 操作，以生成严重程度的概率向量。
+
+	在阶段 D2 中，我们确定最终的疾病概率向量。同样，我们使用阶段 D1 中子模型的输出，进行向量融合，通过 FC 层并进行 softmax 操作，输出潜在疾病的概率，供眼科医生参考。
 
@@
 		\centering
-	\includegraphics[width=\linewidth]{Figs/model_overview.pdf}
-	\caption{Model overview}
+		\includegraphics[width=\linewidth]{Figs/model_overview.png}
+		\caption{模型总览}
 		\vspace{0.3cm}
 		\label{fig:3_parts}
+		\vspace{1cm}
 	\end{figure}
+
+	\begin{multicols}{2}
+
+	在 MAAM 中，我们利用融合操作整合不同子模型的结果。如图~\ref{fig:fusion} 所示，MAAM 中总共有三次融合操作。
+
+	第一次融合发生在 OCT 模型或眼底模型的输出中。在实际场景中，可以使用多个 OCT 和眼底图像进行眼科疾病诊断。每张图像通过 OCT 或眼底模型后得到一个概率向量。为了利用所有图像的概率结果，我们对所有向量进行了最大化融合，从而得到一个 OCT 异常概率向量和一个眼底异常概率向量，均取最大值。
+
+	第二次融合发生在异常模型与阶段 D1 之间的接口。我们将 OCT 异常概率向量和眼底异常概率向量进行拼接融合，作为阶段 D1 所有子模型的输入。
+
+	第三次融合发生在阶段 D1 与阶段 D2 之间的接口。我们将所有严重程度向量进行拼接，输入阶段 D2 模型。融合向量通过 FC 层并经过 softmax 操作，输出最终结果。
+
+	\section{异常模型}
+
+	\subsection{数据准备}
+
+	用于训练的图像和标签主要从公共数据库中下载，但部分异常不包含在这些数据库中。对于这些异常，我们使用搜索引擎作为额外的数据来源获取图像。各数据来源获得的图像数量如表~\ref{tb:OCT_source} 和表~\ref{tb:Fundus_source} 所示。图像的搜索引擎链接详见“附录”。
+
+	对于图像少于 1000 张的 OCT 异常，我们使用 Cycle-GAN \autocite{Zhu_Park_Isola_Efros_2020}生成新图像。我们训练一个 Cycle-GAN 网络，将健康图像与异常图像进行转换，取出将健康图像转换为异常图像的生成器，用其生成新的异常图像。我们检查所有生成的图像，选取那些清晰显示了目标异常的图像。采纳率见表~\ref{tb:cycleGAN_number}。由于生成的眼底图像过于模糊，眼底异常通常不如 OCT 明显，Cycle-GAN 无法从少量眼底图像中学习，因此我们不使用 Cycle-GAN 生成眼底图像。
+
+	\end{multicols}
 
@@
 		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
-		\caption{OCT abnormities \autocite{Duker_Waheed_Goldman_2022}}
+		\caption{OCT异常 \autocite{Duker_Waheed_Goldman_2022}}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
-		\caption{Fundus abnormities \autocite{Wolf_Kirchhof_Reim_2006}}
+		\caption{眼底异常 \autocite{Wolf_Kirchhof_Reim_2006}}
 		\vspace{0.3cm}
@@
 
-	\begin{multicols}{2}
-
-	The Abnormity Models also contain 2 submodels: the OCT Model and the Fundus Model, which classify OCT and fundus abnormities, respectively.
-Both of the submodels leverage CNNs with modified final fully-connected (FC) layers.
-We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18 \autocite{He_Zhang_Ren_Sun_2016} and VGG16 \autocite{Simonyan_Zisserman_2015}, and choose the best one for each submodel.
-The final FC layer in each CNN is modified so that the size of its output vector is equal to the number of OCT or fundus abnormities.
-In order to normalize the output vector, we perform the softmax operation.
-Each submodel outputs a probability vector for all the abnormities.
-
-	\vspace{0.5cm}
-
-	The Diagnosis Model consists of two stages: Stage D1 and Stage D2.
-
-	\vspace{0.2cm}
-
-	In Stage D1, we determine the severity level for each disease from the probability vectors from the Abnormity Models.
-We use Abnormity-to-Disease Deduction Criteria (shown in Fig.~\ref{fig:criteria}) as ground truth.
-There are multiple submodels in Stage D1 and each one corresponds to one disease.
-Based on the deduction criteria, we determine the number of abnormities for one disease and use the number to define the severity levels.
-For example, there are totally 5 abnormities that are present in the disease ``rDR'': OCT abnormity ``DME'' and Fundus abnormities ``HM'', ``VA'', ``MA'', and ``CWP''.
-Therefore, taking into account the healthy status, we end up with 6 severity levels for disease ``rDR''.
-
-	We use the fused vector as an input for each submodels in Stage D1, and have the vector go through a FC layer with softmax operation to yield severity level probability vectors.
-
-	\end{multicols}
-
 	\begin{figure}[htbp]
 		\centering
-		\includegraphics[width=0.7\linewidth]{Figs/criteria.pdf}
-		\caption{Abnormity-to-disease Deduction Criteria}
+		\includegraphics[width=0.7\linewidth]{Figs/criteria.png}
+		\caption{异常-疾病推导标准}
 		\vspace{0.3cm}
@@
 
-	\begin{multicols}{2}	
-	In Stage D2, we determine the final disease probability vector.
-Similarly, we use a fused vector from the outputs of submodels in Stage D1, and have the vector go through a FC layer with softmax operation.
-The result presents potential diseases that can be referenced by ophthalmologists.
-
-	\vspace{0.5cm}
-
-	In the MAAM, we leverage the fusion operation to incorporate all the results from different submodels. As shown in Fig.~\ref{fig:fusion}, there are totally 3 fusion operations in MAAM.
-
-	The first fusion occurs at the output of OCT Model or Fundus Model.
-In real scenarios, multiple OCT and Fundus images can be used for ocular disease diagnosis.
-Each image goes through either the OCT Model or the Fundus Model to yield a probability vector.
-To use the probability results from all the images, a maximization fusion is implemented for all the vectors so that the fusion yields one OCT abnormity probability vector and one Fundus abnormity probability vector with maximum values.
-
-	The second fusion occurs at the interface between Abnormity Model and Stage D1.
-A concatenation fusion is implemented for OCT abnormity probability vector and Fundus abnormity probability vector.
-The fused vector works as an input to all the submodels in Stage D1.
-
-	The third fusion occurs at the interface between Stage D1 and Stage D2.
-We concatenation all the severity level vectors to feed the model in Stage D2.
-The fused vector goes through the FC layer and undergoes a softmax operation to yield the final result.
-
-	\end{multicols}
-
 	\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=\linewidth]{Figs/fusion.pdf}
-	\caption{Fusion mechanism}
+	\includegraphics[width=\linewidth]{Figs/fusion.png}
+	\caption{融合机制}
 	\vspace{0.3cm}
@@
 
+	\pagebreak
+
 	\begin{multicols}{2}
-
-	\section{Abnormity Models}
-
-	\subsection{Data Preparation}
-
-	The images and labels used for training are mainly downloaded from public databases, but some abnormities are not included in these databases.
-For those abnormities, we use the search engine as an additional data source to get images.
-The numbers of images acquired from each data source are shown in Table~\ref{tb:OCT_source} and Table~\ref{tb:Fundus_source}.
-As to the links of the images from the search engine, refer to ``Appendix''.
-
-	For OCT abnormities with less than 1000 images, we use Cycle-GAN \autocite{Zhu_Park_Isola_Efros_2020} to generate new images.
-We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.
-We go through all generated images and adopt those that clearly display only the abnormity of interest.
-The adoption rates are shown in Table~\ref{tb:cycleGAN_number}.
-Fundus images are not generated using Cycle-GAN because generated fundus images are too blurry; in addition, fundus abnormities are usually less salient than OCT ones and cannot be properly learned by Cycle-GAN, given that we only have a small number of fundus images.
+	我们将包括生成图像在内的图像分成训练和测试数据集，并对图像进行一系列变换，包括水平翻转、亮度随机变化（-10\% 到 +10\%）、水平和垂直随机平移（-5\% 到 +5\%）、随机缩放（-20\% 到 +20\%）和随机旋转（OCT 图像为 -10° 到 +10°，眼底图像为 -30° 到 +30°）。旋转仅应用于训练数据集中的图像。最终，我们为每个 OCT 异常获得 5000 张训练图像和 500 张测试图像，为每个眼底异常获得 3000 张训练图像和 300 张测试图像。
 	\end{multicols}
@@
 					\begin{longtable}{cccccc}
-					\caption{OCT Data sources}
+						\caption{OCT数据源}
 						\label{tb:OCT_source}\\
 						\toprule
-					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
+						\multirow{2}{*}{异常}&\multicolumn{4}{c}{数据源}&\multirow{2}{*}{总数据量}\\
 						&1&2&3&4&\\
@@
 
-					\item Search engine
+						\item 搜索引擎
 						\vspace{-0.2cm}
@@
 					\begin{longtable}{cccccccc}
-					\caption{Fundus Data sources}
+						\caption{眼底数据源}
 						\label{tb:Fundus_source}\\
 						\toprule
-					\multirow{2}{*}{Abnormity}&\multicolumn{6}{c}{Source}&\multirow{2}{*}{Total}\\
+						\multirow{2}{*}{异常}&\multicolumn{6}{c}{数据源}&\multirow{2}{*}{总数据量}\\
 						&1&2&3&4&5&6&\\
@@
 				\begin{longtable}{ccccc}
-				\caption{Adoption rates of Cycle-GAN-generated OCT images}
+					\caption{Cycle-GAN生成的OCT图片的采用率}
 					\label{tb:cycleGAN_number}\\
 					\toprule
-				Abnormity&Original&Generated&Adopted&Adoption Rate\\
+					异常&原图数量&生成数量&采用数量&采用率\\
 					\midrule
@@
 	\begin{multicols}{2}
-	We split the images, including generated images, into training and test datasets, and implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images.
-The rotation is only applied to images in the train dataset.
-Eventually, we get 5000 train images and 500 test images for each OCT abnormity, and 3000 train images and 300 test images for each fundus abnormity.
-
-	\subsection{Training}
+	\subsection{训练}
 	\label{sec:a_training}
 
-	The model training is on a desktop computer with Intel$^®$ Xeon$^®$ Platinum 8352V Processor, 256GB of RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 48GB VRAM.
-The training uses cross entropy loss, ADAM optimizer with learning rate 0.001, a batch size of 32 and five-fold cross-validation.
-The code is written with PyTorch in an Anaconda environment.
-Refer to ``Appendix'' for the link to the code repository on GitHub.
+		模型训练在一台台式计算机上进行，配备 Intel$^®$ Xeon$^®$ Platinum 8352V 处理器、256GB 内存和 2 张 NVIDIA GeForce RTX 4090 GPU（48GB 显存）。训练使用交叉熵损失、学习率为 0.001 的 ADAM 优化器、批大小为 32 以及五折交叉验证。代码在 Anaconda 环境下用 PyTorch 编写。代码库的 GitHub 链接参见“附录”。
 
@@
 
-	For the Abnormity Models, we employ a strategy of transfer learning to finetuning.
+		对于异常模型，我们采用迁移学习微调策略。
 
-	In the transfer learning phase, pretrained weights from ImageNet \autocite{Krizhevsky_Sutskever_Hinton_2017} are used.
-We freeze the weights in all the convolutional layers and only vary the weights in the final FC layer.
-The training lasts for 100 epochs.
-Every 10 epochs, weights of the model with the best validation accuracy are saved.
-In order to prevent overfitting on the train dataset, we introduce a measure called overall accuracy, which is the weighted average of validation and test accuracy.
-For all the saved models, we calculate the overall accuracy to select the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.
+		在迁移学习阶段，使用 ImageNet \autocite{Krizhevsky_Sutskever_Hinton_2017}的预训练权重。我们冻结所有卷积层中的权重，仅调整最终 FC 层的权重。训练持续 100 个 epoch。每 10 个 epoch，保存验证集准确率最高的模型权重。为防止训练数据集的过拟合，我们引入总体准确率，计算验证集和测试集的加权平均准确率。对于所有保存的模型，计算其总体准确率，从中选择验证集和测试集表现最好的模型，进行微调。
 
-	In the finetuning phase, we start from the best model in the transfer learning phase, unfreezing all weights in the model.
-We train the model for 30 epochs.
-Similarly, we save the weights of the model with the best validation accuracy every 10 epochs, and find the model with the highest overall accuracy.
-Finally, we compare the overall accuracies of the best model in the transfer learning phase and the finetuning phase to determine the best model of all.
+		在微调阶段，从迁移学习阶段的最佳模型开始，解冻模型中的所有权重。训练 30 个 epoch。每 10 个 epoch 保存验证集准确率最高的模型权重，选出总体准确率最高的模型。最终比较迁移学习阶段和微调阶段的最佳模型的总体准确率，以确定最佳模型。
 
-	For both OCT and Fundus Models, we trained 4 commonly used CNNs: ResNet152, ResNet50, ResNet18, and VGG16.
-The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:A_train}.
+		对于 OCT 和眼底模型，我们训练了四种常用的 CNN：ResNet152、ResNet50、ResNet18 和 VGG16。训练和验证阶段的准确率和损失如图~\ref{fig:A_train} 所示。
 
@@
 
-	We can observe that finetuning significantly increases the model accuracy and, therefore, all the final models are finetuned models.
-As shown in Table~\ref{tb:A_accuracies}, the best CNN for OCT Model is ResNet50 and the best for Fundus Model is ResNet152.
-ResNet50 performed better than ResNet152 on OCT, possibly because it has fewer parameters and is less likely to overfit on OCT images, which has fewer and clearer traits; on the other hand, ResNet152 is better on fundus possibly because it has more parameters and can better discern the complex traits in fundus images.
-ResNet18 may have too few parameters, so it performs less well over all; and VGG16 sometimes experiences large dips in accuracy, possibly due to gradient vanishing, and this impairs its performance.
+		微调显著提高了模型的准确率，因此所有最终模型均为微调模型。表 4 显示了 OCT 模型的最佳 CNN 为 ResNet50，而眼底模型的最佳 CNN 为 ResNet152。ResNet50 在 OCT 上表现优于 ResNet152，可能是因为参数较少，较不易在 OCT 图像上过拟合；而 ResNet152 在眼底图像上更具优势，可能是因为其参数较多，能够更好地辨别眼底图像中的复杂特征。ResNet18 的参数可能过少，整体表现较弱；而 VGG16 有时出现准确率大幅下降，可能是梯度消失所致，从而影响其性能。
 
@@
 
-	After all the training and comparisons, we determine to use a finetuned model with ResNet50 for OCT Model and a finetuned model with ResNet152 for Fundus Model.
+		经过所有的训练和比较，我们最终选择使用 ResNet50 的微调模型作为 OCT 模型，使用 ResNet152 的微调模型作为眼底模型。
 
+		\subsection{结果}
+
+		表~\ref{tb:OCT_test} 和表~\ref{tb:Fundus_test} 显示了测试数据集上的预测值。图~\ref{fig:A_ROC} 显示了 ROC 曲线，图~\ref{fig:A_conf_mat} 显示了混淆矩阵，图~\ref{fig:A_tSNE} 显示了每种异常的 t-SNE 图。
+
+		OCT 模型有过拟合倾向，而眼底模型在深度学习方面无法达到令人满意的水平。总体来看，OCT 模型的性能显著优于眼底模型。
+
+		眼底异常往往不如 OCT 异常明显，因为眼底图像中的异常通常较小且分散。此外，一张眼底图像通常包含多个异常，而大多数 OCT 图像每张仅包含一个异常。考虑到眼底图像的数量比 OCT 图像少，因此眼底分类的难度有所增加。
+
+		为了让异常模型能够识别一张图像中的多个异常，我们采用一种方法来确定共显异常。我们将图像输入异常模型，并得到异常概率向量。如果概率最高的异常值大于 0.9，则将其视为显著异常；否则，继续选择下一个概率较高的异常，直到所选异常的概率总和达到 0.9 或选择的异常数量达到最大值 4，所有选定的异常都视为共显异常。
+
+		\vspace{0.3cm}
+
+		我们可以使用 Grad-CAM \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra}突出图像中对最终分类贡献较大的区域。如果模型正确训练，则应等效于突出显示异常。在图~\ref{fig:gradCAM} 中，每对图像中的左图为原始 OCT 或眼底图像，右图为通过 Grad-CAM 成功突出显示异常的图像。
+
+		此外，Grad-CAM 可指定突出显示的异常，因此也可用于突出共显异常。在图~\ref{fig:gradCAM_multi_abnormity} 中，中间图为原始 OCT 和眼底图像，左图和右图则使用 Grad-CAM 突出显示共显异常。
 	\end{multicols}
@@
 			\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
-		\caption{Abnormity Models training }
+			\caption{异常模型训练}
 			\label{fig:A_train}
 		\end{figure}
+
+		\pagebreak
 
@@
 				\centering
-			\caption{Overall accuracies using different CNNs}
+				\caption{使用不同CNN的总体准确率}
 				\label{tb:A_accuracies}
@@
 					\toprule
-				Model&ResNet152&ResNet50&ResNet18&VGG16\\
+					模型&ResNet152&ResNet50&ResNet18&VGG16\\
 					\midrule
-				OCT Model   &91.906\%&\textbf{92.183\%}&91.011\%&89.744\% \\
-				Fundus Model&\textbf{89.111\%}&88.926\%&86.605\%&79.185\% \\
+					OCT模型   &91.906\%&\textbf{92.183\%}&91.011\%&89.744\% \\
+					Fundus模型&\textbf{89.111\%}&88.926\%&86.605\%&79.185\% \\
 					\bottomrule
@@
 			\fontsize{9}{12}\selectfont{
-		\caption{Test results of the OCT Model}
+			\caption{OCT模型的测试结果}
 			\label{tb:OCT_test}
@@
 			columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
-		columns/Abnormity/.style={string type, column name=Abnormities},
-		columns/Precision/.style={string type, column name=Precision},
-		columns/Sensitivity/.style={string type, column name=Sensitivity},
-		columns/Specificity/.style={string type, column name=Specificity},
-		columns/FOne/.style={string type, column name={F1 Score}},
+			columns/Abnormity/.style={string type, column name=异常},
+			columns/Precision/.style={string type, column name=精确率},
+			columns/Sensitivity/.style={string type, column name=敏感性},
+			columns/Specificity/.style={string type, column name=特异性},
+			columns/FOne/.style={string type, column name={F1分数}},
 			columns/AUC/.style={string type, column name=AUC},
@@
 			\fontsize{9}{12}\selectfont{
-		\caption{Test results of the Fundus Model}
+			\caption{眼底模型的测试结果}
 			\label{tb:Fundus_test}
@@
 		\begin{figure}[htbp]
+			\vspace{3.5cm}
 			\centering
 			\includegraphics[width=\linewidth]{Figs/abnormity_ROC.pdf}
-		\caption{ROCs of the Abnormity Models}
+			\caption{异常模型的ROC曲线}
 			\vspace{0.3cm}
@@
 			\includegraphics[width=\linewidth]{Figs/abnormity_confusion_matrix.pdf}
-		\caption{Confusion matrices of the Abnormity Models}
+			\caption{异常模型的混淆矩阵}
 			\vspace{0.3cm}
@@
 			\includegraphics[width=\linewidth]{Figs/abnormity_tSNE.pdf}
-		\caption{t-SNE graph of the Abnormity Models}
+			\caption{异常模型的t-SNE图}
 			\vspace{0.3cm}
@@
 			\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.pdf}
-		\caption{Grad-CAM highlighting of abnormities}
+			\caption{Grad-CAM高亮显示异常}
 			\vspace{0.3cm}
@@
 			\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
-		\caption{Grad-CAM highlighting of multiple abnormities}
+			\caption{Grad-CAM高亮显示多处异常}
 			\vspace{0.3cm}
@@
 
+	\pagebreak
+
 	\begin{multicols}{2}
+	\section{诊断模型}
 
-		\subsection{Results}
+	\subsection{数据准备}
 
-		Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values on the test dataset.
-Fig.~\ref{fig:A_ROC} shows the ROCs, Fig.~\ref{fig:A_conf_mat} shows the confusion matrices and Fig.~\ref{fig:A_tSNE} shows the t-SNE graphs for each abnormity.
+	阶段 D1 的目的是确定每种疾病的严重程度，每种疾病对应一个子模型。我们根据异常到疾病推导标准（见图~\ref{fig:criteria}）为每个子模型准备数据。如第~\ref{sec:overview}~节所述，我们确定一种疾病的目标异常，并根据目标异常的数量定义严重程度。如果某种疾病有 5 个目标异常，则考虑到健康状态，共有 6 个严重程度级别，即 0 至 5。我们使用一组图像作为子模型的输入，每组图像的严重程度标签等于该组中出现的目标异常数量。我们随机选择 OCT 和眼底图像集，为每组确定严重程度。最终，我们为每个严重程度获得 10000 组训练输入和 10000 组测试输入。
 
-		The OCT Model tends to overfit, while the Fundus Model cannot reach a satisfying level in terms of DL.
-Overall, the performance of the OCT Model is significantly better than that of the Fundus Model.
+	阶段 D2 的目的是输出疾病概率向量。对于每种疾病，我们使用异常到疾病推导标准找到目标异常，随机选择每个目标异常的一组图像，将这些图像集标记为该疾病。我们为每种疾病获取了 10000 组训练图像集和 10000 组测试图像集。
 
-		Fundus abnormities tend to be less prominent than those of OCT, since the abnormity in fundus image are usually quite small and scattered.
-Moreover, one fundus image usually contains more than one abnormity, while most OCT images contain only one abnormity per image.
-Also, given that we have fewer fundus images than OCT ones, the difficulties for fundus classification increases.
+	\subsection{训练}
 
-		In order to allow the Abnormity Models to identify multiple abnormities in one image, we employ a method to determine the codominant abnormities.
-We input an image to the Abnormity Models and get the abnormity probabilities vector.
-If the abnormity with the highest probability has probability greater than 0.9, it is regarded as dominant; if not, we continue taking the abnormity with the next high probability until either the sum of the probabilities of the chosen abnormities reaches 0.9, or the number of abnormities reaches the maximum, which is 4, and all the chosen abnormities are regarded as codominant.
+	诊断模型与异常模型使用相同的硬件进行训练。阶段 D1 子模型训练 10 个 epoch，阶段 D2 模型训练 30 个 epoch，其余超参数与异常模型相同，详情参见第~\ref{sec:a_training}~节。
 
-		\vspace{0.3cm}
+	阶段 D1 的子模型和阶段 D2 的模型在训练和验证过程中迅速达到较高的准确率，因为训练数据充足，且模型结构相对简单。
 
-		We can use Grad-CAM \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra} to highlight areas on the image that make a large contribution to the final classification.
-If the model had been trained correctly, this would be equivalent to highlighting the abnormity.
-In Fig.~\ref{fig:gradCAM}, the left image in each pair of images is the original OCT or Fundus image, and the right one is the image with the abnormity correctly highlighted with Grad-CAM.
+	\subsection{结果}
 
-		Furthermore, Grad-CAM can highlight any designated abnormity, so it can be used to highlight codominant abnormities.
-In Fig.~\ref{fig:gradCAM_multi_abnormity}, the middle images are the original OCT and fundus images.
-In the images on the left and right, we use Grad-CAM to highlight the codominant abnormities.
+	图~\ref{fig:D1_acc_bar} 显示了阶段 D1 子模型的准确率，图~\ref{fig:D1_conf_mat} 显示了阶段 D1 的混淆矩阵。表~\ref{tb:diagnosis_test} 显示了阶段 D2 的预测值，图~\ref{fig:D2_ROC} 显示了 ROC 曲线，图~\ref{fig:D2_conf_mat} 显示了混淆矩阵，图~\ref{fig:D2_tSNE} 显示了 t-SNE 图。
 
-	\section{Diagnosis Model}
+	阶段 D1 的子模型在预测结果上常常比标签偏差一个级别，这降低了阶段 D1 子模型的准确率。然而，阶段 D2 部分解决了此问题，因为阶段 D2 模型的准确率高于阶段 D1 子模型的平均准确率。
 
-	\subsection{Data Preparation}
-
-	The purpose of Stage D1 is to determine the severity level for all diseases, each of which has a corresponding submodel.
-We prepare data for each submodel according to the Abnormity-to-Disease Deduction Criteria (shown in Fig.~\ref{fig:criteria}).
-As stated in Section~\ref{sec:overview}, we determine the target abnormities for one disease and use the number of target abnormities to define the severity levels.
-If a disease has 5 target abnormities, then, taking into account the healthy status, we get 6 severity levels, namely 0 to 5.
-We use sets of images as inputs to the submodel, and the severity level label for one set is equal to the number of target abnormities that appear in the set.
-We randomly choose sets of images from the OCT and fundus images and determine the severity level for each set.
-In the end, we get 10000 inputs for training and 10000 inputs for testing for each severity level.
-
-	The purpose of Stage D2 is to output the disease probability vectors.
-For each disease, we use the Abnormity-to-Disease Deduction Criteria to find the target abnormities, randomly choose sets of images where each of them is from one target abnormitiy, and label the sets of images with the disease.
-We get 10000 sets of images for training and 10000 sets of images for testing for each of the disease.
-
-	\subsection{Training}
-
-	The Diagnosis Model is trained with the same hardware as the Abnormity Models.
-Stage D1 submodels are trained for 10 epochs and Stage D2 model is trained for 30 epochs, and all the other hyperparameters are identical to those of the Abnormity Models.
-Refer to Section~\ref{sec:a_training} for details.
-
-	Submodels in Stage D1 and the model in Stage D2 quickly reach very high accuracies during training and validation because there are plenty of training data and the models leverage relatively simpler networks.
-
-	\subsection{Results}
-
-	Fig.~\ref{fig:D1_conf_mat} shows the confusion matrices for Stage D1 and Fig.~\ref{fig:D1_acc_bar} shows the accuracies of the submodels of Stage D1.
-Table~\ref{tb:diagnosis_test} shows the predictive values of Stage D2, Fig.~\ref{fig:D2_ROC} shows the ROCs, Fig.~\ref{fig:D2_conf_mat} shows the confusion matrix and Fig~\ref{fig:D2_tSNE} shows the t-SNE graph.
-
-	The submodels of Stage D1 tend to yield results where the predicted severity level is 1 level offset from the label.
-This impairs the accuracies of the submodels of Stage D1.
-However, Stage D2 partly solves this problem, as the model in Stage D2 has a higher accuracy than the average accuracy of the Stage D1 submodels.
-
-	Stage D2 performs quite well on classifying the diseases.
-Furthermore, considering that some diseases may look alike each other, we employ a method similar to the codominant abnormities method to allow Stage D2 to give up to 3 codominant diseases.
-As shown in Fig.~\ref{fig:D1_acc_bar}, if the codominant diseases method is used, the accuracy of Stage D2 further increases.
-
+	阶段 D2 在疾病分类方面表现相当出色。考虑到某些疾病可能相似，我们使用了类似共显异常的方法，使阶段 D2 能够输出最多 3 个共显疾病。正如图~\ref{fig:D1_acc_bar} 所示，若使用共显疾病方法，阶段 D2 的准确率进一步提高。
 	\end{multicols}
@@
 		\centering
+		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
+		\caption{诊断模型的准确率（*：只取概率最高的疾病的准确率；**：考虑共显疾病的准确率）}
+		\vspace{0.3cm}
+		\label{fig:D1_acc_bar}
+	\end{figure}
+
+	\begin{figure}[htbp]
+		\centering
 		\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.pdf}
-		\caption{Confusion matrices of Stage D1}
+		\caption{阶段D1的混淆矩阵}
 		\vspace{0.3cm}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
-		\caption{Accuracies of the Diagnosis Model (*: accuracy in terms of the disease with highest probability; **: accuracy in terms of codominant diseases)}
-		\vspace{0.3cm}
-		\label{fig:D1_acc_bar}
-	\end{figure}
-
-	\begin{figure}[htbp]
-		\centering
 		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
-		\caption{ROCs of Stage D2}
-		\vspace{0.3cm}
+		\vspace{-0.8cm}
+		\caption{阶段D2的ROC曲线}
 		\label{fig:D2_ROC}
@@
 		\vspace{-0.8cm}
-		\caption{Confusion matrix of Stage D2}
+		\caption{阶段D2的混淆矩阵}
 		\label{fig:D2_conf_mat}
@@
 		\vspace{-0.3cm}
-		\caption{t-SNE graph of Stage D2}
+		\caption{阶段D2的t-SNE图}
 		\label{fig:D2_tSNE}
@@
 		\fontsize{9}{12}\selectfont{
-			\caption{Test results of Stage D2}
+			\caption{阶段D2的测试结果}
 			\label{tb:diagnosis_test}
@@
 			columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
-			columns/Abnormity/.style={string type, column name=Diseases},
-			columns/Precision/.style={string type, column name=Precision},
-			columns/Sensitivity/.style={string type, column name=Sensitivity},
-			columns/Specificity/.style={string type, column name=Specificity},
-			columns/FOne/.style={string type, column name={F1 Score}},
+			columns/Abnormity/.style={string type, column name=疾病},
+			columns/Precision/.style={string type, column name=精确率},
+			columns/Sensitivity/.style={string type, column name=敏感性},
+			columns/Specificity/.style={string type, column name=特异性},
+			columns/FOne/.style={string type, column name={F1分数}},
 			columns/AUC/.style={string type, column name=AUC},
@@
 
-	\vspace{1cm}
+	\pagebreak
 
 	\begin{multicols}{2}
-	\section{Discussion}
+	\section{讨论}
 
-	There are some studies working on classifying OCT abnormities.
-For examples, \citeauthor{leandro2023oct}'s model is trained on 10770 images (most images belong to multiple classes), classifies 8 abnormities, and has overall accuracy between 93\% and 99\% \autocite{leandro2023oct}.
-\citeauthor{li2019deep}'s model is trained on 21357 images, classifies 4 abnormities, and has overall accuracy 97.3\% \autocite{li2019deep}.
-And there are some studies working on classifying fundus abnormities.
-For example,  	\citeauthor{Son2023}'s model is trained on 103262 images, classifies 15 abnormities, and has a mean AUC of 0.980 \autocite{Son2023}.
-In comparison, our OCT Model is trained on 15632 images, classifies 11 abnormities, and has overall accuracy less than 80\%.
-And our Fundus Model is trained on 1734 images, classifies 8 abnormities, and has a mean AUC of 0.909.
-As a matter of fact, our Abnormity Models are not satisfying in terms of performance.
+	一些研究专注于 OCT 异常分类。例如，\citeauthor{leandro2023oct} 等人的模型在 10770 张图像上训练（大多数图像属于多个类别），能分类 8 种异常，总体准确率在 93\% 到 99\% 之间 \autocite{leandro2023oct}。\citeauthor{li2019deep} 等人的模型在 21357 张图像上训练，能分类 4 种异常，总体准确率为 97.3\% \autocite{li2019deep}。另一些研究专注于眼底异常分类。例如，\citeauthor{Son2023} 等人的模型在 103262 张图像上训练，能分类 15 种异常，平均 AUC 为 0.980 \autocite{Son2023}。相比之下，我们的 OCT 模型在 15632 张图像上训练，能分类 11 种异常，总体准确率不足 80\%；而眼底模型在 1734 张图像上训练，能分类 8 种异常，平均 AUC 为 0.909。事实上，我们的异常模型在性能上并不理想。
 
-	Our data are collected from various online sources and therefore lack a uniform standard.
-Furthermore, some of the data are labeled by ourselves, while we do not have the expertise of ophthalmologists.
-Moreover, our data is not sufficient.
-There is also an imbalance between the number of images of different abnormities.
-In the OCT Model, the imbalance is partly neutralized by using Cycle-GAN.
-However, in the Fundus Model, we could only perform transformations to generate more images, which may increase the model's tendency of being overfitting and make it hard for the model to extract the correct features.
-Also as mentioned before, in our model, there are often multiple abnormities on one image, which increase the difficulty to identify one specific abnormity correctly.
+	我们的数据来自各种在线来源，因此缺乏统一标准。此外，部分数据由我们自己标注，但我们并不具备眼科医生的专业知识。此外，我们的数据量不足，各异常之间的图像数量不平衡。在 OCT 模型中，我们通过使用 Cycle-GAN 部分中和了这种不平衡。然而在眼底模型中，我们只能进行图像变换以生成更多图像，这可能会增加模型的过拟合倾向，使其难以提取正确的特征。此外，如前所述，我们的模型中一张图像上通常存在多个异常，这增加了正确识别特定异常的难度。
 
@@
 
-	In MAAM, the Diagnosis Model improves the overall performance successfully.
-There are also some studies using similar framework.
-For example, \citeauthor{Son2023}'s diagnosis model classifies 8 diseases and has mean AUC 0.992\autocite{Son2023}.
-In comparison, our Diagnosis Model classifies 12 diseases and has mean AUC of 0.984 which is close to other studies.
+	在 MAAM 中，诊断模型成功提高了整体性能。也有一些研究使用类似框架。例如，\citeauthor{Son2023} 等人的诊断模型能分类 8 种疾病，平均 AUC 为 0.992 \autocite{Son2023}。相比之下，我们的诊断模型能分类 12 种疾病，平均 AUC 为 0.984，与其他研究接近。
 
-	It is noted that the goal of MAAM is not to identify one specific disease.
-It is developed for identifying all the potential diseases, which is different from other studies mentioned in this paper.
-Therefore, we introduced codominant abnormities and codominant diseases, which buff up the performances.
-Moreover, the Diagnosis Model performs two additional feature extractions.
-While the Abnormity Models only have accuracies between 70\% and 80\%, after we extracted the features of severity levels of diseases in Stage D1, the average accuracy increases.
-And after we extracted the features of disease in Stage D2, the accuracy keep on increasing up to a satisfying level.
-These two stages enhance the performance of the Abnormity Models and make the features of the diseases more distinct.	Also, in training the Diagnosis Model, we use the Abnormity-to-Disease Deduction Criteria to generate ground truth, which is reliable even without involving ophthalmologists.
+	需要注意的是，MAAM 的目标并非识别单一疾病，而是识别所有潜在疾病，这与本文提到的其他研究有所不同。因此，我们引入了共显异常和共显疾病的概念，提升了模型的表现。此外，诊断模型进行了两次特征提取。虽然异常模型的准确率仅在 70\% 到 80\% 之间，但在阶段 D1 提取疾病严重程度的特征后，平均准确率有所提高。并且在阶段 D2 提取疾病特征后，准确率进一步提高，达到了令人满意的水平。这两个阶段提升了异常模型的性能，使疾病特征更加清晰。此外，在训练诊断模型时，我们使用异常到疾病推导标准生成了可靠的标签，即使不涉及眼科医生的专业知识也具备一定的可靠性。
 
-	\section{Conclusion}
+	\section{结论}
 
-	The main goal of this study is to devise a novel model and verify its feasibility.
-The MAAM takes both OCT and fundus images as input.
-We integrate information from different sources by employing the fusion mechanism.
-Moreover, we deduce disease from abnormities and simulate the decision-making process of ophthalmologists.
-We also introduced codominant abnormities and diseases, providing more information for reference.
-As a result, the model breaks the black box of complex neural network and exposes more information.
-On the other hand, there is some room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model, etc.
-
-	\phantomsection
-	\addcontentsline{toc}{section}{References}
-	\newrefcontext[sorting=nyt]
-	\printbibliography
+	本研究的主要目标是设计一种新颖的模型并验证其可行性。MAAM 以 OCT 和眼底图像为输入，利用融合机制整合来自不同来源的信息。此外，我们从异常推导疾病，模拟了眼科医生的决策过程。我们还引入了共显异常和共显疾病，提供了更多的参考信息。因此，该模型打破了复杂神经网络的“黑箱”，揭示了更多信息。另一方面，模型仍有改进空间，例如收集更多真实数据、引入眼科医生的专业知识、优化异常到疾病推导标准以及改进诊断模型结构等。
 
@@
 	\pagebreak
-	\section*{Appendix}
+	\phantomsection
+	\addcontentsline{toc}{section}{参考文献}
+	\newrefcontext[sorting=nyt]
+	\begin{multicols}{2}
+	\printbibliography
+	\end{multicols}
 
-	\subsection*{Code}
+	\pagebreak
+	\section*{附录}
 
-	The link for the GitHub repository is \url{https://github.com/SiqiPan2008/MAAM/}.
+	\subsection*{代码}
 
-	\subsection*{Abnormities and Diseases}
+	GitHub 仓库的链接是 \url{https://github.com/SiqiPan2008/MAAM/}。
+
+	\subsection*{异常与疾病}
 
@@
 			\begin{longtable}{llp{9.5cm}}
-				\caption*{OCT Abnormities}
+				\caption*{OCT异常}
 				\label{tb:oct-abnormites}\\
 				\toprule
-				Abnormity&Abbr.&Description\\
+				异常&缩写&描述\\
 				\toprule
 
-				Choroidal neovascularization
+				脉络膜新生血管
 				& CNV
-				& The abnormal growth of new blood vessels in the choroid layer.\\
+				& 脉络膜层中血管异常生长。\\
 
-				Central serous chorioretinopathy
+				中心性浆液性脉络膜视网膜病
 				& CSC
-				& The accumulation of fluid underneath the retina.\\
+				& 视网膜下方液体的积聚。\\
 
-				Diabetic macular edema
+				糖尿病黄斑水肿
 				& DME
-				& The accumulation of fluid in the macula associated with diabetic retinopathy. \\
+				& 与糖尿病视网膜病相关的黄斑液体积聚。\\
 
-				Drusen
+				脉络膜小疣
 				& Drusen
-				& Small deposits of extracellular material that accumulate beneath the retinal pigment epithelium (RPE) or between the RPE and the photoreceptor layer in the macular region of the retina.\\
+				& 在视网膜色素上皮（RPE）下或RPE与感光细胞层之间积聚的细小外源性物质沉积物。\\
 
-				Epiretinal membrane
+				视网膜上膜
 				& ERM
-				& A thin layer of fibrous tissue forms on the surface of the retina, particularly the macula.\\
+				& 在视网膜表面（尤其是黄斑）形成的一层薄薄的纤维组织。\\
 
-				Intraretinal fluid
+				视网膜内积液
 				& IF
-				& The accumulation of fluid within the layers of the retina.\\
+				& 视网膜层内液体的积聚。\\
 
-				Macular hole
+				黄斑裂洞
 				& MH
-				& Disruption or discontinuity in the normal retinal layers surrounding the macular hole.\\
+				& 环绕黄斑孔的正常视网膜层的破坏或不连续。\\
 
-				Macular telangiectasia
+				黄斑毛细管扩张
 				& Mactel
-				& Abnormities in the macular blood vessels, leading to changes in the macular structure and function.\\
+				& 黄斑血管的异常，导致黄斑结构和功能的改变。\\
 
-				Retinitis pigmentosa
+				视网膜色素变性
 				& RP
-				& Thinning of the retinal layers. Disruption of photoreceptor layers. Attenuation of retinal vasculature.\\
+				& 视网膜层变薄，感光细胞层的破坏，视网膜血管的衰退。\\
 
-				Stargardt disease
+				斯塔格特病
 				& ST
-				& Thinning and atrophy of the retina. Disruption of photoreceptor layers. Presence of subretinal deposits.\\
+				& 视网膜变薄和萎缩，感光细胞层的破坏，视网膜下沉积物的存在。\\
 
-				Subretinal fluid
+				视网膜下积液
 				& SF
-				& The accumulation of fluid between the neurosensory retina and the retinal pigment epithelium (RPE)\\
+				& 神经感光视网膜与视网膜色素上皮（RPE）之间液体的积聚。\\
 
@@
 			\begin{longtable}{llp{11.2cm}}
-				\caption*{Fundus Abnormalities}
+				\caption*{Fundus异常}
 				\label{tb:fundus-ab}\\
 				\toprule
-				Abnormity&Abbr.&Description\\
+				异常&缩写&描述\\
 				\toprule
 
-				Cotton wool patch
+				棉絮样斑块
 				& CWP
-				& White or off-white lesions. Irregular shapes and margins. Also called soft exudates. \\
+				& 白色或近白色病变，形状和边缘不规则，也称为软性渗出物。\\
 
-				Drusen
+				脉络膜小疣
 				& Drusen
-				& Small, round or oval-shaped yellow or white deposits.\\
+				& 小而圆或椭圆形的黄色或白色沉积物。\\
 
-				Hard exudate
+				硬性渗出物
 				& HE
-				& Yellow or Yellow-White Deposits. Hard Borders. Distribution. Clustering Around Blood Vessels\\
+				& 黄色或黄白色沉积物，边缘清晰，通常分布在血管周围。\\
 
-				Hemorrhage
+				出血
 				& HM
-				& Small dot-like to larger blot.
-Fresh hemorrhages typically appear bright red or deep red in color, indicating the presence of oxygenated blood.
-Over time, as the blood undergoes degradation and clotting, the hemorrhage may change color to darker red, orange, or yellowish hues.\\
+				& 从小点状出血到较大的斑点，鲜红色或深红色，表明氧合血液的存在，随着时间推移，出血颜色可变为深红、橙色或黄色。\\
 
-				Macular hole
+				黄斑裂洞
 				& MH
-				& Full-thickness macular hole showing a surrounding cuff of subretinal fluid.\\
+				& 完全厚度的黄斑孔，周围有视网膜下液体的环形带。\\
 
-				Microaneurysm
+				微动脉瘤
 				& MA
-				& Small vascular dilatations observed in retinal blood vessels, visible as tiny red dots scattered in the retina posteriorly.\\
+				& 视网膜血管中观察到的小血管扩张，表现为视网膜后部散布的小红点。\\
 
-				Retinitis pigmentosa
+				视网膜色素变性
 				& RP
-				& Arteriolar attenuation. Retinal pigmentary changes (either hypopigmentation and/or hyperpigmentation in the form of bone-spicule and pigment clumpings). Waxy disc pallor.\\
+				& 动脉小管变细，视网膜色素变化（低色素或高色素，呈骨刺样或色素聚集）。蜡样盘苍白。\\
 
-				Vascular abnormity
+				血管异常
 				& VA
-				& Retinal Vessel Tortuosity. Retinal Vessel Caliber Changes. \\
+				& 视网膜血管的扭曲和口径变化。\\
 
@@
 
+	\pagebreak
+
 	{
@@
 			\begin{longtable}{cc}
-				\caption*{Diseases}
+				\caption*{疾病}
 				\label{tb:diseases}\\
 				\toprule
-				Disease&Abbr.\\
+				疾病&缩写\\
 				\toprule
 
-				Branch or hemi-central retinal vein occlusion&BRVO\\
-				Central retinal vein occlusion&CRVO\\
-				Central serous chorioretinopathy&CSC\\
-				Dry age-related macular degeneration&dAMD\\
-				Epiretinal membrane&ERM\\
-				Macular telangiectasia&Mactel\\
-				Macular hole&MH\\
-				Mild diabetic retinopathy&mDR\\
-				Referable diabetic retinopathy&rDR\\
-				Retinitis pigmentosa&RP\\
-				Stargardt disease&ST\\
-				Wet age-related macular degeneration&wAMD\\
+				支或半中心视网膜静脉阻塞&BRVO\\
+				中心视网膜静脉阻塞&CRVO\\
+				中心性浆液性脉络膜病&CSC\\
+				干性年龄相关性黄斑变性&dAMD\\
+				视网膜上膜&ERM\\
+				黄斑毛细血管扩张症&Mactel\\
+				黄斑裂洞&MH\\
+				轻度糖尿病视网膜病&mDR\\
+				可转介糖尿病视网膜病&rDR\\
+				视网膜色素变性&RP\\
+				斯塔格特病&ST\\
+				湿性年龄相关性黄斑变性&wAMD\\
 				\bottomrule
@@
 
-	\subsection*{Image Sources}
+	\subsection*{图片来源}
 
@@
 
-	\subsubsection*{Fundus -- MH}
+	\subsubsection*{眼底 -- MH}
 	\vspace{0.5cm}
@@
 
-	\subsubsection*{Fundus -- RP}
+	\subsubsection*{眼底 -- RP}
 	\vspace{0.5cm}

### 2024-10-27 Paper-Translated/Paper.tex
Minor revisions

@@
 
-	在阶段 D1 中，我们根据异常模型的概率向量确定每种疾病的严重程度。我们使用异常到疾病推导标准（见图~\ref{fig:criteria}）作为判断依据。阶段 D1 中有多个子模型，每个子模型对应一种疾病。根据推导标准，我们确定一种疾病的异常数量，并以此来定义严重程度。例如，疾病“rDR”中共有 5 种异常：OCT 异常“DME”以及眼底异常“HM”、“VA”、“MA”和“CWP”。因此，考虑到健康状态，我们将“rDR”定义为 6 个严重程度级别。
+	在阶段 D1 中，我们根据异常模型的概率向量确定每种疾病的严重程度。我们使用异常-疾病推导标准（见图~\ref{fig:criteria}）作为判断依据。阶段 D1 中有多个子模型，每个子模型对应一种疾病。根据推导标准，我们确定一种疾病的异常数量，并以此来定义严重程度。例如，疾病“rDR”中共有 5 种异常：OCT 异常“DME”以及眼底异常“HM”、“VA”、“MA”和“CWP”。因此，考虑到健康状态，我们将“rDR”定义为 6 个严重程度级别。
 
@@
 					OCT模型   &91.906\%&\textbf{92.183\%}&91.011\%&89.744\% \\
-					Fundus模型&\textbf{89.111\%}&88.926\%&86.605\%&79.185\% \\
+					眼底模型&\textbf{89.111\%}&88.926\%&86.605\%&79.185\% \\
 					\bottomrule
@@
 
-	阶段 D1 的目的是确定每种疾病的严重程度，每种疾病对应一个子模型。我们根据异常到疾病推导标准（见图~\ref{fig:criteria}）为每个子模型准备数据。如第~\ref{sec:overview}~节所述，我们确定一种疾病的目标异常，并根据目标异常的数量定义严重程度。如果某种疾病有 5 个目标异常，则考虑到健康状态，共有 6 个严重程度级别，即 0 至 5。我们使用一组图像作为子模型的输入，每组图像的严重程度标签等于该组中出现的目标异常数量。我们随机选择 OCT 和眼底图像集，为每组确定严重程度。最终，我们为每个严重程度获得 10000 组训练输入和 10000 组测试输入。
+	阶段 D1 的目的是确定每种疾病的严重程度，每种疾病对应一个子模型。我们根据异常-疾病推导标准（见图~\ref{fig:criteria}）为每个子模型准备数据。如第~\ref{sec:overview}~节所述，我们确定一种疾病的目标异常，并根据目标异常的数量定义严重程度。如果某种疾病有 5 个目标异常，则考虑到健康状态，共有 6 个严重程度级别，即 0 至 5。我们使用一组图像作为子模型的输入，每组图像的严重程度标签等于该组中出现的目标异常数量。我们随机选择 OCT 和眼底图像集，为每组确定严重程度。最终，我们为每个严重程度获得 10000 组训练输入和 10000 组测试输入。
 
-	阶段 D2 的目的是输出疾病概率向量。对于每种疾病，我们使用异常到疾病推导标准找到目标异常，随机选择每个目标异常的一组图像，将这些图像集标记为该疾病。我们为每种疾病获取了 10000 组训练图像集和 10000 组测试图像集。
+	阶段 D2 的目的是输出疾病概率向量。对于每种疾病，我们使用异常-疾病推导标准找到目标异常，随机选择每个目标异常的一组图像，将这些图像集标记为该疾病。我们为每种疾病获取了 10000 组训练图像集和 10000 组测试图像集。
 
@@
 
-	需要注意的是，MAAM 的目标并非识别单一疾病，而是识别所有潜在疾病，这与本文提到的其他研究有所不同。因此，我们引入了共显异常和共显疾病的概念，提升了模型的表现。此外，诊断模型进行了两次特征提取。虽然异常模型的准确率仅在 70\% 到 80\% 之间，但在阶段 D1 提取疾病严重程度的特征后，平均准确率有所提高。并且在阶段 D2 提取疾病特征后，准确率进一步提高，达到了令人满意的水平。这两个阶段提升了异常模型的性能，使疾病特征更加清晰。此外，在训练诊断模型时，我们使用异常到疾病推导标准生成了可靠的标签，即使不涉及眼科医生的专业知识也具备一定的可靠性。
+	需要注意的是，MAAM 的目标并非识别单一疾病，而是识别所有潜在疾病，这与本文提到的其他研究有所不同。因此，我们引入了共显异常和共显疾病的概念，提升了模型的表现。此外，诊断模型进行了两次特征提取。虽然异常模型的准确率仅在 70\% 到 80\% 之间，但在阶段 D1 提取疾病严重程度的特征后，平均准确率有所提高。并且在阶段 D2 提取疾病特征后，准确率进一步提高，达到了令人满意的水平。这两个阶段提升了异常模型的性能，使疾病特征更加清晰。此外，在训练诊断模型时，我们使用异常-疾病推导标准生成了可靠的标签，即使不涉及眼科医生的专业知识也具备一定的可靠性。
 
@@
 
-	本研究的主要目标是设计一种新颖的模型并验证其可行性。MAAM 以 OCT 和眼底图像为输入，利用融合机制整合来自不同来源的信息。此外，我们从异常推导疾病，模拟了眼科医生的决策过程。我们还引入了共显异常和共显疾病，提供了更多的参考信息。因此，该模型打破了复杂神经网络的“黑箱”，揭示了更多信息。另一方面，模型仍有改进空间，例如收集更多真实数据、引入眼科医生的专业知识、优化异常到疾病推导标准以及改进诊断模型结构等。
+	本研究的主要目标是设计一种新颖的模型并验证其可行性。MAAM 以 OCT 和眼底图像为输入，利用融合机制整合来自不同来源的信息。此外，我们从异常推导疾病，模拟了眼科医生的决策过程。我们还引入了共显异常和共显疾病，提供了更多的参考信息。因此，该模型打破了复杂神经网络的“黑箱”，揭示了更多信息。另一方面，模型仍有改进空间，例如收集更多真实数据、引入眼科医生的专业知识、优化异常-疾病推导标准以及改进诊断模型结构等。
 

### 2024-11-02 Paper-Translated/Paper.tex
Substitute all figures in translated paper with png files

@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
+		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.png}
 		\caption{OCT异常 \autocite{Duker_Waheed_Goldman_2022}}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
+		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.png}
 		\caption{眼底异常 \autocite{Wolf_Kirchhof_Reim_2006}}
@@
 			\centering
-			\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
-			\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
+			\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.png}
+			\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.png}
 			\caption{异常模型训练}
@@
 			\centering
-			\includegraphics[width=\linewidth]{Figs/abnormity_ROC.pdf}
+			\includegraphics[width=\linewidth]{Figs/abnormity_ROC.png}
 			\caption{异常模型的ROC曲线}
@@
 			\centering
-			\includegraphics[width=\linewidth]{Figs/abnormity_confusion_matrix.pdf}
+			\includegraphics[width=\linewidth]{Figs/abnormity_confusion_matrix.png}
 			\caption{异常模型的混淆矩阵}
@@
 			\centering
-			\includegraphics[width=\linewidth]{Figs/abnormity_tSNE.pdf}
+			\includegraphics[width=\linewidth]{Figs/abnormity_tSNE.png}
 			\caption{异常模型的t-SNE图}
@@
 			\centering
-			\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.pdf}
+			\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.png}
 			\caption{Grad-CAM高亮显示异常}
@@
 			\centering
-			\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
+			\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.png}
 			\caption{Grad-CAM高亮显示多处异常}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
+		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.png}
 		\caption{诊断模型的准确率（*：只取概率最高的疾病的准确率；**：考虑共显疾病的准确率）}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.pdf}
+		\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.png}
 		\caption{阶段D1的混淆矩阵}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
+		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.png}
 		\vspace{-0.8cm}
@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{Figs/diagnosis2_confusion_matrix.pdf}
+		\includegraphics[width=0.7\linewidth]{Figs/diagnosis2_confusion_matrix.png}
 		\vspace{-0.8cm}
@@
 		\centering
-		\includegraphics[width=0.65\linewidth]{Figs/diagnosis2_tSNE.pdf}
+		\includegraphics[width=0.65\linewidth]{Figs/diagnosis2_tSNE.png}
 		\vspace{-0.3cm}

### 2024-11-04 Paper/Paper.tex
Minor revisions
try to use Frontiers-Harvard.bst

@@
 \usepackage{enumitem}
-\usepackage[style=ieee,sorting=nyt]{biblatex}
-\assignrefcontextentries[]{*}
-\addbibresource{References.bib}
+\bibliographystyle{Frontiers-Harvard.bst}
+\bibliography{References.bib}
 \geometry{left=1in, right=1in, top=1in, bottom=1in}
@@
 \CTEXoptions[today=old, contentsname=Contents]
-\newcommand{\authyear}[1]{\citeauthor{#1} (\citeyear{#1})}
+\newcommand{\authyear}[1]{\author{#1} (\year{#1})}
 \setmainfont{Arial}
@@
 	\begin{multicols}{2}
-	\section{Background}
+	\section{Introduction}
 	Ocular diseases can be diagnosed through various methods, including using optical coherence tomography (OCT) and color fundus images.
@@
 Traditionally, the diagnosis primarily depends on the professional experience and knowledge of the ophthalmologists, which may result in high misdiagnosis rate and under-utilization of medical data.
-With the widespread application of artificial intelligence (AI), deep learning (DL) has made great contributions in providing support to patients in remote areas by sharing expert knowledge \autocite{Ichhpujani_Thakur_2021}.
+With the widespread application of artificial intelligence (AI), deep learning (DL) has made great contributions in providing support to patients in remote areas by sharing expert knowledge \cite{Ichhpujani_Thakur_2021}.
 By leveraging DL, researchers have developed auxiliary diagnosis programs to help ophthalmologists in the process.
 Many studies use convolutional neural networks (CNN) to analyze ocular images.
-Some commonly used CNNs are VGG, ResNet, and Inception \autocite{daich2023artificial}.
-And for segmenting images and finding abnormalities, U-net is widely used \autocite{Ronneberger_Fischer_Brox_2015}.
+Some commonly used CNNs are VGG, ResNet, and Inception \cite{daich2023artificial}.
+And for segmenting images and finding abnormalities, U-net is widely used \cite{Ronneberger_Fischer_Brox_2015}.
 With regards to training CNNs, most studies use transferred learning, which consists of three steps: learning, fine-tuning, and validation.
@@
 	\authyear{li2019deep} used ResNet to analyze OCT images and distinguish between choroidal neovascularization (CNV), diabetic macular edema (DME), drusen, and healthy eyes.
-In addition, they performed occlusion testing to find out the regions that are the most important in diagnosis \autocite{li2019deep}.
-	\authyear{yoo2021feasibility} used generative adversarial network (GAN) and Inception-v3 together with a few-shot dataset to investigate the feasibility of improving OCT diagnosis of rare ocular diseases \autocite{yoo2021feasibility}.
+In addition, they performed occlusion testing to find out the regions that are the most important in diagnosis \cite{li2019deep}.
+	\authyear{yoo2021feasibility} used generative adversarial network (GAN) and Inception-v3 together with a few-shot dataset to investigate the feasibility of improving OCT diagnosis of rare ocular diseases \cite{yoo2021feasibility}.
 They handled the issues of training image shortage and data imbalance by creating ocular disease OCT images from healthy OCT images.
 \authyear{Kermany2018} conducts medical diagnosis and identifies treatable diseases by image-based deep learning.
-They also provided a widely used database including more than one hundred thousand OCT labeled images for 3 diseases \autocite{Kermany2018}.
+They also provided a widely used database including more than one hundred thousand OCT labeled images for 3 diseases \cite{Kermany2018}.
 
 	Some other studies can identify ocular abnormalities from annotated OCT images.
-	\authyear{camino2018deep} used DL to identify the region of preserved photoreceptors on \textit{en face} OCT in choroideremia and retinitis pigmentosa (RP) \autocite{camino2018deep}. 
-	\authyear{srinivasan2014fully} detected DME and dry age-related macular degeneration (dry AMD) from OCT images by flattening the image and using support vector machine (SVM) to extract the thickness information of the retinal layers \autocite{srinivasan2014fully}.
-	\authyear{leandro2023oct} implemented VGG to identify up to 8 kinds of key abnormalities and hence detect multiple diseases by using central fovea cross-section OCT \autocite{leandro2023oct}.
+	\authyear{camino2018deep} used DL to identify the region of preserved photoreceptors on \textit{en face} OCT in choroideremia and retinitis pigmentosa (RP) \cite{camino2018deep}. 
+	\authyear{srinivasan2014fully} detected DME and dry age-related macular degeneration (dry AMD) from OCT images by flattening the image and using support vector machine (SVM) to extract the thickness information of the retinal layers \cite{srinivasan2014fully}.
+	\authyear{leandro2023oct} implemented VGG to identify up to 8 kinds of key abnormalities and hence detect multiple diseases by using central fovea cross-section OCT \cite{leandro2023oct}.
 \authyear{Fang_Wang2019} developed a novel lesion-aware CNN, called LACNN, to simulate the ophthalmologists' diagnosis that focuses on ocular abnormalities.
-The LACNN is a U-net-like CNN which incorporates VGG16 as the baseline, and the result is impressive \autocite{Fang_Wang2019}.
+The LACNN is a U-net-like CNN which incorporates VGG16 as the baseline, and the result is impressive \cite{Fang_Wang2019}.
 
 	Other studies use fundus images to predict ocular diseases.
-	\authyear{masumoto2019accuracy} trained deep CNN with ultrawide-field fundus images to make the CNN capable of diagnosing RP \autocite{masumoto2019accuracy}. 
-	\authyear{chen2021artificial} uses color fundus photographs and multiple types of CNN (Inception V3, Inception Resnet V2, and Xception) to develop a method of early detection of RP \autocite{chen2021artificial}.
-	\authyear{li2022development} uses CNN to detect up to 12 fundus diseases based on colour fundus photography \autocite{li2022development}.
+	\authyear{masumoto2019accuracy} trained deep CNN with ultrawide-field fundus images to make the CNN capable of diagnosing RP \cite{masumoto2019accuracy}. 
+	\authyear{chen2021artificial} uses color fundus photographs and multiple types of CNN (Inception V3, Inception Resnet V2, and Xception) to develop a method of early detection of RP \cite{chen2021artificial}.
+	\authyear{li2022development} uses CNN to detect up to 12 fundus diseases based on colour fundus photography \cite{li2022development}.
 \authyear{Son2023} presented a novel architectural and algorithmic design to comprehensively identify 15 abnormalities and diagnose 8 major ocular diseases from macula-centered fundus images.
-They defined a notion of counterfactual attribution ratio (CAR) to interpret the system's diagnostic reason and disclose the relationship between abnormalities and diseases \autocite{Son2023}.
+They defined a notion of counterfactual attribution ratio (CAR) to interpret the system's diagnostic reason and disclose the relationship between abnormalities and diseases \cite{Son2023}.
 
@@
 It is not always necessary to yield a better automated diagnosis result, but it does help ophthalmologist to make more accurate and holistic clinical decisions.
-For instance, \authyear{liu2023prediction} combined OCT and fundus images to evaluate visual impairment in RP in terms of best-corrected visual acuity(BCVA) \autocite{liu2023prediction}.
-\authyear{Xu2021} leveraged a bi-modal CNN to diagnose AMD and polypoidal choroidal vasculopathy (PCV), where the architecture uses fundus and OCT images as input for transferred learning CNN and concatenates the retrieved features to classify 3 diseases including dry AMD, wet AMD and PCV \autocite{Xu2021}.
-And \author{Andrearczyk2018} ingeniously combined medical images and biomedical textual information to discriminate different diseases, which is a novel method for the usage of multi-modal application \autocite{Andrearczyk2018}.
+For instance, \authyear{liu2023prediction} combined OCT and fundus images to evaluate visual impairment in RP in terms of best-corrected visual acuity(BCVA) \cite{liu2023prediction}.
+\authyear{Xu2021} leveraged a bi-modal CNN to diagnose AMD and polypoidal choroidal vasculopathy (PCV), where the architecture uses fundus and OCT images as input for transferred learning CNN and concatenates the retrieved features to classify 3 diseases including dry AMD, wet AMD and PCV \cite{Xu2021}.
+And \author{Andrearczyk2018} ingeniously combined medical images and biomedical textual information to discriminate different diseases, which is a novel method for the usage of multi-modal application \cite{Andrearczyk2018}.
 
@@
 There are three types of fusion, namely early, late, and hybrid fusion.
-Deciding on the optimal type of fusion is part of the exploratory process in the application of DL methods \autocite{Ichhpujani_Thakur_2021}.
+Deciding on the optimal type of fusion is part of the exploratory process in the application of DL methods \cite{Ichhpujani_Thakur_2021}.
 
@@
 		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
-		\caption{OCT abnormities \autocite{Duker_Waheed_Goldman_2022}}
+		\caption{OCT abnormities \cite{Duker_Waheed_Goldman_2022}}
 		\vspace{0.3cm}
@@
 		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
-		\caption{Fundus abnormities \autocite{Wolf_Kirchhof_Reim_2006}}
+		\caption{Fundus abnormities \cite{Wolf_Kirchhof_Reim_2006}}
 		\vspace{0.3cm}
@@
 Both of the submodels leverage CNNs with modified final fully-connected (FC) layers.
-We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18 \autocite{He_Zhang_Ren_Sun_2016} and VGG16 \autocite{Simonyan_Zisserman_2015}, and choose the best one for each submodel.
+We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18 \cite{He_Zhang_Ren_Sun_2016} and VGG16 \cite{Simonyan_Zisserman_2015}, and choose the best one for each submodel.
 The final FC layer in each CNN is modified so that the size of its output vector is equal to the number of OCT or fundus abnormities.
@@
 
-	For OCT abnormities with less than 1000 images, we use Cycle-GAN \autocite{Zhu_Park_Isola_Efros_2020} to generate new images.
+	For OCT abnormities with less than 1000 images, we use Cycle-GAN \cite{Zhu_Park_Isola_Efros_2020} to generate new images.
 We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images.
@@
 				\begin{enumerate}
-					\item Normal Disease Database \autocite{Kermany_database}
+					\item Normal Disease Database \cite{Kermany_database}
 					\vspace{-0.2cm}
 
-					\item OCTID \autocite{Gholami_Roy_Parthasarathy_Lakshminarayanan_2020}
+					\item OCTID \cite{Gholami_Roy_Parthasarathy_Lakshminarayanan_2020}
 					\vspace{-0.2cm}
 
-					\item Few-shot \autocite{Yoo_2020}
+					\item Few-shot \cite{Yoo_2020}
 					\vspace{-0.2cm}
@@
 
-					\item E-ophtha \autocite{E_ophtha}.
+					\item E-ophtha \cite{E_ophtha}.
 					\vspace{-0.2cm}
 
-					\item Kaggle1000 \autocite{1000Fundus_Pytorch_TransferLearning}
+					\item Kaggle1000 \cite{1000Fundus_Pytorch_TransferLearning}
 					\vspace{-0.2cm}
 
-					\item HRF \autocite{HRF_2013}
+					\item HRF \cite{HRF_2013}
 					\vspace{-0.2cm}
 
-					\item STARE \autocite{STARE}
+					\item STARE \cite{STARE}
 					\vspace{-0.2cm}
 
-					\item EyePACS \autocite{DR_dataset}
+					\item EyePACS \cite{DR_dataset}
 					\vspace{-0.2cm}
@@
 
-	In the transfer learning phase, pretrained weights from ImageNet \autocite{Krizhevsky_Sutskever_Hinton_2017} are used.
+	In the transfer learning phase, pretrained weights from ImageNet \cite{Krizhevsky_Sutskever_Hinton_2017} are used.
 We freeze the weights in all the convolutional layers and only vary the weights in the final FC layer.
@@
 
-		We can use Grad-CAM \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra} to highlight areas on the image that make a large contribution to the final classification.
+		We can use Grad-CAM \cite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra} to highlight areas on the image that make a large contribution to the final classification.
 If the model had been trained correctly, this would be equivalent to highlighting the abnormity.
@@
 	There are some studies working on classifying OCT abnormities.
-For examples, \citeauthor{leandro2023oct}'s model is trained on 10770 images (most images belong to multiple classes), classifies 8 abnormities, and has overall accuracy between 93\% and 99\% \autocite{leandro2023oct}.
-\citeauthor{li2019deep}'s model is trained on 21357 images, classifies 4 abnormities, and has overall accuracy 97.3\% \autocite{li2019deep}.
+For examples, \citeauthor{leandro2023oct}'s model is trained on 10770 images (most images belong to multiple classes), classifies 8 abnormities, and has overall accuracy between 93\% and 99\% \cite{leandro2023oct}.
+\citeauthor{li2019deep}'s model is trained on 21357 images, classifies 4 abnormities, and has overall accuracy 97.3\% \cite{li2019deep}.
 And there are some studies working on classifying fundus abnormities.
-For example,  	\citeauthor{Son2023}'s model is trained on 103262 images, classifies 15 abnormities, and has a mean AUC of 0.980 \autocite{Son2023}.
+For example,  	\citeauthor{Son2023}'s model is trained on 103262 images, classifies 15 abnormities, and has a mean AUC of 0.980 \cite{Son2023}.
 In comparison, our OCT Model is trained on 15632 images, classifies 11 abnormities, and has overall accuracy less than 80\%.
@@
 There are also some studies using similar framework.
-For example, \citeauthor{Son2023}'s diagnosis model classifies 8 diseases and has mean AUC 0.992\autocite{Son2023}.
+For example, \citeauthor{Son2023}'s diagnosis model classifies 8 diseases and has mean AUC 0.992\cite{Son2023}.
 In comparison, our Diagnosis Model classifies 12 diseases and has mean AUC of 0.984 which is close to other studies.
